### 2017-08-25 Paper/Threshold/Compare.tex
Upload paper source codes

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=0.20cm, right=0.20cm, top=0.50cm, bottom=0.50cm]{geometry}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}

\begin{document}

	\section{Linear Weight}
		$$T = \frac{\sigma_B \mu_A + \sigma_A \mu_B}{\sigma_B + \sigma_A}$$

		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                                \\ \hline
				& Centralized & 41.09 & 32.95 & 40.70 & {\color[HTML]{FE0000} \textbf{38.25}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 37.69 & 38.89 & 41.26 & {\color[HTML]{FE0000} \textbf{39.28}} & 62.96  & 64.00  & 53.85  & {\color[HTML]{FE0000} \textbf{60.27}}  \\ \hline
				& Centralized & 55.68 & 46.59 & 47.96 & {\color[HTML]{FE0000} \textbf{50.08}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 46.95 & 44.36 & 50.96 & {\color[HTML]{FE0000} \textbf{47.42}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \hline
			\end{tabular}
		\end{table}

	\section{\textcolor{blue}{Square-Root Weight}}
		$$T = \frac{\sqrt{\sigma_B} \mu_A + \sqrt{\sigma_A} \mu_B}{\sqrt{\sigma_B} + \sqrt{\sigma_A}}$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                                \\ \hline
				& Centralized & 97.22 & 98.15 & 97.45 & {\color[HTML]{FE0000} \textbf{97.61}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 68.50 & 70.59 & 68.87 & {\color[HTML]{FE0000} \textbf{69.32}} & 19.51  & 30.43  & 39.47  & {\color[HTML]{FE0000} \textbf{29.80}}  \\ \hline
				& Centralized & 71.22 & 73.86 & 78.68 & {\color[HTML]{FE0000} \textbf{74.59}} & 95.83  & 96.77  & 91.89  & {\color[HTML]{FE0000} \textbf{94.83}}  \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 77.57 & 81.27 & 80.59 & {\color[HTML]{FE0000} \textbf{79.81}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Logarithmic Weight}
		$$T = \frac{(ln\sigma_B)\mu_A + (ln\sigma_A)\mu_B}{ln\sigma_B + ln\sigma_A}$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                            \\ \hline
				& Centralized & 99.23 & 99.25 & 99.63 & {\color[HTML]{FE0000} \textbf{99.37}} & 55.88 & 53.57 & 70.37 & {\color[HTML]{FE0000} \textbf{59.94}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 95.80 & 95.04 & 95.11 & {\color[HTML]{FE0000} \textbf{95.32}} & 9.09  & 3.03  & 3.45  & {\color[HTML]{FE0000} \textbf{5.19}}  \\ \hline
				& Centralized & 91.37 & 94.74 & 90.49 & {\color[HTML]{FE0000} \textbf{92.20}} & 97.50 & 68.97 & 93.75 & {\color[HTML]{FE0000} \textbf{86.74}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 97.70 & 99.26 & 99.26 & {\color[HTML]{FE0000} \textbf{98.74}} & 85.29 & 95.83 & 96.00 & {\color[HTML]{FE0000} \textbf{92.37}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Square-Log Weight}
		$$T = \frac{(\sqrt{|ln\sigma_B|})\mu_A + (\sqrt{|ln\sigma_A|})\mu_B}{\sqrt{|ln\sigma_B|} + \sqrt{|ln\sigma_A|}}$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                              \\ \hline
				& Centralized & 99.24 & 99.26 & 99.25 & {\color[HTML]{FE0000} \textbf{99.25}} & 53.13  & 52.17 & 56.67  & {\color[HTML]{FE0000} \textbf{53.99}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 93.89 & 94.81 & 95.45 & {\color[HTML]{FE0000} \textbf{94.72}} & 3.03   & 8.00  & 6.45   & {\color[HTML]{FE0000} \textbf{5.83}}  \\ \hline
				& Centralized & 91.92 & 89.92 & 88.01 & {\color[HTML]{FE0000} \textbf{89.95}} & 65.71  & 92.59 & 85.71  & {\color[HTML]{FE0000} \textbf{81.34}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 95.88 & 99.23 & 97.76 & {\color[HTML]{FE0000} \textbf{97.62}} & 100.00 & 88.89 & 100.00 & {\color[HTML]{FE0000} \textbf{96.30}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Log-Square Weight}
		$$T = \frac{(ln\sqrt{\sigma_B})\mu_A + (ln\sqrt{\sigma_A})\mu_B}{ln\sqrt{\sigma_B} + ln\sqrt{\sigma_A}}$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                             \\ \hline
				& Centralized & 99.25 & 99.25 & 99.62 & {\color[HTML]{FE0000} \textbf{99.37}} & 51.85 & 40.74  & 43.33 & {\color[HTML]{FE0000} \textbf{45.31}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 95.45 & 93.51 & 94.93 & {\color[HTML]{FE0000} \textbf{94.63}} & 6.45  & 6.06   & 5.26  & {\color[HTML]{FE0000} \textbf{5.92}}  \\ \hline
				& Centralized & 91.70 & 93.21 & 89.27 & {\color[HTML]{FE0000} \textbf{91.39}} & 83.33 & 100.00 & 94.12 & {\color[HTML]{FE0000} \textbf{92.48}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 99.62 & 99.63 & 97.37 & {\color[HTML]{FE0000} \textbf{98.87}} & 93.10 & 80.77  & 96.55 & {\color[HTML]{FE0000} \textbf{90.14}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Linear Additional Weight}
		$$T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                                \\ \hline
				& Centralized & 20.44 & 23.11 & 22.05 & {\color[HTML]{FE0000} \textbf{21.87}} & 100.00 & 100.00 & 96.88  & {\color[HTML]{FE0000} \textbf{98.96}}  \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 22.26 & 22.93 & 23.79 & {\color[HTML]{FE0000} \textbf{22.99}} & 76.19  & 75.86  & 80.77  & {\color[HTML]{FE0000} \textbf{77.61}}  \\ \hline
				& Centralized & 17.10 & 17.60 & 16.54 & {\color[HTML]{FE0000} \textbf{17.08}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 17.18 & 17.23 & 17.36 & {\color[HTML]{FE0000} \textbf{17.26}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Square-Root Additional Weight}
		$$T = \frac{(\sigma_B \sqrt{1 - \alpha}) \mu_A + (\sigma_A \sqrt{\alpha}) \mu_B}{\sigma_B \sqrt{1 - \alpha} + \sigma_A \sqrt{\alpha}}$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                                \\ \hline
				& Centralized & 25.77 & 24.34 & 29.30 & {\color[HTML]{FE0000} \textbf{26.47}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 27.31 & 26.64 & 27.76 & {\color[HTML]{FE0000} \textbf{27.24}} & 83.33  & 77.78  & 78.13  & {\color[HTML]{FE0000} \textbf{79.75}}  \\ \hline
				& Centralized & 20.91 & 18.96 & 19.10 & {\color[HTML]{FE0000} \textbf{19.66}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 17.74 & 17.16 & 17.91 & {\color[HTML]{FE0000} \textbf{17.60}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Logarithmic Additional Weight}
		$$
		T = \frac{\big[\sigma_B ln(1 - \alpha)\big] \mu_A
			+ \big[\sigma_A ln\alpha\big] \mu_B}
		{\sigma_B ln(1 - \alpha) + \sigma_A ln\alpha}
		$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                               & \multicolumn{4}{c|}{True Positive}                            \\ \hline
				& Centralized & 99.62  & 99.62 & 99.61  & {\color[HTML]{FE0000} \textbf{99.62}}  & 23.53 & 25.00 & 19.44 & {\color[HTML]{FE0000} \textbf{22.66}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 96.85  & 96.18 & 97.73  & {\color[HTML]{FE0000} \textbf{96.92}}  & 4.88  & 3.03  & 12.90 & {\color[HTML]{FE0000} \textbf{6.94}}  \\ \hline
				& Centralized & 97.72  & 96.63 & 98.87  & {\color[HTML]{FE0000} \textbf{97.74}}  & 25.00 & 42.86 & 48.28 & {\color[HTML]{FE0000} \textbf{38.71}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 100.00 & 99.62 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} & 47.83 & 37.93 & 46.15 & {\color[HTML]{FE0000} \textbf{43.97}} \\ \hline
			\end{tabular}
		\end{table}

	\section{\textcolor{blue}{Square-Log Additional Weight}}
		$$
		T = \frac{\mu_A \sigma_B \sqrt{-ln(1 - \alpha)}
			+ \mu_B \sigma_A \sqrt{-ln\alpha}}
		{\sigma_B \sqrt{-ln(1 - \alpha)} + \sigma_A \sqrt{-ln\alpha}}
		$$
		\begin{table}[!ht]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                              \\ \hline
				& Centralized & 98.47 & 98.48 & 98.13 & {\color[HTML]{FE0000} \textbf{98.36}} & 82.35 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{94.12}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 88.93 & 89.02 & 89.63 & {\color[HTML]{FE0000} \textbf{89.19}} & 9.09  & 22.58  & 16.00  & {\color[HTML]{FE0000} \textbf{15.89}} \\ \hline
				& Centralized & 96.28 & 95.09 & 95.44 & {\color[HTML]{FE0000} \textbf{95.60}} & 73.08 & 66.67  & 84.38  & {\color[HTML]{FE0000} \textbf{74.71}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 99.26 & 98.49 & 96.67 & {\color[HTML]{FE0000} \textbf{98.14}} & 91.30 & 100.00 & 96.00  & {\color[HTML]{FE0000} \textbf{95.77}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Log-Square Additional Weight}
		$$
		T = \frac{\mu_A \sigma_B ln\sqrt{1 - \alpha}
			+ \mu_B \sigma_A ln\sqrt{\alpha}}
		{\sigma_B ln\sqrt{1 - \alpha} + \sigma_A ln\sqrt{\alpha}}
		$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                              & \multicolumn{4}{c|}{True Positive}                            \\ \hline
				& Centralized & 99.24  & 99.63 & 99.63  & {\color[HTML]{FE0000} \textbf{99.50}} & 18.18 & 21.43 & 18.52 & {\color[HTML]{FE0000} \textbf{19.38}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 95.91  & 96.01 & 95.20  & {\color[HTML]{FE0000} \textbf{95.70}} & 0.00  & 0.00  & 0.00  & {\color[HTML]{FE0000} \textbf{0.00}}  \\ \hline
				& Centralized & 98.48  & 98.43 & 99.63  & {\color[HTML]{FE0000} \textbf{98.85}} & 25.00 & 27.50 & 37.04 & {\color[HTML]{FE0000} \textbf{29.85}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 100.00 & 99.27 & 100.00 & {\color[HTML]{FE0000} \textbf{99.76}} & 32.14 & 54.55 & 31.03 & {\color[HTML]{FE0000} \textbf{39.24}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Square-Log Combined Weight}
		$$
		T = \frac{\mu_A \sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|}
			+ \mu_B \sqrt{|ln(\sigma_A \alpha)|}}
		{\sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_A \alpha)|}}
		$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                             \\ \hline
				& Centralized & 99.26 & 99.22 & 99.62 & {\color[HTML]{FE0000} \textbf{99.37}} & 50.00  & 59.46 & 39.39 & {\color[HTML]{FE0000} \textbf{49.62}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 94.70 & 94.70 & 95.20 & {\color[HTML]{FE0000} \textbf{94.87}} & 12.90  & 0.00  & 4.17  & {\color[HTML]{FE0000} \textbf{5.69}}  \\ \hline
				& Centralized & 94.98 & 95.17 & 89.59 & {\color[HTML]{FE0000} \textbf{93.25}} & 87.50  & 88.46 & 92.31 & {\color[HTML]{FE0000} \textbf{89.42}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 97.00 & 99.23 & 95.96 & {\color[HTML]{FE0000} \textbf{97.40}} & 100.00 & 76.47 & 95.65 & {\color[HTML]{FE0000} \textbf{90.71}} \\ \hline
			\end{tabular}
		\end{table}

	\section{Log-Square Combined Weight}
		$$
		T = \frac{\mu_A ln\sqrt{\sigma_B (1 - \alpha)}
			+ \mu_B ln\sqrt{\sigma_A \alpha}}
		{ln\sqrt{\sigma_B (1 - \alpha)} + ln\sqrt{\sigma_A \alpha}}
		$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                            \\ \hline
				& Centralized & 99.26 & 99.62 & 99.64 & {\color[HTML]{FE0000} \textbf{99.51}} & 36.00 & 45.71 & 38.89 & {\color[HTML]{FE0000} \textbf{40.20}} \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 95.57 & 95.17 & 95.51 & {\color[HTML]{FE0000} \textbf{95.42}} & 4.17  & 0.00  & 3.57  & {\color[HTML]{FE0000} \textbf{2.58}}  \\ \hline
				& Centralized & 94.31 & 93.94 & 94.30 & {\color[HTML]{FE0000} \textbf{94.18}} & 87.10 & 63.52 & 78.13 & {\color[HTML]{FE0000} \textbf{76.25}} \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 99.62 & 98.89 & 99.62 & {\color[HTML]{FE0000} \textbf{99.38}} & 78.79 & 70.83 & 75.86 & {\color[HTML]{FE0000} \textbf{75.16}} \\ \hline
			\end{tabular}
		\end{table}

	\section{\textcolor{blue}{Linear Balanced}}
		$$T = \mathop{\arg\min}_{\mu_A \le T \le \mu_B}\ \alpha \cdot \int_{-\infty}^{T}P_B(x)dx + (1 - \alpha) \cdot \int_{T}^{+\infty}P_A(x)dx$$
		\begin{table}[!h]
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
				\hline
				&             & \multicolumn{4}{c|}{True Negative}                            & \multicolumn{4}{c|}{True Positive}                                \\ \hline
				& Centralized & 95.47 & 88.81 & 85.50 & {\color[HTML]{FE0000} \textbf{89.93}} & 100.00 & 96.30  & 100.00 & {\color[HTML]{FE0000} \textbf{98.77}}  \\ \cline{2-10} 
				\multirow{-2}{*}{1st Order} & Equalized   & 73.99 & 80.52 & 79.85 & {\color[HTML]{FE0000} \textbf{78.12}} & 40.91  & 30.14  & 11.11  & {\color[HTML]{FE0000} \textbf{27.39}}  \\ \hline
				& Centralized & 77.70 & 78.88 & 76.87 & {\color[HTML]{FE0000} \textbf{77.82}} & 96.15  & 84.09  & 96.30  & {\color[HTML]{FE0000} \textbf{92.18}}  \\ \cline{2-10} 
				\multirow{-2}{*}{2nd Order} & Equalized   & 72.35 & 78.83 & 77.17 & {\color[HTML]{FE0000} \textbf{76.12}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \hline
			\end{tabular}
		\end{table}

	\section*{Total}

\end{document}

### 2017-08-25 Paper/DataAnomaly/paper.tex
Upload main paper source codes

\documentclass[a4paper]{IEEEtran}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{paper}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Locating Data Flow Anomaly With Statistical Distance}
\author{Ruoyu Wang}
\date{2017.05.04}

\begin{document}
	\maketitle

	\begin{abstract}
		[abstract]
	\end{abstract}

	\section{Introduction}
		Big data industry has been blooming within this decade, reshaping the form of life and work across the globe. According to~\autocite{letouze2014official}, 1.2ZB data had been produced from 2012 to 2014. And the amount doubles every two years. Currently, there are totally 2.7ZB data in the digital universe~\autocite{bigDataStatistics}. Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.

		However, it will be harder in the future to harness the exploding volumes of data since problems have already appeared in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems. Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\autocite{saha2014data}.

		Those data anomalies may arise due to both internal and external reasons with respect to a certain system. From one hand, components inside the system may generate problematic source data. For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\autocite{rassam2014adaptive}. Data packages will be lost if sensor nodes fail to connect to network or some sensor hub goes down~\autocite{herodotou2014scalable}. Also, human operators act as a heavily vulnerable part to bugs and mistakes. Some even deliberately modify system configurations for malicious compromises~\autocite{schuster2015vc3}. A study~\autocite{humanError} found that 65\% of organizations state that human errors are the main  cause of data problems.

		On the other hand, data manipulation~\autocite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability. Taken Apache Hadoop as an example. It's security issues has long been discussed within communities and industry~\autocite{sharif2015current,terzi2015survey,jam2014survey,sharma2014securing}. As is shown in Figure~\ref{fig:hadoop-security}, the two basic vulnerabilities: \textit{lack of access control} and the \textit{absence of encryption} expose the entire cluster to dangerous threats. Data flows can be intercepted and modified; services can also be altered and blocked~\autocite{huang2014denial}. Although there are several frameworks(e.g. Kerberos, Sentry, Knox etc.) and algorithms providing basic protection~\autocite{zheng2017towards,sikdar2017spatio,xu2016high,yu2015enhancing,cohen2014towards}, clever attackers can always bypass the barriers and sneak into the core of data pipelines. Several approaches are developed as sentinels to detect probable infiltrations. However, these approaches are not able to locate corrupted data under carefully planned manipulations. Nor can they figure out the exact reasons and recover the original records. To locate and diagnose anomalies in data pipelines under carefully planned and disguised data manipulations are still on demand by industry and academia.

		\begin{figure}[!t]
			\includegraphics[width=\linewidth]{fig/HadoopSecurity}
			\caption{Security Issues of Hadoop Clusters}
			\label{fig:hadoop-security}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\includegraphics[width=0.75\linewidth]{fig/Example}
			\caption{Example Cumulative Distribution Function of Original And Modified Data}
			\label{fig:example}
		\end{figure}

		According to our observation, typical data manipulations on numerical data will lead to the drift of its distribution. For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original. The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions. These anomalies inside data pipelines will severely affect mining and learning algorithms and further change the final decision given by the entire system.

		In order to address issues resulted from data manipulation and pipeline errors, we propose a novel mechanism to detect and locate corrupted data within a data pipeline via statistical distance. As far as we know, this algorithm is the first attempt against data anomaly via statistical distance. Evaluations are performed on synthetic and real-world data sets, demonstrating the correctness and effectiveness of the mechanism.

		The rest of the paper is organised as follow: Section~\ref{sec:related-work} introduces recent works on data anomaly detection and pipeline error detection. Some background knowledge is provided in section~\ref{sec:preliminaries}. Then in section~\ref{sec:algorithm-details}, details of the detection and locating algorithm is proposed. Section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm. And all contents are concluded in section~\ref{sec:conclusion}.

	\section{Related Work}\label{sec:related-work}
		\subsection{Data Anomaly Detection}

		\subsection{Pipeline Error Detection}

		\subsection{Provenance}

	\section{Preliminaries}\label{sec:preliminaries}
		\subsection{Statistical Distance}

		\subsection{TDA?}

	\section{Algorithm Details}\label{sec:algorithm-details}
		\subsection{Technical Points}
			\textbf{[Can be divided and settled inside later two subsections]}
			\begin{enumerate}
				\item Which classifier should be chosen?
				\item How to determine the classifier threshold?\textbf{[fixed value, 3$\sigma$]}
				\item How to locate the compromised component?
				\item How to deal with slightly drifting distribution?
				\item .[to be continued \dots]
			\end{enumerate}

		\subsection{Basic Algorithm}

		\subsection{Dynamic Algorithm}

	\section{Evaluation}\label{sec:evaluation}
		\subsection{Experiment Environment}

		\subsection{Methodology}
			\textbf{Raise and answer some research questions. Present test background and methods.}

		\subsection{Experiment on Synthetic Data}
			\textbf{Test basic properties of statistical distance and algorithm}

		\subsection{Experiment on Real World Data}
			\textbf{Test performance of algorithm}

	\section{Conclusion}\label{sec:conclusion}

	\section*{Acknowledgement}

	\printbibliography
\end{document}

### 2017-08-25 Paper/DataAnomaly/paper.tex
Modify introduction of paper

@@
 			\centering
-			\includegraphics[width=0.75\linewidth]{fig/Example}
+			\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
 			\caption{Example Cumulative Distribution Function of Original And Modified Data}
-			\label{fig:example}
+			\label{fig:example-ecdf}
 		\end{figure}
@@
 		According to our observation, typical data manipulations on numerical data will lead to the drift of its distribution.
-For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original.
+For example, a Taobao online seller's transaction records can be ``click farmed'' to increase the volume of sales.
+Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day.
+The curve for cheated data is emulated according to a popular method for click farming.
+It can be observed that there exists clearly a gap between these two distributions.
+		%For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original.
 The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.

### 2017-08-25 Synthetic/tmp.py

@@ -1,21 +1,44 @@
-from math import *
+import csv
+import Divergence
+import statistics
+import random
+import scipy.stats as stats
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import math
+import sys
 
-sa = 0.006571
-ua = 0.009587
-sb = 0.03078
-ub = 0.06759
-alpha = 0.1
 
-A = sb * sb - sa * sa
-B = -2 * (ua * sb * sb - ub * sa * sa)
-C = ua * ua * sb * sb - ub * ub * sa * sa - 2 * sa * sa * sb * sb * log(((1 - alpha) * sb) / (alpha * sa))
+reader = csv.reader(open("Correct/92.csv", 'r'))
+data = list(int(row[2]) for row in reader)
+reader = csv.reader(open("Centralized/92.csv", 'r'))
+data_cen = list(int(row[2]) for row in reader)
+step = 1403
 
-D = B * B - 4 * A * C
-print(A)
-print(B)
-print(C)
-print(D)
+dropped, dist = Divergence.histogram(data, step)
+dropped, dist_cen = Divergence.histogram(data_cen, step)
 
-print("Solution: ")
-print((-B + sqrt(D)) / (2 * A))
-print((-B - sqrt(D)) / (2 * A))
+figure = plt.figure(figsize=(1500/300, 900/300), dpi=300)
+acc = 0
+x = []
+ecdf = []
+for i in range(60):
+    if i in dist:
+        acc += dist[i]
+    x += [i, i+1]
+    ecdf += [acc, acc]
+plt.plot(x, ecdf, 'k', label="Correct")
+
+acc = 0
+x = []
+ecdf = []
+for i in range(60):
+    if i in dist_cen:
+        acc += dist_cen[i]
+    x += [i, i+1]
+    ecdf += [acc, acc]
+plt.plot(x, ecdf, 'r', label="Cheated")
+plt.legend()
+plt.grid()
+figure.savefig("ECDF.png")

### 2017-08-31 Paper/Threshold/Compare.tex
Test F1 score for different threshold formulea.

@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                      & \multicolumn{5}{c|}{2nd Order}                               \\ \hline
+				& TP & FP  & TN  & FN                        & F1 Score                               & TP & FP  & TN  & FN & F1 Score                               \\ \hline
+				& 34 & 172 & 89  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2833}} & 37 & 111 & 146 & 1  & {\color[HTML]{FE0000} \textbf{0.3978}} \\ \cline{2-11} 
+				& 33 & 166 & 96  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2845}} & 39 & 141 & 115 & 0  & {\color[HTML]{FE0000} \textbf{0.3562}} \\ \cline{2-11} 
+				& 23 & 178 & 94  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2054}} & 27 & 122 & 146 & 0  & {\color[HTML]{FE0000} \textbf{0.3068}} \\ \cline{2-11} 
+				& 31 & 148 & 116 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2952}} & 34 & 116 & 145 & 0  & {\color[HTML]{FE0000} \textbf{0.3696}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 26 & 173 & 96  & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2311}} & 34 & 146 & 115 & 0  & {\color[HTML]{FE0000} \textbf{0.3178}} \\ \hline
+				& 18 & 168 & 99  & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.1682}} & 25 & 134 & 136 & 0  & {\color[HTML]{FE0000} \textbf{0.2717}} \\ \cline{2-11} 
+				& 17 & 170 & 99  & {\color[HTML]{333333} 9}  & {\color[HTML]{FE0000} \textbf{0.1596}} & 31 & 136 & 128 & 0  & {\color[HTML]{FE0000} \textbf{0.3131}} \\ \cline{2-11} 
+				& 14 & 161 & 108 & {\color[HTML]{333333} 12} & {\color[HTML]{FE0000} \textbf{0.1393}} & 30 & 140 & 125 & 0  & {\color[HTML]{FE0000} \textbf{0.3000}} \\ \cline{2-11} 
+				& 25 & 157 & 98  & {\color[HTML]{333333} 15} & {\color[HTML]{FE0000} \textbf{0.2252}} & 28 & 115 & 152 & 0  & {\color[HTML]{FE0000} \textbf{0.3275}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 18 & 145 & 117 & {\color[HTML]{333333} 15} & {\color[HTML]{FE0000} \textbf{0.1837}} & 23 & 136 & 136 & 0  & {\color[HTML]{FE0000} \textbf{0.2527}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section{\textcolor{blue}{Square-Root Weight}}
@@
 				\multirow{-2}{*}{2nd Order} & Equalized   & 77.57 & 81.27 & 80.59 & {\color[HTML]{FE0000} \textbf{79.81}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \hline
+			\end{tabular}
+		\end{table}
+
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 30 & 6  & 259 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9091}} & 20 & 48 & 227 & 0  & {\color[HTML]{FE0000} \textbf{0.4545}} \\ \cline{2-11} 
+				& 35 & 8  & 252 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8974}} & 24 & 25 & 246 & 0  & {\color[HTML]{FE0000} \textbf{0.6575}} \\ \cline{2-11} 
+				& 27 & 7  & 261 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8852}} & 30 & 48 & 217 & 0  & {\color[HTML]{FE0000} \textbf{0.5556}} \\ \cline{2-11} 
+				& 36 & 6  & 253 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9231}} & 33 & 48 & 214 & 0  & {\color[HTML]{FE0000} \textbf{0.5789}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 23 & 7  & 256 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8679}} & 32 & 48 & 215 & 0  & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \hline
+				& 7  & 73 & 194 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.1296}} & 33 & 23 & 239 & 0  & {\color[HTML]{FE0000} \textbf{0.7416}} \\ \cline{2-11} 
+				& 11 & 68 & 190 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.1897}} & 27 & 45 & 223 & 0  & {\color[HTML]{FE0000} \textbf{0.5455}} \\ \cline{2-11} 
+				& 10 & 90 & 171 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.1493}} & 27 & 66 & 202 & 0  & {\color[HTML]{FE0000} \textbf{0.4500}} \\ \cline{2-11} 
+				& 9  & 81 & 181 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.1463}} & 31 & 30 & 234 & 0  & {\color[HTML]{FE0000} \textbf{0.6739}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 5  & 83 & 193 & {\color[HTML]{333333} 14} & {\color[HTML]{FE0000} \textbf{0.0935}} & 24 & 46 & 225 & 0  & {\color[HTML]{FE0000} \textbf{0.5106}} \\ \hline
 			\end{tabular}
@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 13 & 2  & 264 & {\color[HTML]{333333} 16} & {\color[HTML]{FE0000} \textbf{0.5909}} & 23 & 24 & 246 & 2  & {\color[HTML]{FE0000} \textbf{0.6389}} \\ \cline{2-11} 
+				& 10 & 2  & 270 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.5714}} & 24 & 16 & 250 & 5  & {\color[HTML]{FE0000} \textbf{0.6957}} \\ \cline{2-11} 
+				& 29 & 2  & 242 & {\color[HTML]{333333} 22} & {\color[HTML]{FE0000} \textbf{0.7073}} & 23 & 24 & 245 & 3  & {\color[HTML]{FE0000} \textbf{0.6301}} \\ \cline{2-11} 
+				& 14 & 2  & 262 & {\color[HTML]{333333} 17} & {\color[HTML]{FE0000} \textbf{0.5957}} & 23 & 32 & 234 & 1  & {\color[HTML]{FE0000} \textbf{0.6292}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 14 & 1  & 263 & {\color[HTML]{333333} 17} & {\color[HTML]{FE0000} \textbf{0.6087}} & 21 & 23 & 248 & 3  & {\color[HTML]{FE0000} \textbf{0.6176}} \\ \hline
+				& 1  & 13 & 260 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.0556}} & 35 & 9  & 250 & 1  & {\color[HTML]{FE0000} \textbf{0.8750}} \\ \cline{2-11} 
+				& 1  & 13 & 260 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.0556}} & 22 & 5  & 267 & 1  & {\color[HTML]{FE0000} \textbf{0.8800}} \\ \cline{2-11} 
+				& 2  & 12 & 254 & {\color[HTML]{333333} 17} & {\color[HTML]{FE0000} \textbf{0.0930}} & 27 & 2  & 261 & 5  & {\color[HTML]{FE0000} \textbf{0.8852}} \\ \cline{2-11} 
+				& 5  & 13 & 246 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.1852}} & 33 & 8  & 253 & 1  & {\color[HTML]{FE0000} \textbf{0.8800}}  \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 3  & 13 & 253 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.1333}} & 26 & 6  & 261 & 2  & {\color[HTML]{FE0000} \textbf{0.8667}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section{Square-Log Weight}
@@
 				\multirow{-2}{*}{2nd Order} & Equalized   & 95.88 & 99.23 & 97.76 & {\color[HTML]{FE0000} \textbf{97.62}} & 100.00 & 88.89 & 100.00 & {\color[HTML]{FE0000} \textbf{96.30}} \\ \hline
+			\end{tabular}
+		\end{table}
+
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 21 & 1  & 260 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.7500}} & 29 & 26 & 240 & 0  & {\color[HTML]{FE0000} \textbf{0.6905}} \\ \cline{2-11} 
+				& 15 & 1  & 267 & {\color[HTML]{333333} 12} & {\color[HTML]{FE0000} \textbf{0.6977}} & 28 & 41 & 221 & 5  & {\color[HTML]{FE0000} \textbf{0.5490}} \\ \cline{2-11} 
+				& 9  & 2  & 263 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.4390}} & 29 & 14 & 249 & 3  & {\color[HTML]{FE0000} \textbf{0.7733}} \\ \cline{2-11} 
+				& 11 & 2  & 264 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.5238}} & 28 & 28 & 236 & 3  & {\color[HTML]{FE0000} \textbf{0.6437}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 8  & 2  & 274 & {\color[HTML]{333333} 11} & {\color[HTML]{FE0000} \textbf{0.5517}} & 31 & 18 & 243 & 3  & {\color[HTML]{FE0000} \textbf{0.7470}} \\ \hline
+				& 1  & 16 & 249 & {\color[HTML]{333333} 29} & {\color[HTML]{FE0000} \textbf{0.0426}} & 21 & 11 & 263 & 0  & {\color[HTML]{FE0000} \textbf{0.7925}} \\ \cline{2-11} 
+				& 5  & 10 & 249 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.1961}} & 24 & 15 & 256 & 0  & {\color[HTML]{FE0000} \textbf{0.7619}} \\ \cline{2-11} 
+				& 1  & 18 & 250 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0435}} & 35 & 8  & 252 & 0  & {\color[HTML]{FE0000} \textbf{0.8974}} \\ \cline{2-11} 
+				& 2  & 13 & 243 & {\color[HTML]{333333} 37} & {\color[HTML]{FE0000} \textbf{0.0741}} & 25 & 5  & 263 & 2  & {\color[HTML]{FE0000} \textbf{0.8772}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 3  & 12 & 250 & {\color[HTML]{333333} 30} & {\color[HTML]{FE0000} \textbf{0.1250}} & 32 & 4  & 253 & 6  & {\color[HTML]{FE0000} \textbf{0.8649}} \\ \hline
 			\end{tabular}
@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 11 & 2  & 263 & {\color[HTML]{333333} 19} & {\color[HTML]{FE0000} \textbf{0.5116}} & 25 & 20 & 248 & 2  & {\color[HTML]{FE0000} \textbf{0.6944}} \\ \cline{2-11} 
+				& 7  & 1  & 262 & {\color[HTML]{333333} 25} & {\color[HTML]{FE0000} \textbf{0.3500}} & 25 & 18 & 250 & 2  & {\color[HTML]{FE0000} \textbf{0.7143}} \\ \cline{2-11} 
+				& 11 & 2  & 272 & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.6471}} & 29 & 16 & 248 & 2  & {\color[HTML]{FE0000} \textbf{0.7632}} \\ \cline{2-11} 
+				& 11 & 2  & 264 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.5238}} & 23 & 20 & 244 & 8  & {\color[HTML]{FE0000} \textbf{0.6216}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 15 & 2  & 248 & {\color[HTML]{333333} 30} & {\color[HTML]{FE0000} \textbf{0.4839}} & 27 & 20 & 242 & 6  & {\color[HTML]{FE0000} \textbf{0.6750}} \\ \hline
+				& 2  & 12 & 253 & {\color[HTML]{333333} 28} & {\color[HTML]{FE0000} \textbf{0.0909}} & 25 & 4  & 264 & 2  & {\color[HTML]{FE0000} \textbf{0.8929}} \\ \cline{2-11} 
+				& 0  & 17 & 249 & {\color[HTML]{333333} 29} & {\color[HTML]{FE0000} \textbf{0.0000}} & 28 & 11 & 255 & 1  & {\color[HTML]{FE0000} \textbf{0.8235}} \\ \cline{2-11} 
+				& 1  & 13 & 250 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.0435}} & 23 & 4  & 263 & 5  & {\color[HTML]{FE0000} \textbf{0.8364}} \\ \cline{2-11} 
+				& 2  & 14 & 254 & {\color[HTML]{333333} 25} & {\color[HTML]{FE0000} \textbf{0.0930}} & 21 & 5  & 267 & 2  & {\color[HTML]{FE0000} \textbf{0.8571}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 1  & 13 & 261 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.0571}} & 25 & 1  & 266 & 3  & {\color[HTML]{FE0000} \textbf{0.9259}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section{Linear Additional Weight}
@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP  & TN & FN                        & F1 Score                               & TP & FP  & TN & FN & F1 Score                               \\ \hline
+				& 34 & 202 & 59 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2519}} & 29 & 222 & 44 & 0  & {\color[HTML]{FE0000} \textbf{0.2071}} \\ \cline{2-11} 
+				& 30 & 202 & 63 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2290}} & 33 & 217 & 45 & 0  & {\color[HTML]{FE0000} \textbf{0.2332}} \\ \cline{2-11} 
+				& 24 & 216 & 55 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.1818}} & 33 & 216 & 46 & 0  & {\color[HTML]{FE0000} \textbf{0.2340}} \\ \cline{2-11} 
+				& 31 & 201 & 63 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2357}} & 33 & 216 & 46 & 0  & {\color[HTML]{FE0000} \textbf{0.2340}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 36 & 202 & 57 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.2628}} & 40 & 207 & 48 & 0  & {\color[HTML]{FE0000} \textbf{0.2787}} \\ \hline
+				& 23 & 208 & 55 & {\color[HTML]{333333} 9}  & {\color[HTML]{FE0000} \textbf{0.1749}} & 25 & 228 & 42 & 0  & {\color[HTML]{FE0000} \textbf{0.1799}} \\ \cline{2-11} 
+				& 20 & 206 & 59 & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.1563}} & 25 & 225 & 45 & 0  & {\color[HTML]{FE0000} \textbf{0.1818}} \\ \cline{2-11} 
+				& 22 & 203 & 65 & {\color[HTML]{333333} 5}  & {\color[HTML]{FE0000} \textbf{0.1746}} & 17 & 234 & 44 & 0  & {\color[HTML]{FE0000} \textbf{0.1269}} \\ \cline{2-11} 
+				& 15 & 217 & 55 & {\color[HTML]{333333} 8}  & {\color[HTML]{FE0000} \textbf{0.1176}} & 34 & 220 & 41 & 0  & {\color[HTML]{FE0000} \textbf{0.2361}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 22 & 210 & 53 & {\color[HTML]{333333} 10} & {\color[HTML]{FE0000} \textbf{0.1667}} & 23 & 228 & 44 & 0  & {\color[HTML]{FE0000} \textbf{0.1679}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section{Square-Root Additional Weight}
@@
 				\multirow{-2}{*}{2nd Order} & Equalized   & 17.74 & 17.16 & 17.91 & {\color[HTML]{FE0000} \textbf{17.60}} & 100.00 & 100.00 & 100.00 & {\color[HTML]{FE0000} \textbf{100.00}} \\ \hline
+			\end{tabular}
+		\end{table}
+
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                    & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP  & TN & FN                       & F1 Score                               & TP & FP  & TN & FN & F1 Score                               \\ \hline
+				& 33 & 193 & 63 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.2548}} & 28 & 219 & 48 & 0  & {\color[HTML]{FE0000} \textbf{0.2036}} \\ \cline{2-11} 
+				& 24 & 199 & 72 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.1943}} & 36 & 207 & 52 & 0  & {\color[HTML]{FE0000} \textbf{0.2581}} \\ \cline{2-11} 
+				& 38 & 183 & 74 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.2934}} & 36 & 206 & 53 & 0  & {\color[HTML]{FE0000} \textbf{0.2590}} \\ \cline{2-11} 
+				& 25 & 201 & 69 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.1992}} & 35 & 205 & 55 & 0  & {\color[HTML]{FE0000} \textbf{0.2545}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 28 & 199 & 68 & {\color[HTML]{333333} 0} & {\color[HTML]{FE0000} \textbf{0.2196}} & 26 & 216 & 53 & 0  & {\color[HTML]{FE0000} \textbf{0.1940}} \\ \hline
+				& 26 & 190 & 76 & {\color[HTML]{333333} 3} & {\color[HTML]{FE0000} \textbf{0.2122}} & 22 & 224 & 49 & 0  & {\color[HTML]{FE0000} \textbf{0.1642}} \\ \cline{2-11} 
+				& 17 & 201 & 70 & {\color[HTML]{333333} 7} & {\color[HTML]{FE0000} \textbf{0.1405}} & 25 & 222 & 48 & 0  & {\color[HTML]{FE0000} \textbf{0.1838}} \\ \cline{2-11} 
+				& 22 & 191 & 77 & {\color[HTML]{333333} 5} & {\color[HTML]{FE0000} \textbf{0.1833}} & 26 & 220 & 49 & 0  & {\color[HTML]{FE0000} \textbf{0.1912}} \\ \cline{2-11} 
+				& 16 & 200 & 73 & {\color[HTML]{333333} 6} & {\color[HTML]{FE0000} \textbf{0.1345}} & 26 & 224 & 45 & 0  & {\color[HTML]{FE0000} \textbf{0.1884}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 17 & 202 & 71 & {\color[HTML]{333333} 5} & {\color[HTML]{FE0000} \textbf{0.1411}} & 29 & 219 & 47 & 0  & {\color[HTML]{FE0000} \textbf{0.2094}} \\ \hline
 			\end{tabular}
@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 6  & 2  & 267 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.3750}} & 7  & 5  & 264 & 19 & {\color[HTML]{FE0000} \textbf{0.3684}} \\ \cline{2-11} 
+				& 10 & 2  & 270 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.5714}} & 7  & 4  & 263 & 21 & {\color[HTML]{FE0000} \textbf{0.3590}} \\ \cline{2-11} 
+				& 8  & 1  & 262 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.3902}} & 12 & 5  & 265 & 13 & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \cline{2-11} 
+				& 11 & 1  & 259 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.4681}} & 7  & 4  & 263 & 21 & {\color[HTML]{FE0000} \textbf{0.3590}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 12 & 1  & 262 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.5333}} & 12 & 2  & 265 & 16 & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \hline
+				& 0  & 11 & 252 & {\color[HTML]{333333} 32} & {\color[HTML]{FE0000} \textbf{0.0000}} & 12 & 0  & 262 & 21 & {\color[HTML]{FE0000} \textbf{0.5333}} \\ \cline{2-11} 
+				& 0  & 11 & 253 & {\color[HTML]{333333} 31} & {\color[HTML]{FE0000} \textbf{0.0000}} & 10 & 0  & 270 & 15 & {\color[HTML]{FE0000} \textbf{0.5714}} \\ \cline{2-11} 
+				& 1  & 12 & 258 & {\color[HTML]{333333} 24} & {\color[HTML]{FE0000} \textbf{0.0526}} & 18 & 0  & 254 & 23 & {\color[HTML]{FE0000} \textbf{0.6101}} \\ \cline{2-11} 
+				& 2  & 9  & 261 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.1111}} & 10 & 0  & 267 & 18 & {\color[HTML]{FE0000} \textbf{0.5263}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 2  & 9  & 257 & {\color[HTML]{333333} 27} & {\color[HTML]{FE0000} \textbf{0.1000}} & 13 & 0  & 260 & 22 & {\color[HTML]{FE0000} \textbf{0.5417}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section{\textcolor{blue}{Square-Log Additional Weight}}
@@
 				\multirow{-2}{*}{2nd Order} & Equalized   & 99.26 & 98.49 & 96.67 & {\color[HTML]{FE0000} \textbf{98.14}} & 91.30 & 100.00 & 96.00  & {\color[HTML]{FE0000} \textbf{95.77}} \\ \hline
+			\end{tabular}
+		\end{table}
+
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 24 & 2  & 266 & {\color[HTML]{333333} 3}  & {\color[HTML]{FE0000} \textbf{0.9057}} & 19 & 12 & 252 & 12 & {\color[HTML]{FE0000} \textbf{0.6129}} \\ \cline{2-11} 
+				& 28 & 3  & 264 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9492}} & 29 & 14 & 248 & 4  & {\color[HTML]{FE0000} \textbf{0.7632}} \\ \cline{2-11} 
+				& 27 & 4  & 264 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.9310}} & 23 & 14 & 253 & 5  & {\color[HTML]{FE0000} \textbf{0.7077}} \\ \cline{2-11} 
+				& 26 & 3  & 265 & {\color[HTML]{333333} 1}  & {\color[HTML]{FE0000} \textbf{0.9286}} & 17 & 13 & 256 & 9  & {\color[HTML]{FE0000} \textbf{0.6071}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 31 & 4  & 257 & {\color[HTML]{333333} 3}  & {\color[HTML]{FE0000} \textbf{0.8986}} & 18 & 14 & 257 & 6  & {\color[HTML]{FE0000} \textbf{0.6429}} \\ \hline
+				& 8  & 25 & 242 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.2623}} & 24 & 10 & 261 & 0  & {\color[HTML]{FE0000} \textbf{0.8276}} \\ \cline{2-11} 
+				& 4  & 27 & 243 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.1429}} & 30 & 6  & 258 & 1  & {\color[HTML]{FE0000} \textbf{0.8955}} \\ \cline{2-11} 
+				& 3  & 32 & 239 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.1017}} & 34 & 9  & 252 & 0  & {\color[HTML]{FE0000} \textbf{0.8831}} \\ \cline{2-11} 
+				& 4  & 29 & 229 & {\color[HTML]{333333} 33} & {\color[HTML]{FE0000} \textbf{0.1143}} & 20 & 1  & 262 & 12 & {\color[HTML]{FE0000} \textbf{0.7547}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 1  & 33 & 235 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0328}} & 34 & 2  & 257 & 2  & {\color[HTML]{FE0000} \textbf{0.9444}} \\ \hline
 			\end{tabular}
@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 11 & 1  & 262 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.5000}} & 8  & 5  & 259 & 23 & {\color[HTML]{FE0000} \textbf{0.3636}} \\ \cline{2-11} 
+				& 5  & 1  & 266 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.2941}} & 9  & 3  & 271 & 12 & {\color[HTML]{FE0000} \textbf{0.5455}} \\ \cline{2-11} 
+				& 6  & 2  & 264 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.3243}} & 10 & 2  & 267 & 16 & {\color[HTML]{FE0000} \textbf{0.5263}} \\ \cline{2-11} 
+				& 6  & 1  & 270 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.3871}} & 16 & 3  & 256 & 20 & {\color[HTML]{FE0000} \textbf{0.5818}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 7  & 0  & 267 & {\color[HTML]{333333} 21} & {\color[HTML]{FE0000} \textbf{0.4000}} & 9  & 6  & 261 & 19 & {\color[HTML]{FE0000} \textbf{0.4186}} \\ \hline
+				& 0  & 11 & 262 & {\color[HTML]{333333} 22} & {\color[HTML]{FE0000} \textbf{0.0000}} & 17 & 0  & 254 & 24 & {\color[HTML]{FE0000} \textbf{0.5862}} \\ \cline{2-11} 
+				& 1  & 9  & 257 & {\color[HTML]{333333} 28} & {\color[HTML]{FE0000} \textbf{0.0513}} & 6  & 0  & 269 & 20 & {\color[HTML]{FE0000} \textbf{0.3750}} \\ \cline{2-11} 
+				& 1  & 10 & 258 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0526}} & 13 & 0  & 264 & 18 & {\color[HTML]{FE0000} \textbf{0.5909}} \\ \cline{2-11} 
+				& 0  & 12 & 255 & {\color[HTML]{333333} 28} & {\color[HTML]{FE0000} \textbf{0.0000}} & 15 & 0  & 255 & 25 & {\color[HTML]{FE0000} \textbf{0.5455}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 1  & 10 & 238 & {\color[HTML]{333333} 46} & {\color[HTML]{FE0000} \textbf{0.0345}} & 13 & 0  & 264 & 18 & {\color[HTML]{FE0000} \textbf{0.5909}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section{Square-Log Combined Weight}
@@
 				\multirow{-2}{*}{2nd Order} & Equalized   & 97.00 & 99.23 & 95.96 & {\color[HTML]{FE0000} \textbf{97.40}} & 100.00 & 76.47 & 95.65 & {\color[HTML]{FE0000} \textbf{90.71}} \\ \hline
+			\end{tabular}
+		\end{table}
+
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 25 & 2  & 256 & {\color[HTML]{333333} 12} & {\color[HTML]{FE0000} \textbf{0.7813}} & 22 & 17 & 250 & 6  & {\color[HTML]{FE0000} \textbf{0.6567}} \\ \cline{2-11} 
+				& 15 & 2  & 260 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.6000}} & 23 & 23 & 247 & 2  & {\color[HTML]{FE0000} \textbf{0.6479}} \\ \cline{2-11} 
+				& 12 & 1  & 262 & {\color[HTML]{333333} 20} & {\color[HTML]{FE0000} \textbf{0.5333}} & 24 & 15 & 250 & 6  & {\color[HTML]{FE0000} \textbf{0.6957}} \\ \cline{2-11} 
+				& 13 & 2  & 267 & {\color[HTML]{333333} 13} & {\color[HTML]{FE0000} \textbf{0.6341}} & 28 & 27 & 235 & 5  & {\color[HTML]{FE0000} \textbf{0.6364}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 12 & 0  & 272 & {\color[HTML]{333333} 11} & {\color[HTML]{FE0000} \textbf{0.6857}} & 21 & 29 & 242 & 3  & {\color[HTML]{FE0000} \textbf{0.5676}} \\ \hline
+				& 2  & 12 & 256 & {\color[HTML]{333333} 25} & {\color[HTML]{FE0000} \textbf{0.0976}} & 20 & 3  & 270 & 2  & {\color[HTML]{FE0000} \textbf{0.8889}} \\ \cline{2-11} 
+				& 2  & 12 & 238 & {\color[HTML]{333333} 43} & {\color[HTML]{FE0000} \textbf{0.0678}} & 43 & 7  & 244 & 1  & {\color[HTML]{FE0000} \textbf{0.9149}} \\ \cline{2-11} 
+				& 3  & 11 & 244 & {\color[HTML]{333333} 37} & {\color[HTML]{FE0000} \textbf{0.1111}} & 16 & 1  & 276 & 2  & {\color[HTML]{FE0000} \textbf{0.9143}} \\ \cline{2-11} 
+				& 0  & 17 & 245 & {\color[HTML]{333333} 33} & {\color[HTML]{FE0000} \textbf{0.0000}} & 29 & 7  & 259 & 0  & {\color[HTML]{FE0000} \textbf{0.8923}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 3  & 11 & 259 & {\color[HTML]{333333} 22} & {\color[HTML]{FE0000} \textbf{0.1538}} & 27 & 5  & 261 & 2  & {\color[HTML]{FE0000} \textbf{0.8852}} \\ \hline
 			\end{tabular}
@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 12 & 1  & 263 & {\color[HTML]{333333} 19} & {\color[HTML]{FE0000} \textbf{0.5455}} & 24 & 14 & 247 & 10 & {\color[HTML]{FE0000} \textbf{0.6667}} \\ \cline{2-11} 
+				& 6  & 1  & 274 & {\color[HTML]{333333} 14} & {\color[HTML]{FE0000} \textbf{0.4444}} & 19 & 20 & 254 & 2  & {\color[HTML]{FE0000} \textbf{0.6333}} \\ \cline{2-11} 
+				& 19 & 0  & 248 & {\color[HTML]{333333} 28} & {\color[HTML]{FE0000} \textbf{0.5758}} & 16 & 17 & 256 & 6  & {\color[HTML]{FE0000} \textbf{0.5818}} \\ \cline{2-11} 
+				& 19 & 1  & 259 & {\color[HTML]{333333} 16} & {\color[HTML]{FE0000} \textbf{0.6909}} & 21 & 17 & 250 & 7  & {\color[HTML]{FE0000} \textbf{0.6364}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 8  & 0  & 269 & {\color[HTML]{333333} 18} & {\color[HTML]{FE0000} \textbf{0.4706}} & 15 & 14 & 261 & 5  & {\color[HTML]{FE0000} \textbf{0.6122}} \\ \hline
+				& 3  & 11 & 258 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.1500}} & 23 & 2  & 264 & 6  & {\color[HTML]{FE0000} \textbf{0.8519}} \\ \cline{2-11} 
+				& 0  & 13 & 247 & {\color[HTML]{333333} 35} & {\color[HTML]{FE0000} \textbf{0.0000}} & 24 & 0  & 261 & 10 & {\color[HTML]{FE0000} \textbf{0.8276}} \\ \cline{2-11} 
+				& 0  & 12 & 257 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0000}} & 19 & 0  & 272 & 4  & {\color[HTML]{FE0000} \textbf{0.9048}} \\ \cline{2-11} 
+				& 2  & 12 & 255 & {\color[HTML]{333333} 26} & {\color[HTML]{FE0000} \textbf{0.0952}} & 15 & 1  & 266 & 13 & {\color[HTML]{FE0000} \textbf{0.6818}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 2  & 11 & 255 & {\color[HTML]{333333} 27} & {\color[HTML]{FE0000} \textbf{0.0952}} & 26 & 3  & 264 & 2  & {\color[HTML]{FE0000} \textbf{0.9123}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section{\textcolor{blue}{Linear Balanced}}
@@
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{5}{c|}{1st Order}                                                     & \multicolumn{5}{c|}{2nd Order}                              \\ \hline
+				& TP & FP & TN  & FN                        & F1 Score                               & TP & FP & TN  & FN & F1 Score                               \\ \hline
+				& 24 & 17 & 254 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.7385}} & 25 & 57 & 210 & 3  & {\color[HTML]{FE0000} \textbf{0.4545}} \\ \cline{2-11} 
+				& 30 & 11 & 254 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8451}} & 30 & 58 & 206 & 1  & {\color[HTML]{FE0000} \textbf{0.5042}} \\ \cline{2-11} 
+				& 26 & 33 & 236 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.6118}} & 28 & 59 & 203 & 5  & {\color[HTML]{FE0000} \textbf{0.4667}} \\ \cline{2-11} 
+				& 27 & 28 & 240 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.6585}} & 27 & 52 & 216 & 0  & {\color[HTML]{FE0000} \textbf{0.5094}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Centralized} & 32 & 14 & 249 & {\color[HTML]{333333} 0}  & {\color[HTML]{FE0000} \textbf{0.8205}} & 32 & 60 & 203 & 0  & {\color[HTML]{FE0000} \textbf{0.5161}} \\ \hline
+				& 6  & 63 & 199 & {\color[HTML]{333333} 27} & {\color[HTML]{FE0000} \textbf{0.1176}} & 32 & 51 & 212 & 0  & {\color[HTML]{FE0000} \textbf{0.5565}} \\ \cline{2-11} 
+				& 13 & 53 & 214 & {\color[HTML]{333333} 15} & {\color[HTML]{FE0000} \textbf{0.2766}} & 35 & 48 & 212 & 0  & {\color[HTML]{FE0000} \textbf{0.5932}} \\ \cline{2-11} 
+				& 5  & 66 & 194 & {\color[HTML]{333333} 30} & {\color[HTML]{FE0000} \textbf{0.0943}} & 22 & 36 & 237 & 0  & {\color[HTML]{FE0000} \textbf{0.5500}} \\ \cline{2-11} 
+				& 10 & 50 & 212 & {\color[HTML]{333333} 23} & {\color[HTML]{FE0000} \textbf{0.2151}} & 23 & 51 & 221 & 0  & {\color[HTML]{FE0000} \textbf{0.4742}} \\ \cline{2-11} 
+				\multirow{-5}{*}{Equalized}   & 3  & 62 & 208 & {\color[HTML]{333333} 22} & {\color[HTML]{FE0000} \textbf{0.0667}} & 38 & 55 & 202 & 0  & {\color[HTML]{FE0000} \textbf{0.5802}} \\ \hline
+			\end{tabular}
+		\end{table}
+
 	\section*{Total}
 
+		\begin{table}[!h]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|}
+				\hline
+				& \multicolumn{2}{c|}{1st Order} & \multicolumn{2}{c|}{2nd Order}&\\
+				\hline
+				No. & Centralized & Equalized & Centralized & Equalized & Sum\\
+				\hline
+				1 & 0.2410 & 0.1752 & 0.3496 & 0.2930 & 1.0588\\
+				\hline
+				2 & 0.8965 & 0.1417 & 0.5636 & 0.5843 & 2.1861\\
+				\hline
+				3 & 0.6148 & 0.1045 & 0.6423 & 0.8774 & 2.2390\\
+				\hline
+				4 & 0.5924 & 0.0963 & 0.6807 & 0.8388 & 2.2082\\
+				\hline
+				5 & 0.5033 & 0.0569 & 0.6937 & 0.8672 & 2.1211\\
+				\hline
+				6 & 0.2322 & 0.1580 & 0.2001 & 0.1785 & 0.7688\\
+				\hline
+				7 & 0.2323 & 0.1623 & 0.2338 & 0.1874 & 0.8158\\
+				\hline
+				8 & 0.4676 & 0.0527 & 0.4458 & 0.5566 & 1.5227\\
+				\hline
+				9 & 0.9226 & 0.1508 & 0.6668 & 0.8611 & 2.6013\\
+				\hline
+				10 & 0.3811 & 0.0277 & 0.4872 & 0.5195 & 1.4155\\
+				\hline
+				11 & 0.6469 & 0.0861 & 0.6409 & 0.8991 & 2.2730\\
+				\hline
+				12 & 0.5454 & 0.0681 & 0.6261 & 0.8357 & 2.0753\\
+				\hline
+				13 & 0.7349 & 0.1541 & 0.4902 & 0.5508 & 1.9300\\
+				\hline
+			\end{tabular}
+		\end{table}
+		Order:
+
+		$9 > 11 > 3 > 4 > 2 > 5 > 12 > 13 > 8 > 10 > 1 > 7 > 6$
+
+	\section*{Test with Gaussian Data}
+		\centering
+		\begin{tabular}{|c|c|c|}
+			\hline 
+			& F1 & False Rate(\%) \\ 
+			\hline 
+			1 & 0.5810 & 17.12 \\ 
+			\hline 
+			2 & 0.5718 & 18.06 \\ 
+			\hline 
+			3 & 0.3860 & 31.50 \\ 
+			\hline 
+			4 & 0.5515 & 19.31 \\ 
+			\hline 
+			5 & 0.3811 & 30.31 \\ 
+			\hline 
+			6 & 0.3515 & 36.16 \\ 
+			\hline 
+			7 & 0.4510 & 26.54 \\ 
+			\hline 
+			8 & 0.5523 & 13.32 \\ 
+			\hline 
+			9 & 0.5791 & 14.71 \\ 
+			\hline 
+			10 & 0.5578 & 13.23 \\ 
+			\hline 
+			11 & 0.5600 & 17.98 \\ 
+			\hline 
+			12 & 0.2808 & 27.01 \\ 
+			\hline 
+			13 & 0.6072 & 12.69 \\ 
+			\hline 
+		\end{tabular}
+
 \end{document}

### 2017-08-31 Synthetic/TestFirstOrder.py

@@ -81,10 +81,10 @@ for i in range(30, 325):
     jsd_mean_err = statistics.mean(jsd_evidence_err)
     jsd_sigma_err = statistics.stdev(jsd_evidence_err)
 
-    w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
-    w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
-    threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
-    #threshold = linearBalancedThreshold(jsd_mean, jsd_sigma, jsd_mean_err, jsd_sigma_err, error_rate)
+    #w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
+    #w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
+    #threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
+    threshold = linearBalancedThreshold(jsd_mean, jsd_sigma, jsd_mean_err, jsd_sigma_err, error_rate)
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'
@@ -155,6 +155,16 @@ try:
        100 * error_recognized / error_cnt, error_recognized, error_cnt))
 except ZeroDivisionError as e:
     print(e)
+
+tp = error_recognized
+fp = correct_cnt - correct_recognized
+tn = correct_recognized
+fn = error_cnt - error_recognized
+
+pre = tp / (tp + fp)
+rec = tp / (tp + fn)
+f1 = 2 * pre * rec / (pre + rec)
+print("tp=%d, fp=%d, tn=%d, fn=%d, f1=%f\n" % (tp, fp, tn, fn, f1))
 
 # Show JSD History
 figure = plt.figure(figsize=(6000/300, 3000/300), dpi=300)

### 2017-08-31 Synthetic/TestSecondOrder.py

@@ -29,7 +29,7 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Centralized"
+input_dir_err = "Equalized"
 
 error_rate = 0.1
 #sigma_coefficient = 3  # Don't think about this now
@@ -83,10 +83,10 @@ for i in range(30, 325):
     jsd_mean_err = statistics.mean(jsd_evidence_err)
     jsd_sigma_err = statistics.stdev(jsd_evidence_err)
 
-    w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
-    w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
-    threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
-    #threshold = linearBalancedThreshold(jsd_mean, jsd_sigma, jsd_mean_err, jsd_sigma_err, error_rate)
+    #w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
+    #w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
+    #threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
+    threshold = linearBalancedThreshold(jsd_mean, jsd_sigma, jsd_mean_err, jsd_sigma_err, error_rate)
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'
@@ -159,6 +159,16 @@ try:
        100 * error_recognized / error_cnt, error_recognized, error_cnt))
 except ZeroDivisionError as e:
     print(e)
+
+tp = error_recognized
+fp = correct_cnt - correct_recognized
+tn = correct_recognized
+fn = error_cnt - error_recognized
+
+pre = tp / (tp + fp)
+rec = tp / (tp + fn)
+f1 = 2 * pre * rec / (pre + rec)
+print("tp=%d, fp=%d, tn=%d, fn=%d, f1=%f\n" % (tp, fp, tn, fn, f1))
 
 # Show JSD History
 figure = plt.figure(figsize=(6000 / 300, 3000 / 300), dpi=300)

### 2017-08-31 Synthetic/TestWithGaussianData.py

@@ -1,0 +1,125 @@
+import math
+import numpy
+import statistics
+
+
+def linearBalancedThreshold(ua, sa, ub, sb, alpha):
+    A = sb * sb - sa * sa
+    B = -2 * (ua * sb * sb - ub * sa * sa)
+    C = ua * ua * sb * sb - ub * ub * sa * sa - 2 * sa * sa * sb * sb * math.log(((1 - alpha) * sb) / (alpha * sa))
+    D = B * B - 4 * A * C
+    if D < 0:
+        return ub
+    sol1 = (-B + math.sqrt(D)) / (2 * A)
+    sol2 = (-B - math.sqrt(D)) / (2 * A)
+    # if ua <= sol1 <= ub:
+    #     return sol1
+    # elif ua <= sol2 <= ub:
+    #     return sol2
+    # else:
+    #     return (ua * sb + ub * sa) / (sa + sb)
+    if ua <= sol1 <= ub:
+        return sol1
+    elif ua <= sol2 <= ub:
+        return sol2
+    else:
+        return ub
+
+alpha = 0.1
+
+f1s = []
+falses = []
+n = 500
+
+for round in range(n):
+    ua = numpy.random.random() * 10
+    sa = numpy.random.random() * 5
+    ub = numpy.random.random() * 10 + ua
+    sb = numpy.random.random() * 5
+
+    total_cnt = 100000
+    correct_cnt = int(total_cnt * (1 - alpha))
+    correct_recognized = 0
+    error_cnt = int(total_cnt * alpha)
+    error_recognized = 0
+
+    data = list(numpy.random.normal(ua, sa, correct_cnt))
+    data_err = list(numpy.random.normal(ub, sb, error_cnt))
+
+    # 1
+    # w = sb
+    # w_err = sa
+
+    # 2
+    # w = math.sqrt(sb)
+    # w_err = math.sqrt(sa)
+
+    # 3
+    # w = math.log(sb)
+    # w_err = math.log(sa)
+
+    # 4
+    # w = math.sqrt(abs(math.log(sb)))
+    # w_err = math.sqrt(abs(math.log(sa)))
+
+    # 5
+    # w = math.log(math.sqrt(sb))
+    # w_err = math.log(math.sqrt(sa))
+
+    # 6
+    # w = sb * (1 - alpha)
+    # w_err = sa * alpha
+
+    # 7
+    # w = sb * math.sqrt(1 - alpha)
+    # w_err = sa * math.sqrt(alpha)
+
[…]

### 2017-09-02 Paper/DataAnomaly/paper.tex
Modify paper, write new content in "Related Work"

@@
 		\subsection{Data Anomaly Detection}
+			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.
+According to a systematic classification in~\cite{chandola2009anomaly}, anomaly detection algorithms deal with input data in the form of points(or records), sequences, graphs and spatial relationships, where point data is the simplest and well studied, others are attracting more attention in new studies.
+
+			Prevalent anomalies can be classified into \textit{Point Anomalies}, \textit{Contextual(or Conditional) Anomalies} and \textit{Collective Anomalies}.
+Point anomalies refers to an individual data instance that is considered anomalous with respect to others.
+But if it is anomalous only in certain circumstances or a specific context, the data is regarded as contextual anomaly.
+If a group of related data(e.g.
+a segment of sequence) instances is anomalous with respect to other groups in the data set(e.g.
+the entire sequence), it is called a collective anomaly.
+
+			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection.
+As the name suggests, supervised detection methods train models on completely labeled data while unsupervised detection leverages data without any labeling.
+Semi-supervised detection approaches train model on data that has labeled instances for only the normal class.
+Supervised detection is commonly applied when both normal and anomalous data can be obtained.
+When it comes to the circumstances that anomalous data is hard to obtain or there exist too many diverse types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
+
+			To make the final decision, detection algorithms mostly yield a score from each input instance, denoting how likely it is anomalous.
+The algorithm then selects top few as anomalies or compare the score with a threshold.
+Or, detection algorithms output a label on each instance, then decide whether each label belongs to the normal class.
+
+			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} algorithms seize most attention.
+Others adopted tree isolation~\cite{zhang2017lshiforest}, model based~\cite{yin2016model} and statistical methods~\cite{zhu2002statstream} in certain applications.
+
+			(or group anomaly)\cite{yu2015glad}.
 
@@
 		\subsection{Provenance}
+
+		\subsection{Click Farming Detection}
 

### 2017-09-04 Paper/DataAnomaly/paper.tex
Write Section 'Algorithm Details' in the paper.

@@
 \usepackage{graphicx}
+\usepackage{amsmath,amsfonts}
+\usepackage{algorithm,algorithmicx,algpseudocode}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 
-		The rest of the paper is organised as follow: Section~\ref{sec:related-work} introduces recent works on data anomaly detection and pipeline error detection.
-Some background knowledge is provided in section~\ref{sec:preliminaries}.
-Then in section~\ref{sec:algorithm-details}, details of the detection and locating algorithm is proposed.
+		The rest of the paper is organised as follow: Section~\ref{sec:related-work} introduces preliminaries and recent works on data anomaly detection and statistical distance.
+Algorithm details are proposed in section~\ref{sec:algorithm-details}.
 Section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm.
@@
 
-	\section{Related Work}\label{sec:related-work}
+	\section{Preliminaries and Related Work}\label{sec:related-work}
 		\subsection{Data Anomaly Detection}
@@
 Point anomalies refers to an individual data instance that is considered anomalous with respect to others.
-But if it is anomalous only in certain circumstances or a specific context, the data is regarded as contextual anomaly.
+But if it is anomalous only in certain circumstances or a specific context, the instance is regarded as contextual anomaly.
 If a group of related data(e.g.
@@
 
-			(or group anomaly)\cite{yu2015glad}.
-
-		\subsection{Pipeline Error Detection}
-
-		\subsection{Provenance}
+			To detect collective anomalies,~\cite{caudell1993adaptive} adopted the \textit{ART(Adoptive Resonance Theory)} neural networks to detect time-series anomalies.
+\textit{Box Modeling} is proposed in ~\cite{chan2005modeling}.
+And \textit{Longest Common Subsequence} was leveraged in ~\cite{budalakoti2006anomaly} as similarity metric for symbolic sequence.
+Markovian modeling techniques are also popular in this domain\cite{ye2000markov,warrender1999detecting,pavlov2003sequence}.
+\cite{yu2015glad} depicted groups in social media as combinations of different ``roles'' and compare groups according to the proportion of each role within each group.
 
@@
 
-	\section{Preliminaries}\label{sec:preliminaries}
-		\subsection{Statistical Distance}
+		\subsection{Statistical Divergence}
+			Statistical divergence, also called statistical distance, is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
+Suppose $S$ is a space of probability distributions, then a divergence is a function from $S$ to non-negative real numbers:
+			\begin{equation}
+				D(\cdot || \cdot): S \times S \rightarrow \mathbb{R^+}
+			\end{equation}
 
-		\subsection{TDA?}
+			Divergence between two distributions $P$ and $Q$, written as $D(P||Q)$, satisfies:
+
+			\begin{enumerate}
+				\item $D(P||Q) \ge 0, \forall P, Q \in S$
+				\item $D(P||Q) = 0$, if and only if $P=Q$
+			\end{enumerate}
+
+			There are many ways to calculate divergence, such as f-divergences, M-divergences and S-divergences.
+Some of them provides better properties which brings conveniences to the design and implementation of our approach.
+
+			\subsubsection{Kullback-Leibler Divergence}
+			$P,Q$ are discrete probability distributions, $Q(i)=0$ implies $P(i)=0$ for $\forall i$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:
+
+			\begin{equation}
+			KLD(P||Q) = \sum_{Q(i)\ne 0} P(i)log\Big(\frac{P(i)}{Q(i)}\Big)
+			\end{equation}
+
+			\subsubsection{Jensen-Shannon Divergence}
+			$P,Q$ are discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:
+
+			\begin{equation}
+			JSD(P||Q) = \frac{1}{2}KLD(P||M) + \frac{1}{2}KLD(Q||M)
+			\end{equation}
+			where $\displaystyle M = \frac{1}{2}(P+Q)$.
+
+			A more generalized form is defined to be:
+
+			\begin{equation}
+			JSD_{\pi_1, \dots, \pi_n}(P_1, \dots, P_n) = \sum_{i=1}^{n}\frac{1}{\pi_i}KLD(P_i||M)
+			\end{equation}
+			where $\displaystyle M = \sum_{i=1}^{n}\frac{1}{\pi_i}P_i$ and $\displaystyle \sum_{i=1}^{n}\frac{1}{\pi_i} = 1$.
+
+			Jensen-Shannon divergence has some fine properties:
+			\begin{enumerate}
+				\item $JSD(P||Q) = JSD(Q||P), \forall P, Q\in S$.
+				\item $0 \le JSD_{\pi_1, \dots, \pi_n}(P_1, \dots, P_n) \le log_k(n)$. If a $k$ based algorithm is adopted.
+				\item To calculate $JSD(P||Q)$, it need not necessarily to be true that $Q(i)=0$ implies $P(i)=0$.
+			\end{enumerate}
+
+			\textbf{[If P, Q are continuous distribution?]}
 
 	\section{Algorithm Details}\label{sec:algorithm-details}
+		Diverse data sets in the real world show certain structures which may be resulted from hidden patterns or relationships among records in a collection of data.
+For example, the volume of vehicles in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
+Manipulation on those data(e.g.
+Fig~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm.
+		Although the population parameters(e.g. mean, variance, etc.) are unknown and usually impossible to obtain, it can be sampled and estimated according to the central limitation theorem.
+
 		\subsection{Technical Points}
@@
 		\subsection{Basic Algorithm}
+			Suppose data chunks in the given data set $S$ are groups of instances sampled from a population driven by a static distribution.
+And we are given in advance an evidence set $E$ which contains $n(n\ge2)$ collections of correct sample data.
+Then each data collection in $S$ can be checked by the following algorithm.
+
+			\begin{algorithm}[!ht]
+				\caption{Static Classification}
+				\label{alg:static}
+				\begin{algorithmic}[1]
+					\Require Evidence set $E = \{D_1, \dots, D_n\}$, new data chunk $D'$
+					\Ensure Whether $D'$ is anomaly
+					\For{$i \gets 1$ to $n$ do}
+						\State $P_i \gets$ the distribution of $D_i$
+					\EndFor
+					\State $M \gets \frac{1}{n}\sum_{i=1}^{n}P_i$\label{line:population-estimation}
+					\For{$i \gets 1$ to $n$ do}
+						\State $J_i \gets JSD(P_i||M)$
+					\EndFor
+					\State $N \gets$ normal distribution estimated from $J_1, \dots, J_n$
+					\State $P' \gets$ distribution of $D'$
+					\State $J' \gets JSD(P'||M)$
+					\State $p \gets$ probability density of $J'$ in $N$
+					\If{$p <$ threshold $T$}
+						\State \textbf{Return} True
+					\Else
+						\State \textbf{Return} False
+					\EndIf
+				\end{algorithmic}
+			\end{algorithm}
+
+			As shown in Algorithm~\ref{alg:static}, $n$ evidence collections are used to estimate the ground truth population distribution $M$.
+Then $n$ evidence divergences are calculated, composing a gaussian classifier to classify the new distribution sample.
+Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$.
+It is not suitable for classification.
+Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes larger.
+
+			Similar to the fact that sampling values around a certain parameter will yield a gaussian distribution, sampling divergences around a certain population distribution yields a gaussian distribution $N(\mu, \sigma)$ where $\mu$ is a value slightly larger than zero.
+$\mu$ can not be zero according to line~\ref{line:population-estimation}.
+$M$ takes into consideration all existing values in every distribution sample and averages corresponding probabilities.
+Thus $M$ may consist entries that does not exist in $P_i$ and probability in certain entries in $M$ may vary from that in $P_i$.
+For example, suppose $P_1(1)=0.5, P_1(2)=0.3, P_1(3)=0.2$; $P_2(1) = 0.3, P_2(2) = 0.4, P_2(3) = 0.3$; $P_3(1)=0.3, P_3(3)=0.5, P_3(4)=0.2$, then $M(1) = \frac{11}{3}, M(2)=\frac{7}{3}, M(3)=\frac{10}{3}, M(4)=\frac{2}{3}$.
+None of $P_1, P_2, P_3$ is the same with $M$.
+Although the distance cannot be negative values, normal distribution is the closest to the distribution of all JSD values.
+
+		\subsection{Histogram}
+			It is possible, in some specific circumstances, to assign a continuous function as the model of a collection of sampled data, which will get more accurate results.
+However, in the consideration of generality and computational cost, a discrete approximation of the distribution sample will be adopted.
+It means that every data collection will be counted into a histogram according to a certain order, yielding a discrete probability distribution.
+
+			When constructing histograms, step size is the most important parameter the algorithm should receive.
+If the size is too small then the resulting histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape.
+According to statistics theory, when dealing with a sample size of $k$, a step size of $l = c \sigma k^{-0.2}$ will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g.
+for normal distribution, $c=$).
+
+		\subsection{Threshold}
 

### 2017-09-05 Paper/DataAnomaly/paper.tex
Paper writing: Section 'Algorithm Detials'

@@
 
-		\subsection{Basic Algorithm}
+		\subsection{Divergence-Based Collective Anomaly Detection}
 			Suppose data chunks in the given data set $S$ are groups of instances sampled from a population driven by a static distribution.
@@
 			\begin{algorithm}[!ht]
-				\caption{Static Classification}
+				\caption{Basic Classification}
 				\label{alg:static}
 				\begin{algorithmic}[1]
-					\Require Evidence set $E = \{D_1, \dots, D_n\}$, new data chunk $D'$
-					\Ensure Whether $D'$ is anomaly
+					\Require Evidence set $E = \{D_1, \dots, D_n\}$; New data collection $D'$
+					\Ensure Whether $D'$ is anomalous
 					\For{$i \gets 1$ to $n$ do}
@@
 
-		\subsection{Histogram}
-			It is possible, in some specific circumstances, to assign a continuous function as the model of a collection of sampled data, which will get more accurate results.
-However, in the consideration of generality and computational cost, a discrete approximation of the distribution sample will be adopted.
-It means that every data collection will be counted into a histogram according to a certain order, yielding a discrete probability distribution.
+		\subsection{Distribution Histogram}\label{sec:alg-histogram}
+			Not all data collections can be assumed subject to known distribution models.
+Parameter approximation will probably lead to errors above our expectation.
+For example, the distribution of vehicle volume in the highway may not correspond to any of the prevalent distribution model.
+Few assumption of parameters can be made in advance on such data.
+For the sake of generality, non-parametric estimation should be applied.
 
-			When constructing histograms, step size is the most important parameter the algorithm should receive.
+			Surely, the kernel density estimation approaches will give a smooth, continuous distribution curve under on any sampled data.
+The computational cost will be much higher than applying a coarse histogram approximation.
+			Moreover, even if we applied a distribution model upon a collection of sampled data, yielding more accurate results, the computation of divergence will be much more complex on continuous functions than discrete distributions.
+
+			Histogram methods can not only be applied to non-parametric distributions, but also to miscellaneous data types.
+From a general point of view, as long as there exits a function mapping the input data instance into a subset of real numbers, this data collection can be counted into a histogram.
+For example, date, time and single characters.
+
+			In order to generate a accurate approximation, step size is the most important parameter the algorithm should determine.
 If the size is too small then the resulting histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape.
 According to statistics theory, when dealing with a sample size of $k$, a step size of $l = c \sigma k^{-0.2}$ will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g.
-for normal distribution, $c=$).
+for normal distribution, $c=1.05$).
 
-		\subsection{Threshold}
+		\subsection{Threshold}\label{sec:alg-threshold}
+			One important factor in the algorithm is the value of threshold.
+A higher threshold rejects more instances, improving the sensitivity of anomalous data while increasing the number of false alarms.
+A lower threshold provide higher true negative rates yet neglecting more possible threats.
 
-		\subsection{Dynamic Algorithm}
+			A naive but prevalent approach is to set a fixed value as threshold.
+This approach is easy to implement and may give satisfying results in specific cases.
+However, a fixed threshold requires analysis of the specific problem, manual observation and tuning of parameters, which involves lots of human labor.
+The rule of ``$3 \sigma$'' can be used to automatically determine a threshold.
+But in some cases that the anomalous data intersecting at the boundary with normal instances, the threshold may fail more often to discover those manipulated ones.
+
+			However, applying divergence as the distance metric among data collection distributions provides a fine property.
+That is, divergences of normal data collections assemble together, forming a quasi-normal distribution.
+And those of anomalous data collections lies in the right-hand-side interval on the real number axis.
+As a result of further observation, the divergence of anomalous data collections also assemble to be a quasi-normal distribution, since statistical distance has been restricted by a strict upper bound.
+
+			\textbf{[Better give a point drawing for each JSD value]}
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
+				\caption{Threshold Example}
+				\label{fig:example-threshold}
+			\end{figure}
+
+			As shown in Fig~\ref{fig:example-threshold}, the black curve($PDF_{normal}(x)$) displays the probability density function(PDF) fitting those JSDs calculated from normal data collections; the blue curve($PDF_{anomalous}(x)$) displays the PDF derived from anomalous data collections.
+Threshold is to minimize total error(False Negative and False Positive).
+
+			Suppose:
+
+			\begin{align}
+				PDF_{normal}(x) &\approx N(\mu_n, \sigma_n)\\
+				PDF_{anomalous}(x) &\approx N(\mu_a, \sigma_a)
+			\end{align}
+
+			Then the optimal threshold $T$ is:
+
+			\begin{equation}\label{equ:linear-weight}
+				\small
+				\begin{split}
+					T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{anomalous}(x)dx +
+					 \int_{T}^{log_k2}PDF_{normal}(x)dx\\
+					& \approx \mathop{\arg\min}_{T}
+					\int_{-\infty}^{T}
+					\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
+					+ \int_{T}^{+\infty}
+					\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\\
+					& = \frac{\mu_n\sigma_a + \mu_a\sigma_n}{\sigma_a + \sigma_n}
+				\end{split}
+			\end{equation}
+
+			According to equation(\ref{equ:linear-weight}), threshold value can be automatically determined.
+The optimal threshold will minimize total errors, yielding an optimal outcome.
+The only requirement for this technique is another evidence set containing data point derived from anomalous data collections.
+
+			However, this is not accurate enough, since equation(\ref{equ:linear-weight}) implicate an assumption that the chances are the same for a new data collection to be either anomalous or not.
+If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as:
+
+			\begin{equation}\label{equ:linear-balanced}
+				\small
+				\begin{split}
+					T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{anomalous}(x)dx +
+				(1-\alpha)\int_{T}^{log_k2}PDF_{normal}(x)dx\\
+					& \approx \mathop{\arg\min}_{T}
+					\alpha\int_{-\infty}^{T}
+					\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
+					+ (1-\alpha)\int_{T}^{+\infty}
+					\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx
+				\end{split}
+			\end{equation}
+
+			Where $\alpha$ is the anomaly probability.
+Equation(\ref{equ:linear-balanced}) is much more complicated than (\ref{equ:linear-weight}).
+It can be reduced to a quadratic equation.
+But may not have real roots in all cases.
+
+			From another point of view, equation (\ref{equ:linear-weight}) can be regarded as a weighted averaging between two mean value: $\mu_n$ and $\mu_a$.
+From this aspect, we can derive some similar approximations:
+
+			\begin{align}
+				T &= \frac{\mu_n \sqrt{\sigma_a} + \mu_a \sqrt{\sigma_n}}{\sqrt{\sigma_a} + \sqrt{\sigma_n}}
+				\label{equ:sqrt-weight}\\
+				T &= \frac{\mu_n \sigma_a \sqrt{-ln(1 - \alpha)}
+					+ \mu_a \sigma_n \sqrt{-ln\alpha}}
+				{\sigma_a \sqrt{-ln(1 - \alpha)} + \sigma_n \sqrt{-ln\alpha}}
+				\label{equ:sqrt-log-add-weight}\\
+				T &= \frac{\mu_n \sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|}
+					+ \mu_a \sqrt{|ln(\sigma_n \alpha)|}}
+				{\sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_n \alpha)|}}
+				\label{equ:sqrt-log-combined-weight}
+			\end{align}
+
+			Due to the restriction sample capacity, the replacement of JSD distributions by guassian distribution may lose too much accuracy.
+Compared with equation (\ref{equ:sqrt-weight}), (\ref{equ:sqrt-log-add-weight})and (\ref{equ:sqrt-log-combined-weight}), (\ref{equ:linear-balanced}) may not give a best result.
+
+		\subsection{Dynamic DCAD}
+			Another important factor that should be seriously considered is the assumption in Algorithm~\ref{alg:static}.
+In most cases, real world data is always in the process of evolution and fluctuation.
+Therefore, the algorithms should automatically adapt to the trend at any time.
+To meet the need, a sliding window technique has been applied to the basic algorithm frame work.
+Considering discussion in section~\ref{sec:alg-histogram} and~\ref{sec:alg-threshold}, a dynamic version is proposed as follow:
+
+			\begin{algorithm}[!ht]
+				\caption{Dynamic DAD}
+				\label{alg:dynamic}
+				\begin{algorithmic}[1]
+					\Require Normal evidence set $E_N = \{D_{N_1}, \dots, D_{N_n}\}$ by given order; Anomalous evidence set $E_A = \{D_{A_1}, \dots, D_{A_m}\}$ by given order; New data collection $D'$; Estimated anomalous probability $\alpha$
+					\Ensure Whether $D'$ is anomalous
+					\For{$i \gets 1$ to $n$}
+						\State $P_{N_i} \gets$ histogram of $D_{N_i}$
+					\EndFor
+					\For{$i \gets 1$ to $m$}
+						\State $P_{A_i} \gets$ histogram of $D_{A_i}$
+					\EndFor
+					\State $P' \gets$ histogram of $D'$
+					\State $M \gets \frac{1}{n}\sum_{i=1}^{n}P_{N_i}$
+					\For{$i \gets 1$ to $n$}
+						\State $J_{N_i} \gets JSD(P_{N_i}||M)$
+					\EndFor
+					\For{$i \gets 1$ to $m$}
+						\State $J_{A_i} \gets JSD(P_{A_i}||M)$
+					\EndFor
+					\State $J' = JSD(P'|||M)$
+					\State $(\mu_N, \sigma_N) \gets$ estimated from $\{J_{N_1}, \dots, J_{N_n}\}$
+					\State $(\mu_A, \sigma_A) \gets$ estimated from $\{J_{A_1}, \dots, J_{A_m}\}$
+					\State $T \gets$ proper threshold derived from $(\mu_N, \sigma_N)$, $(\mu_A, \sigma_A)$ and $\alpha$
+					\If{$J' < T$}
+						\State $E_N \gets E_N \backslash \{D_{N_0}\} \cup \{D'\}$\label{line:update-normal-evidence}
+						\State \textbf{Return} False
+					\Else
+						\State $E_A \gets E_A \backslash \{D_{A_0}\} \cup \{D'\}$\label{line:update-anomalous-evidence}
+						\State \textbf{Return} True
+					\EndIf
+				\end{algorithmic}
+			\end{algorithm}
+
+			Algorithm~\ref{alg:dynamic} uses $E_N$ and $E_A$ as two sliding windows, keeping up with latest trend of both normal and anomalous features.
+Thus, the two window sizes $n$ and $m$ cannot be too large.
+Otherwise the evolving features will be flattened and aligned to the older ones.
+For the sake of estimation accuracy, they cannot be too small either.
+The size should refer to ratio of both data updates and feature evolution.
+
+			Line~\ref{line:update-normal-evidence} and~\ref{line:update-anomalous-evidence} update the evidence sets, replacing the most outdated one, moving the sliding window forward one step ahead.
+Moreover, $\alpha$ can also be updated according to a history sequence of return values, if necessary.
 
@@
 		\subsection{Experiment Environment}
+			The algorithm was implemented and interpreted in Python 3.6. All experiments was tested on Ubuntu 17.04.
 

### 2017-09-07 Paper/DataAnomaly/paper.tex
Write paper, section 'Test'

@@
 
+			We adopted a data set containing Taobao online sellers' transaction records\footcite{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition.
+The data package contains seller features data set, user payments data set and user browsing behaviour data set.
+An example of the user payments data set is shown in Table~\ref{tab:user-payment-sample}.
+
+			\begin{table}[!ht]
+				\centering
+				\caption{User Payment Record Exmaple}
+				\label{tab:user-payment-sample}
+				\begin{tabular}{|c|c|c|}
+					\hline
+					User ID & Seller ID & Payment Time\\
+					\hline
+					10523185 & 1629 & 2015-11-11 17:00:00\\
+					\hline
+					2 & 2 & 2\\
+					\hline
+					3 & 3 & 3\\
+					\hline
+					\vdots & \vdots & \vdots\\
+					\hline
+				\end{tabular}
+			\end{table}
+
+			We randomly chose one seller(ID: 1629) and extracted transaction history of this seller, records ranging from Nov.
+11th 2015 to Oct.
+31st 2016.
+Entire transaction set was then divided into 325 collections, each containing records in one day.
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=0.75\linewidth]{fig/DailyTransactionVolume.png}
+				\caption{Daily Transaction Volumes}
+				\label{fig:daily-transaction-volume}
+			\end{figure}
+
+			\begin{figure}[ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/SaleDistributionSamples.png}
+				\caption{Randomly selected 3 days and draw histograms by hourly sale}
+				\label{fig:sale-distribution-sample}
+			\end{figure}
+
+			Fig.~\ref{fig:daily-transaction-volume} shows the daily transaction volume of the seller.
+It sees a trend of daily sale which is slightly moving as the time goes.
+And the daily selling distributions, as is shown in Fig.~\ref{fig:sale-distribution-sample}, display a roughly similar shape.
+
+			Click farmed data was generated according to patterns described in online reports\textbf{[ref here]}.
+The most popular way of click farming is to call online a group of people, assign each of them an amount of transaction.
+And those ``employees'' individually buy certain products via different buyer accounts.
+Therefore, a significant feature of this approach is that the cheating transactions usually assemble together in a short period of time.
+It is called ``Centralized Farming''.
+Some other ``employers'' are more clever.
+They usually arrange a time table for each employee to create new transactions.
+Thus the transaction distribution may not vary too much with and without click farming.
+This is called ``Equalized Farming''.
+
+			To emulate ``Centralized Click Farming'', we randomly inserted some gaussian-distributed transactions in a chosen collection, where the total number of new records is the same of the original volume.
+To emulate a extremely clever ``Equalized Click Farmer'', we simply doubled each record in the chosen collection to make the new distribution exactly the same as the original one, which is harder for the online platform to discover.
+
+			To play the role of purchasing platform, we surveillance two levels of transaction distribution.
+The first level is simply drawing a histogram on time spans.
+The second level is to draw a histogram on the sub-volumes of each time span.
+For example, shown in Fig.~\ref{fig:histogram-example}, the first level histogram can be drawn by counting the number of hourly sales.
+The frequencies of each bucket in 1st level histogram is: $F=$\{0, 0, 0, 0, 0, 0, 0, 1, 13, 30, 37, 68, 60, 66, 72, 94, 75, 113, 127, 182, 165, 61, 0, 0\}.
+Then, counting $F$ with a step size 20 gives the 2nd level histogram.
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/HistogramExample.png}
+				\caption{Example of 1st and 2nd Level Histogram}
+				\label{fig:histogram-example}
+			\end{figure}
+
+			In order to test the performance of Algorithm~\ref{alg:dynamic}, every single collection was fed into the algorithm by the time order.
+Each collection input has a probability of $\alpha$ to be anomalous, namely, click farmed.
+The algorithm checks each collection with 1st or 2nd level histogram and give an answer of true and false.
+Then a F1 score was computed as the result of the experiment.
+
+		\subsection{Experiment on Raw Data}
+			We first tested Algorithm~\ref{alg:dynamic} on raw data set in order to see how and why the algorithm works.
+Due to desensitization process, time stamps in raw data set only tell which hour the transaction was committed.
+Thus, the histogram was drawn by counting hourly volume of each collection.
+For $\alpha = 0.2$, we select first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections.
+The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}, \textit{false positive rate} and \textit{accuracy} were recorded.
+
+			\begin{table}[!ht]
+				\centering
+				\caption{Classification Results on Raw Data}
+				\label{tab:result-raw-1st}
+				\begin{tabular}{|c|c|c|c|c|c|c|}
+					\hline
+					& \multicolumn{3}{c|}{Centralized} & \multicolumn{3}{c|}{Equalized}\\
+					\hline
+					& TPR & FAR & ACC & TPR & FAR & ACC\\
+					\hline
+					1st Level & 100 & 4.05 & 96.72 & 26.64 & 28.03 & 62.49\\
+					\hline
+					2nd Level & 88.01 & 7.68 & 91.41 & 83.89 & 15.78 & 84.07\\
+					\hline
+				\end{tabular}
+			\end{table}
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/Raw1stLevelHist.png}
+				\caption{1st Level Histogram of Raw Data}
+				\label{fig:raw-hist-1st}
+			\end{figure}
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/Raw2ndLevelHist}
+				\caption{2nd Level Histogram of Raw Data}
+				\label{fig:raw-hist-2nd}
+			\end{figure}
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/RawOverview1st.png}
+				\caption{JSD of 1st Level Histograms}
+				\label{fig:raw-overview-1st}
+			\end{figure}
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/RawOverview2nd.png}
+				\caption{JSD of 2nd Level Histogram}
+				\label{fig:raw-overview-2nd}
+			\end{figure}
+
+			When classifying toward 1st level histograms, centralized click farming behaviours can be easily discovered.
+As displayed in the left two columns in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click farmed ones abruptly violates the original shape.
+However, as a clever click farmer, equalized click farming did not in the least distorted the distribution.
+Most of them escaped the security check under the perfect disguise.
+			But when it comes to 2nd level histogram, the ``clever disguise'' does not work any longer.
+It can be clearly seen in Fig.~\ref{fig:raw-hist-2nd} that both types of click farming shows an obvious difference from the normal ones, while the normal ones still share a similar distribution.
+			From the overview in Fig.~\ref{fig:raw-overview-1st} and~\ref{fig:raw-overview-2nd}, the difference between normal and anomalous collections can be observed more intuitively.
+
 		\subsection{Experiment on Synthetic Data}
-			\textbf{Test basic properties of statistical distance and algorithm}
+			As is put in the former section, every single record in the transaction set only gives a time stamp aligned at hours.
+Part of the information was erased with the absence of minutes and seconds.
+In the following experiments, Every time stamp was assigned a random value for minutes and seconds.
+Therefore, the synthetic data set should be closer to the real world data.
 
-		\subsection{Experiment on Real World Data}
-			\textbf{Test performance of algorithm}
+		\subsection{Threshold Optimization}
+			\textbf{give results of the comparison of different threshold equations}
 

### 2017-09-07 RealWorld/ROC.py

@@ -1,0 +1,12 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+fpr_cen_1 = (0.09916, 0.01734, 0.00784, 0.00532, 0.00402, 0.002651, 0.00405, 0.00392, 0.00405, 0.00267)
+tpr_cen_1 = (1, 1, 1, 0.9412, 0.7566, 0.5912, 0.4019, 0.3027, 0.3261, 0.0882)
+
+figure = plt.figure(figsize=(9, 9), dpi=100)
+plt.plot(fpr_cen_1, tpr_cen_1, label='1st Level Centralized')
+plt.legend()
+
+figure.savefig("ROC.png")

### 2017-09-07 RealWorld/SamplePDF.py

@@ -3,50 +3,92 @@ import Divergence
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
+import matplotlib.axis as ax
 
-day = 5
+days = (5, 113, 287)
+lim_x = 40
+lim_y = 0.3
 
-reader = csv.reader(open("Correct/%d.csv" % day, 'r'))
-reader_cen = csv.reader(open("Centralized/%d.csv" % day, 'r'))
-reader_equ = csv.reader(open("Equalized/%d.csv" % day, 'r'))
+figure = plt.figure(figsize=(9, 9), dpi=100)
+for ii in range(3):
+    day = days[ii]
+    reader = csv.reader(open("Correct/%d.csv" % day, 'r'))
+    reader_cen = csv.reader(open("Centralized/%d.csv" % day, 'r'))
+    reader_equ = csv.reader(open("Equalized/%d.csv" % day, 'r'))
 
-data = list(int(row[2]) for row in reader)
-data_cen = list(int(row[2]) for row in reader_cen)
-data_equ = list(int(row[2]) for row in reader_equ)
+    freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), step=1)
+    freq_cen, dropped = Divergence.histogram(list(int(row[2]) for row in reader_cen), step=1)
+    freq_equ, dropped = Divergence.histogram(list(int(row[2]) for row in reader_equ), step=1)
 
-step = 1
-print("Step: %f" % step)
+    data = freq.values()
+    data_cen = freq_cen.values()
+    data_equ = freq_equ.values()
+    step = 21.48
 
-hist = Divergence.histogram(data, step)
-hist_cen = Divergence.histogram(data_cen, step)
-hist_equ = Divergence.histogram(data_equ, step)
+    # data = list(int(row[2]) for row in reader)
+    # data_cen = list(int(row[2]) for row in reader_cen)
+    # data_equ = list(int(row[2]) for row in reader_equ)
+    #
+    # step = 1
+    #
+    dropped, hist = Divergence.histogram(data, step)
+    droped, hist_cen = Divergence.histogram(data_cen, step)
+    dropped, hist_equ = Divergence.histogram(data_equ, step)
 
-figure = plt.figure(figsize=(1800/300, 600/300), dpi=300)
-plt.subplot(132)
-x = []
[…]

### 2017-09-07 RealWorld/ShowDistribution.py

@@ -1,0 +1,47 @@
+import csv
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import random
+
+# figure = plt.figure(figsize=(9, 3), dpi=100)
+# plt_cnt = 0
+# for day in (5, 113, 287):
+#     reader = csv.reader(open("Correct/%d.csv" % day, 'r'))
+#     freq = {}
+#     for i in range(24):
+#         freq[i] = 0
+#     for row in reader:
+#         freq[int(row[2])] += 1
+#
+#     plt_cnt += 1
+#     plt.subplot(1, 3, plt_cnt)
+#     plt.bar(list(range(24)), freq.values(), label="day %d" % day)
+#     plt.legend(loc="upper left")
+#
+# plt.savefig("SaleDistributions.png")
+
+reader = csv.reader(open("Correct/5.csv", 'r'))
+freq1 = {}
+for i in range(24):
+    freq1[i] = 0
+for row in reader:
+    freq1[int(row[2])] += 1
+
+freq2 = {}
+for i in range(10):
+    freq2[i] = 0
+for i in freq1.keys():
+    bsk = int(freq1[i] / 20)
+    freq2[bsk] += 1
+
+figure = plt.figure(figsize=(8, 4), dpi=100)
+plt.subplot(1, 2, 1)
+plt.bar(list(range(24)), freq1.values(), label="1st Level")
+plt.legend()
+
+plt.subplot(1, 2, 2)
+plt.bar(list(range(10)), freq2.values(), label="2st Level")
+plt.legend()
+
+plt.savefig("HistogramExample.png")

### 2017-09-07 RealWorld/ShowOverview.py

@@ -1,0 +1,20 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+jsd = [0.008748994684134268, 0.015240537320908422, 0.0015240513988232995, 0.0031051148679070014, 0.0033735233256568784, 0.002421185881730095, 0.0036073414352532987, 0.003849237851658265, 0.010703146709061117, 0.001975003412196996, 0.0032388009910297787, 0.0033171020847916253, 0.0022375245606253186, 0.008835788288123213, 0.002251804174186225, 0.012975544998831311, 0.0029251502647842263, 0.003520611946407365, 0.0027328098662684546, 0.004669021702278735, 0.004389173710159215, 0.0052263420164222665, 0.00925964078586519, 0.0019185349128100077, 0.003406742393244508, 0.0026002231282451225, 0.003045507093689207, 0.0067725270507850675, 0.004615923237517347, 0.009494840581165086, 0.0046539826922372025, 0.0029901092897060464, 0.0015919472396219618, 0.002341132882329799, 0.008668640534694039, 0.002719877015996795, 0.005893563638018638, 0.0023407478450889006, 0.0010666309765906018, 0.003181317882297267, 0.0008688960500944033, 0.0018644504769192028, 0.002971659222288935, 0.007900296035128162, 0.000539324172271058, 0.002070575204687525, 0.002406317190937706, 0.0025697463695358285, 0.007139095707732642, 0.004222044168417817, 0.007282998170726579, 0.011216860395627186, 0.008315359831170488, 0.004959953982169934, 0.0076942042005910555, 0.002873583360384834, 0.01007298973427609, 0.18211119159482825, 0.0531437787736118, 0.020538666252942844, 0.008202611396243096, 0.013486987254674272, 0.007025516692222527, 0.007968103980006257, 0.00565440793585731, 0.007850874676782024, 0.006883947056933503, 0.004533591600688811, 0.0074019467571685696, 0.007666759799457192, 0.0020304089373184312, 0.008168592036003026, 0.006297009040415333, 0.006545417318380353, 0.004279373035834545, 0.005463314780357911, 0.009132897705699949, 0.0012589590299461146, 0.003077497457671197, 0.007169884482741821, 0.006497335566025242, 0.005035924853373506, 0.005213834137590346, 0.010163536422927676, 0.0034621070971155832, 0.004928462153098465, 0.003895404550470798, 0.0029072073566535858, 0.003232659843
[…]

### 2017-09-07 RealWorld/Test1stLevel.py

@@ -1,0 +1,160 @@
+import csv
+import Divergence
+import statistics
+import random
+import scipy.stats as stats
+import sys
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import math
+
+input_dir = "Correct"
+input_dir_err = "Centralized"
+# queue = []
+
+error_rate = 1
+
+print("\nTest %s Cheating..." % input_dir_err)
+# Collecting History
+evidence = []
+for i in range(30):
+    reader = csv.reader(open("%s/%d.csv" % (input_dir, i), 'r'))
+    evidence += [list(int(row[2]) for row in reader)]
+
+evidence_err = []
+for i in range(30 - max(10, int(30 * error_rate)), 30):
+    reader = csv.reader(open("%s/%d.csv" % (input_dir_err, i), 'r'))
+    evidence_err += [list(int(row[2]) for row in reader)]
+
+# Run algorithm with cheating data
+jsd_history = []
+jsd_record = {"evidence":[], "evidence_err":[], "correct":-1, "error":-1}
+correct_cnt = 0
+correct_recognized = 0
+error_cnt = 0
+error_recognized = 0
+for i in range(30, 325):
+    # Calculate Step
+    step = 1
+
+    # Calculate evidence distributions and estimated population distribution
+    dists = []
+    for data in evidence:
+        dropped, tmp_dist = Divergence.histogram(data, step)
+        dists += [tmp_dist]
+    dist_pop = Divergence.blendDistributions(dists)
+    jsd_evidence = []
+    for tmp_dist in dists:
+        jsd_evidence += [Divergence.jsd(dist_pop, tmp_dist)]
+    jsd_mean = statistics.mean(jsd_evidence)
+    jsd_sigma = statistics.stdev(jsd_evidence)
+
+    jsd_evidence_err = []
+    for data in evidence_err:
+        dropped, tmp_dist = Divergence.histogram(data, step)
+        jsd_evidence_err += [Divergence.jsd(dist_pop, tmp_dist)]
+    jsd_mean_err = statistics.mean(jsd_evidence_err)
+    jsd_sigma_err = statistics.stdev(jsd_evidence_err)
+
+    w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
+    w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
+    threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
[…]

### 2017-09-07 RealWorld/Test2ndLevel.py

@@ -1,0 +1,172 @@
+import csv
+import Divergence
+import statistics
+import random
+import scipy.stats as stats
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import math
+import sys
+
+
+input_dir = "Correct"
+input_dir_err = "Equalized"
+queue = []
+
+error_rate = 1
+#sigma_coefficient = 3  # Don't think about this now
+time_span = 1
+
+print("\nTest %s Cheating..." % input_dir_err)
+# Collecting History
+evidence = []
+for i in range(30):
+    reader = csv.reader(open("%s/%d.csv" % (input_dir, i), 'r'))
+    tmp_freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), time_span)
+    evidence += [list(tmp_freq.values())]
+
+evidence_err = []
+for i in range(30 - max(10, int(30 * error_rate)), 30):
+    reader = csv.reader(open("%s/%d.csv" % (input_dir_err, i), 'r'))
+    tmp_freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), time_span)
+    evidence_err += [list(tmp_freq.values())]
+
+# Run algorithm with centralized cheating data
+jsd_history = []
+jsd_record = {}
+correct_cnt = 0
+correct_recognized = 0
+error_cnt = 0
+error_recognized = 0
+for i in range(30, 325):
+    # Calculate Step
+    tmp = []
+    for data in evidence:
+        tmp += data
+    sigma = statistics.stdev(tmp)
+    step = 0.5 * sigma * (statistics.mean(list(len(data) for data in evidence)) ** -0.2)
+
+    # Calculate evidence distributions and estimated population distribution
+    dists = []
+    for data in evidence:
+        dropped, tmp_dist = Divergence.histogram(data, step)
+        dists += [tmp_dist]
+    dist_pop = Divergence.blendDistributions(dists)
+    jsd_evidence = []
+    for tmp_dist in dists:
+        jsd_evidence += [Divergence.jsd(dist_pop, tmp_dist)]
+    jsd_mean = statistics.mean(jsd_evidence)
+    jsd_sigma = statistics.stdev(jsd_evidence)
+
+    jsd_evidence_err = []
+    for data in evidence_err:
+        dropped, tmp_dist = Divergence.histogram(data, step)
[…]

### 2017-09-07 Paper/DataAnomaly/paper.tex
Paper writing: section 'Experiment'

@@
 		\subsection{Experiment on Raw Data}
-			We first tested Algorithm~\ref{alg:dynamic} on raw data set in order to see how and why the algorithm works.
+			We first tested Algorithm~\ref{alg:dynamic} on raw data set in order to see whether and why the algorithm works.
 Due to desensitization process, time stamps in raw data set only tell which hour the transaction was committed.
@@
 For $\alpha = 0.2$, we select first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections.
+Equation(\ref{equ:sqrt-log-add-weight}) was employed as the threshold calculator.
 The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}, \textit{false positive rate} and \textit{accuracy} were recorded.
@@
 
+			\textbf{How did we get the result?}
+
+			\begin{table}[!ht]
+				\centering
+				\caption{1st Level}
+				\label{tab:syn-result-1st}
+				\begin{tabular}{|c|c|c|c|c|c|c|}
+					\hline
+					& \multicolumn{3}{c|}{Centralized} & \multicolumn{3}{c|}{Equalized}\\
+					\hline
+					$\alpha$ & TPR(\%) & FPR(\%) & ACC(\%) & TPR(\%) & FPR(\%) & ACC(\%) \\ 
+					\hline
+					0.1 & 86.10 & 1.14 & 97.40 & 5.75 & 12.28 & 79.66 \\ 
+					\hline
+					0.2 & 96.43 & 9.83 & 91.30 & 26.97 & 26.47 & 64.29 \\ 
+					\hline
+					0.3 & 97.95 & 16.49 & 87.68 & 37.46 & 39.46 & 53.67 \\ 
+					\hline
+					0.4 & 99.18 & 31.94 & 81.30 & 57.23 & 48.32 & 53.79 \\ 
+					\hline
+					0.5 & 99.33 & 23.40 & 88.25 & 67.67 & 58.23 & 54.46 \\ 
+					\hline
+					0.6 & 99.62 & 25.70 & 89.83 & 67.03 & 73.78 & 51.64 \\ 
+					\hline
+					0.7 & 100.00 & 32.51 & 90.51 & 69.69 & 76.28 & 56.16 \\ 
+					\hline
+					0.8 & 99.72 & 26.97 & 94.35 & 75.56 & 69.44 & 67.00 \\ 
+					\hline
+					0.9 & 99.63 & 15.73 & 98.19 & 76.59 & 75.18 & 70.73\\
+					\hline
+				\end{tabular} 
+			\end{table}
+
+			\begin{table}[!ht]
+				\centering
+				\caption{2nd Level}
+				\label{tab:syn-result-2nd}
+				\begin{tabular}{|c|c|c|c|c|c|c|}
+					\hline
+					& \multicolumn{3}{c|}{Centralized} & \multicolumn{3}{c|}{Equalized}\\
+					\hline
+					$\alpha$ & TPR(\%) & FPR(\%) & ACC(\%) & TPR(\%) & FPR(\%) & ACC(\%) \\ 
+					\hline
+					0.1 & 75.60 & 3.90 & 93.74 & 97.84 & 1.64 & 98..31 \\ 
+					\hline
+					0.2 & 91.93 & 18.43 & 93.73 & 99.42 & 7.39 & 94.01 \\ 
+					\hline
+					0.3 & 95.01 & 23.70 & 81.69 & 100.00 & 23.93 & 83.05 \\ 
+					\hline
+					0.4 & 98.09 & 28.66 & 82.49 & 100.00 & 24.59 & 84.75 \\ 
+					\hline
+					0.5 & 98.33 & 36.54 & 80.00 & 100.00 & 23.76 & 88.36 \\ 
+					\hline
+					0.6 & 98.35 & 40.69 & 83.41 & 100.00 & 35.94 & 84.63 \\ 
+					\hline
+					0.7 & 98.54 & 37.97 & 87.80 & 100.00 & 31.27 & 90.84 \\ 
+					\hline
+					0.8 & 98.47 & 40.38 & 91.19 & 100.00 & 33.04 & 92.66 \\ 
+					\hline
+					0.9 & 98.51 & 47.56 & 94.58 & 100.00 & 28.44 & 97.40\\
+					\hline
+				\end{tabular} 
+			\end{table}
+
+			\textbf{Comment on the result. Explain the trend:(1)$\alpha \uparrow, TPR \uparrow $; (2)$\alpha \uparrow, FPR \uparrow$; (3)$\alpha \uparrow, ACC \downarrow then \uparrow $}
+
 		\subsection{Threshold Optimization}

### 2017-09-07 Synthetic/TestFirstOrder.py

@@ -33,7 +33,7 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
 input_dir = "Correct"
 input_dir_err = "Equalized"
 
-error_rate = 0.1
+error_rate = 0.9
 
 print("\nTest %s Cheating..." % input_dir_err)
 # Collecting History
@@ -81,10 +81,9 @@ for i in range(30, 325):
     jsd_mean_err = statistics.mean(jsd_evidence_err)
     jsd_sigma_err = statistics.stdev(jsd_evidence_err)
 
-    #w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
-    #w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
-    #threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
-    threshold = linearBalancedThreshold(jsd_mean, jsd_sigma, jsd_mean_err, jsd_sigma_err, error_rate)
+    w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
+    w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
+    threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'
@@ -161,21 +160,21 @@ fp = correct_cnt - correct_recognized
 tn = correct_recognized
 fn = error_cnt - error_recognized
 
-pre = tp / (tp + fp)
-rec = tp / (tp + fn)
-f1 = 2 * pre * rec / (pre + rec)
-print("tp=%d, fp=%d, tn=%d, fn=%d, f1=%f\n" % (tp, fp, tn, fn, f1))
+# pre = tp / (tp + fp)
+# rec = tp / (tp + fn)
+# f1 = 2 * pre * rec / (pre + rec)
+print("tp=%d, fp=%d, tn=%d, fn=%d, f1=%f\n" % (tp, fp, tn, fn, 0))
 
 # Show JSD History
-figure = plt.figure(figsize=(6000/300, 3000/300), dpi=300)
-plt.axis("off")
-for i in range(len(jsd_history)):
-    record = jsd_history[i]
-    plt.plot([i] * len(record["evidence"]), record["evidence"], 'r.', ms=0.5)
[…]

### 2017-09-07 Synthetic/TestSecondOrder.py

@@ -29,9 +29,9 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Equalized"
+input_dir_err = "Centralized"
 
-error_rate = 0.1
+error_rate = 0.9
 #sigma_coefficient = 3  # Don't think about this now
 time_span = 300
 
@@ -83,10 +83,9 @@ for i in range(30, 325):
     jsd_mean_err = statistics.mean(jsd_evidence_err)
     jsd_sigma_err = statistics.stdev(jsd_evidence_err)
 
-    #w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
-    #w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
-    #threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
-    threshold = linearBalancedThreshold(jsd_mean, jsd_sigma, jsd_mean_err, jsd_sigma_err, error_rate)
+    w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
+    w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
+    threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'
@@ -165,21 +164,21 @@ fp = correct_cnt - correct_recognized
 tn = correct_recognized
 fn = error_cnt - error_recognized
 
-pre = tp / (tp + fp)
-rec = tp / (tp + fn)
-f1 = 2 * pre * rec / (pre + rec)
-print("tp=%d, fp=%d, tn=%d, fn=%d, f1=%f\n" % (tp, fp, tn, fn, f1))
+# pre = tp / (tp + fp)
+# rec = tp / (tp + fn)
+# f1 = 2 * pre * rec / (pre + rec)
+print("tp=%d, fp=%d, tn=%d, fn=%d, f1=%f\n" % (tp, fp, tn, fn, 0))
 
 # Show JSD History
-figure = plt.figure(figsize=(6000 / 300, 3000 / 300), dpi=300)
-plt.axis("off")
-for i in range(len(jsd_history)):
-    record = jsd_history[i]
[…]

### 2017-09-11 Paper/DataAnomaly/paper.tex
Paper Writing: Performing more experiments

@@
 If the size is too small then the resulting histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape.
-According to statistics theory, when dealing with a sample size of $k$, a step size of $l = c \sigma k^{-0.2}$ will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g.
-for normal distribution, $c=1.05$).
+According to statistics theory, when dealing with a sample size of $k$, a step size of
+
+			\begin{equation}\label{equ:step-size}
+				l = c \sigma k^{-0.2}
+			\end{equation}
+
+			will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g. for normal distribution, $c=1.05$).
 
@@
 In the following experiments, Every time stamp was assigned a random value for minutes and seconds.
-Therefore, the synthetic data set should be closer to the real world data.
-
-			\textbf{How did we get the result?}
+Therefore, the synthetic data set should be closer to the real world case.
+Moreover, the step size in the histograms can now be calculated more precisely.
+In the 1st level histogram, the constant $c$ in equation(\ref{equ:step-size}) was set to 0.5 since the PDF of daily distribution was approximately a linear function.
+And in the 2nd level histogram, sub-volumes of every 300 seconds were counted, producing more data points in the 2nd level data collections.
+Then, constant $c$ in equation(\ref{equ:step-size}) was also set to 0.5 given that the 2nd level histogram was also approximately a linear function.
+			We tested algorithm performance for $\alpha \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$, with $E_N$ and $E_A$ the same configuration as before.
+Results were shown in Table~\ref{tab:syn-result-1st} and~\ref{tab:syn-result-2nd}.
 
@@
 
-			\textbf{Comment on the result. Explain the trend:(1)$\alpha \uparrow, TPR \uparrow $; (2)$\alpha \uparrow, FPR \uparrow$; (3)$\alpha \uparrow, ACC \downarrow then \uparrow $}
+			The result shows that the algorithm can efficiently distinguish the normal and anomalous data collections.
+No matter how much proportion of data is anomalous, the algorithm always gives a high accuracy.
+That is because the adaptive threshold was designed to minimize the number of total errors, which was irrelevant to TPR or FPR.
+When $\alpha$ was increasing, there were less data collections added into $E_N$.
+Thus the update of $E_N$ became slower and FPR went higher.
+On the contrary, TPR became higher as $\alpha$ increased.
+Moreover, since $|E_N| > |E_A|$, it needs more collection instances for $|E_N|$ then that for $|E_A|$ to keep up to the trend.
+Therefore, it was faster of FPR to increase than TPR to increase.
+As a result of that, there were more false alarms emerged and ACC went lower, as $\alpha$ increased from 0.1 to 0.5.
+After that, however, although FPR was still increasing, total number of normal instances decreased dramatically and those false alarms contributed less to total errors.
+Therefore, ACC rose up again.
+
+			\begin{figure}[!ht]
+				\centering
+				\includegraphics[width=\linewidth]{fig/ROC-alpha}
+				\caption{ROC Curve of 1st and 2nd Level Classifier}
+				\label{fig:roc-alpha}
+			\end{figure}
+
+			Fig.~\ref{fig:roc-alpha} shows the ROC curve of the gaussian classifier dealing with centralized click farming with 1st level histogram and equalized click farming with 2nd level histogram.\textbf{[Comment: This shows that the classifier is efficient]}
+
+			\begin{figure}[!ht]
+				\centering
+				This is the figure
+				\caption{ROC Curve of Different Magnitude of Click Farming}
+				\label{fig:roc-magnitude}
+			\end{figure}
+
+			\textbf{[Next, show a figure of ROC curve for different click farm magnitude.
+Explore how sensitive the classifier is for the click farming problem.
+This requires lots of experiment data.
+Not finished yet]}
 
 		\subsection{Threshold Optimization}
-			\textbf{give results of the comparison of different threshold equations}
+			\textbf{give results of the comparison of different threshold equations, in table~\ref{tab:threshold-comparison}}
+			\begin{table*}[!ht]
+				\centering
+				\caption{Compare of Different Threshold Calculator}
+				\label{tab:threshold-comparison}
+				\begin{tabular}{|c|c|c|}
+					\hline
+					Equation & Synthetic & Gaussian \\ 
+					\hline
+					$T = \frac{\sigma_B \mu_A + \sigma_A \mu_B}{\sigma_B + \sigma_A}$& 1.0588 & 0.5810 \\ 
+					\hline
+					$T = \frac{\sqrt{\sigma_B} \mu_A + \sqrt{\sigma_A} \mu_B}{\sqrt{\sigma_B} + \sqrt{\sigma_A}}$& 2.1861 & 0.5718 \\ 
+					\hline
+					$T = \frac{(ln\sigma_B)\mu_A + (ln\sigma_A)\mu_B}{ln\sigma_B + ln\sigma_A}$& 2.2390 & 0.3860 \\ 
+					\hline
+					$T = \frac{(\sqrt{|ln\sigma_B|})\mu_A + (\sqrt{|ln\sigma_A|})\mu_B}{\sqrt{|ln\sigma_B|} + \sqrt{|ln\sigma_A|}}$& 2.2082 & 0.5515 \\ 
+					\hline
+					$T = \frac{(ln\sqrt{\sigma_B})\mu_A + (ln\sqrt{\sigma_A})\mu_B}{ln\sqrt{\sigma_B} + ln\sqrt{\sigma_A}}$& 2.1211 & 0.3811 \\ 
+					\hline
+					$T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$& 0.7688 & 0.3515 \\ 
+					\hline
+					$T = \frac{(\sigma_B \sqrt{1 - \alpha}) \mu_A + (\sigma_A \sqrt{\alpha}) \mu_B}{\sigma_B \sqrt{1 - \alpha} + \sigma_A \sqrt{\alpha}}$& 0.8158 & 0.4510 \\ 
+					\hline
+					$
+					T = \frac{\big[\sigma_B ln(1 - \alpha)\big] \mu_A
+						+ \big[\sigma_A ln\alpha\big] \mu_B}
+					{\sigma_B ln(1 - \alpha) + \sigma_A ln\alpha}
+					$& 1.5227 & 0.5523 \\ 
+					\hline
+					$
+					T = \frac{\mu_A \sigma_B \sqrt{-ln(1 - \alpha)}
+						+ \mu_B \sigma_A \sqrt{-ln\alpha}}
+					{\sigma_B \sqrt{-ln(1 - \alpha)} + \sigma_A \sqrt{-ln\alpha}}
+					$& 2.6013 & 0.5791 \\ 
+					\hline
+					$
+					T = \frac{\mu_A \sigma_B ln\sqrt{1 - \alpha}
+						+ \mu_B \sigma_A ln\sqrt{\alpha}}
+					{\sigma_B ln\sqrt{1 - \alpha} + \sigma_A ln\sqrt{\alpha}}
+					$& 1.4155 & 0.5578 \\ 
+					\hline
+					$
+					T = \frac{\mu_A \sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|}
+						+ \mu_B \sqrt{|ln(\sigma_A \alpha)|}}
+					{\sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_A \alpha)|}}
+					$& 2.2730 & 0.5600 \\ 
+					\hline
+					$
+					T = \frac{\mu_A ln\sqrt{\sigma_B (1 - \alpha)}
+						+ \mu_B ln\sqrt{\sigma_A \alpha}}
+					{ln\sqrt{\sigma_B (1 - \alpha)} + ln\sqrt{\sigma_A \alpha}}
+					$& 2.0753 & 0.2808 \\ 
+					\hline
+					$T = \mathop{\arg\min}_{\mu_A \le T \le \mu_B}\ \alpha \cdot \int_{-\infty}^{T}P_B(x)dx + (1 - \alpha) \cdot \int_{T}^{+\infty}P_A(x)dx$ & 1.9300 & 0.6072\\
+					\hline
+				\end{tabular} 
+			\end{table*}
+
+			\textbf{[Comment: Which equation is the best in each case? Why?]}
+
+		\subsection{Comparison with other collective classification algorithms}
+			\textbf{It would be better to have this comparison, but it requires much more experiments and the data set may not be very suitable.}
 

### 2017-09-11 Synthetic/GenerateCentralized.py

@@ -7,8 +7,10 @@ import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
+ratio = 0.8
+
 input_dir = "Correct"
-output_dir = "Centralized(2.0)"
+output_dir = "Centralized(%.1f)" % (1 + ratio)
 d = os.path.abspath(output_dir)
 if not os.path.exists(d):
     os.makedirs(d)
@@ -22,7 +24,7 @@ for file in os.listdir(input_dir):
                 cnt += 1
                 ofile.write(line)
             #num_new = numpy.random.randint(int(cnt * 1.5), int(cnt * 2.0))
-            num_new = cnt
+            num_new = int(cnt * ratio)
             center = numpy.random.randint(10, 21)
             for item in numpy.random.normal(center * 3600, 1.5 * 3600, num_new):
                 if (item >= (7 * 3600)) and (item < 24 * 3600):

### 2017-09-11 Synthetic/PlotROC.py

@@ -1,0 +1,53 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+alphas = [0.1, 0.3, 0.5, 0.7, 0.9]
+TPRs1 = [
+    [1, 0.99, 0.828, 0.556, 0.263],
+    [1, 0.989, 0.827, 0.424, 0.28],
+    [1, .993, .771, .579, .281],
+    [1, .991, .717, .473, .276],
+    [1, .97, .686, .5, .318]
+]
+FPRs1 = [
+    [0.165, 0.018, 0.006, 0.008, 0.004],
+    [0.17, 0.015, 0.007, 0.006, 0.003],
+    [.16, .015, .014, .005, .007],
+    [.104, .004, .01, .007, 0],
+    [.127, .023, .004, .013, 0]
+]
+
+TPRs2 = [
+    [1, 1, .867, .655, .346],
+    [1, 1, .833, .357, .085],
+    [1, 1, .770, .188, .048],
+    [1, 1, .832, .090, .028],
+    [1, 1, 1, .215, .015]
+]
+FPRs2 = [
+    [.376, .064, .008, 0, 0],
+    [.386, .076, .001, 0, 0],
+    [.357, .108, .014, 0, 0],
+    [.352, .146, .040, .047, .012],
+    [.346, .111, .059, .080, 0]
+]
+
+figure = plt.figure(figsize=(10, 5), dpi=100)
+plt.subplot(1, 2, 1)
+for i in range(5):
+    plt.plot(FPRs1[i], TPRs1[i], label="alpha=%.1f" % alphas[i])
+plt.title("1st Level Classifier")
+plt.legend()
+plt.xlabel("FPR")
+plt.ylabel("TPR")
+
+plt.subplot(1, 2, 2)
+for i in range(5):
+    plt.plot(FPRs2[i], TPRs2[i], label="alpha=%.1f" % alphas[i])
+plt.title("2nd Level Classifier")
+plt.legend()
+plt.xlabel("FPR")
+plt.ylabel("TPR")
+
+figure.savefig("ROC-alpha.png")

### 2017-09-11 Synthetic/TestFirstOrder.py

@@ -31,9 +31,9 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Equalized"
+input_dir_err = "Centralized(1.2)"
 
-error_rate = 0.9
+error_rate = 0.5
 
 print("\nTest %s Cheating..." % input_dir_err)
 # Collecting History
@@ -81,9 +81,10 @@ for i in range(30, 325):
     jsd_mean_err = statistics.mean(jsd_evidence_err)
     jsd_sigma_err = statistics.stdev(jsd_evidence_err)
 
-    w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
-    w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
-    threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
+    # w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
+    # w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
+    # threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
+    threshold = 0.01
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'

### 2017-09-11 Synthetic/TestSecondOrder.py

@@ -29,7 +29,7 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Centralized"
+input_dir_err = "Equalized"
 
 error_rate = 0.9
 #sigma_coefficient = 3  # Don't think about this now
@@ -83,9 +83,10 @@ for i in range(30, 325):
     jsd_mean_err = statistics.mean(jsd_evidence_err)
     jsd_sigma_err = statistics.stdev(jsd_evidence_err)
 
-    w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
-    w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
-    threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
+    # w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
+    # w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
+    # threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
+    threshold = 0.05
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'
@@ -135,6 +136,7 @@ for i in range(30, 325):
         new_data = list(freq.values())
         dropped, dist = Divergence.histogram(new_data, step)
         tmp_jsd = Divergence.jsd(dist_pop, dist)
+        print("Jsd: %g" % tmp_jsd)
 
         if tmp_jsd <= threshold:
             # Slide window forward

### 2017-09-16 Paper/DataAnomaly/paper.tex
Revision

@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+\usepackage{color}
 
@@
 	\section{Introduction}
-		Big data industry has been blooming within this decade, reshaping the form of life and work across the globe.
-According to~\autocite{letouze2014official}, 1.2ZB data had been produced from 2012 to 2014.
-And the amount doubles every two years.
-Currently, there are totally 2.7ZB data in the digital universe~\autocite{bigDataStatistics}.
+		Major improvements in data acquisition, transmission and storage are driving increased data availability and affordability.
+Currently, there are totally 2.7ZB data in the digital universe~\autocite{bigDataStatistics} and the growing speed is doubling every two years.
+		%In Facebook, there is about 100 terabytes of data uploaded every day~\cite{bigDataFacebook}.
 		Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.
 
-		However, it will be harder in the future to harness the exploding volumes of data since problems have already appeared in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
+		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
 		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\autocite{saha2014data}.
+		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years.
+And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}.
+System configuration problems, as a matter of fact, also draw scratches in the messy picture.
+They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.
 
 		Those data anomalies may arise due to both internal and external reasons with respect to a certain system.
-From one hand, components inside the system may generate problematic source data.
+On one hand, components inside the system may generate problematic source data.
 For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\autocite{rassam2014adaptive}.
@@
 Also, human operators act as a heavily vulnerable part to bugs and mistakes.
-Some even deliberately modify system configurations for malicious compromises~\autocite{schuster2015vc3}.
+Some insiders even deliberately modify system configurations for malicious compromises~\autocite{schuster2015vc3}.
 A study~\autocite{humanError} found that 65\% of organizations state that human errors are the main  cause of data problems.
@@
 		On the other hand, data manipulation~\autocite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability.
+\textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
 Taken Apache Hadoop as an example.
@@
 		According to our observation, typical data manipulations on numerical data will lead to the drift of its distribution.
-For example, a Taobao online seller's transaction records can be ``click farmed'' to increase the volume of sales.
+For example, a Taobao online seller's transaction records(see section~\ref{sec:exp-methodology}) can be ``click farmed'' to increase the volume of sales.
 Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day.
@@
 The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.
-		These anomalies inside data pipelines will severely affect mining and learning algorithms and further change the final decision given by the entire system.
+		These anomalies inside data \textbf{sets/collections} will severely affect mining and learning algorithms and further change the final decision given by the entire system.
 
-		In order to address issues resulted from data manipulation and pipeline errors, we propose a novel mechanism to detect and locate corrupted data within a data pipeline via statistical distance.
-As far as we know, this algorithm is the first attempt against data anomaly via statistical distance.
-Evaluations are performed on synthetic and real-world data sets, demonstrating the correctness and effectiveness of the mechanism.
+		In order to address issues caused by data manipulation, we propose a technique to detect corrupted data collections via statistical distance.
+As far as we know, this algorithm is the first attempt against collective data anomaly via statistical distance.
+Evaluations are performed on real-world and synthetic data sets, demonstrating the correctness and effectiveness of the technique.
 
-		The rest of the paper is organised as follow: Section~\ref{sec:related-work} introduces preliminaries and recent works on data anomaly detection and statistical distance.
-Algorithm details are proposed in section~\ref{sec:algorithm-details}.
+		The rest of the paper is organised as follow: Section~\ref{sec:related-work} states related works on data anomaly detection and describes a real world problem.
+Section~\ref{sec:preliminaries} introduces statistical distance.
+Details of the technique are proposed in section~\ref{sec:algorithm-details}.
 Section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm.
@@
 
-	\section{Preliminaries and Related Work}\label{sec:related-work}
+	\section{Related Work}\label{sec:related-work}
 		\subsection{Data Anomaly Detection}
 			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.
-According to a systematic classification in~\cite{chandola2009anomaly}, anomaly detection algorithms deal with input data in the form of points(or records), sequences, graphs and spatial relationships, where point data is the simplest and well studied, others are attracting more attention in new studies.
+According to a comprehensive study in~\cite{chandola2009anomaly}, anomaly detection algorithms deal with input data in the form of points(or records), sequences, graphs and spatial relationships, where point data is the simplest and well studied, others are attracting more attention in new studies.
 
@@
 
-		\subsection{Click Farming Detection}
+		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
+			Since the establishment of Taobao in 2003, the online business platform has been growing from the rookies in the market to the No.1 service provider in B2B and B2C markets, possessing a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}.
+Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products.
+Under the super-pressure from massive competition, most of the sellers choose to use some cheating techniques to raise reputation and product sale volumes, then improve rankings in search lists.
 
-		\subsection{Statistical Divergence}
-			Statistical divergence, also called statistical distance, is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
-Suppose $S$ is a space of probability distributions, then a divergence is a function from $S$ to non-negative real numbers:
+			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of buyer accounts to create fake transaction records and give high remarks on products.
+Professional click farmers are usually well organized groups or companies containing thousands of people.
+Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions.
+Some companies even develop professional applications that can be deployed on common PCs to improve productivity\textbf{[A Citation in Chinese]}.
+
+			A research performed in China showed that 81.9\% of the people investigated had heard of the behaviour of click farming, 51.2\% of them had seen people around them click farmed and 18.9\% of them had experience of click farming themselves\textbf{[Chinese Citation?]}.
+American researchers reported in 2015 that over 11000 sellers were detected to have click farmed records and only 2.2\% of 4000 investigaed sellers had been penalized because of the cheating attempts~\cite{netease2015research}.
+
+			Current detection techniques for click farming mainly focus on user behaviours, such as browsing frequencies and periods, most common purchasing time, favourite products, remarks and whether they communicate with sellers~\cite{simpleDetection}.
+Those techniques require the platform to keep lots of records and user features.
+However, the detection can be easily bypassed by trained workers and some well programmed applications.
+
+			Although it is hard to classify users as honest and malicious, we can still find clues from the sellers' aspect.
+For normal sellers, their customers are usually similar since choices of products are seldom changed.
+Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable.
+No matter how much alike between the employed users or robots with honest users, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
+Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
+
+	\section{Preliminaries}\label{sec:preliminaries}
+		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
+This mathematical tool can be adopted in our solution to map distributions into one dimensional points, turning collective anomaly detection problem into point anomaly detection problem.
+Then a concrete point anomaly detection classifier can be used to find out the cheaters.
+
+		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
+Let $S$ be a space of probability distributions, then a divergence is a function from $S$ to non-negative real numbers:
 		\begin{equation}
@@
 		\subsubsection{Kullback-Leibler Divergence}
-			$P,Q$ are discrete probability distributions, $Q(i)=0$ implies $P(i)=0$ for $\forall i$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:
+		Let $P,Q$ be discrete probability distributions, $Q(i)=0$ implies $P(i)=0$ for $\forall i$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:
 
@@
 
+		For $P,Q$ being continuous distributions:
+
+		\begin{equation}
+			KLD(P||Q) = \int_{-\infty}^{+\infty} P(x)log\frac{P(x)}{Q(x)}dx
+		\end{equation}
+
 		\subsubsection{Jensen-Shannon Divergence}
-			$P,Q$ are discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:
+		Let $P,Q$ be discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:
 
@@
 
-			\textbf{[If P, Q are continuous distribution?]}
-
-	\section{Algorithm Details}\label{sec:algorithm-details}
-		Diverse data sets in the real world show certain structures which may be resulted from hidden patterns or relationships among records in a collection of data.
-For example, the volume of vehicles in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
+	\section{Statistical Detection}\label{sec:algorithm-details}
+		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records in a collection of data.
+For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
 Manipulation on those data(e.g.
 Fig~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm.
-		Although the population parameters(e.g. mean, variance, etc.) are unknown and usually impossible to obtain, it can be sampled and estimated according to the central limitation theorem.
+Main idea of the solution is simple.
+But there are several detailed difficulties to be solved in the design and implementation of the technique:
 
-		\subsection{Technical Points}
-			\textbf{[Can be divided and settled inside later two subsections]}
 		\begin{enumerate}
-				\item Which classifier should be chosen?
-				\item How to determine the classifier threshold?\textbf{[fixed value, 3$\sigma$]}
-				\item How to locate the compromised component?
-				\item How to deal with slightly drifting distribution?
-				\item .[to be continued \dots]
+			\item Are the corresponding one-dimensional points distinguishable after mapping form normal and anomalous distributions? And which classifier is efficient towards those points?
+			\item Is there a general approach that can effectively depict different distributions in various circumstances?
+			\item What classifier specific metric should be adopted to filter out anomalies? Can it be further optimized?
+			\item Online shops are often in the process of expanding or dwindling.
+Thus the sales distribution will slightly change as time goes on.
+How to make the technique adapt to these drifting distributions?
 		\end{enumerate}
@@
 		\subsection{Divergence-Based Collective Anomaly Detection}
-			Suppose data chunks in the given data set $S$ are groups of instances sampled from a population driven by a static distribution.
-And we are given in advance an evidence set $E$ which contains $n(n\ge2)$ collections of correct sample data.
-Then each data collection in $S$ can be checked by the following algorithm.
+			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions.
+In a set of data collections, we can only draw a complete graph that each node denotes one certain collection and each edge refers to the divergence of two data collections.
+From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies.
+This may work if anomalous ones do not compose a large proportion of all points.
+However the procedure will be too complicated to work out with large amounts of instances.
+
+			Otherwise we need a frame of reference and yielding absolute distances rather than the relative ones.
+Therefore, we should keep an evidence set $E$ which consists of several already known correct distributions.
+Then the real distribution can be estimated by averaging all distributions in $E$.
+This process is similar to the parameter estimation within a certain sample set.
+Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside or outside $E$, yielding absolute distances.
+
+			Fig.~\ref{fig:raw-hist-1st} and~\ref{fig:raw-hist-2nd} in section~\ref{sec:exp-raw} show the result of the above process.
+Red dots refer to the distances calculated from normal transaction data collections, blue and green ones are from click farmed collections.
+Clearly, distances of normal data collections assembles together around a small value while anomalous ones are distributed around a larger distance value.
+Intuitively, a simple gaussian classifier can be suitable here to discover anomalous data points.
+The basic framework of the algorithm is shown as follows:
 
@@
 				\begin{algorithmic}[1]
-					\Require Evidence set $E = \{D_1, \dots, D_n\}$; New data collection $D'$
+					\Require Evidence set $E = \{D_1, \dots, D_n\}(n\ge2)$; New data collection $D'$
 					\Ensure Whether $D'$ is anomalous
@@
 
-			As shown in Algorithm~\ref{alg:static}, $n$ evidence collections are used to estimate the ground truth population distribution $M$.
-Then $n$ evidence divergences are calculated, composing a gaussian classifier to classify the new distribution sample.
+			Let $S$ be set of the daily transaction collections, if $E$ is already given, we can run the algorithm with $E$ and $\forall D \in S$ and discover the anomalies.
 Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$.
-It is not suitable for classification.
-Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes larger.
+It is not viable for classification.
+Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes very large.
 
-			Similar to the fact that sampling values around a certain parameter will yield a gaussian distribution, sampling divergences around a certain population distribution yields a gaussian distribution $N(\mu, \sigma)$ where $\mu$ is a value slightly larger than zero.
-$\mu$ can not be zero according to line~\ref{line:population-estimation}.
+			According to the property of statistical divergence, we can infer that the true distribution of JSDs calculated form normal data collections are close to but not exactly a gaussian distribution $N(\mu, \sigma)$ since for each point, there are both definite upper and lower bounds instead of infinities.
+Therefore, $\mu$ should be slightly larger than zero.
+The reason why $\mu$ can not be exactly zero is hidden in line~\ref{line:population-estimation}.
 $M$ takes into consideration all existing values in every distribution sample and averages corresponding probabilities.
-Thus $M$ may consist entries that does not exist in $P_i$ and probability in certain entries in $M$ may vary from that in $P_i$.
-For example, suppose $P_1(1)=0.5, P_1(2)=0.3, P_1(3)=0.2$; $P_2(1) = 0.3, P_2(2) = 0.4, P_2(3) = 0.3$; $P_3(1)=0.3, P_3(3)=0.5, P_3(4)=0.2$, then $M(1) = \frac{11}{3}, M(2)=\frac{7}{3}, M(3)=\frac{10}{3}, M(4)=\frac{2}{3}$.
+Thus for a large $|S|$, $M$ may highly probably contains entries that does not exist in $P_i$ and certain probability entries in $M$ may vary from that in $P_i$.
+For a concrete example, suppose $P_1(1)=0.5, P_1(2)=0.3, P_1(3)=0.2$; $P_2(1) = 0.3, P_2(2) = 0.4, P_2(3) = 0.3$; $P_3(1)=0.3, P_3(3)=0.5, P_3(4)=0.2$, then $M(1) = \frac{11}{3}, M(2)=\frac{7}{3}, M(3)=\frac{10}{3}, M(4)=\frac{2}{3}$.
 None of $P_1, P_2, P_3$ is the same with $M$.
-Although the distance cannot be negative values, normal distribution is the closest to the distribution of all JSD values.
 
 		\subsection{Distribution Histogram}\label{sec:alg-histogram}
-			Not all data collections can be assumed subject to known distribution models.
-Parameter approximation will probably lead to errors above our expectation.
+			Not all data collections can be assumed subject to known distributions.
+Parameter approximation will probably lead to errors far beyond our expectation.
 For example, the distribution of vehicle volume in the highway may not correspond to any of the prevalent distribution model.
@@
 			As shown in Fig~\ref{fig:example-threshold}, the black curve($PDF_{normal}(x)$) displays the probability density function(PDF) fitting those JSDs calculated from normal data collections; the blue curve($PDF_{anomalous}(x)$) displays the PDF derived from anomalous data collections.
-Threshold is to minimize total error(False Negative and False Positive).
+Threshold is chosen to minimize total errors(False Negative and False Positive).
 
@@
 		\subsection{Dynamic DCAD}
-			Another important factor that should be seriously considered is the assumption in Algorithm~\ref{alg:static}.
+			In Algorithm~\ref{alg:static}, there is a hidden assumption that it regards every data collection to be sampled from a static population.
+That is to say the seller will never change his or her products and customer volume always remain the same.
 In most cases, real world data is always in the process of evolution and fluctuation.
+Online shops are often in the process of expanding or dwindling.
+Thus the sales distribution will slightly change as time goes on.
 Therefore, the algorithms should automatically adapt to the trend at any time.
@@
 	\section{Evaluation}\label{sec:evaluation}
-		\subsection{Experiment Environment}
-			The algorithm was implemented and interpreted in Python 3.6. All experiments was tested on Ubuntu 17.04.
+		The algorithm was implemented and interpreted in Python 3.6. All experiments was tested on Ubuntu 17.04. In the following experiments, we would like to figure out:
 
-		\subsection{Methodology}
-			\textbf{Raise and answer some research questions. Present test background and methods.}
+		\begin{enumerate}
+			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:algorithm-details} applicable and accurate in real world data sets.
+			\item How to emulate different types of click farming?
+			\item Is the technique efficient against click farming? And How sensitive will the classifier be confronting different magnitude of click farming?
+			\item What is the performance of different adaptive thresholds?
+		\end{enumerate}
 
+		\subsection{Methodology}\label{sec:exp-methodology}
 			We adopted a data set containing Taobao online sellers' transaction records\footcite{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition.
@@
 
-		\subsection{Experiment on Raw Data}
+		\subsection{Experiment on Raw Data}\label{sec:exp-raw}
 			We first tested Algorithm~\ref{alg:dynamic} on raw data set in order to see whether and why the algorithm works.
@@
 				\centering
-				\includegraphics[width=\linewidth]{fig/ROC-alpha}
+				\includegraphics[width=\linewidth]{fig/ROC-Alpha.png}
 				\caption{ROC Curve of 1st and 2nd Level Classifier}
@@
 
-			Fig.~\ref{fig:roc-alpha} shows the ROC curve of the gaussian classifier dealing with centralized click farming with 1st level histogram and equalized click farming with 2nd level histogram.\textbf{[Comment: This shows that the classifier is efficient]}
+			Fig.~\ref{fig:roc-alpha} shows the ROC curve($\nu=1.0$) of the gaussian classifier dealing with centralized click farming with 1st level histograms and equalized manipulation with 2nd level histograms.
+The curves are pretty close to the upper left corner of the diagram and size under the curves are very large.
+For different $\alpha$s, the classifier can efficiently distinguish normal and anomalous data collections.
 
@@
 				\centering
-				This is the figure
+				\includegraphics[width=\linewidth]{fig/ROC-Nu.png}
 				\caption{ROC Curve of Different Magnitude of Click Farming}
@@
 
-			\textbf{[Next, show a figure of ROC curve for different click farm magnitude.
-Explore how sensitive the classifier is for the click farming problem.
-This requires lots of experiment data.
-Not finished yet]}
+			In Fig.~\ref{fig:roc-magnitude}, we tested the classifier with different magnitude of centralised click farming.
+In former experiments, the manipulation of centralized click farming always creates as many new transaction records as the original ones.
+Let $\nu$ denote the magnitude coefficient, then $|D_{anomalous}| = (1 + \nu) |D_{normal}|$.
+If $\nu $ is smaller, then it will be harder for the classifier to identify anomalous data collections since the anomalous distribution will be closer to normal ones.
+It can be concluded from the figure that the 1st level classifier can be efficient even when $\nu = 0.3$.
+However the 2nd level classifier is less sensitive when $\nu = 0.5$.
+That is because the 1st level histogram provides more probability entries than 2nd level histograms.
+Data collections are compressed from 1st to 2nd level.
+But for real world click farming behaviours(usually, $\nu > 1$) both classifiers can be efficient enough.
 
 		\subsection{Threshold Optimization}
-			\textbf{give results of the comparison of different threshold equations, in table~\ref{tab:threshold-comparison}}
+			Section~\ref{sec:alg-threshold} mentions only four equations for calculating adaptive thresholds.
+Table~\ref{tab:threshold-comparison} gives the comparison of more equations in similar forms.
+We tested those calculators on synthetic data set with $\alpha = 0.1, \nu = 1$.
+Testing each level of classifier and each type of anomalies, we got 4 F1 scores and added them up.
+Equation 9 gives best performance.
+Then those equations were tested on large amount of gaussian distributed data instances.
+90K and 10K data points were sampled from 500 pairs of random gaussian distributions which represent normal and anomalous distributions respectively, yielding 500 F1 scores for each equation.
+We compared the average score and discovered that equation 13 gives the best result.
+
+			Equation 13 gives best classification result for two gaussian distributions but does not outperform others in real world data.
+Part of the reasons are mentioned in section~\ref{sec:alg-threshold}.
+Another reason is that the size of evidence sets are too restricted, that the gaussian distribution may not be well approximated.
+
 			\begin{table*}[!ht]
 				\centering
-				\caption{Compare of Different Threshold Calculator}
+				\caption{F1 Scores of Different Threshold Calculators}
 				\label{tab:threshold-comparison}
-				\begin{tabular}{|c|c|c|}
+				\begin{tabular}{|c|c|c|c|}
 					\hline
-					Equation & Synthetic & Gaussian \\ 
+					& Equation & Synthetic & Gaussian \\ 
 					\hline
-					$T = \frac{\sigma_B \mu_A + \sigma_A \mu_B}{\sigma_B + \sigma_A}$& 1.0588 & 0.5810 \\ 
+					1 & $\displaystyle T = \frac{\sigma_B \mu_A + \sigma_A \mu_B}{\sigma_B + \sigma_A}$& 1.0588 & 0.5810 \\ 
 					\hline
-					$T = \frac{\sqrt{\sigma_B} \mu_A + \sqrt{\sigma_A} \mu_B}{\sqrt{\sigma_B} + \sqrt{\sigma_A}}$& 2.1861 & 0.5718 \\ 
+					2 & $\displaystyle T = \frac{\sqrt{\sigma_B} \mu_A + \sqrt{\sigma_A} \mu_B}{\sqrt{\sigma_B} + \sqrt{\sigma_A}}$& 2.1861 & 0.5718 \\ 
 					\hline
-					$T = \frac{(ln\sigma_B)\mu_A + (ln\sigma_A)\mu_B}{ln\sigma_B + ln\sigma_A}$& 2.2390 & 0.3860 \\ 
+					3 & $\displaystyle T = \frac{(ln\sigma_B)\mu_A + (ln\sigma_A)\mu_B}{ln\sigma_B + ln\sigma_A}$& 2.2390 & 0.3860 \\ 
 					\hline
-					$T = \frac{(\sqrt{|ln\sigma_B|})\mu_A + (\sqrt{|ln\sigma_A|})\mu_B}{\sqrt{|ln\sigma_B|} + \sqrt{|ln\sigma_A|}}$& 2.2082 & 0.5515 \\ 
+					4 & $\displaystyle T = \frac{(\sqrt{|ln\sigma_B|})\mu_A + (\sqrt{|ln\sigma_A|})\mu_B}{\sqrt{|ln\sigma_B|} + \sqrt{|ln\sigma_A|}}$& 2.2082 & 0.5515 \\ 
 					\hline
-					$T = \frac{(ln\sqrt{\sigma_B})\mu_A + (ln\sqrt{\sigma_A})\mu_B}{ln\sqrt{\sigma_B} + ln\sqrt{\sigma_A}}$& 2.1211 & 0.3811 \\ 
+					5 & $\displaystyle T = \frac{(ln\sqrt{\sigma_B})\mu_A + (ln\sqrt{\sigma_A})\mu_B}{ln\sqrt{\sigma_B} + ln\sqrt{\sigma_A}}$& 2.1211 & 0.3811 \\ 
 					\hline
-					$T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$& 0.7688 & 0.3515 \\ 
 					\hline
-					$T = \frac{(\sigma_B \sqrt{1 - \alpha}) \mu_A + (\sigma_A \sqrt{\alpha}) \mu_B}{\sigma_B \sqrt{1 - \alpha} + \sigma_A \sqrt{\alpha}}$& 0.8158 & 0.4510 \\ 
+					6 & $\displaystyle T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$& 0.7688 & 0.3515 \\ 
 					\hline
-					$
+					7 & $\displaystyle T = \frac{(\sigma_B \sqrt{1 - \alpha}) \mu_A + (\sigma_A \sqrt{\alpha}) \mu_B}{\sigma_B \sqrt{1 - \alpha} + \sigma_A \sqrt{\alpha}}$& 0.8158 & 0.4510 \\ 
+					\hline
+					8 & $\displaystyle 
 					T = \frac{\big[\sigma_B ln(1 - \alpha)\big] \mu_A
@@
 					\hline
-					$
+					9 & $\displaystyle 
 					T = \frac{\mu_A \sigma_B \sqrt{-ln(1 - \alpha)}
@@
 					{\sigma_B \sqrt{-ln(1 - \alpha)} + \sigma_A \sqrt{-ln\alpha}}
-					$& 2.6013 & 0.5791 \\ 
+					$& \color{blue}\textbf{2.6013} & 0.5791 \\ 
 					\hline
-					$
+					10 & $\displaystyle 
 					T = \frac{\mu_A \sigma_B ln\sqrt{1 - \alpha}
@@
 					\hline
-					$
+					11 & $\displaystyle 
 					T = \frac{\mu_A \sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|}
@@
 					\hline
-					$
+					12 & $\displaystyle 
 					T = \frac{\mu_A ln\sqrt{\sigma_B (1 - \alpha)}
@@
 					\hline
-					$T = \mathop{\arg\min}_{\mu_A \le T \le \mu_B}\ \alpha \cdot \int_{-\infty}^{T}P_B(x)dx + (1 - \alpha) \cdot \int_{T}^{+\infty}P_A(x)dx$ & 1.9300 & 0.6072\\
+					\hline
+					13 & $\displaystyle T = \mathop{\arg\min}_{\mu_A \le T \le \mu_B}\ \alpha \cdot \int_{-\infty}^{T}P_B(x)dx + (1 - \alpha) \cdot \int_{T}^{+\infty}P_A(x)dx$ & 1.9300 & \color{blue}\textbf{0.6072}\\
 					\hline
@@
 
-			\textbf{[Comment: Which equation is the best in each case? Why?]}
-
 		\subsection{Comparison with other collective classification algorithms}
@@
 
-	\section{Conclusion}\label{sec:conclusion}
+	\section{Conclusion \& Future Work}\label{sec:conclusion}
+		This paper proposed an dynamic collective anomaly detection algorithm with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
+Different from existing algorithms detecting collective anomalies, our approach employs statistical distance as the similarity metric, mapping data collections to a restricted one dimensional space.
+We explained several technical points involved in the design of the algorithm and performed a thorough experiment to test its efficiency.
+It showed that the algorithm can efficiently discover anomalies within the data sequences and the classifier is sensitive enough toward real world data manipulations.
+
+		However, the modelling of the JSD distributions is not precise enough, resulting in several threshold equations unexplained.
+The efficiency of different adaptive thresholds should be tested on different real world circumstances to get a more complete view of their performances.
+Moreover, a comparison with other collective detection algorithm should be executed in order to get an performance overview of similar algorithms.
 

### 2017-09-16 RealWorld/ShowOverview.py

@@ -1,6 +1,10 @@
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
+import statistics
+import Divergence
+import math
+
 
 jsd = [0.008748994684134268, 0.015240537320908422, 0.0015240513988232995, 0.0031051148679070014, 0.0033735233256568784, 0.002421185881730095, 0.0036073414352532987, 0.003849237851658265, 0.010703146709061117, 0.001975003412196996, 0.0032388009910297787, 0.0033171020847916253, 0.0022375245606253186, 0.008835788288123213, 0.002251804174186225, 0.012975544998831311, 0.0029251502647842263, 0.003520611946407365, 0.0027328098662684546, 0.004669021702278735, 0.004389173710159215, 0.0052263420164222665, 0.00925964078586519, 0.0019185349128100077, 0.003406742393244508, 0.0026002231282451225, 0.003045507093689207, 0.0067725270507850675, 0.004615923237517347, 0.009494840581165086, 0.0046539826922372025, 0.0029901092897060464, 0.0015919472396219618, 0.002341132882329799, 0.008668640534694039, 0.002719877015996795, 0.005893563638018638, 0.0023407478450889006, 0.0010666309765906018, 0.003181317882297267, 0.0008688960500944033, 0.0018644504769192028, 0.002971659222288935, 0.007900296035128162, 0.000539324172271058, 0.002070575204687525, 0.002406317190937706, 0.0025697463695358285, 0.007139095707732642, 0.004222044168417817, 0.007282998170726579, 0.011216860395627186, 0.008315359831170488, 0.004959953982169934, 0.0076942042005910555, 0.002873583360384834, 0.01007298973427609, 0.18211119159482825, 0.0531437787736118, 0.020538666252942844, 0.008202611396243096, 0.013486987254674272, 0.007025516692222527, 0.007968103980006257, 0.00565440793585731, 0.007850874676782024, 0.006883947056933503, 0.004533591600688811, 0.0074019467571685696, 0.007666759799457192, 0.0020304089373184312, 0.008168592036003026, 0.006297009040415333, 0.006545417318380353, 0.004279373035834545, 0.005463314780357911, 0.009132897705699949, 0.0012589590299461146, 0.003077497457671197, 0.007169884482741821, 0.006497335566025242, 0.005035924853373506, 0.005213834137590346, 0.010163536422927676, 0.0034621070971155832, 0.004928462153098465, 0.00389540
[…]

### 2017-09-16 Synthetic/GenerateCentralized.py

@@ -7,7 +7,7 @@ import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
-ratio = 0.8
+ratio = 0.5
 
 input_dir = "Correct"
 output_dir = "Centralized(%.1f)" % (1 + ratio)

### 2017-09-16 Synthetic/PlotROC.py

@@ -2,41 +2,72 @@ import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
-alphas = [0.1, 0.3, 0.5, 0.7, 0.9]
+# alphas = [0.1, 0.3, 0.5, 0.7, 0.9]
+# TPRs1 = [
+#     [1, 0.99, 0.828, 0.556, 0.263],
+#     [1, 0.989, 0.827, 0.424, 0.28],
+#     [1, .993, .771, .579, .281],
+#     [1, .991, .717, .473, .276],
+#     [1, .97, .686, .5, .318]
+# ]
+# FPRs1 = [
+#     [0.165, 0.018, 0.006, 0.008, 0.004],
+#     [0.17, 0.015, 0.007, 0.006, 0.003],
+#     [.16, .015, .014, .005, .007],
+#     [.104, .004, .01, .007, 0],
+#     [.127, .023, .004, .013, 0]
+# ]
+#
+# TPRs2 = [
+#     [1, 1, .867, .655, .346],
+#     [1, 1, .833, .357, .085],
+#     [1, 1, .770, .188, .048],
+#     [1, 1, .832, .090, .028],
+#     [1, 1, 1, .215, .015]
+# ]
+# FPRs2 = [
+#     [.376, .064, .008, 0, 0],
+#     [.386, .076, .001, 0, 0],
+#     [.357, .108, .014, 0, 0],
+#     [.352, .146, .040, .047, .012],
+#     [.346, .111, .059, .080, 0]
+# ]
+
+news = [0.1, 0.2, 0.3, 0.4, 0.5]
 TPRs1 = [
-    [1, 0.99, 0.828, 0.556, 0.263],
-    [1, 0.989, 0.827, 0.424, 0.28],
-    [1, .993, .771, .579, .281],
-    [1, .991, .717, .473, .276],
-    [1, .97, .686, .5, .318]
+    [1, .92279, .80455, .62685, .45796, .24602, 0],
+    [1, .93594, .82058, .69506, .5223, .43642, 0],
+    [1, .93685, .84652, .70603, .62435, .47604, 0],
+    [1, .93213, .90753, .75155, .64573, .54155, 0],
+    [1, .95324, .83864, .81978, .70387, .64501, 0]
 ]
 FPRs1 = [
-    [0.165, 0.018, 0.006, 0.008, 0.004],
-    [0.17, 0.015, 0.007, 0.006, 0.003],
-    [.16, .015, .014, .005, .007],
[…]

### 2017-09-16 Synthetic/TestFirstOrder.py

@@ -31,7 +31,7 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Centralized(1.2)"
+input_dir_err = "Centralized(1.5)"
 
 error_rate = 0.5
 
@@ -84,7 +84,7 @@ for i in range(30, 325):
     # w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
     # w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
     # threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
-    threshold = 0.01
+    threshold = 0.018
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'

### 2017-09-16 Synthetic/TestSecondOrder.py

@@ -29,9 +29,9 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Equalized"
+input_dir_err = "Centralized(1.5)"
 
-error_rate = 0.9
+error_rate = 0.5
 #sigma_coefficient = 3  # Don't think about this now
 time_span = 300
 
@@ -86,7 +86,7 @@ for i in range(30, 325):
     # w = jsd_sigma_err * math.sqrt(-math.log(1 - error_rate))
     # w_err = jsd_sigma * math.sqrt(-math.log(error_rate))
     # threshold = (jsd_mean * w + jsd_mean_err * w_err) / (w + w_err)
-    threshold = 0.05
+    threshold = 0.1
     #print("Test File: %d.csv(%d/325) Threshold jsd: %g(PD: %g)"
     #      % (i, i, threshold, stats.norm.pdf(threshold, jsd_mean, jsd_sigma)))
     ch = '-'

### 2017-09-17 Paper/DataAnomaly/paper.tex
Write Abstract

@@
 	\begin{abstract}
-		[abstract]
+		Hackers can infiltrate networks via any attack vector, find their way into databases and applications.
+Not only can they steal chunks of data and hold them for ransom, but also alter key information contained in those systems, setting up traps hard to discover and causing damages unlikely to recover.
+Although the influence of data altering is not significant in single data record, the change can be observed and detect in a collective scale.
+		In this paper, we present a dynamic collective anomaly detection technique based on statistical distance.
+The technique extracts distribution similarities among data collections, reducing collective anomalies into point anomalies.
+It dynamically calculate metrics which is adaptive to the slightly evolving features.
+This technique provides a basic solution where several components can be replaced by other scenario specific ones, further improving the performance of detection.
+		To illustrate details of the technique and explore its efficiency, we applied the algorithm into a real world problem of click farming detection against malicious online sellers.
+The evaluation shows that the technique maps normal and anomalous data collections into two distinct clusters, yielding efficient classifiers.
+And those classifiers are sensitive enough to a much smaller magnitude of manipulation compared with real world malicious behaviours.
 	\end{abstract}

### 2017-09-28 Paper/DataAnomaly/paper.tex
Using template for paper

--- 2017-09-16 Paper/DataAnomaly/paper.tex
@@
 \usepackage{color}
-
-\title{Locating Data Flow Anomaly With Statistical Distance}
-\author{Ruoyu Wang}
-\date{2017.05.04}
+\title{Dynamic Anomaly Detection for Collective Data Via Statistical Distance}
+%
+\author{%
+	% author names are typeset in 11pt, which is the default size in the author block
+	{Ruoyu Wang{\small $~^{\#1}$}, Daniel Sun{\small $~^{*2}$}, Guoqiang Li{\small $~^{\#3}$} }%
+	% add some space between author names and affils
+	\vspace{1.6mm}\\
+	\fontsize{10}{10}\selectfont\itshape
+	% 20080211 CAUSAL PRODUCTIONS
+	% separate superscript on following line from affiliation using narrow space
+	$^{\#}$\,School of Software Engineering, Shanghai Jiao Tong University\\
+	No.800 Dongchuan Rd. Shanghai, 200240, China\\
+	\fontsize{9}{9}\selectfont\ttfamily\upshape
+	%
+	% 20080211 CAUSAL PRODUCTIONS
+	% in the following email addresses, separate the superscript from the email address 
+	% using a narrow space \,
+	% the reason is that Acrobat Reader has an option to auto-detect urls and email
+	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
+	% in the email address and corrupts it.
+	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
+	$^{1}$\,solftwarewry@sjtu.edu.cn\\
+	$^{3}$\,li.g@sjtu.edu.cn%
+	% add some space between email and affil
+	\vspace{1.2mm}\\
+	\fontsize{10}{10}\selectfont\rmfamily\itshape
+	% 20080211 CAUSAL PRODUCTIONS
+	% separated superscript on following line from affiliation using narrow space \,
+	$^{*}$\,Data61, Commonwealth Scientific and Industrial Research Organization, Australia\\
+	\fontsize{9}{9}\selectfont\ttfamily\upshape
+	% 20080211 CAUSAL PRODUCTIONS
+	% removed ~ from pre-superscript since it does not seem to serve any purpose
+	$^{2}$\,daniel.sun@data61.csiro.au
+}
 
@@
 	\begin{abstract}
-		[abstract]
+		Hackers can infiltrate networks and find their way into databases and software systems. Not only
+		can they steal chunks of data and hold them for ransom, but
+		also alter key information contained in those systems, setting up
+		traps hard to discover and causing damages unlikely to recover.
+		Although altering single record may not oblige correct value scope such that it is hard to detect, the change, especially to a subset of data, can be observed and detected in a collective
+		scale. In this paper, we present a collective anomaly
+		detection technique based on statistical distance. The technique
+		extracts distribution similarities among data collections, and then uses the statistical distance to detect
+		collective anomalies. In order to adapt to data dynamics, our technique continuously evaluates 
+		metrics as evolving features. Aiming at broad generalisation, this
+		technique can replace several components of our solution to further improve the
+		performance of detection for various scenarios. To illustrate details of the technique
+		and explore its efficiency, we case-studied a real
+		world problem of click farming detection against malicious online
+		sellers. The evaluation shows that the technique maps normal
+		and anomalous data collections into two distinct clusters by yielding
+		efficient classifiers. Those classifiers are sensitive sufficiently to
+		a much smaller magnitude of data alerting, compared with real
+		world malicious behaviours--that is--it is applicable in the real world.
+
+		%Hackers can infiltrate networks via any attack vector, find their way into databases and applications.
+Not only can they steal chunks of data and hold them for ransom, but also alter key information contained in those systems, setting up traps hard to discover and causing damages unlikely to recover.
+Although the influence of data altering is not significant in single data record, the change can be observed and detect in a collective scale.
+		%In this paper, we present a dynamic collective anomaly detection technique based on statistical distance.
+The technique extracts distribution similarities among data collections, reducing collective anomalies into point anomalies.
+It dynamically calculate metrics which is adaptive to the slightly evolving features.
+This technique provides a basic solution where several components can be replaced by other scenario specific ones, further improving the performance of detection.
+		%To illustrate details of the technique and explore its efficiency, we applied the algorithm into a real world problem of click farming detection against malicious online sellers.
+The evaluation shows that the technique maps normal and anomalous data collections into two distinct clusters, yielding efficient classifiers.
+And those classifiers are sensitive enough to a much smaller magnitude of manipulation compared with real world malicious behaviours.
 	\end{abstract}
@@
 		%In Facebook, there is about 100 terabytes of data uploaded every day~\cite{bigDataFacebook}.
-		Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.
+		%Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.
+		%
+		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
 
-		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
 		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\autocite{saha2014data}.
@@
 And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}.
-System configuration problems, as a matter of fact, also draw scratches in the messy picture.
+System configuration problems, as a matter of fact, also draw scratches to the messy picture.
 They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.
@@
 \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
-Taken Apache Hadoop as an example.
-It's security issues has long been discussed within communities and industry~\autocite{sharif2015current,terzi2015survey,jam2014survey,sharma2014securing}.
+		% Take an example of Apache Hadoop, Hadoop's security issues has long been discussed within communities and industry~\autocite{sharif2015current,terzi2015survey,jam2014survey,sharma2014securing}.
 As is shown in Figure~\ref{fig:hadoop-security}, the two basic vulnerabilities: \textit{lack of access control} and the \textit{absence of encryption} expose the entire cluster to dangerous threats.
@@
 Several approaches are developed as sentinels to detect probable infiltrations.
-However, these approaches are not able to locate corrupted data under carefully planned manipulations.
+However, these approaches are not able to detect corrupted data under carefully planned manipulations.
 Nor can they figure out the exact reasons and recover the original records.
-To locate and diagnose anomalies in data pipelines under carefully planned and disguised data manipulations are still on demand by industry and academia.
+		If data inside the system is compromised, they will severely affect mining and learning algorithms and further change the final decision given by the entire system.
+In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.
+		% To locate and diagnose anomalies in data pipelines under carefully planned and disguised data manipulations are still in demand by industry and academia.
 
-		\begin{figure}[!t]
-			\includegraphics[width=\linewidth]{fig/HadoopSecurity}
-			\caption{Security Issues of Hadoop Clusters}
-			\label{fig:hadoop-security}
-		\end{figure}
+		%\begin{figure}[!t]
+		%	\includegraphics[width=\linewidth]{fig/HadoopSecurity}
+		%	\caption{Security Issues of Hadoop Clusters}
+		%	\label{fig:hadoop-security}
+		%\end{figure}
 
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
-			\caption{Example Cumulative Distribution Function of Original And Modified Data}
-			\label{fig:example-ecdf}
-		\end{figure}
-
-		According to our observation, typical data manipulations on numerical data will lead to the drift of its distribution.
-For example, a Taobao online seller's transaction records(see section~\ref{sec:exp-methodology}) can be ``click farmed'' to increase the volume of sales.
+		However, from the aspect of data itself, we can still detect malicious data manipulation behaviours.
+		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution.
+With the reshaping measurable, we can enclose data collections with similar distribution forms inside the same cluster and filter out those strange shaped ones.
+In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions.
+Comparing with a estimated ground truth, each data collection can be mapped to a single real number within a definite interval.
+Then a gaussian classifier can be applied to detect outliers derived from manipulated data.
+To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence.
+And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.
+		%For example, a Taobao online seller's transaction records(see section~\ref{sec:exp-methodology}) can be ``click farmed'' to increase the volume of sales.
 Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day.
@@
 The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.
-		These anomalies inside data \textbf{sets/collections} will severely affect mining and learning algorithms and further change the final decision given by the entire system.
-
-		In order to address issues caused by data manipulation, we propose a technique to detect corrupted data collections via statistical distance.
-As far as we know, this algorithm is the first attempt against collective data anomaly via statistical distance.
-Evaluations are performed on real-world and synthetic data sets, demonstrating the correctness and effectiveness of the technique.
+		Details of the technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.
 
@@
 a segment of sequence) instances is anomalous with respect to other groups in the data set(e.g.
-the entire sequence), it is called a collective anomaly.
+the entire sequence), it is called a collective anomaly~\cite{goldberger2000components}.
 
@@
 Semi-supervised detection approaches train model on data that has labeled instances for only the normal class.
-Supervised detection is commonly applied when both normal and anomalous data can be obtained.
-When it comes to the circumstances that anomalous data is hard to obtain or there exist too many diverse types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
+Supervised detection is commonly applied when both normal and anomalous data can be obtained.~\cite{fujimaki2005approach} When it comes to the circumstances that anomalous data is hard to obtain or there exist too many diverse types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
 
@@
 Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions.
-Some companies even develop professional applications that can be deployed on common PCs to improve productivity\textbf{[A Citation in Chinese]}.
+Some companies even develop professional applications that can be deployed on common PCs to improve productivity~\cite{zhao2016on}.
 
-			A research performed in China showed that 81.9\% of the people investigated had heard of the behaviour of click farming, 51.2\% of them had seen people around them click farmed and 18.9\% of them had experience of click farming themselves\textbf{[Chinese Citation?]}.
+			A research performed in China showed that 81.9\% of the people investigated had heard of the behaviour of click farming, 51.2\% of them had seen people around them click farmed and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}.
 American researchers reported in 2015 that over 11000 sellers were detected to have click farmed records and only 2.2\% of 4000 investigaed sellers had been penalized because of the cheating attempts~\cite{netease2015research}.
@@
 No matter how much alike between the employed users or robots with honest users, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
+To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records(see section~\ref{sec:exp-methodology}) and emulated the circumstances if it had been click farmed.
+Figure~\ref{fig:example-ecdf} shows the difference between one daily distribution with and without click farming.
+
+			\begin{figure}[!t]
+				\centering
+				\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
+				\caption{Example Cumulative Distribution Function of Original And Click Farmed Daily Transaction Data}
+				\label{fig:example-ecdf}
+			\end{figure}
+
 			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
@@
 		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
-This mathematical tool can be adopted in our solution to map distributions into one dimensional points, turning collective anomaly detection problem into point anomaly detection problem.
+		% This mathematical tool can be adopted in our solution to map distributions into one dimensional points, turning collective anomaly detection problem into point anomaly detection problem.
 Then a concrete point anomaly detection classifier can be used to find out the cheaters.
-
 		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
@@
 		\begin{equation}
-			D(\cdot || \cdot): S \times S \rightarrow \mathbb{R^+}
+			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+}
 		\end{equation}
@@
 
+		For our purposes, we do not require the function $D$ to have the property: $D(P||Q) = D(Q||P)$.
+But we do need it to be true that if $Q$ is more similar with $P$ than $U$, then $D(Q||P) < D(U||P)$.
 There are many ways to calculate divergence, such as f-divergences, M-divergences and S-divergences.
-Some of them provides better properties which brings conveniences to the design and implementation of our approach.
+		%Some of them provides better properties which brings conveniences to the design and implementation of our approach. 
+		Considering that the sensitivity and computational cost of the function are directly related to the performance of our technique, we chose Jensen-Shannon divergence which is derived from Kullback-Leibler as the measurement.
 
@@
 		\begin{enumerate}
-			\item $JSD(P||Q) = JSD(Q||P), \forall P, Q\in S$.
+			\item $JSD(P||Q) = JSD(Q||P), \forall P, Q\in \mathbb{S}$.
 			\item $0 \le JSD_{\pi_1, \dots, \pi_n}(P_1, \dots, P_n) \le log_k(n)$. If a $k$ based algorithm is adopted.
@@
 Main idea of the solution is simple.
-But there are several detailed difficulties to be solved in the design and implementation of the technique:
+But there are several difficulties to be solved in the design and implementation of the technique:
 
@@
 
-		\subsection{Divergence-Based Collective Anomaly Detection}
+		\ref{sec:alg-basic} answers the first question and introduces a basic framework of our technique.
+The second question is studied in~\ref{sec:alg-histogram}.
+\ref{sec:alg-threshold} gives an analysis about adaptive metric that minimizes total error.
+And a dynamic framework is proposed in~\ref{sec:alg-dynamic}.
+
+		\subsection{Divergence-Based Collective Anomaly Detection}\label{sec:alg-basic}
 			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions.
@@
 			Otherwise we need a frame of reference and yielding absolute distances rather than the relative ones.
-Therefore, we should keep an evidence set $E$ which consists of several already known correct distributions.
-Then the real distribution can be estimated by averaging all distributions in $E$.
+Therefore, we should keep an evidence set $\mathbb{E}$ which consists of several already known correct distributions.
+Then the real distribution can be estimated by averaging all distributions in $\mathbb{E}$.
 This process is similar to the parameter estimation within a certain sample set.
-Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside or outside $E$, yielding absolute distances.
+Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside or outside $\mathbb{E}$, yielding absolute distances.
 
@@
 Intuitively, a simple gaussian classifier can be suitable here to discover anomalous data points.
-The basic framework of the algorithm is shown as follows:
+The basic framework of the algorithm is shown in Algorithm~\ref{alg:static}:
 
-			\begin{algorithm}[!ht]
+			\begin{algorithm}[!t]
 				\caption{Basic Classification}
@@
 				\begin{algorithmic}[1]
-					\Require Evidence set $E = \{D_1, \dots, D_n\}(n\ge2)$; New data collection $D'$
+					\Require Evidence set $\mathbb{E} = \{D_1, \dots, D_n\}(n\ge2)$; New data collection $D'$
 					\Ensure Whether $D'$ is anomalous
@@
 					\State $p \gets$ probability density of $J'$ in $N$
-					\If{$p <$ threshold $T$}
+					\If{$p <$ Threshold}
 					\State \textbf{Return} True
@@
 
-			Let $S$ be set of the daily transaction collections, if $E$ is already given, we can run the algorithm with $E$ and $\forall D \in S$ and discover the anomalies.
-Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$.
-It is not viable for classification.
+			Let $\mathbb{S}$ be set of the daily transaction collections, if $\mathbb{E}$ is already given, we can run the algorithm with $\mathbb{E}$ and $\forall D \in \mathbb{S}$ and discover the anomalies.
+Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$, it is not viable for classification.
 Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes very large.
+For example, suppose $P(1) = P(2) = P(3) = \frac{1}{3}$ and $P'(1) = \frac{1}{6}, P'(2) = \frac{1}{3}, P'(3) = \frac{1}{2}$, then $JSD(P||P') \approx 0.023$ and $JSD(P, P, P, P') \approx 0.017$.
 
@@
 Therefore, $\mu$ should be slightly larger than zero.
-The reason why $\mu$ can not be exactly zero is hidden in line~\ref{line:population-estimation}.
-$M$ takes into consideration all existing values in every distribution sample and averages corresponding probabilities.
+The reason why $\mu$ cannot be exactly zero is hidden in line~\ref{line:population-estimation}.
+			For $\mu = 0$ if and only if $J_i = 0$ for $\forall i = 1, \dots, n$, which is equivalent to $P_i = P_j$ for $\forall i, j = 1, \dots, n$.
+And, $\lim_{n\rightarrow+\infty}P(P_i = P_j,\forall i, j = 1, \dots, n)=0$.
+Thus it is highly unlikely for real world data sets to have $u=0$.
+			%$M$ takes into consideration all existing values in every distribution sample and averages corresponding probabilities.
 Thus for a large $|S|$, $M$ may highly probably contains entries that does not exist in $P_i$ and certain probability entries in $M$ may vary from that in $P_i$.
@@
 
-			will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g. for normal distribution, $c=1.05$).
+			will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g.
+for normal distribution, $c=1.05$).
+For data sets with a large number of elements, a random sampling method, such as Monte-Carlo method, can be applied to speed up the estimation procedure.
 
@@
 This approach is easy to implement and may give satisfying results in specific cases.
-However, a fixed threshold requires analysis of the specific problem, manual observation and tuning of parameters, which involves lots of human labor.
+However, a fixed threshold requires specific analysis in the certain scenario, manual observation and tuning of parameters, which involves lots of human labour.
 The rule of ``$3 \sigma$'' can be used to automatically determine a threshold.
-But in some cases that the anomalous data intersecting at the boundary with normal instances, the threshold may fail more often to discover those manipulated ones.
+But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimal when concrete data is provided.
+It would be either higher than the optimum if anomalous data lies far away from the cluster consisting normal data records, or lower than the optimum if the anomalies sit more within the boundary.
 
-			However, applying divergence as the distance metric among data collection distributions provides a fine property.
-That is, divergences of normal data collections assemble together, forming a quasi-normal distribution.
-And those of anomalous data collections lies in the right-hand-side interval on the real number axis.
-As a result of further observation, the divergence of anomalous data collections also assemble to be a quasi-normal distribution, since statistical distance has been restricted by a strict upper bound.
+			\begin{figure}[!t]
+				\centering
+				\includegraphics[width=\linewidth]{fig/JSD-Dist.png}
+				\caption{Distribution of JSD values for everyday data collection. It can be approximately regarded as a gaussian distribution.}
+			\end{figure}
 
-			\textbf{[Better give a point drawing for each JSD value]}
+			However, applying divergence as the distance measurement among data collection distributions provides a fine property.
+That is, divergences of normal data collections assemble together, forming a quasi-gaussian distribution.
+And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side interval on the real number axis.
+As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error.
+That is due to the unknown randomness within real world data.
+Few assumptions can be applied in real world data sets, let alone data volume is sometimes relatively low.
+This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model.
+However, in the scenarios that better models can be calculated, distributions here can be replaced to produce better results.
+For the simplicity of our proposal, we assume the distributions of JSDs to be gaussian.
+			%the divergence of anomalous data collections also assemble to be a quasi-normal distribution, since statistical distance has been restricted by a strict upper bound.
 
-			\begin{figure}[!ht]
+			\textbf{[Better give a Histogram drawing JSD distribution]}
+
+			\begin{figure}[!t]
 				\centering
 				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
-				\caption{Threshold Example}
+				\caption{Threshold can be determined either by a probability density value, or a radius from the centre.
+In the scenario shown in the figure, the threshold can be determined by the position between two means of the distribution, denoted as ``T'' here.
+This form of threshold can also be applied to other types of distributions even there is no intersection between these two.}
 				\label{fig:example-threshold}
@@
 It can be reduced to a quadratic equation.
-But may not have real roots in all cases.
+But may not have real roots in some cases.
 
-			From another point of view, equation (\ref{equ:linear-weight}) can be regarded as a weighted averaging between two mean value: $\mu_n$ and $\mu_a$.
+			Section~\ref{sec:exp-threshold} compares some estimations for optimal threshold under a real world circumstance.
+It shows the difference among calculators and the scenario that equation~\ref{equ:linear-balanced} outperforms others.
+
+			%From another point of view, equation (\ref{equ:linear-weight}) can be regarded as a weighted averaging between two mean value: $\mu_n$ and $\mu_a$.
 From this aspect, we can derive some similar approximations:
 
-			\begin{align}
-				T &= \frac{\mu_n \sqrt{\sigma_a} + \mu_a \sqrt{\sigma_n}}{\sqrt{\sigma_a} + \sqrt{\sigma_n}}
-				\label{equ:sqrt-weight}\\
-				T &= \frac{\mu_n \sigma_a \sqrt{-ln(1 - \alpha)}
-					+ \mu_a \sigma_n \sqrt{-ln\alpha}}
-				{\sigma_a \sqrt{-ln(1 - \alpha)} + \sigma_n \sqrt{-ln\alpha}}
-				\label{equ:sqrt-log-add-weight}\\
-				T &= \frac{\mu_n \sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|}
-					+ \mu_a \sqrt{|ln(\sigma_n \alpha)|}}
-				{\sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_n \alpha)|}}
-				\label{equ:sqrt-log-combined-weight}
-			\end{align}
+			%\begin{align}
+			%	T &= \frac{\mu_n \sqrt{\sigma_a} + \mu_a \sqrt{\sigma_n}}{\sqrt{\sigma_a} + \sqrt{\sigma_n}}
+			%	\label{equ:sqrt-weight}\\
+			%	T &= \frac{\mu_n \sigma_a \sqrt{-ln(1 - \alpha)}
+			%		+ \mu_a \sigma_n \sqrt{-ln\alpha}}
+			%	{\sigma_a \sqrt{-ln(1 - \alpha)} + \sigma_n \sqrt{-ln\alpha}}
+			%	\label{equ:sqrt-log-add-weight}\\
+			%	T &= \frac{\mu_n \sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|}
+			%		+ \mu_a \sqrt{|ln(\sigma_n \alpha)|}}
+			%	{\sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_n \alpha)|}}
+			%	\label{equ:sqrt-log-combined-weight}
+			%\end{align}
 
-			Due to the restriction sample capacity, the replacement of JSD distributions by guassian distribution may lose too much accuracy.
+			%Due to the restriction sample capacity, the replacement of JSD distributions by guassian distribution may lose too much accuracy.
 Compared with equation (\ref{equ:sqrt-weight}), (\ref{equ:sqrt-log-add-weight})and (\ref{equ:sqrt-log-combined-weight}), (\ref{equ:linear-balanced}) may not give a best result.
 
-		\subsection{Dynamic DCAD}
+		\subsection{Dynamic DCAD}\label{sec:alg-dynamic}
 			In Algorithm~\ref{alg:static}, there is a hidden assumption that it regards every data collection to be sampled from a static population.
@@
 				\begin{algorithmic}[1]
-					\Require Normal evidence set $E_N = \{D_{N_1}, \dots, D_{N_n}\}$ by given order; Anomalous evidence set $E_A = \{D_{A_1}, \dots, D_{A_m}\}$ by given order; New data collection $D'$; Estimated anomalous probability $\alpha$
+					\Require Normal evidence set $\mathbb{E}_N = \{D_{N_1}, \dots, D_{N_n}\}$ by given order; Anomalous evidence set $\mathbb{E}_A = \{D_{A_1}, \dots, D_{A_m}\}$ by given order; New data collection $D'$; Estimated anomalous probability $\alpha$
 					\Ensure Whether $D'$ is anomalous
 					\For{$i \gets 1$ to $n$}
-						\State $P_{N_i} \gets$ histogram of $D_{N_i}$
+						\State $P_{N_i} \gets$ histogram of $D_{N_i}$\label{line:hist-1}
 					\EndFor
 					\For{$i \gets 1$ to $m$}
-						\State $P_{A_i} \gets$ histogram of $D_{A_i}$
+						\State $P_{A_i} \gets$ histogram of $D_{A_i}$\label{line:hist-2}
 					\EndFor
@@
 					\State $J' = JSD(P'|||M)$
-					\State $(\mu_N, \sigma_N) \gets$ estimated from $\{J_{N_1}, \dots, J_{N_n}\}$
-					\State $(\mu_A, \sigma_A) \gets$ estimated from $\{J_{A_1}, \dots, J_{A_m}\}$
+					\State $(\mu_N, \sigma_N) \gets$ estimated from $\{J_{N_1}, \dots, J_{N_n}\}$\label{line:gaussian-1}
+					\State $(\mu_A, \sigma_A) \gets$ estimated from $\{J_{A_1}, \dots, J_{A_m}\}$\label{line:gaussian-2}
 					\State $T \gets$ proper threshold derived from $(\mu_N, \sigma_N)$, $(\mu_A, \sigma_A)$ and $\alpha$
@@
 
-			Algorithm~\ref{alg:dynamic} uses $E_N$ and $E_A$ as two sliding windows, keeping up with latest trend of both normal and anomalous features.
+			Algorithm~\ref{alg:dynamic} uses $\mathbb{E}_N$ and $\mathbb{E}_A$ as two sliding windows, keeping up with latest trend of both normal and anomalous features.
 Thus, the two window sizes $n$ and $m$ cannot be too large.
@@
 
+			Note that line~\ref{line:hist-1} and~\ref{line:hist-2} can be replaced by other estimation methods if better assumptions can be made.
+Line~\ref{line:gaussian-1} and~\ref{line:gaussian-2} can be replaced by other models for more accuracy.
 Line~\ref{line:update-normal-evidence} and~\ref{line:update-anomalous-evidence} update the evidence sets, replacing the most outdated one, moving the sliding window forward one step ahead.
@@
 		\begin{enumerate}
+			\item How to emulate different types of click farming?
 			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:algorithm-details} applicable and accurate in real world data sets.
-			\item How to emulate different types of click farming?
 			\item Is the technique efficient against click farming? And How sensitive will the classifier be confronting different magnitude of click farming?
@@
 
+		These four questions are answered in the following subsections respectively.
+		%Methodology is first introduced in section~\ref{sec:exp-methodology}.
+And section~\ref{sec:exp-raw} tested on raw data sets and explained the working details of the technique.
+Experiments in section~\ref{sec:exp-synthetic} were performed on synthetic data, figuring out comprehensive performance of our technique.
+Then several different threshold calculators were compared in section~\ref{sec:exp-threshold}.
+
 		\subsection{Methodology}\label{sec:exp-methodology}
-			We adopted a data set containing Taobao online sellers' transaction records\footcite{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition.
+			We adopted a data set containing Taobao online sellers' transaction records\footcite{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition where all records are collected from the real world business scenarios and are desensitized.
 The data package contains seller features data set, user payments data set and user browsing behaviour data set.
@@
 					\hline
-					2 & 2 & 2\\
+					13799128 & 1862 & 2016-07-05 12:00:00\\
 					\hline
-					3 & 3 & 3\\
+					22127870 & 1862 & 2015-12-25 17:00:00\\
 					\hline
@@
 Entire transaction set was then divided into 325 collections, each containing records in one day.
+There are some days with no records because the online shop temporarily closed in those days.
 
@@
 				\includegraphics[width=0.75\linewidth]{fig/DailyTransactionVolume.png}
-				\caption{Daily Transaction Volumes}
+				\caption{Changing of the daily sales volume shows that some features of online sales has been changing all the time. Business transactions shall be checked with the dynamic algorithm.}
 				\label{fig:daily-transaction-volume}
@@
 				\includegraphics[width=\linewidth]{fig/SaleDistributionSamples.png}
-				\caption{Randomly selected 3 days and draw histograms by hourly sale}
+				\caption{We selected 3 days randomly and drew sales distribution by counting hourly volume. Although sales volume has changed from day to day, the shape of the distribution remain almost alike.}
 				\label{fig:sale-distribution-sample}
@@
 
-			Click farmed data was generated according to patterns described in online reports\textbf{[ref here]}.
-The most popular way of click farming is to call online a group of people, assign each of them an amount of transaction.
-And those ``employees'' individually buy certain products via different buyer accounts.
-Therefore, a significant feature of this approach is that the cheating transactions usually assemble together in a short period of time.
-It is called ``Centralized Farming''.
-Some other ``employers'' are more clever.
-They usually arrange a time table for each employee to create new transactions.
+			Click farmed data was generated according to patterns described in section~\ref{sec:related-realworld}.
+We adopted two prevalent types of click farming: \textit{Centralized Click Farming} and \textit{Equalized Click Farming}.
+Centralized click farming emulates the scenarios that a group of people are called out and assigned tasks by a casual leader that does not care much about the click farm timing.
+A significant feature of this approach is that the cheating transactions usually assemble together in a short period of time.
+Equalized click farming emulates the circumstances that click farms are arranged by some well programmed applications or teams carefully managed and strictly commit transactions according to a timetable.
 Thus the transaction distribution may not vary too much with and without click farming.
-This is called ``Equalized Farming''.
+According to investigations\textbf{[ref here?]}, the magnitude of click farm varies and depends on the payment the seller can afford.
+But usually, the click farmed transactions are several times more than the transaction volume it should have.
+In our experiments, we use $\nu$ to denote the magnitude coefficient of click farm, then $|D_{anomalous}| = (1 + \nu)|D_{normal}|$.
+In the following experiments without extra illustration, we adopt $\nu = 1$.
 
-			To emulate ``Centralized Click Farming'', we randomly inserted some gaussian-distributed transactions in a chosen collection, where the total number of new records is the same of the original volume.
-To emulate a extremely clever ``Equalized Click Farmer'', we simply doubled each record in the chosen collection to make the new distribution exactly the same as the original one, which is harder for the online platform to discover.
+			To emulate centralized click farming, we randomly inserted some gaussian-distributed transactions in a chosen collection, where the total number of new records is the same of the original volume.
+As for emulating the equalized click farmers, we simply doubled each record in the chosen collection to make the new distribution exactly the same as the original one, which is harder for the online platform to discover.
 
 			To play the role of purchasing platform, we surveillance two levels of transaction distribution.
-The first level is simply drawing a histogram on time spans.
+The first level is simply drawing a histogram aligned to time spans.
 The second level is to draw a histogram on the sub-volumes of each time span.
 For example, shown in Fig.~\ref{fig:histogram-example}, the first level histogram can be drawn by counting the number of hourly sales.
-The frequencies of each bucket in 1st level histogram is: $F=$\{0, 0, 0, 0, 0, 0, 0, 1, 13, 30, 37, 68, 60, 66, 72, 94, 75, 113, 127, 182, 165, 61, 0, 0\}.
-Then, counting $F$ with a step size 20 gives the 2nd level histogram.
+The frequencies of each bucket in 1st level histogram is: $\mathbb{F}=$\{0, 0, 0, 0, 0, 0, 0, 1, 13, 30, 37, 68, 60, 66, 72, 94, 75, 113, 127, 182, 165, 61, 0, 0\}.
+Then, counting $\mathbb{F}$ with a step size 20 gives the 2nd level histogram.
 
@@
 Each collection input has a probability of $\alpha$ to be anomalous, namely, click farmed.
-The algorithm checks each collection with 1st or 2nd level histogram and give an answer of true and false.
-Then a F1 score was computed as the result of the experiment.
+The algorithm checks each collection with 1st or 2nd level histogram and give an answer of true or false.
+Several metrics were explored in the following experiments.
 
@@
 For $\alpha = 0.2$, we select first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections.
-Equation(\ref{equ:sqrt-log-add-weight}) was employed as the threshold calculator.
+Equation(9) was employed as the threshold calculator.
 The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}, \textit{false positive rate} and \textit{accuracy} were recorded.
@@
 				\includegraphics[width=\linewidth]{fig/Raw1stLevelHist.png}
-				\caption{1st Level Histogram of Raw Data}
+				\caption{1st level histogram of day 5, 113 and 287, each day in a column.
+Distributions after centralized and equalized click farming are in 1st and 3rd row correspondingly.
+And the original distributions are shown in 2nd row.}
 				\label{fig:raw-hist-1st}
@@
 				\includegraphics[width=\linewidth]{fig/Raw2ndLevelHist}
-				\caption{2nd Level Histogram of Raw Data}
+				\caption{2nd level histogram of day 5, 113 and 287, each day in a column. Distribution after centralized click farming in day 287 uses another time scale since it deviates a lot from others.}
 				\label{fig:raw-hist-2nd}
@@
 				\includegraphics[width=\linewidth]{fig/RawOverview1st.png}
-				\caption{JSD of 1st Level Histograms}
-				\label{fig:raw-overview-1st}
-			\end{figure}
-
-			\begin{figure}[!ht]
-				\centering
+				(a)
 				\includegraphics[width=\linewidth]{fig/RawOverview2nd.png}
-				\caption{JSD of 2nd Level Histogram}
-				\label{fig:raw-overview-2nd}
+				(b)
+				\caption{This figure shows the JSD values of 1st and 2nd level histogram in each day in three different version: normal, centralized click farmed and equalized click farmed.
+Both (a) and (b) shows that centralized ones are usually larger than normal ones and most of them clearly distinguishable.
+In (a), 1st level histogram cannot tell anything different between normal ones and equalized ones.
+But in (b), 2nd level histograms map the equalized click farmers to the right side of normal ones.}
+				\label{fig:raw-overview}
 			\end{figure}
@@
 It can be clearly seen in Fig.~\ref{fig:raw-hist-2nd} that both types of click farming shows an obvious difference from the normal ones, while the normal ones still share a similar distribution.
-			From the overview in Fig.~\ref{fig:raw-overview-1st} and~\ref{fig:raw-overview-2nd}, the difference between normal and anomalous collections can be observed more intuitively.
+			From the overview in Fig.~\ref{fig:raw-overview}, the difference between normal and anomalous collections can be observed more intuitively.
 
-		\subsection{Experiment on Synthetic Data}
+		\subsection{Experiment on Synthetic Data}\label{sec:exp-synthetic}
 			As is put in the former section, every single record in the transaction set only gives a time stamp aligned at hours.
@@
 That is because the adaptive threshold was designed to minimize the number of total errors, which was irrelevant to TPR or FPR.
-When $\alpha$ was increasing, there were less data collections added into $E_N$.
-Thus the update of $E_N$ became slower and FPR went higher.
+When $\alpha$ was increasing, there were less data collections added into $\mathbb{E}_N$.
+Thus the update of $\mathbb{E}_N$ became slower and FPR went higher.
 On the contrary, TPR became higher as $\alpha$ increased.
-Moreover, since $|E_N| > |E_A|$, it needs more collection instances for $|E_N|$ then that for $|E_A|$ to keep up to the trend.
+Moreover, since $|\mathbb{E}_N| > |\mathbb{E}_A|$, it needs more collection instances for $|\mathbb{E}_N|$ then that for $|\mathbb{E}_A|$ to keep up to the trend.
 Therefore, it was faster of FPR to increase than TPR to increase.
@@
 				\includegraphics[width=\linewidth]{fig/ROC-Alpha.png}
-				\caption{ROC Curve of 1st and 2nd Level Classifier}
+				\caption{ROC curve of 1st and 2nd level classifier given different values of $\alpha$. The performance of the classifier does not change much for different error rates.}
 				\label{fig:roc-alpha}
@@
 The curves are pretty close to the upper left corner of the diagram and size under the curves are very large.
-For different $\alpha$s, the classifier can efficiently distinguish normal and anomalous data collections.
+For different $\alpha$'s, the classifier can efficiently distinguish normal and anomalous data collections.
 
@@
 				\includegraphics[width=\linewidth]{fig/ROC-Nu.png}
-				\caption{ROC Curve of Different Magnitude of Click Farming}
+				\caption{ROC curve of different magnitude of click farming. In real world scenarios, $\nu$ is normally larger than 1.}
 				\label{fig:roc-magnitude}
@@
 
-		\subsection{Threshold Optimization}
-			Section~\ref{sec:alg-threshold} mentions only four equations for calculating adaptive thresholds.
-Table~\ref{tab:threshold-comparison} gives the comparison of more equations in similar forms.
+		\subsection{Threshold Optimization}\label{sec:exp-threshold}
+			Section~\ref{sec:alg-threshold} mentions only two equations for calculating adaptive thresholds.
+Table~\ref{tab:threshold-comparison} gives the comparison of more equations out of similar considerations.
+From the aspect of weighted average(i.e.
+equation(1)) and taken $\alpha$ into consideration, we composes several other formulas with different operation on $\alpha$ and $\sigma$, yielding other possible balanced points within the interval $[\mu_N, \mu_A]$.
+
 			 We tested those calculators on synthetic data set with $\alpha = 0.1, \nu = 1$.
 Testing each level of classifier and each type of anomalies, we got 4 F1 scores and added them up.
-Equation 9 gives best performance.
+Equation 5 gives best performance.
 Then those equations were tested on large amount of gaussian distributed data instances.
@@
 Part of the reasons are mentioned in section~\ref{sec:alg-threshold}.
-Another reason is that the size of evidence sets are too restricted, that the gaussian distribution may not be well approximated.
+Another reason is that the size of evidence sets are too small, that the gaussian distribution may not be well approximated.
 
@@
 					\hline
-					2 & $\displaystyle T = \frac{\sqrt{\sigma_B} \mu_A + \sqrt{\sigma_A} \mu_B}{\sqrt{\sigma_B} + \sqrt{\sigma_A}}$& 2.1861 & 0.5718 \\ 
+					%2 & $\displaystyle T = \frac{\sqrt{\sigma_B} \mu_A + \sqrt{\sigma_A} \mu_B}{\sqrt{\sigma_B} + \sqrt{\sigma_A}}$& 2.1861 & 0.5718 \\ 
+					%\hline
+					%3 & $\displaystyle T = \frac{(ln\sigma_B)\mu_A + (ln\sigma_A)\mu_B}{ln\sigma_B + ln\sigma_A}$& 2.2390 & 0.3860 \\ 
+					%\hline
+					%4 & $\displaystyle T = \frac{(\sqrt{|ln\sigma_B|})\mu_A + (\sqrt{|ln\sigma_A|})\mu_B}{\sqrt{|ln\sigma_B|} + \sqrt{|ln\sigma_A|}}$& 2.2082 & 0.5515 \\ 
+					%\hline
+					%5 & $\displaystyle T = \frac{(ln\sqrt{\sigma_B})\mu_A + (ln\sqrt{\sigma_A})\mu_B}{ln\sqrt{\sigma_B} + ln\sqrt{\sigma_A}}$& 2.1211 & 0.3811 \\ 
+					%\hline
+					%\hline
+					2 & $\displaystyle T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$& 0.7688 & 0.3515 \\ 
 					\hline
-					3 & $\displaystyle T = \frac{(ln\sigma_B)\mu_A + (ln\sigma_A)\mu_B}{ln\sigma_B + ln\sigma_A}$& 2.2390 & 0.3860 \\ 
+					3 & $\displaystyle T = \frac{(\sigma_B \sqrt{1 - \alpha}) \mu_A + (\sigma_A \sqrt{\alpha}) \mu_B}{\sigma_B \sqrt{1 - \alpha} + \sigma_A \sqrt{\alpha}}$& 0.8158 & 0.4510 \\ 
 					\hline
-					4 & $\displaystyle T = \frac{(\sqrt{|ln\sigma_B|})\mu_A + (\sqrt{|ln\sigma_A|})\mu_B}{\sqrt{|ln\sigma_B|} + \sqrt{|ln\sigma_A|}}$& 2.2082 & 0.5515 \\ 
-					\hline
-					5 & $\displaystyle T = \frac{(ln\sqrt{\sigma_B})\mu_A + (ln\sqrt{\sigma_A})\mu_B}{ln\sqrt{\sigma_B} + ln\sqrt{\sigma_A}}$& 2.1211 & 0.3811 \\ 
-					\hline
-					\hline
-					6 & $\displaystyle T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$& 0.7688 & 0.3515 \\ 
-					\hline
-					7 & $\displaystyle T = \frac{(\sigma_B \sqrt{1 - \alpha}) \mu_A + (\sigma_A \sqrt{\alpha}) \mu_B}{\sigma_B \sqrt{1 - \alpha} + \sigma_A \sqrt{\alpha}}$& 0.8158 & 0.4510 \\ 
-					\hline
-					8 & $\displaystyle 
+					4 & $\displaystyle 
 					T = \frac{\big[\sigma_B ln(1 - \alpha)\big] \mu_A
@@
 					\hline
-					9 & $\displaystyle 
+					5 & $\displaystyle 
 					T = \frac{\mu_A \sigma_B \sqrt{-ln(1 - \alpha)}
@@
 					\hline
-					10 & $\displaystyle 
+					6 & $\displaystyle 
 					T = \frac{\mu_A \sigma_B ln\sqrt{1 - \alpha}
@@
 					\hline
-					11 & $\displaystyle 
+					7 & $\displaystyle 
 					T = \frac{\mu_A \sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|}
@@
 					\hline
-					12 & $\displaystyle 
+					8 & $\displaystyle 
 					T = \frac{\mu_A ln\sqrt{\sigma_B (1 - \alpha)}
@@
 					$& 2.0753 & 0.2808 \\ 
+					%\hline
 					\hline
-					\hline
-					13 & $\displaystyle T = \mathop{\arg\min}_{\mu_A \le T \le \mu_B}\ \alpha \cdot \int_{-\infty}^{T}P_B(x)dx + (1 - \alpha) \cdot \int_{T}^{+\infty}P_A(x)dx$ & 1.9300 & \color{blue}\textbf{0.6072}\\
+					9 & $\displaystyle T = \mathop{\arg\min}_{\mu_A \le T \le \mu_B}\ \alpha \cdot \int_{-\infty}^{T}P_B(x)dx + (1 - \alpha) \cdot \int_{T}^{+\infty}P_A(x)dx$ & 1.9300 & \color{blue}\textbf{0.6072}\\
 					\hline
@@
 
-		\subsection{Comparison with other collective classification algorithms}
-			\textbf{It would be better to have this comparison, but it requires much more experiments and the data set may not be very suitable.}
+		%\subsection{Comparison with other collective classification algorithms}
+		%	\textbf{It would be better to have this comparison, but it requires much more experiments and the data set may not be very suitable.}
 
@@
 		This paper proposed an dynamic collective anomaly detection algorithm with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
-Different from existing algorithms detecting collective anomalies, our approach employs statistical distance as the similarity metric, mapping data collections to a restricted one dimensional space.
-We explained several technical points involved in the design of the algorithm and performed a thorough experiment to test its efficiency.
+Different from existing algorithms detecting collective anomalies, our approach employs statistical distance as the similarity measurement, mapping data collections to a restricted one dimensional space.
+We explored several technical points involved in the design of the algorithm and performed a thorough experiment to test its efficiency.
 It showed that the algorithm can efficiently discover anomalies within the data sequences and the classifier is sensitive enough toward real world data manipulations.
 
-		However, the modelling of the JSD distributions is not precise enough, resulting in several threshold equations unexplained.
+		However, the modelling of the JSD distributions is not precise enough.
 The efficiency of different adaptive thresholds should be tested on different real world circumstances to get a more complete view of their performances.
-Moreover, a comparison with other collective detection algorithm should be executed in order to get an performance overview of similar algorithms.
+Moreover, a comparison with other collective detection algorithm should be adopted in the future to get an performance overview of similar algorithms.
+Since the algorithm adapts to the slowly evolving feature, when attacks disguise itself in the long run as if it was one of the changing features, the technique may fail to detect.
+In this case, other techniques may be applied as assistances.
 

### 2017-09-28 Paper/Template/paper.tex
Using template for paper

--- 2017-09-28 Paper/DataAnomaly/paper.tex
@@
-\documentclass[a4paper]{IEEEtran}
-
-\usepackage[backend=bibtex]{biblatex}
-\addbibresource{paper}
-\usepackage{hyperref}
+% IEEE Paper Template for US-LETTER Page Size (V1)
+% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
+% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
+% Permission is granted to distribute and revise this file provided that
+% this header remains intact.
+%
+% REVISION HISTORY
+% 20080211 changed some space characters in the title-author block
+%
+\documentclass[10pt,conference,letterpaper]{IEEEtran}
+\usepackage{times,amsmath,amsfonts,epsfig}
 \usepackage{graphicx}
-\usepackage{amsmath,amsfonts}
 \usepackage{algorithm,algorithmicx,algpseudocode}
@@
 \usepackage{color}
-\title{Dynamic Anomaly Detection for Collective Data Via Statistical Distance}
+%
+\title{Dynamic Anomaly Detection for Collective Data via Statistical Distance}
 %
@@
 
+%
 \begin{document}
 \maketitle
-
+%
 	\begin{abstract} 
@@
 		world malicious behaviours--that is--it is applicable in the real world. 
-
-		%Hackers can infiltrate networks via any attack vector, find their way into databases and applications.
-Not only can they steal chunks of data and hold them for ransom, but also alter key information contained in those systems, setting up traps hard to discover and causing damages unlikely to recover.
-Although the influence of data altering is not significant in single data record, the change can be observed and detect in a collective scale.
-		%In this paper, we present a dynamic collective anomaly detection technique based on statistical distance.
-The technique extracts distribution similarities among data collections, reducing collective anomalies into point anomalies.
-It dynamically calculate metrics which is adaptive to the slightly evolving features.
-This technique provides a basic solution where several components can be replaced by other scenario specific ones, further improving the performance of detection.
-		%To illustrate details of the technique and explore its efficiency, we applied the algorithm into a real world problem of click farming detection against malicious online sellers.
-The evaluation shows that the technique maps normal and anomalous data collections into two distinct clusters, yielding efficient classifiers.
-And those classifiers are sensitive enough to a much smaller magnitude of manipulation compared with real world malicious behaviours.
 	\end{abstract}
 
+% NOTE keywords are not used for conference papers so do not populate them
+% \begin{keywords}
+% keyword-1, keyword-2, keyword-3
+% \end{keywords}
+%
 	\section{Introduction}
 		Major improvements in data acquisition, transmission and storage are driving increased data availability and affordability.
-Currently, there are totally 2.7ZB data in the digital universe~\autocite{bigDataStatistics} and the growing speed is doubling every two years.
-		%In Facebook, there is about 100 terabytes of data uploaded every day~\cite{bigDataFacebook}.
-		%Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.
-		%
+Currently, there are totally 2.7ZB data in the digital universe~\cite{bigDataStatistics} and the growing speed is doubling every two years.
 		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
-
-		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\autocite{saha2014data}.
-		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years.
+		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those occurred at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years.
 And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}.
-System configuration problems, as a matter of fact, also draw scratches to the messy picture.
+System configuration problems, as a matter of fact, are also responsible for the disturbing situation.
 They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.
 
+		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\cite{saha2014data}.
 Those data anomalies may arise due to both internal and external reasons with respect to a certain system.
 On one hand, components inside the system may generate problematic source data.
-For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\autocite{rassam2014adaptive}.
-Data packages will be lost if sensor nodes fail to connect to network or some sensor hub goes down~\autocite{herodotou2014scalable}.
+For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\cite{rassam2014adaptive}.
+Data packages will be lost if sensor nodes fail to connect to network or some sensor hubs break down~\cite{herodotou2014scalable}.
 Also, human operators act as a heavily vulnerable part to bugs and mistakes.
-Some insiders even deliberately modify system configurations for malicious compromises~\autocite{schuster2015vc3}.
-A study~\autocite{humanError} found that 65\% of organizations state that human errors are the main  cause of data problems.
+Malicious insiders even deliberately modify system configurations for fatal compromises~\cite{schuster2015vc3}.
+A study~\cite{humanError} found that 65\% of organizations state that human errors are the main  cause of data problems.
 
-		On the other hand, data manipulation~\autocite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability.
+		On the other hand, data manipulation~\cite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability.
 \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
-		% Take an example of Apache Hadoop, Hadoop's security issues has long been discussed within communities and industry~\autocite{sharif2015current,terzi2015survey,jam2014survey,sharma2014securing}.
-As is shown in Figure~\ref{fig:hadoop-security}, the two basic vulnerabilities: \textit{lack of access control} and the \textit{absence of encryption} expose the entire cluster to dangerous threats.
-Data flows can be intercepted and modified; services can also be altered and blocked~\autocite{huang2014denial}.
-Although there are several frameworks(e.g.
-Kerberos, Sentry, Knox etc.) and algorithms providing basic protection~\autocite{zheng2017towards,sikdar2017spatio,xu2016high,yu2015enhancing,cohen2014towards}, clever attackers can always bypass the barriers and sneak into the core of data pipelines.
-Several approaches are developed as sentinels to detect probable infiltrations.
-However, these approaches are not able to detect corrupted data under carefully planned manipulations.
-Nor can they figure out the exact reasons and recover the original records.
 		If data inside the system is compromised, they will severely affect mining and learning algorithms and further change the final decision given by the entire system.
 In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.
-		% To locate and diagnose anomalies in data pipelines under carefully planned and disguised data manipulations are still in demand by industry and academia.
-
-		%\begin{figure}[!t]
-		%	\includegraphics[width=\linewidth]{fig/HadoopSecurity}
-		%	\caption{Security Issues of Hadoop Clusters}
-		%	\label{fig:hadoop-security}
-		%\end{figure}
 
@@
 		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution.
-With the reshaping measurable, we can enclose data collections with similar distribution forms inside the same cluster and filter out those strange shaped ones.
+With the reshaping measurable, we can enclose data collections with similar distribution patterns inside the same cluster and filter out those strange shaped ones.
 In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions.
-Comparing with a estimated ground truth, each data collection can be mapped to a single real number within a definite interval.
+Comparing with a estimated ground truth, each data collection can be mapped into a single real number within a definite interval.
 Then a gaussian classifier can be applied to detect outliers derived from manipulated data.
@@
 And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.
-		%For example, a Taobao online seller's transaction records(see section~\ref{sec:exp-methodology}) can be ``click farmed'' to increase the volume of sales.
-Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day.
-The curve for cheated data is emulated according to a popular method for click farming.
-It can be observed that there exists clearly a gap between these two distributions.
-		%For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original.
-The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.
 		Details of the technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.
 
-		The rest of the paper is organised as follow: Section~\ref{sec:related-work} states related works on data anomaly detection and describes a real world problem.
+		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related works on data anomaly detection and describes a real world problem.
 Section~\ref{sec:preliminaries} introduces statistical distance.
 Details of the technique are proposed in section~\ref{sec:algorithm-details}.
-Section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm.
-And all contents are concluded in section~\ref{sec:conclusion}.
+Then section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm.
+Finally, all contents are concluded and discussed in section~\ref{sec:conclusion}.
 
@@
 
-			Prevalent anomalies can be classified into \textit{Point Anomalies}, \textit{Contextual(or Conditional) Anomalies} and \textit{Collective Anomalies}.
-Point anomalies refers to an individual data instance that is considered anomalous with respect to others.
+			Prevalent anomalies can be classified into \textit{point anomalies}, \textit{contextual(or conditional) anomalies} and \textit{collective anomalies}.
+Point anomaly refers to an individual data instance that is considered anomalous with respect to others.
 But if it is anomalous only in certain circumstances or a specific context, the instance is regarded as contextual anomaly.
-If a group of related data(e.g.
-a segment of sequence) instances is anomalous with respect to other groups in the data set(e.g.
+If a group of related data instances(e.g.
+a segment of sequence) is anomalous with respect to other groups in the data set(e.g.
 the entire sequence), it is called a collective anomaly~\cite{goldberger2000components}.
@@
 Semi-supervised detection approaches train model on data that has labeled instances for only the normal class.
-Supervised detection is commonly applied when both normal and anomalous data can be obtained.~\cite{fujimaki2005approach} When it comes to the circumstances that anomalous data is hard to obtain or there exist too many diverse types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
+Supervised detection is commonly applied when both normal and anomalous data can be obtained.~\cite{fujimaki2005approach} When it comes to the circumstances that anomalous data is hard to obtain or there exist too many types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
 
@@
 		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
-			Since the establishment of Taobao in 2003, the online business platform has been growing from the rookies in the market to the No.1 service provider in B2B and B2C markets, possessing a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}.
+			Since the establishment of Taobao in 2003, its online business platform has been growing from a follower in the market to the No.1 service provider in B2B and B2C markets, possessing a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}.
 Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products.
-Under the super-pressure from massive competition, most of the sellers choose to use some cheating techniques to raise reputation and product sale volumes, then improve rankings in search lists.
+Under the super-pressure caused by massive competitors, most of the sellers choose to use some cheating techniques to raise reputation and product sale volumes, then improve rankings in search lists.
 
-			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of buyer accounts to create fake transaction records and give high remarks on products.
+			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of dedicated customer accounts to create fake transaction records and give high remarks on products.
 Professional click farmers are usually well organized groups or companies containing thousands of people.
@@
 Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable.
-No matter how much alike between the employed users or robots with honest users, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
-To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records(see section~\ref{sec:exp-methodology}) and emulated the circumstances if it had been click farmed.
-Figure~\ref{fig:example-ecdf} shows the difference between one daily distribution with and without click farming.
+No matter how much alike between honest users and robots or the employed workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
+To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records and emulated the circumstances if it had been click farmed(see section~\ref{sec:exp-methodology}).
+Fig.~\ref{fig:example-ecdf} shows the difference between normal and click farmed distributions of one day in the data set.
+			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
 
@@
 				\centering
-				\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
+				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
 				\caption{Example Cumulative Distribution Function of Original And Click Farmed Daily Transaction Data}
@@
 
-			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
-
 	\section{Preliminaries}\label{sec:preliminaries}
 		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
-		% This mathematical tool can be adopted in our solution to map distributions into one dimensional points, turning collective anomaly detection problem into point anomaly detection problem.
-Then a concrete point anomaly detection classifier can be used to find out the cheaters.
 		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
-Let $S$ be a space of probability distributions, then a divergence is a function from $S$ to non-negative real numbers:
+Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers:
 		\begin{equation}
@@
 		\begin{enumerate}
-			\item $D(P||Q) \ge 0, \forall P, Q \in S$
+			\item $D(P||Q) \ge 0, \forall P, Q \in \mathbb{S}$
 			\item $D(P||Q) = 0$, if and only if $P=Q$
@@
 There are many ways to calculate divergence, such as f-divergences, M-divergences and S-divergences.
-		%Some of them provides better properties which brings conveniences to the design and implementation of our approach. 
-		Considering that the sensitivity and computational cost of the function are directly related to the performance of our technique, we chose Jensen-Shannon divergence which is derived from Kullback-Leibler as the measurement.
+		Considering that the sensitivity and computational cost of the function are directly related to the performance of our technique, we chose Jensen-Shannon divergence, which is derived from Kullback-Leibler divergence, as the measurement.
 
-		\subsubsection{Kullback-Leibler Divergence}
+		\subsection{Kullback-Leibler Divergence}
 			Let $P,Q$ be discrete probability distributions, $Q(i)=0$ implies $P(i)=0$ for $\forall i$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:
@@
 
-		\subsubsection{Jensen-Shannon Divergence}
+		\subsection{Jensen-Shannon Divergence}
 			Let $P,Q$ be discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:
@@
 Manipulation on those data(e.g.
-Fig~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm.
+Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm.
 Main idea of the solution is simple.
-But there are several difficulties to be solved in the design and implementation of the technique:
+But there are several difficulties to be solved in the specific design and implementation of the technique:
 
@@
 
+		These questions are addressed in the following subsections correspondingly.
 		\ref{sec:alg-basic} answers the first question and introduces a basic framework of our technique.
 The second question is studied in~\ref{sec:alg-histogram}.
-\ref{sec:alg-threshold} gives an analysis about adaptive metric that minimizes total error.
+Then \ref{sec:alg-threshold} gives an analysis about adaptive metric that minimizes total error.
 And a dynamic framework is proposed in~\ref{sec:alg-dynamic}.
@@
 			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions.
-In a set of data collections, we can only draw a complete graph that each node denotes one certain collection and each edge refers to the divergence of two data collections.
+In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the divergence between two connected nodes.
 From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies.
-This may work if anomalous ones do not compose a large proportion of all points.
-However the procedure will be too complicated to work out with large amounts of instances.
+This may work if anomalous nodes do not compose a large proportion.
+However the procedure will be too complicated to work out with large amounts of data collections.
 
-			Otherwise we need a frame of reference and yielding absolute distances rather than the relative ones.
-Therefore, we should keep an evidence set $\mathbb{E}$ which consists of several already known correct distributions.
+			Otherwise we need a frame of reference that provides absolute coordinates rather than the relative ones.
+Therefore, we should keep an evidence set $\mathbb{E}$ which consists of several correct distributions that have already been given.
 Then the real distribution can be estimated by averaging all distributions in $\mathbb{E}$.
 This process is similar to the parameter estimation within a certain sample set.
-Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside or outside $\mathbb{E}$, yielding absolute distances.
+Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside and outside $\mathbb{E}$, yielding absolute distances.
 
-			Fig.~\ref{fig:raw-hist-1st} and~\ref{fig:raw-hist-2nd} in section~\ref{sec:exp-raw} show the result of the above process.
-Red dots refer to the distances calculated from normal transaction data collections, blue and green ones are from click farmed collections.
-Clearly, distances of normal data collections assembles together around a small value while anomalous ones are distributed around a larger distance value.
+			Fig.~\ref{fig:raw-overview} in section~\ref{sec:exp-raw} demonstrates the result of the above process.
+Red dots refer to the distances calculated from normal data collections, blue and green ones are from click farmed data collections.
+Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value.
 Intuitively, a simple gaussian classifier can be suitable here to discover anomalous data points.
-The basic framework of the algorithm is shown in Algorithm~\ref{alg:static}:
+The basic framework of the algorithm is shown in Algorithm~\ref{alg:static}.
 
@@
 			Let $\mathbb{S}$ be set of the daily transaction collections, if $\mathbb{E}$ is already given, we can run the algorithm with $\mathbb{E}$ and $\forall D \in \mathbb{S}$ and discover the anomalies.
+JSD here cannot be replaced by KLD since entries in $P'$ are not necessarily defined in $M$.
 Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$, it is not viable for classification.
@@
 Thus it is highly unlikely for real world data sets to have $u=0$.
-			%$M$ takes into consideration all existing values in every distribution sample and averages corresponding probabilities.
-Thus for a large $|S|$, $M$ may highly probably contains entries that does not exist in $P_i$ and certain probability entries in $M$ may vary from that in $P_i$.
-For a concrete example, suppose $P_1(1)=0.5, P_1(2)=0.3, P_1(3)=0.2$; $P_2(1) = 0.3, P_2(2) = 0.4, P_2(3) = 0.3$; $P_3(1)=0.3, P_3(3)=0.5, P_3(4)=0.2$, then $M(1) = \frac{11}{3}, M(2)=\frac{7}{3}, M(3)=\frac{10}{3}, M(4)=\frac{2}{3}$.
-None of $P_1, P_2, P_3$ is the same with $M$.
 
@@
 Parameter approximation will probably lead to errors far beyond our expectation.
-For example, the distribution of vehicle volume in the highway may not correspond to any of the prevalent distribution model.
+For example, the distribution of vehicle volume in the highway may be of the shape of two connected gaussian curves and does not correspond to any of the prevalent distribution models.
 Few assumption of parameters can be made in advance on such data.
@@
 
-			Surely, the kernel density estimation approaches will give a smooth, continuous distribution curve under on any sampled data.
-The computational cost will be much higher than applying a coarse histogram approximation.
+			Surely, the kernel density estimation approaches will give a smooth, continuous distribution curve on any sampled data.
+But the computational cost will be much higher than applying a coarse histogram approximation.
 			Moreover, even if we applied a distribution model upon a collection of sampled data, yielding more accurate results, the computation of divergence will be much more complex on continuous functions than discrete distributions.
@@
 
-			In order to generate a accurate approximation, step size is the most important parameter the algorithm should determine.
+			In order to generate an accurate approximation, step size is the most important parameter the algorithm should determine.
 If the size is too small then the resulting histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape.
@@
 
-			will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g.
+			will give a best partition size, where $c$ is a constant relative to the shape of distribution(e.g.
 for normal distribution, $c=1.05$).
@@
 For the simplicity of our proposal, we assume the distributions of JSDs to be gaussian.
-			%the divergence of anomalous data collections also assemble to be a quasi-normal distribution, since statistical distance has been restricted by a strict upper bound.
 
@@
 It shows the difference among calculators and the scenario that equation~\ref{equ:linear-balanced} outperforms others.
-
-			%From another point of view, equation (\ref{equ:linear-weight}) can be regarded as a weighted averaging between two mean value: $\mu_n$ and $\mu_a$.
-From this aspect, we can derive some similar approximations:
-
-			%\begin{align}
-			%	T &= \frac{\mu_n \sqrt{\sigma_a} + \mu_a \sqrt{\sigma_n}}{\sqrt{\sigma_a} + \sqrt{\sigma_n}}
-			%	\label{equ:sqrt-weight}\\
-			%	T &= \frac{\mu_n \sigma_a \sqrt{-ln(1 - \alpha)}
-			%		+ \mu_a \sigma_n \sqrt{-ln\alpha}}
-			%	{\sigma_a \sqrt{-ln(1 - \alpha)} + \sigma_n \sqrt{-ln\alpha}}
-			%	\label{equ:sqrt-log-add-weight}\\
-			%	T &= \frac{\mu_n \sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|}
-			%		+ \mu_a \sqrt{|ln(\sigma_n \alpha)|}}
-			%	{\sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_n \alpha)|}}
-			%	\label{equ:sqrt-log-combined-weight}
-			%\end{align}
-
-			%Due to the restriction sample capacity, the replacement of JSD distributions by guassian distribution may lose too much accuracy.
-Compared with equation (\ref{equ:sqrt-weight}), (\ref{equ:sqrt-log-add-weight})and (\ref{equ:sqrt-log-combined-weight}), (\ref{equ:linear-balanced}) may not give a best result.
 
@@
 		These four questions are answered in the following subsections respectively.
-		%Methodology is first introduced in section~\ref{sec:exp-methodology}.
-And section~\ref{sec:exp-raw} tested on raw data sets and explained the working details of the technique.
-Experiments in section~\ref{sec:exp-synthetic} were performed on synthetic data, figuring out comprehensive performance of our technique.
-Then several different threshold calculators were compared in section~\ref{sec:exp-threshold}.
 
 		\subsection{Methodology}\label{sec:exp-methodology}
-			We adopted a data set containing Taobao online sellers' transaction records\footcite{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition where all records are collected from the real world business scenarios and are desensitized.
+			We adopted a data set containing Taobao online sellers' transaction records\footnote{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition where all records are collected from the real world business scenarios and are desensitized.
 The data package contains seller features data set, user payments data set and user browsing behaviour data set.
@@
 
-			\begin{table*}[!ht]
+			\begin{table*}[!t]
 				\centering
@@
 					\hline
-					%2 & $\displaystyle T = \frac{\sqrt{\sigma_B} \mu_A + \sqrt{\sigma_A} \mu_B}{\sqrt{\sigma_B} + \sqrt{\sigma_A}}$& 2.1861 & 0.5718 \\ 
-					%\hline
-					%3 & $\displaystyle T = \frac{(ln\sigma_B)\mu_A + (ln\sigma_A)\mu_B}{ln\sigma_B + ln\sigma_A}$& 2.2390 & 0.3860 \\ 
-					%\hline
-					%4 & $\displaystyle T = \frac{(\sqrt{|ln\sigma_B|})\mu_A + (\sqrt{|ln\sigma_A|})\mu_B}{\sqrt{|ln\sigma_B|} + \sqrt{|ln\sigma_A|}}$& 2.2082 & 0.5515 \\ 
-					%\hline
-					%5 & $\displaystyle T = \frac{(ln\sqrt{\sigma_B})\mu_A + (ln\sqrt{\sigma_A})\mu_B}{ln\sqrt{\sigma_B} + ln\sqrt{\sigma_A}}$& 2.1211 & 0.3811 \\ 
-					%\hline
-					%\hline
 					2 & $\displaystyle T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$& 0.7688 & 0.3515 \\ 
@@
 
-		%\subsection{Comparison with other collective classification algorithms}
-		%	\textbf{It would be better to have this comparison, but it requires much more experiments and the data set may not be very suitable.}
-
 	\section{Conclusion \& Future Work}\label{sec:conclusion}
@@
 
-	\section*{Acknowledgement}
+\section*{Acknowledgment}
 
-	\printbibliography
+\bibliographystyle{IEEEtran}
+
+\bibliography{IEEEabrv,paper}
+
 \end{document}

### 2017-09-28 Synthetic/PlotCDF.py

@@ -1,0 +1,45 @@
+import csv
+import Divergence
+import statistics
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+reader = csv.reader(open("Correct/3.csv", 'r'))
+data = list(int(row[2]) for row in reader)
+
+reader_err = csv.reader(open("Centralized/3.csv", 'r'))
+data_err = list(int(row[2]) for row in reader_err)
+
+sigma = statistics.stdev(data)
+step = 0.5 * sigma * (len(data) ** -0.2)
+
+dropped, dist = Divergence.histogram(data, step)
+dropped, dist_err = Divergence.histogram(data_err, step)
+
+figure = plt.figure(figsize=(8, 4.5), dpi=100)
+x = []
+y = []
+p = 0
+for i in range(70):
+    if i in dist:
+        p += dist[i]
+    x += [i, i+1]
+    y += [p, p]
+plt.plot(x, y, 'k', label="Correct")
+
+x = []
+y = []
+p = 0
+for i in range(70):
+    if i in dist_err:
+        p += dist_err[i]
+    x += [i, i+1]
+    y += [p, p]
+plt.plot(x, y, 'r', label="Cheated")
+
+plt.legend(fontsize='large')
+plt.xlabel("Time Span", fontsize='x-large')
+plt.ylabel("Cumulative Probability", fontsize='x-large')
+
+figure.savefig("ExampleCDF.png")

### 2017-09-28 RealWorld/ShowDistribution.py
Redraw some figures

@@ -4,9 +4,10 @@ matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import random
 
-# figure = plt.figure(figsize=(9, 3), dpi=100)
+# figure = plt.figure(figsize=(8, 4.2), dpi=120)
 # plt_cnt = 0
 # for day in (5, 113, 287):
+#     #figure = plt.figure(figsize=(5, 5), dpi=100)
 #     reader = csv.reader(open("Correct/%d.csv" % day, 'r'))
 #     freq = {}
 #     for i in range(24):
@@ -16,8 +17,16 @@ import random
 #
 #     plt_cnt += 1
 #     plt.subplot(1, 3, plt_cnt)
-#     plt.bar(list(range(24)), freq.values(), label="day %d" % day)
-#     plt.legend(loc="upper left")
+#     plt.bar(list(range(24)), freq.values())
+#     plt.title("Day %d" % day)
+#     if 2 == plt_cnt:
+#         plt.xlabel("Hour", fontsize='x-large')
+#     else:
+#         plt.xlabel(' ', fontsize='x-large')
+#     if 1 == plt_cnt:
+#         plt.ylabel("Transaction Volume", fontsize='x-large')
+#     #plt.savefig("SaleDistributions-%d.png" % plt_cnt)
+#     #figure.savefig("SaleDistributions-%d.png" % plt_cnt)
 #
 # plt.savefig("SaleDistributions.png")
 
@@ -35,13 +44,19 @@ for i in freq1.keys():
     bsk = int(freq1[i] / 20)
     freq2[bsk] += 1
 
-figure = plt.figure(figsize=(8, 4), dpi=100)
+figure = plt.figure(figsize=(8, 4.4), dpi=100)
 plt.subplot(1, 2, 1)
 plt.bar(list(range(24)), freq1.values(), label="1st Level")
-plt.legend()
+plt.title("1st Level")
+plt.xlabel("Time Span", fontsize='x-large')
+plt.ylabel("Transaction Volume", fontsize='x-large')
+#plt.legend()
 
 plt.subplot(1, 2, 2)
 plt.bar(list(range(10)), freq2.values(), label="2st Level")
-plt.legend()
+plt.title("2nd Level")
+plt.xlabel("Volume Span", fontsize='x-large')
+plt.ylabel("Frequency", fontsize='x-large')
+#plt.legend()
 
 plt.savefig("HistogramExample.png")

### 2017-09-28 RealWorld/ShowOverview.py

@@ -14,7 +14,7 @@ jsd2 = [0.10912704201369046, 0.19845387518896526, 0.06636123715181373, 0.2296597
 jsd_cen2 = [0.32256760379361726, 0.3810239639317933, 0.28386663245410493, 0.35230754830673466, 0.28189384029941755, 0.2990176428977388, 0.24311679125495256, 0.3692207262558338, 0.34815422147146746, 0.3086180294974303, 0.2190867719629146, 0.2944877706533938, 0.23662774226146438, 0.3309871042516204, 0.43175927961812877, 0.35225026853698854, 0.3506640374165292, 0.25018682290870126, 0.2018944636423843, 0.19958628735050707, 0.2511881602458358, 0.21825640670517163, 0.3277881493146352, 0.23731398417432872, 0.2651893172458749, 0.25987672849498034, 0.1981169965350415, 0.3305360563766058, 0.3013549901242266, 0.28440338403422183, 0.28229077822524445, 0.24597592507096025, 0.2689289289249557, 0.26723613384157013, 0.26051423720450034, 0.4598711221548436, 0.29199940349935083, 0.2251773592006137, 0.22380082229940482, 0.2459725847967571, 0.32849376864464885, 0.1908232890968055, 0.31989906513324307, 0.32991462184432313, 0.31619989409047616, 0.29599589101452783, 0.33142278114623064, 0.2800054579791898, 0.3281902150886128, 0.3242061842283341, 0.28508548123760513, 0.3165442627196493, 0.29439248623540115, 0.280880018188317, 0.4402812786150543, 0.22841474211560983, 0.3752587645937397, 0.250537545003473, 0.236924835544984, 0.143041665652949, 0.19756006910399015, 0.20170043820336014, 0.22989958013678133, 0.20357673808875332, 0.2823378671559504, 0.3020928363649714, 0.18589749572654715, 0.31343670974684334, 0.2337374009942335, 0.30641242467725643, 0.31438688575758694, 0.3663003586378917, 0.26690527231045974, 0.290334571377121, 0.27951540668418196, 0.24195819156521706, 0.2637679765623775, 0.2926738393659329, 0.2649750293539159, 0.2541129910728474, 0.23056036822725479, 0.2420132797701976, 0.26567316524371415, 0.2340119173868865, 0.2763747331629617, 0.34789842920122444, 0.26551206992806975, 0.2970711176190934, 0.2785566291322321, 0.2586713412063521, 0.2996400865965023, 0.25534
[…]

### 2017-09-28 Paper/Template/paper.tex
2nd Version paper

@@
 But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimal when concrete data is provided.
-It would be either higher than the optimum if anomalous data lies far away from the cluster consisting normal data records, or lower than the optimum if the anomalies sit more within the boundary.
+It would be either higher than the optimum if anomalous data lies far away from the normal cluster, or lower than the optimum if the anomalies sit close to the cluster centre.
 
@@
 				\caption{Distribution of JSD values for everyday data collection. It can be approximately regarded as a gaussian distribution.}
+				\label{fig:jsd-dist}
 			\end{figure}
 
-			However, applying divergence as the distance measurement among data collection distributions provides a fine property.
+			However, applying divergence as the distance measurement among data collections provides a fine property.
 That is, divergences of normal data collections assemble together, forming a quasi-gaussian distribution.
-And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side interval on the real number axis.
-As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error.
+And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side to the other one on the real number axis.
+As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error(Fig.~\ref{fig:jsd-dist}).
 That is due to the unknown randomness within real world data.
@@
 
-			\textbf{[Better give a Histogram drawing JSD distribution]}
-
 			\begin{figure}[!t]
@@
 				\caption{Threshold can be determined either by a probability density value, or a radius from the centre.
-In the scenario shown in the figure, the threshold can be determined by the position between two means of the distribution, denoted as ``T'' here.
+In the scenario shown in the figure, the threshold can be determined by the position between two centres of the distribution, denoted as ``T'' here.
 This form of threshold can also be applied to other types of distributions even there is no intersection between these two.}
@@
 
-			As shown in Fig~\ref{fig:example-threshold}, the black curve($PDF_{normal}(x)$) displays the probability density function(PDF) fitting those JSDs calculated from normal data collections; the blue curve($PDF_{anomalous}(x)$) displays the PDF derived from anomalous data collections.
-Threshold is chosen to minimize total errors(False Negative and False Positive).
+			As shown in Fig~\ref{fig:example-threshold}, the black curve($PDF_{normal}(x)$ or in short $PDF_n(x)$) displays the probability density function(PDF) fitting those JSDs calculated from normal data collections; the blue curve($PDF_{anomalous}(x)$ or in short $PDF_a(x)$) displays the PDF derived from anomalous data collections.
+Threshold is chosen to minimize total errors(both false negative and false positive).
 
@@
 			\begin{align}
-				PDF_{normal}(x) &\approx N(\mu_n, \sigma_n)\\
-				PDF_{anomalous}(x) &\approx N(\mu_a, \sigma_a)
+				PDF_{n}(x) &\approx N(\mu_n, \sigma_n)\\
+				PDF_{a}(x) &\approx N(\mu_a, \sigma_a)
 			\end{align}
@@
 			\begin{equation}\label{equ:linear-weight}
-				\small
+				%\small
 				\begin{split}
-					T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{anomalous}(x)dx +
-					\int_{T}^{log_k2}PDF_{normal}(x)dx\\
+					T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{a}(x)dx +
+					\int_{T}^{log_k2}PDF_{n}(x)dx\\
 					& \approx \mathop{\arg\min}_{T}
-					\int_{-\infty}^{T}
+					\int_{0}^{T}
 					\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-					+ \int_{T}^{+\infty}
+					+ \int_{T}^{log_k2}
 					\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\\
@@
 
-			However, this is not accurate enough, since equation(\ref{equ:linear-weight}) implicate an assumption that the chances are the same for a new data collection to be either anomalous or not.
+			However, this is not accurate enough, since equation(\ref{equ:linear-weight}) implicates an assumption that the chances are the same for a new data collection to be either anomalous or not.
 If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as:
@@
 			\begin{equation}\label{equ:linear-balanced}
-				\small
+				{\footnotesize
 				\begin{split}
-					T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{anomalous}(x)dx +
-					(1-\alpha)\int_{T}^{log_k2}PDF_{normal}(x)dx\\
+					T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
+					(1-\alpha)\int_{T}^{log_k2}PDF_{n}(x)dx\\
 					& \approx \mathop{\arg\min}_{T}
-					\alpha\int_{-\infty}^{T}
+					\alpha\int_{0}^{T}
 					\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-					+ (1-\alpha)\int_{T}^{+\infty}
+					+ 
+					(1-\alpha)\int_{T}^{log_k2}
 					\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx
-				\end{split}
+				\end{split}}
 			\end{equation}
 
-			Where $\alpha$ is the anomaly probability.
-Equation(\ref{equ:linear-balanced}) is much more complicated than (\ref{equ:linear-weight}).
-It can be reduced to a quadratic equation.
-But may not have real roots in some cases.
-
+			Where $\alpha$ is the anomaly probability. Equation(\ref{equ:linear-balanced}) is much more complicated. But it can be reduced to a quadratic equation.
 			Section~\ref{sec:exp-threshold} compares some estimations for optimal threshold under a real world circumstance.
-It shows the difference among calculators and the scenario that equation~\ref{equ:linear-balanced} outperforms others.
+It shows the difference among calculators and that equation(\ref{equ:linear-balanced}) outperforms others when $PDF_n(x)$ and $PDF_a(x)$ are actually gaussian.
 
 		\subsection{Dynamic DCAD}\label{sec:alg-dynamic}
-			In Algorithm~\ref{alg:static}, there is a hidden assumption that it regards every data collection to be sampled from a static population.
-That is to say the seller will never change his or her products and customer volume always remain the same.
+			In Algorithm~\ref{alg:static}, there is a hidden assumption that it regards every data collection to be sampled from a static environment.
+That is to say the seller will never change his or her products and customer volumes always remain the same.
 In most cases, real world data is always in the process of evolution and fluctuation.
@@
 To meet the need, a sliding window technique has been applied to the basic algorithm frame work.
-Considering discussion in section~\ref{sec:alg-histogram} and~\ref{sec:alg-threshold}, a dynamic version is proposed as follow:
+And considering discussion in section~\ref{sec:alg-histogram} and~\ref{sec:alg-threshold}, a dynamic version is proposed in Algorithm~\ref{alg:dynamic}.
 
-			\begin{algorithm}[!ht]
-				\caption{Dynamic DAD}
+			\begin{algorithm}[!t]
+				\caption{Dynamic Classification}
 				\label{alg:dynamic}
@@
 					\If{$J' < T$}
-					\State $E_N \gets E_N \backslash \{D_{N_0}\} \cup \{D'\}$\label{line:update-normal-evidence}
+					\State $\mathbb{E}_N \gets \mathbb{E}_N \backslash \{D_{N_0}\} \cup \{D'\}$\label{line:update-normal-evidence}
 					\State \textbf{Return} False
 					\Else
-					\State $E_A \gets E_A \backslash \{D_{A_0}\} \cup \{D'\}$\label{line:update-anomalous-evidence}
+					\State $\mathbb{E}_A \gets \mathbb{E}_A \backslash \{D_{A_0}\} \cup \{D'\}$\label{line:update-anomalous-evidence}
 					\State \textbf{Return} True
@@
 Thus, the two window sizes $n$ and $m$ cannot be too large.
-Otherwise the evolving features will be flattened and aligned to the older ones.
+Otherwise the evolving features will be flattened and aligned to the older version.
 For the sake of estimation accuracy, they cannot be too small either.
@@
 			\item How to emulate different types of click farming?
-			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:algorithm-details} applicable and accurate in real world data sets.
+			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:alg-basic} applicable and accurate in real world data sets.
 			\item Is the technique efficient against click farming? And How sensitive will the classifier be confronting different magnitude of click farming?
@@
 				\centering
-				\caption{User Payment Record Exmaple}
+				\caption{User Payment Record Examples}
 				\label{tab:user-payment-sample}
@@
 
-			\begin{figure}[!ht]
+			\begin{figure}[!t]
 				\centering
 				\includegraphics[width=0.75\linewidth]{fig/DailyTransactionVolume.png}
-				\caption{Changing of the daily sales volume shows that some features of online sales has been changing all the time. Business transactions shall be checked with the dynamic algorithm.}
+				\caption{Changing of the daily sales volume shows that environment of online sales has been changing all the time. Business transactions shall be checked with the dynamic algorithm.}
 				\label{fig:daily-transaction-volume}
@@
 
-			\begin{figure}[ht]
+			\begin{figure}[!t]
 				\centering
-				\includegraphics[width=\linewidth]{fig/SaleDistributionSamples.png}
+				\includegraphics[width=\linewidth]{fig/SaleDistributions.png}
 				\caption{We selected 3 days randomly and drew sales distribution by counting hourly volume. Although sales volume has changed from day to day, the shape of the distribution remain almost alike.}
@@
 			Click farmed data was generated according to patterns described in section~\ref{sec:related-realworld}.
-We adopted two prevalent types of click farming: \textit{Centralized Click Farming} and \textit{Equalized Click Farming}.
+We adopted two prevalent types of click farming: \textit{centralized click farming} and \textit{equalized click farming}.
 Centralized click farming emulates the scenarios that a group of people are called out and assigned tasks by a casual leader that does not care much about the click farm timing.
@@
 Thus the transaction distribution may not vary too much with and without click farming.
-According to investigations\textbf{[ref here?]}, the magnitude of click farm varies and depends on the payment the seller can afford.
-But usually, the click farmed transactions are several times more than the transaction volume it should have.
-In our experiments, we use $\nu$ to denote the magnitude coefficient of click farm, then $|D_{anomalous}| = (1 + \nu)|D_{normal}|$.
+Usually, the click farmed transactions are several times more than the volume it original has, if the seller hires a group of organized workers.
+In our experiments, we use $\nu$ to denote the magnitude coefficient of click farming.
+Hence $|D_{anomalous}| = (1 + \nu)|D_{normal}|$.
 In the following experiments without extra illustration, we adopt $\nu = 1$.
 
-			To emulate centralized click farming, we randomly inserted some gaussian-distributed transactions in a chosen collection, where the total number of new records is the same of the original volume.
+			To emulate centralized click farming, we randomly inserted some gaussian-distributed transactions in the chosen collection.
 As for emulating the equalized click farmers, we simply doubled each record in the chosen collection to make the new distribution exactly the same as the original one, which is harder for the online platform to discover.
@@
 The first level is simply drawing a histogram aligned to time spans.
-The second level is to draw a histogram on the sub-volumes of each time span.
-For example, shown in Fig.~\ref{fig:histogram-example}, the first level histogram can be drawn by counting the number of hourly sales.
+The second level is to draw a histogram on the sub-volumes in each time span.
+For example, as shown in Fig.~\ref{fig:histogram-example}, the first level histogram can be drawn by counting the number of hourly sales.
 The frequencies of each bucket in 1st level histogram is: $\mathbb{F}=$\{0, 0, 0, 0, 0, 0, 0, 1, 13, 30, 37, 68, 60, 66, 72, 94, 75, 113, 127, 182, 165, 61, 0, 0\}.
@@
 
-			\begin{figure}[!ht]
+			\begin{figure}[!t]
 				\centering
@@
 			In order to test the performance of Algorithm~\ref{alg:dynamic}, every single collection was fed into the algorithm by the time order.
-Each collection input has a probability of $\alpha$ to be anomalous, namely, click farmed.
+Each input collection has a probability of $\alpha$ to be anomalous, namely, click farmed.
 The algorithm checks each collection with 1st or 2nd level histogram and give an answer of true or false.
@@
 
-		\subsection{Experiment on Raw Data}\label{sec:exp-raw}
+		\subsection{Experiments on Raw Data}\label{sec:exp-raw}
 			We first tested Algorithm~\ref{alg:dynamic} on raw data set in order to see whether and why the algorithm works.
-Due to desensitization process, time stamps in raw data set only tell which hour the transaction was committed.
+Due to desensitization process, time stamps in raw data set only tell which hour each transaction was committed.
 Thus, the histogram was drawn by counting hourly volume of each collection.
-For $\alpha = 0.2$, we select first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections.
-Equation(9) was employed as the threshold calculator.
-The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}, \textit{false positive rate} and \textit{accuracy} were recorded.
+For $\alpha = 0.2$, we selected first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections.
+Equation(5) in Table~\ref{tab:threshold-comparison} was employed as the threshold calculator.
+The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}(TPR), \textit{false positive rate}(FPR) and \textit{accuracy}(ACC) were recorded.
 
@@
 					\hline
-					& TPR & FAR & ACC & TPR & FAR & ACC\\
+					Level & TPR & FPR & ACC & TPR & FPR & ACC\\
 					\hline
-					1st Level & 100 & 4.05 & 96.72 & 26.64 & 28.03 & 62.49\\
+					1st & 100.00 & 4.05 & 96.72 & 26.64 & 28.03 & 62.49\\
 					\hline
-					2nd Level & 88.01 & 7.68 & 91.41 & 83.89 & 15.78 & 84.07\\
+					2nd & 88.01 & 7.68 & 91.41 & 83.89 & 15.78 & 84.07\\
 					\hline
@@
 Most of them escaped the security check under the perfect disguise.
-			But when it comes to 2nd level histogram, the ``clever disguise'' does not work any longer.
+			But when it comes to 2nd level histograms, the ``clever disguise'' does not work any longer.
 It can be clearly seen in Fig.~\ref{fig:raw-hist-2nd} that both types of click farming shows an obvious difference from the normal ones, while the normal ones still share a similar distribution.
@@
 		\subsection{Experiment on Synthetic Data}\label{sec:exp-synthetic}
-			As is put in the former section, every single record in the transaction set only gives a time stamp aligned at hours.
+			As is put in the former section, every single record in transaction collections gives only a time stamp aligned at hours.
 Part of the information was erased with the absence of minutes and seconds.
-In the following experiments, Every time stamp was assigned a random value for minutes and seconds.
+In the following experiments, every time stamp was assigned a random value for minutes and seconds.
 Therefore, the synthetic data set should be closer to the real world case.
@@
 Then, constant $c$ in equation(\ref{equ:step-size}) was also set to 0.5 given that the 2nd level histogram was also approximately a linear function.
-			We tested algorithm performance for $\alpha \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$, with $E_N$ and $E_A$ the same configuration as before.
-Results were shown in Table~\ref{tab:syn-result-1st} and~\ref{tab:syn-result-2nd}.
+			We tested algorithm performance for $\alpha \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$, with $\mathbb{E}_N$ and $\mathbb{E}_A$ the same configuration as before.
+Results are shown in Table~\ref{tab:syn-result-1st} and~\ref{tab:syn-result-2nd}.
 
@@
 				\centering
-				\caption{1st Level}
+				\caption{Classification on 1st Level Histogram}
 				\label{tab:syn-result-1st}
@@
 					\hline
-					$\alpha$ & TPR(\%) & FPR(\%) & ACC(\%) & TPR(\%) & FPR(\%) & ACC(\%) \\ 
+					$\alpha$ & TPR & FPR & ACC & TPR & FPR & ACC \\ 
 					\hline
@@
 				\centering
-				\caption{2nd Level}
+				\caption{Classification on 2nd Level Histogram}
 				\label{tab:syn-result-2nd}
@@
 			The result shows that the algorithm can efficiently distinguish the normal and anomalous data collections.
-No matter how much proportion of data is anomalous, the algorithm always gives a high accuracy.
-That is because the adaptive threshold was designed to minimize the number of total errors, which was irrelevant to TPR or FPR.
+No matter how much proportion in them is anomalous, the algorithm always gives a high accuracy.
+That is because the adaptive threshold was designed to minimize the number of total errors, which was not relevant directly to TPR or FPR.
 When $\alpha$ was increasing, there were less data collections added into $\mathbb{E}_N$.
@@
 Moreover, since $|\mathbb{E}_N| > |\mathbb{E}_A|$, it needs more collection instances for $|\mathbb{E}_N|$ then that for $|\mathbb{E}_A|$ to keep up to the trend.
-Therefore, it was faster of FPR to increase than TPR to increase.
+Therefore, it was faster of FPR to increase than that of TPR.
 As a result of that, there were more false alarms emerged and ACC went lower, as $\alpha$ increased from 0.1 to 0.5.
@@
 
-			Fig.~\ref{fig:roc-alpha} shows the ROC curve($\nu=1.0$) of the gaussian classifier dealing with centralized click farming with 1st level histograms and equalized manipulation with 2nd level histograms.
+			Fig.~\ref{fig:roc-alpha} shows the ROC curve of the gaussian classifier dealing with centralized click farming with 1st level histograms and equalized click farming with 2nd level histograms.
 The curves are pretty close to the upper left corner of the diagram and size under the curves are very large.
@@
 			In Fig.~\ref{fig:roc-magnitude}, we tested the classifier with different magnitude of centralised click farming.
-In former experiments, the manipulation of centralized click farming always creates as many new transaction records as the original ones.
-Let $\nu$ denote the magnitude coefficient, then $|D_{anomalous}| = (1 + \nu) |D_{normal}|$.
+In former experiments, $\nu = 1$.
 If $\nu $ is smaller, then it will be harder for the classifier to identify anomalous data collections since the anomalous distribution will be closer to normal ones.
 It can be concluded from the figure that the 1st level classifier can be efficient even when $\nu = 0.3$.
-However the 2nd level classifier is less sensitive when $\nu = 0.5$.
-That is because the 1st level histogram provides more probability entries than 2nd level histograms.
+However the 2nd level classifier is less sensitive.
+That is because the 1st level histogram provides more probability entries than 2nd level histograms do.
 Data collections are compressed from 1st to 2nd level.
@@
 		\subsection{Threshold Optimization}\label{sec:exp-threshold}
+			\begin{table*}[h]
+				\centering
+				\caption{F1 Scores of Different Threshold Calculators}
+				\label{tab:threshold-comparison}
+				\begin{tabular}{|c|c|c|c|}
+					\hline
+					& Equation & Synthetic & Gaussian \\ 
+					\hline
+					1 & $\displaystyle T = \frac{\mu_n \sigma_a + \mu_a \sigma_n}{\sigma_a + \sigma_n}$& 1.0588 & 0.5810 \\ 
+					\hline
+					2 & $\displaystyle T = \frac{\mu_n \sigma_a (1 - \alpha) + \mu_a \sigma_n \alpha}{\sigma_a (1 - \alpha) + \sigma_n \alpha}$& 0.7688 & 0.3515 \\ 
+					\hline
+					3 & $\displaystyle T = \frac{\mu_n \sigma_a \sqrt{1 - \alpha} + \mu_a \sigma_n \sqrt{\alpha}}{\sigma_a \sqrt{1 - \alpha} + \sigma_n \sqrt{\alpha}}$& 0.8158 & 0.4510 \\ 
+					\hline
+					4 & $\displaystyle 
+					T = \frac{\mu_n \sigma_a ln(1 - \alpha)
+						+ \mu_a \sigma_n ln\alpha}
+					{\sigma_a ln(1 - \alpha) + \sigma_n ln\alpha}
+					$& 1.5227 & 0.5523 \\ 
+					\hline
+					5 & $\displaystyle 
+					T = \frac{\mu_n \sigma_a \sqrt{-ln(1 - \alpha)}
+						+ \mu_a \sigma_n \sqrt{-ln\alpha}}
+					{\sigma_a \sqrt{-ln(1 - \alpha)} + \sigma_n \sqrt{-ln\alpha}}
+					$& \color{blue}\textbf{2.6013} & 0.5791 \\ 
+					\hline
+					6 & $\displaystyle 
+					T = \frac{\mu_n \sigma_a ln\sqrt{1 - \alpha}
+						+ \mu_a \sigma_n ln\sqrt{\alpha}}
+					{\sigma_a ln\sqrt{1 - \alpha} + \sigma_n ln\sqrt{\alpha}}
+					$& 1.4155 & 0.5578 \\ 
+					\hline
+					7 & $\displaystyle 
+					T = \frac{\mu_n \sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|}
+						+ \mu_a \sqrt{|ln(\sigma_n \alpha)|}}
+					{\sqrt{|ln\big[\sigma_a (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_n \alpha)|}}
+					$& 2.2730 & 0.5600 \\ 
+					\hline
+					8 & $\displaystyle 
+					T = \frac{\mu_n ln\sqrt{\sigma_a (1 - \alpha)}
+						+ \mu_a ln\sqrt{\sigma_n \alpha}}
+					{ln\sqrt{\sigma_a (1 - \alpha)} + ln\sqrt{\sigma_n \alpha}}
+					$& 2.0753 & 0.2808 \\ 
+					%\hline
+					\hline
+					9 & $\displaystyle T = \mathop{\arg\min}_{\mu_n \le T \le \mu_a}\ \alpha \cdot \int_{0}^{T}PDF_a(x)dx + (1 - \alpha) \cdot \int_{T}^{log_k2}PDF_n(x)dx$ & 1.9300 & \color{blue}\textbf{0.6072}\\
+					\hline
+				\end{tabular} 
+			\end{table*}
+
 			Section~\ref{sec:alg-threshold} mentions only two equations for calculating adaptive thresholds.
@@
 90K and 10K data points were sampled from 500 pairs of random gaussian distributions which represent normal and anomalous distributions respectively, yielding 500 F1 scores for each equation.
-We compared the average score and discovered that equation 13 gives the best result.
+We compared the average score and discovered that equation 9 gives the best result.
 
-			Equation 13 gives best classification result for two gaussian distributions but does not outperform others in real world data.
+			Equation 9 gives best classification result for two gaussian distributions but does not outperform others in real world data.
 Part of the reasons are mentioned in section~\ref{sec:alg-threshold}.
@@
 
-			\begin{table*}[!t]
-				\centering
-				\caption{F1 Scores of Different Threshold Calculators}
-				\label{tab:threshold-comparison}
-				\begin{tabular}{|c|c|c|c|}
-					\hline
-					& Equation & Synthetic & Gaussian \\ 
-					\hline
-					1 & $\displaystyle T = \frac{\sigma_B \mu_A + \sigma_A \mu_B}{\sigma_B + \sigma_A}$& 1.0588 & 0.5810 \\ 
-					\hline
-					2 & $\displaystyle T = \frac{\sigma_B (1 - \alpha) \mu_A + \sigma_A \alpha \mu_B}{\sigma_B (1 - \alpha) + \sigma_A \alpha}$& 0.7688 & 0.3515 \\ 
-					\hline
-					3 & $\displaystyle T = \frac{(\sigma_B \sqrt{1 - \alpha}) \mu_A + (\sigma_A \sqrt{\alpha}) \mu_B}{\sigma_B \sqrt{1 - \alpha} + \sigma_A \sqrt{\alpha}}$& 0.8158 & 0.4510 \\ 
-					\hline
-					4 & $\displaystyle 
-					T = \frac{\big[\sigma_B ln(1 - \alpha)\big] \mu_A
-						+ \big[\sigma_A ln\alpha\big] \mu_B}
-					{\sigma_B ln(1 - \alpha) + \sigma_A ln\alpha}
-					$& 1.5227 & 0.5523 \\ 
-					\hline
-					5 & $\displaystyle 
-					T = \frac{\mu_A \sigma_B \sqrt{-ln(1 - \alpha)}
-						+ \mu_B \sigma_A \sqrt{-ln\alpha}}
-					{\sigma_B \sqrt{-ln(1 - \alpha)} + \sigma_A \sqrt{-ln\alpha}}
-					$& \color{blue}\textbf{2.6013} & 0.5791 \\ 
-					\hline
-					6 & $\displaystyle 
-					T = \frac{\mu_A \sigma_B ln\sqrt{1 - \alpha}
-						+ \mu_B \sigma_A ln\sqrt{\alpha}}
-					{\sigma_B ln\sqrt{1 - \alpha} + \sigma_A ln\sqrt{\alpha}}
-					$& 1.4155 & 0.5578 \\ 
-					\hline
-					7 & $\displaystyle 
-					T = \frac{\mu_A \sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|}
-						+ \mu_B \sqrt{|ln(\sigma_A \alpha)|}}
-					{\sqrt{|ln\big[\sigma_B (1 - \alpha)\big]|} + \sqrt{|ln(\sigma_A \alpha)|}}
-					$& 2.2730 & 0.5600 \\ 
-					\hline
-					8 & $\displaystyle 
-					T = \frac{\mu_A ln\sqrt{\sigma_B (1 - \alpha)}
-						+ \mu_B ln\sqrt{\sigma_A \alpha}}
-					{ln\sqrt{\sigma_B (1 - \alpha)} + ln\sqrt{\sigma_A \alpha}}
-					$& 2.0753 & 0.2808 \\ 
-					%\hline
-					\hline
-					9 & $\displaystyle T = \mathop{\arg\min}_{\mu_A \le T \le \mu_B}\ \alpha \cdot \int_{-\infty}^{T}P_B(x)dx + (1 - \alpha) \cdot \int_{T}^{+\infty}P_A(x)dx$ & 1.9300 & \color{blue}\textbf{0.6072}\\
-					\hline
-				\end{tabular} 
-			\end{table*}
-
 	\section{Conclusion \& Future Work}\label{sec:conclusion}
-		This paper proposed an dynamic collective anomaly detection algorithm with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
-Different from existing algorithms detecting collective anomalies, our approach employs statistical distance as the similarity measurement, mapping data collections to a restricted one dimensional space.
+		This paper proposed an dynamic collective anomaly detection technique with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
+Different from existing algorithms designed for collective anomalies, our approach employs statistical distance as the similarity measurement, mapping data collections to a restricted one dimensional space.
 We explored several technical points involved in the design of the algorithm and performed a thorough experiment to test its efficiency.
-It showed that the algorithm can efficiently discover anomalies within the data sequences and the classifier is sensitive enough toward real world data manipulations.
+It showed that the algorithm can efficiently discover anomalies within the data collections and the classifier is sensitive enough toward real world data manipulations.
 

### 2017-09-28 RealWorld/SamplePDF.py

@@ -6,31 +6,31 @@ import matplotlib.pyplot as plt
 import matplotlib.axis as ax
 
 days = (5, 113, 287)
-lim_x = 40
-lim_y = 0.3
+lim_x = 24
+lim_y = 0.25
 
-figure = plt.figure(figsize=(9, 9), dpi=100)
+figure = plt.figure(figsize=(7, 7), dpi=100)
 for ii in range(3):
     day = days[ii]
     reader = csv.reader(open("Correct/%d.csv" % day, 'r'))
     reader_cen = csv.reader(open("Centralized/%d.csv" % day, 'r'))
     reader_equ = csv.reader(open("Equalized/%d.csv" % day, 'r'))
 
-    freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), step=1)
-    freq_cen, dropped = Divergence.histogram(list(int(row[2]) for row in reader_cen), step=1)
-    freq_equ, dropped = Divergence.histogram(list(int(row[2]) for row in reader_equ), step=1)
-
-    data = freq.values()
-    data_cen = freq_cen.values()
-    data_equ = freq_equ.values()
-    step = 21.48
-
-    # data = list(int(row[2]) for row in reader)
-    # data_cen = list(int(row[2]) for row in reader_cen)
-    # data_equ = list(int(row[2]) for row in reader_equ)
+    # freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), step=1)
+    # freq_cen, dropped = Divergence.histogram(list(int(row[2]) for row in reader_cen), step=1)
+    # freq_equ, dropped = Divergence.histogram(list(int(row[2]) for row in reader_equ), step=1)
     #
-    # step = 1
-    #
+    # data = freq.values()
+    # data_cen = freq_cen.values()
+    # data_equ = freq_equ.values()
+    # step = 21.48
+
+    data = list(int(row[2]) for row in reader)
+    data_cen = list(int(row[2]) for row in reader_cen)
+    data_equ = list(int(row[2]) for row in reader_equ)
+
+    step = 1
+
     dropped, hist = Divergence.histogram(data, step)
     droped, hist_cen = Divergence.histogram(data_cen, step)
     dropped, hist_equ = Divergence.histogram(data_equ, step)
@@ -50,7 +50,7 @@ for ii in range(3):
         plt.yticks(())
     else:
[…]

### 2017-09-28 RealWorld/ShowOverview.py

@@ -14,28 +14,30 @@ jsd2 = [0.10912704201369046, 0.19845387518896526, 0.06636123715181373, 0.2296597
 jsd_cen2 = [0.32256760379361726, 0.3810239639317933, 0.28386663245410493, 0.35230754830673466, 0.28189384029941755, 0.2990176428977388, 0.24311679125495256, 0.3692207262558338, 0.34815422147146746, 0.3086180294974303, 0.2190867719629146, 0.2944877706533938, 0.23662774226146438, 0.3309871042516204, 0.43175927961812877, 0.35225026853698854, 0.3506640374165292, 0.25018682290870126, 0.2018944636423843, 0.19958628735050707, 0.2511881602458358, 0.21825640670517163, 0.3277881493146352, 0.23731398417432872, 0.2651893172458749, 0.25987672849498034, 0.1981169965350415, 0.3305360563766058, 0.3013549901242266, 0.28440338403422183, 0.28229077822524445, 0.24597592507096025, 0.2689289289249557, 0.26723613384157013, 0.26051423720450034, 0.4598711221548436, 0.29199940349935083, 0.2251773592006137, 0.22380082229940482, 0.2459725847967571, 0.32849376864464885, 0.1908232890968055, 0.31989906513324307, 0.32991462184432313, 0.31619989409047616, 0.29599589101452783, 0.33142278114623064, 0.2800054579791898, 0.3281902150886128, 0.3242061842283341, 0.28508548123760513, 0.3165442627196493, 0.29439248623540115, 0.280880018188317, 0.4402812786150543, 0.22841474211560983, 0.3752587645937397, 0.250537545003473, 0.236924835544984, 0.143041665652949, 0.19756006910399015, 0.20170043820336014, 0.22989958013678133, 0.20357673808875332, 0.2823378671559504, 0.3020928363649714, 0.18589749572654715, 0.31343670974684334, 0.2337374009942335, 0.30641242467725643, 0.31438688575758694, 0.3663003586378917, 0.26690527231045974, 0.290334571377121, 0.27951540668418196, 0.24195819156521706, 0.2637679765623775, 0.2926738393659329, 0.2649750293539159, 0.2541129910728474, 0.23056036822725479, 0.2420132797701976, 0.26567316524371415, 0.2340119173868865, 0.2763747331629617, 0.34789842920122444, 0.26551206992806975, 0.2970711176190934, 0.2785566291322321, 0.2586713412063521, 0.2996400865965023, 0.2553
[…]

### 2017-09-28 Synthetic/PlotROC.py

@@ -2,83 +2,83 @@ import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
-# alphas = [0.1, 0.3, 0.5, 0.7, 0.9]
-# TPRs1 = [
-#     [1, 0.99, 0.828, 0.556, 0.263],
-#     [1, 0.989, 0.827, 0.424, 0.28],
-#     [1, .993, .771, .579, .281],
-#     [1, .991, .717, .473, .276],
-#     [1, .97, .686, .5, .318]
-# ]
-# FPRs1 = [
-#     [0.165, 0.018, 0.006, 0.008, 0.004],
-#     [0.17, 0.015, 0.007, 0.006, 0.003],
-#     [.16, .015, .014, .005, .007],
-#     [.104, .004, .01, .007, 0],
-#     [.127, .023, .004, .013, 0]
-# ]
-#
-# TPRs2 = [
-#     [1, 1, .867, .655, .346],
-#     [1, 1, .833, .357, .085],
-#     [1, 1, .770, .188, .048],
-#     [1, 1, .832, .090, .028],
-#     [1, 1, 1, .215, .015]
-# ]
-# FPRs2 = [
-#     [.376, .064, .008, 0, 0],
-#     [.386, .076, .001, 0, 0],
-#     [.357, .108, .014, 0, 0],
-#     [.352, .146, .040, .047, .012],
-#     [.346, .111, .059, .080, 0]
-# ]
-
-news = [0.1, 0.2, 0.3, 0.4, 0.5]
+alphas = [0.1, 0.3, 0.5, 0.7, 0.9]
 TPRs1 = [
-    [1, .92279, .80455, .62685, .45796, .24602, 0],
-    [1, .93594, .82058, .69506, .5223, .43642, 0],
-    [1, .93685, .84652, .70603, .62435, .47604, 0],
-    [1, .93213, .90753, .75155, .64573, .54155, 0],
-    [1, .95324, .83864, .81978, .70387, .64501, 0]
+    [1, 0.99, 0.828, 0.556, 0.263],
+    [1, 0.989, 0.827, 0.424, 0.28],
+    [1, .993, .771, .579, .281],
+    [1, .991, .717, .473, .276],
+    [1, .97, .686, .5, .318]
 ]
 FPRs1 = [
-    [1, .88467, .6608, .39672, .27765, .13462, 0],
-    [1, .86863, .46568, .2513, .13393, .05964, 0],
[…]

### 2017-10-01 Paper/Template/paper.tex
Modify

@@
 \usepackage{color}
+\usepackage{flushend}
 %
@@
 	% separate superscript on following line from affiliation using narrow space
-	$^{\#}$\,School of Software Engineering, Shanghai Jiao Tong University\\
-	No.800 Dongchuan Rd. Shanghai, 200240, China\\
+	$^{\#}$\,School of Software, Shanghai Jiao Tong University\\
+	Shanghai, 200240, China\\
 	\fontsize{9}{9}\selectfont\ttfamily\upshape
@@
 	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
-	$^{1}$\,solftwarewry@sjtu.edu.cn\\
+	$^{1}$\,trams.wang.ruoyu@gmail.com\\
 	$^{3}$\,li.g@sjtu.edu.cn%

### 2017-10-01 Paper/Template/paper.tex
Add comparison section

@@
 %
-\title{Dynamic Anomaly Detection for Collective Data via Statistical Distance}
+\title{Statistical Detection of Collective Data Anomalies}
 %
@@
 	% author names are typeset in 11pt, which is the default size in the author block
-	{Ruoyu Wang{\small $~^{\#1}$}, Daniel Sun{\small $~^{*2}$}, Guoqiang Li{\small $~^{\#3}$} }%
+	{Ruoyu Wang{\small$^{1}$}, Daniel Sun{\small$^{2}$}, Guoqiang Li{\small$^{1*}$} }%
 	% add some space between author names and affils
@@
 	% separate superscript on following line from affiliation using narrow space
-	$^{\#}$\,School of Software, Shanghai Jiao Tong University\\
-	Shanghai, 200240, China\\
+	$^{1}$\,School of Software, Shanghai Jiao Tong University, China\\
 	\fontsize{9}{9}\selectfont\ttfamily\upshape
@@
 	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
-	$^{1}$\,trams.wang.ruoyu@gmail.com\\
-	$^{3}$\,li.g@sjtu.edu.cn%
+	\{solftwarewry,li.g\}@sjtu.edu.cn
 	% add some space between email and affil
@@
 	% separated superscript on following line from affiliation using narrow space \,
-	$^{*}$\,Data61, Commonwealth Scientific and Industrial Research Organization, Australia\\
+	\,Data61, CSIRO, Australia\\
 	\fontsize{9}{9}\selectfont\ttfamily\upshape
@@
 		can they steal chunks of data and hold them for ransom, but
-		also alter key information contained in those systems, setting up
+		also alter data contained in those systems, setting up
 		traps hard to discover and causing damages unlikely to recover.
-		Although altering single record may not oblige correct value scope such that it is hard to detect, the change, especially to a subset of data, can be observed and detected in a collective
-		scale. In this paper, we present a collective anomaly
+		Without referring to data source, it is hard to detect a single record that is alerted but still remain in correct value scopes.
+However, the change, especially to a subset of data, can be observed and detected in a collective scale.
+		In this paper, we present a collective
 		detection technique based on statistical distance. The technique
@@
 		collective anomalies. In order to adapt to data dynamics, our technique continuously evaluates 
-		metrics as evolving features. Aiming at broad generalisation, this
-		technique can replace several components of our solution to further improve the
-		performance of detection for various scenarios. To illustrate details of the technique
+		metrics as evolving features. To be general, our
+		technique is designed to be adaptive for various scenarios. To illustrate details of the technique
 		and explore its efficiency, we case-studied a real
@@
 	\section{Introduction}
-		Major improvements in data acquisition, transmission and storage are driving increased data availability and affordability.
+		Major improvements in data acquisition, transmission and storage are to increase data availability and affordability.
 Currently, there are totally 2.7ZB data in the digital universe~\cite{bigDataStatistics} and the growing speed is doubling every two years.
-		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
-		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those occurred at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years.
-And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}.
-System configuration problems, as a matter of fact, are also responsible for the disturbing situation.
-They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.
-
+		It has already been hard and will be much harder in the future to harness the exploding volume of data that has resulted in many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
 	Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\cite{saha2014data}.
-Those data anomalies may arise due to both internal and external reasons with respect to a certain system.
-On one hand, components inside the system may generate problematic source data.
+Those data anomalies may arise due to both internal and external reasons.
+On one hand, components inside systems may generate problematic source data.
 For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\cite{rassam2014adaptive}.
@@
 Malicious insiders even deliberately modify system configurations for fatal compromises~\cite{schuster2015vc3}.
-A study~\cite{humanError} found that 65\% of organizations state that human errors are the main  cause of data problems.
-
+A study shows that 65\% of organizations state that human errors are the main  cause of data problems~\cite{humanError} .
 		On the other hand, data manipulation~\cite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability.
 \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
-		If data inside the system is compromised, they will severely affect mining and learning algorithms and further change the final decision given by the entire system.
+		If data is compromised, it will severely affect mining and learning algorithms and further change the final decision driven by the data.
 In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.
 
-		However, from the aspect of data itself, we can still detect malicious data manipulation behaviours.
+It is hard to detect a single record that is alerted but still remain in correct value scopes, but if many data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
 		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution.
-With the reshaping measurable, we can enclose data collections with similar distribution patterns inside the same cluster and filter out those strange shaped ones.
+For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones.
 In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions.
@@
 Then a gaussian classifier can be applied to detect outliers derived from manipulated data.
-To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence.
-And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.
-		Details of the technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.
+\textcolor{red}{[This is not clear at all.
+Why sets == windows?
+Also the whole paragraph fails to tell a clear story especially what you did and why you did.
+Moreover, you need to outline your contributions explicitly] To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence.
+And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.}
+	The details of our technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.
 
-		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related works on data anomaly detection and describes a real world problem.
+		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related work on data anomaly detection and describes a real world problem.
 Section~\ref{sec:preliminaries} introduces statistical distance.
-Details of the technique are proposed in section~\ref{sec:algorithm-details}.
-Then section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm.
-Finally, all contents are concluded and discussed in section~\ref{sec:conclusion}.
+The details of the proposed technique are introduced in Section~\ref{sec:algorithm-details}.
+Then Section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm.
+Finally, the paper is concluded and discussed in Section~\ref{sec:conclusion}.
 
@@
 			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.
-According to a comprehensive study in~\cite{chandola2009anomaly}, anomaly detection algorithms deal with input data in the form of points(or records), sequences, graphs and spatial relationships, where point data is the simplest and well studied, others are attracting more attention in new studies.
+According to a comprehensive study in~\cite{chandola2009anomaly}, anomaly detection algorithms deal with input data in the form of points (or records), sequences, graphs and spatial relationships, where point data is the simplest and well studied, and the others are attracting more attention in new studies.
 
-			Prevalent anomalies can be classified into \textit{point anomalies}, \textit{contextual(or conditional) anomalies} and \textit{collective anomalies}.
+			Prevalent anomalies can be classified into \textit{point anomalies}, \textit{contextual (or conditional) anomalies} and \textit{collective anomalies}.
 Point anomaly refers to an individual data instance that is considered anomalous with respect to others.
 But if it is anomalous only in certain circumstances or a specific context, the instance is regarded as contextual anomaly.
-If a group of related data instances(e.g.
-a segment of sequence) is anomalous with respect to other groups in the data set(e.g.
+If a group of related data instances, e.g.a segment of sequence, is anomalous with respect to other groups in the data set (e.g.
 the entire sequence), it is called a collective anomaly~\cite{goldberger2000components}.
@@
 			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection.
-As the name suggests, supervised detection methods train models on completely labeled data while unsupervised detection leverages data without any labeling.
+As the name suggests, supervised detection methods train models on completely labeled data, while unsupervised detection leverages data without any labeling.
 Semi-supervised detection approaches train model on data that has labeled instances for only the normal class.
-Supervised detection is commonly applied when both normal and anomalous data can be obtained.~\cite{fujimaki2005approach} When it comes to the circumstances that anomalous data is hard to obtain or there exist too many types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
-
+Supervised detection is commonly applied when both normal and anomalous data can be obtained~\cite{fujimaki2005approach}.
+When it comes to the circumstances that anomalous data is hard to obtain or there exist too many types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.
 			To make the final decision, detection algorithms mostly yield a score from each input instance, denoting how likely it is anomalous.
-The algorithm then selects top few as anomalies or compare the score with a threshold.
-Or, detection algorithms output a label on each instance, then decide whether each label belongs to the normal class.
-
-			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} algorithms seize most attention.
+An algorithm then selects top few as anomalies or compare the scores with a threshold, or outputs a label on each instance, and then decides whether each label belongs to the normal class.
+			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} catch most attention.
 Others adopted tree isolation~\cite{zhang2017lshiforest}, model based~\cite{yin2016model} and statistical methods~\cite{zhu2002statstream} in certain applications.
 
-			To detect collective anomalies,~\cite{caudell1993adaptive} adopted the \textit{ART(Adoptive Resonance Theory)} neural networks to detect time-series anomalies.
+			To detect collective anomalies,~\cite{caudell1993adaptive} adopts the \textit{ART (Adoptive Resonance Theory)} neural networks to detect time-series anomalies.
 \textit{Box Modeling} is proposed in ~\cite{chan2005modeling}.
-And \textit{Longest Common Subsequence} was leveraged in ~\cite{budalakoti2006anomaly} as similarity metric for symbolic sequence.
+\textit{Longest Common Subsequence} was leveraged in~\cite{budalakoti2006anomaly} as similarity metric for symbolic sequence.
 Markovian modeling techniques are also popular in this domain\cite{ye2000markov,warrender1999detecting,pavlov2003sequence}.
-\cite{yu2015glad} depicted groups in social media as combinations of different ``roles'' and compare groups according to the proportion of each role within each group.
+\cite{yu2015glad} depicts groups in social media as combinations of different ``roles'' and compare groups according to the proportion of each role within each group.
 
@@
 Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products.
-Under the super-pressure caused by massive competitors, most of the sellers choose to use some cheating techniques to raise reputation and product sale volumes, then improve rankings in search lists.
+Under the super-pressure caused by massive competitors, a number of the sellers choose to use some cheating techniques to raise reputation and sale volumes, then improve rankings in search lists.
 
@@
 
-			A research performed in China showed that 81.9\% of the people investigated had heard of the behaviour of click farming, 51.2\% of them had seen people around them click farmed and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}.
+			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% of them had seen \textcolor{red}{people around them click farmed ????}and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}.
 American researchers reported in 2015 that over 11000 sellers were detected to have click farmed records and only 2.2\% of 4000 investigaed sellers had been penalized because of the cheating attempts~\cite{netease2015research}.
+\textcolor{red}{in which market?}
 
@@
 
-			Although it is hard to classify users as honest and malicious, we can still find clues from the sellers' aspect.
-For normal sellers, their customers are usually similar since choices of products are seldom changed.
-Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable.
-No matter how much alike between honest users and robots or the employed workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
-To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records and emulated the circumstances if it had been click farmed(see section~\ref{sec:exp-methodology}).
-Fig.~\ref{fig:example-ecdf} shows the difference between normal and click farmed distributions of one day in the data set.
-			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
-
-			\begin{figure}[!t]
+			\begin{figure}[ht]
 				\centering
@@
 
+			Although it is hard to classify users as honest and malicious, we can still find clues from the sellers' aspect.
+For normal sellers, their customers are usually similar since choices of products are seldom changed.
+Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable.
+No matter how much alike between honest users and robots or the employed workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
+To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records and emulated the circumstances if it had been click farmed (see section~\ref{sec:exp-methodology}).
+Fig.~\ref{fig:example-ecdf} shows the difference between normal and click farmed distributions of one day in the data set.
+			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
+
 	\section{Preliminaries}\label{sec:preliminaries}
@@
 		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
-Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers:
+Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers\textcolor{red}{wrong!
+how about 0?}:
 		\begin{equation}
@@
 	\section{Statistical Detection}\label{sec:algorithm-details}
-		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records in a collection of data.
+		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records.
 For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
-Manipulation on those data(e.g.
-Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm.
-Main idea of the solution is simple.
-But there are several difficulties to be solved in the specific design and implementation of the technique:
+Manipulation on those data (e.g.
+Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger an alarm.
+There are some difficulties in the specific design and implementation of the technique:
 
 		\begin{enumerate}
-			\item Are the corresponding one-dimensional points distinguishable after mapping form normal and anomalous distributions? And which classifier is efficient towards those points?
+			\item Are the corresponding one-dimensional points distinguishable after mapping betweem normal and anomalous distributions? And which classifier is efficient towards those points?
 			\item Is there a general approach that can effectively depict different distributions in various circumstances?
-			\item What classifier specific metric should be adopted to filter out anomalies? Can it be further optimized?
+			\item What classifier-specific metric should be adopted to filter out anomalies? Can it be further optimized?
 			\item Online shops are often in the process of expanding or dwindling.
@@
 Then \ref{sec:alg-threshold} gives an analysis about adaptive metric that minimizes total error.
-And a dynamic framework is proposed in~\ref{sec:alg-dynamic}.
+A dynamic framework is proposed in~\ref{sec:alg-dynamic}.
 
 		\subsection{Divergence-Based Collective Anomaly Detection}\label{sec:alg-basic}
-			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions.
+			From Section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions.
 In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the divergence between two connected nodes.
@@
 This may work if anomalous nodes do not compose a large proportion.
-However the procedure will be too complicated to work out with large amounts of data collections.
+However the procedure will be too complicated to work out with large amounts of data.
 
-			Otherwise we need a frame of reference that provides absolute coordinates rather than the relative ones.
+			Alternatively we need a frame of reference that provides absolute coordinates rather than the relative ones.
 Therefore, we should keep an evidence set $\mathbb{E}$ which consists of several correct distributions that have already been given.
@@
 
-			Fig.~\ref{fig:raw-overview} in section~\ref{sec:exp-raw} demonstrates the result of the above process.
-Red dots refer to the distances calculated from normal data collections, blue and green ones are from click farmed data collections.
+			Fig.~\ref{fig:raw-overview} in Section~\ref{sec:exp-raw} demonstrates the result of the above process.
+Red dots refer to the distances calculated from normal data collections, blue and green ones are from click-farmed data collections.
 Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value.
@@
 
-			Let $\mathbb{S}$ be set of the daily transaction collections, if $\mathbb{E}$ is already given, we can run the algorithm with $\mathbb{E}$ and $\forall D \in \mathbb{S}$ and discover the anomalies.
+			Let $\mathbb{S}$ be set of the daily transaction collections, if $\mathbb{E}$ is already given, we can run the algorithm with $\mathbb{E}$ and $\forall D \in \mathbb{S}$, and then discover the anomalies.
 JSD here cannot be replaced by KLD since entries in $P'$ are not necessarily defined in $M$.
@@
 Therefore, $\mu$ should be slightly larger than zero.
-The reason why $\mu$ cannot be exactly zero is hidden in line~\ref{line:population-estimation}.
+The reason why $\mu$ cannot be exactly zero is in Line~\ref{line:population-estimation}.
 			For $\mu = 0$ if and only if $J_i = 0$ for $\forall i = 1, \dots, n$, which is equivalent to $P_i = P_j$ for $\forall i, j = 1, \dots, n$.
@@
 But the computational cost will be much higher than applying a coarse histogram approximation.
-			Moreover, even if we applied a distribution model upon a collection of sampled data, yielding more accurate results, the computation of divergence will be much more complex on continuous functions than discrete distributions.
+			Moreover, even if we could apply a distribution model upon a collection of sampled data, yielding more accurate results, the computation of divergence would be much more complex on continuous functions than discrete distributions.
 
@@
 
-			In order to generate an accurate approximation, step size is the most important parameter the algorithm should determine.
-If the size is too small then the resulting histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape.
+			In order to generate an accurate approximation, the step size is the most important parameter the algorithm should determine.
+If the size is too small then the histogram will be over fitting; but if the size is too large then the estimation will be too coarse to depict the original shape.
 According to statistics theory, when dealing with a sample size of $k$, a step size of
-
 			\begin{equation}\label{equ:step-size}
-				l = c \sigma k^{-0.2}
+				l = c \sigma k^{-0.2},
 			\end{equation}
-
-			will give a best partition size, where $c$ is a constant relative to the shape of distribution(e.g.
+			which will give a best partition size, where $c$ is a constant relative to the shape of distribution (e.g.
 for normal distribution, $c=1.05$).
@@
 
-			A naive but prevalent approach is to set a fixed value as threshold.
+			A naive but prevalent approach is to set a fixed value as the threshold.
 This approach is easy to implement and may give satisfying results in specific cases.
 However, a fixed threshold requires specific analysis in the certain scenario, manual observation and tuning of parameters, which involves lots of human labour.
-The rule of ``$3 \sigma$'' can be used to automatically determine a threshold.
-But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimal when concrete data is provided.
+The rule of ``$3 \sigma$'' \textcolor{red}{need citation or simple explanation here}can be used to automatically determine a threshold.
+But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided.
 It would be either higher than the optimum if anomalous data lies far away from the normal cluster, or lower than the optimum if the anomalies sit close to the cluster centre.
@@
 				\includegraphics[width=\linewidth]{fig/JSD-Dist.png}
-				\caption{Distribution of JSD values for everyday data collection. It can be approximately regarded as a gaussian distribution.}
+				\caption{Distribution of JSD values for everyday data collection. }
 				\label{fig:jsd-dist}
@@
 
-			However, applying divergence as the distance measurement among data collections provides a fine property.
+			Fortunately, applying divergence as the distance measurement among data collections provides a fine property.
 That is, divergences of normal data collections assemble together, forming a quasi-gaussian distribution.
-And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side to the other one on the real number axis.
-As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error(Fig.~\ref{fig:jsd-dist}).
+And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side to the other one on the real line.
+As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error (Fig.~\ref{fig:jsd-dist}).
 That is due to the unknown randomness within real world data.
-Few assumptions can be applied in real world data sets, let alone data volume is sometimes relatively low.
+Few assumptions can be applied in real world data sets, no mention that data volume is sometimes relatively low.
 This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model.
-However, in the scenarios that better models can be calculated, distributions here can be replaced to produce better results.
-For the simplicity of our proposal, we assume the distributions of JSDs to be gaussian.
+\textcolor{red}{WHAT do you want to say here? This sentence seems weird. However, in the scenarios that better models can be calculated, distributions here can be replaced to produce better results. }
+For the simplicity of our proposal, we deem the distributions of JSDs to be gaussian.
 
@@
 
-			As shown in Fig~\ref{fig:example-threshold}, the black curve($PDF_{normal}(x)$ or in short $PDF_n(x)$) displays the probability density function(PDF) fitting those JSDs calculated from normal data collections; the blue curve($PDF_{anomalous}(x)$ or in short $PDF_a(x)$) displays the PDF derived from anomalous data collections.
+			As shown in Fig~\ref{fig:example-threshold}, the black curve ($PDF_{normal}(x)$ or in short $PDF_n(x)$) displays the probability density function (PDF) fitting those JSDs calculated from normal data collections; the blue curve ($PDF_{anomalous}(x)$ or in short $PDF_a(x)$) displays the PDF derived from anomalous data collections.
 Threshold is chosen to minimize total errors(both false negative and false positive).
@@
 			Then the optimal threshold $T$ is:
-
 			\begin{equation}\label{equ:linear-weight}
@@
 
-			According to equation(\ref{equ:linear-weight}), threshold value can be automatically determined.
-The optimal threshold will minimize total errors, yielding an optimal outcome.
-The only requirement for this technique is another evidence set containing data point derived from anomalous data collections.
+			According to E.q.(\ref{equ:linear-weight}), the threshold value can be automatically determined.
+The optimal threshold will minimize total errors and yield an optimal outcome.
+\textcolor{red}{The only requirement for this technique is another evidence set containing data point derived from anomalous data collections.}
 
-			However, this is not accurate enough, since equation(\ref{equ:linear-weight}) implicates an assumption that the chances are the same for a new data collection to be either anomalous or not.
+			However, this is not accurate enough, since equation (\ref{equ:linear-weight}) implicates an assumption that the chances are the same for a new data collection to be either anomalous or not.
 If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as:
-
 			\begin{equation}\label{equ:linear-balanced}
@@
 
-			Where $\alpha$ is the anomaly probability. Equation(\ref{equ:linear-balanced}) is much more complicated. But it can be reduced to a quadratic equation.
+			Where $\alpha$ is the anomaly probability. E.q.(\ref{equ:linear-balanced}) is much more complicated. But it can be reduced to a quadratic equation.
 			Section~\ref{sec:exp-threshold} compares some estimations for optimal threshold under a real world circumstance.
@@
 		\subsection{Dynamic DCAD}\label{sec:alg-dynamic}
-			In Algorithm~\ref{alg:static}, there is a hidden assumption that it regards every data collection to be sampled from a static environment.
+Algorithm~\ref{alg:static} regards every data collection to be sampled from a static environment.
 That is to say the seller will never change his or her products and customer volumes always remain the same.
@@
 To meet the need, a sliding window technique has been applied to the basic algorithm frame work.
-And considering discussion in section~\ref{sec:alg-histogram} and~\ref{sec:alg-threshold}, a dynamic version is proposed in Algorithm~\ref{alg:dynamic}.
+Thus, considering discussion in section~\ref{sec:alg-histogram} and~\ref{sec:alg-threshold}, a dynamic version is proposed in Algorithm~\ref{alg:dynamic}.
 
@@
 
-			Note that line~\ref{line:hist-1} and~\ref{line:hist-2} can be replaced by other estimation methods if better assumptions can be made.
+			Note that Line~\ref{line:hist-1} and~\ref{line:hist-2} can be replaced by other estimation methods if better assumptions can be made.
 Line~\ref{line:gaussian-1} and~\ref{line:gaussian-2} can be replaced by other models for more accuracy.
@@
 	\section{Evaluation}\label{sec:evaluation}
-		The algorithm was implemented and interpreted in Python 3.6. All experiments was tested on Ubuntu 17.04. In the following experiments, we would like to figure out:
+		Our algorithm was implemented and interpreted in Python 3.6. All experiments were tested on Ubuntu 17.04. In the following experiments, we would like to figure out:
 
@@
 		\subsection{Methodology}\label{sec:exp-methodology}
-			We adopted a data set containing Taobao online sellers' transaction records\footnote{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition where all records are collected from the real world business scenarios and are desensitized.
+			We adopted a data set containing Taobao online sellers' transaction records\footnote{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} provided by Alibaba Tian Chi big data competition where all records are collected from the real world business scenarios.
 The data package contains seller features data set, user payments data set and user browsing behaviour data set.
@@
 
-			We randomly chose one seller(ID: 1629) and extracted transaction history of this seller, records ranging from Nov.
+			We randomly chose one seller (ID: 1629) and extracted transaction history of this seller, records ranging from Nov.
 11th 2015 to Oct.
@@
 
-			Click farmed data was generated according to patterns described in section~\ref{sec:related-realworld}.
+			Click-farmed data was generated according to patterns described in section~\ref{sec:related-realworld}.
 We adopted two prevalent types of click farming: \textit{centralized click farming} and \textit{equalized click farming}.
-Centralized click farming emulates the scenarios that a group of people are called out and assigned tasks by a casual leader that does not care much about the click farm timing.
+Centralized click farming emulates the scenarios that a group of people are assigned tasks by a casual leader that does not care much about the click farm timing.
 A significant feature of this approach is that the cheating transactions usually assemble together in a short period of time.
@@
 Thus the transaction distribution may not vary too much with and without click farming.
-Usually, the click farmed transactions are several times more than the volume it original has, if the seller hires a group of organized workers.
+			Usually, the click-farmed transactions are several times more than the volume it originally has, if the seller hires a group of organized workers.
 In our experiments, we use $\nu$ to denote the magnitude coefficient of click farming.
@@
 
-			In order to test the performance of Algorithm~\ref{alg:dynamic}, every single collection was fed into the algorithm by the time order.
+			In order to test the performance of Algorithm~\ref{alg:dynamic}, every single collection was fed into the algorithm by time order.
 Each input collection has a probability of $\alpha$ to be anomalous, namely, click farmed.
@@
 Thus, the histogram was drawn by counting hourly volume of each collection.
-For $\alpha = 0.2$, we selected first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections.
-Equation(5) in Table~\ref{tab:threshold-comparison} was employed as the threshold calculator.
-The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}(TPR), \textit{false positive rate}(FPR) and \textit{accuracy}(ACC) were recorded.
+For $\alpha = 0.2$, we selected first 30 days as the evidence set of normal collections; Day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections.
+E.q.(5) in Table~\ref{tab:threshold-comparison} was employed as the threshold calculator.
+The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate} (TPR), \textit{false positive rate} (FPR) and \textit{accuracy} (ACC) were recorded.
 
@@
 			When classifying toward 1st level histograms, centralized click farming behaviours can be easily discovered.
-As displayed in the left two columns in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click farmed ones abruptly violates the original shape.
-However, as a clever click farmer, equalized click farming did not in the least distorted the distribution.
-Most of them escaped the security check under the perfect disguise.
+As displayed in the left two columns in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click-farmed ones abruptly violates the original shape.
+However, as a clever click farmer, equalized click farming \textcolor{red}{did not in the least distorted the distribution.} Most of them escape the security check under the perfect disguise.
 			But when it comes to 2nd level histograms, the ``clever disguise'' does not work any longer.
@@
 Moreover, the step size in the histograms can now be calculated more precisely.
-In the 1st level histogram, the constant $c$ in equation(\ref{equ:step-size}) was set to 0.5 since the PDF of daily distribution was approximately a linear function.
+In the 1st level histogram, the constant $c$ in E.q.(\ref{equ:step-size}) was set to 0.5 since the PDF of daily distribution was approximately a linear function.
 And in the 2nd level histogram, sub-volumes of every 300 seconds were counted, producing more data points in the 2nd level data collections.
-Then, constant $c$ in equation(\ref{equ:step-size}) was also set to 0.5 given that the 2nd level histogram was also approximately a linear function.
+Then, constant $c$ in E.q.(\ref{equ:step-size}) was also set to 0.5 given that the 2nd level histogram was also approximately a linear function.
 			We tested algorithm performance for $\alpha \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$, with $\mathbb{E}_N$ and $\mathbb{E}_A$ the same configuration as before.
@@
 Therefore, ACC rose up again.
+\textcolor{red}{present tense!
+Throughout the experiment section, the problem is always.
+You should know when to use past and when present!}
 
@@
 
-			In Fig.~\ref{fig:roc-magnitude}, we tested the classifier with different magnitude of centralised click farming.
+			In Fig.~\ref{fig:roc-magnitude}, we test the classifier with different magnitude of centralised click farming.
 In former experiments, $\nu = 1$.
@@
 Data collections are compressed from 1st to 2nd level.
-But for real world click farming behaviours(usually, $\nu > 1$) both classifiers can be efficient enough.
+But for real world click farming behaviours (usually, $\nu > 1$) both classifiers can be efficient enough.
 
@@
 Table~\ref{tab:threshold-comparison} gives the comparison of more equations out of similar considerations.
-From the aspect of weighted average(i.e.
-equation(1)) and taken $\alpha$ into consideration, we composes several other formulas with different operation on $\alpha$ and $\sigma$, yielding other possible balanced points within the interval $[\mu_N, \mu_A]$.
+From the aspect of weighted average, i.e.
+E.q.(1), and taken $\alpha$ into consideration, we composes several other formulas with different operations on $\alpha$ and $\sigma$, yielding other possible balanced points within the interval $[\mu_N, \mu_A]$.
 
-			We tested those calculators on synthetic data set with $\alpha = 0.1, \nu = 1$.
-Testing each level of classifier and each type of anomalies, we got 4 F1 scores and added them up.
+			We test those calculators on synthetic data set with $\alpha = 0.1, \nu = 1$.
+After having tested each level of classifier and each type of anomalies, we got 4 F1 scores and added them up.
 Equation 5 gives best performance.
@@
 
+		\subsection{Comparison: Multinomial Goodness-of-Fit}
+			There has been few research on collective anomaly from the aspect of data collection distribution.
+In 2011, Wang et.
+al had proposed a technique, \textit{Multinomial Goodness-of-Fit}(MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence which is indeed a hypothesis test on distributions~\cite{wang2011statistical}.
+The following experiments were performed on the synthetic data sets by MGoF, providing the comparison baseline of our approach.
+
+			We first tested performance of MGoF with different $\alpha$'s.
+Here $T$ is set to the point correspond to 0.95 in chi-square cumulative distribution function, and $c_{th}$ is set to 10.
+For simplicity, we only tested on 1st level classification against centralized click farming and 2nd level classification against equalized click farming.
+			The results are shown in TABLE~\ref{tab:mgof}.
+
+			\begin{table}[!ht]
+				\centering
+				\caption{Performance of Multinomial Goodness-of-Fit}
+				\label{tab:mgof}
+				\begin{tabular}{|c|c|c|c|c|c|c|}
+					\hline
+					& \multicolumn{3}{c|}{1st Level Centralized} & \multicolumn{3}{c|}{2nd Level Equalized}\\
+					\hline 
+					$\alpha$ & TPR & FPR & ACC & TPR & FPR & ACC \\ 
+					\hline 
+					0.1 & 100.00 & 54.08 & 52.43 & 31.51 & 26.52 & 69.72 \\ 
+					\hline 
+					0.2 & 99.40 & 44.82 & 64.63 & 32.96 & 26.29 & 65.20 \\ 
+					\hline 
+					0.3 & 98.88 & 45.25 & 68.36 & 32.86 & 28.22 & 60.00 \\ 
+					\hline 
+					0.4 & 98.86 & 47.47 & 70.73 & 40.38 & 28.76 & 58.08 \\ 
+					\hline 
+					0.5 & 99.56 & 92.62 & 54.35 & 29.71 & 25.57 & 53.45 \\ 
+					\hline 
+					0.6 & 98.90 & 66.22 & 74.46 & 32.54 & 30.26 & 47.12 \\ 
+					\hline 
+					0.7 & 99.52 & 99.22 & 70.40 & 27.11 & 28.26 & 40.48 \\ 
+					\hline 
+					0.8 & 99.25 & 83.76 & 80.90 & 24.41 & 23.58 & 34.58 \\ 
+					\hline 
+					0.9 & 99.63 & 100.00 & 90.40 & 27.10 & 38.49 & 30.96 \\ 
+					\hline 
+				\end{tabular} 
+			\end{table}
+
+		\begin{figure}[!t]
+			\centering
+			\includegraphics[width=0.49\linewidth]{fig/ROC-Alpha-MGOF.png}
+			\includegraphics[width=0.49\linewidth]{fig/ROC-Nu-MGOF.png}
+			\caption{These two diagrams show the ROC curve of MGoF with same parameters in the former experiment.
+Results were generated by classifying against centralized click farmed data via 1st level histograms.
+By adopting different $\alpha$'s and $\nu$'s, we can find that the classifier is not so sensitive as that provided in our technique.}
+			\label{fig:roc-mgof}
+		\end{figure}
+
+		Left half of the table sees both trends of increasing FPR and ACC.
+That is because MGoF always classify as anomalous the first $c_{th}$ distributions correspond to certain null hypothesis.
+Thus when $\alpha$ increases, the proportion of misclassified normal collections also becomes larger.
+While those anomalies are still considered anomalous.
+And given that the total number of normal collections drops down, the overall accuracy tends to increase as more instances are correctly classified as anomalous.
+However, the right half shows a different trend.
+The basic reason is that MGoF uses KLD instead of JSD.
+In the Taobao dataset, the discrete estimation of collect distributions oscillate a lot, leading to many situations that the prerequisite of KLD is unsatisfied.
+Thus the calculation of KLD may not give a correct measurement.
+Furthermore, the 2nd histogram provides fewer probability entries than the 1st level does.
+Thus it shows a more significant deviation from our expectation.
+Another reason that it shows highly unstable trends is that it simply adopts a threshold which is relative only to the hypothesis of normal data.
+The threshold value requires lots of observation and tuning and still may not be adaptive to most of the circumstances.
+
+		Another main drawback of MGoF is that its learning procedure of anomalous probability hypothesis is inefficient.
+To maintain a comprehensive knowledge of the behaviour of anomalies, MGoF has to reserve a single hypothesis entry for every type of them.
+But in reality, it is always the case that we face the heterogeneity of outliers.
+However in our technique, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections.
+
+		Fig.~\ref{fig:roc-mgof} shows two ROC curves as comparisons with those in Fig.~\ref{fig:roc-alpha} and~\ref{fig:roc-magnitude}.
+For classifiers in MGoF, they are vulnerable to a high error rate.
+While our technique outperforms at any proportion of click farmed data and also more efficient.
+For a relatively small magnitude of click farming, the classifier of MGoF quickly breaks down and degraded to be trivial.
+On the contrary, our techniques provides classifier sensitive enough even toward a relatively small magnitude of click farming.
+
 	\section{Conclusion \& Future Work}\label{sec:conclusion}
-		This paper proposed an dynamic collective anomaly detection technique with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
+		This paper proposes an dynamic collective anomaly detection technique with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
 Different from existing algorithms designed for collective anomalies, our approach employs statistical distance as the similarity measurement, mapping data collections to a restricted one dimensional space.
@@
 
-		However, the modelling of the JSD distributions is not precise enough.
+		\textcolor{red}{[This paragraph tells no future work but only incomplete work.
+You should at least find a reference technique, either from papers or common sense, as a baseline.] However, the modelling of the JSD distributions is not precise enough.
 The efficiency of different adaptive thresholds should be tested on different real world circumstances to get a more complete view of their performances.
@@
 Since the algorithm adapts to the slowly evolving feature, when attacks disguise itself in the long run as if it was one of the changing features, the technique may fail to detect.
-In this case, other techniques may be applied as assistances.
+In this case, other techniques may be applied as assistances.}
 
@@
 \end{document}
+
+In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those occurred at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years.
+And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}.
+System configuration problems, as a matter of fact, are also responsible for the disturbing situation.
+They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

### 2017-10-01 RealWorld/GenerateCheatedData.py

@@ -2,7 +2,7 @@ import csv
 import itertools
 import os
 
-dir = "Equalized"
+dir = "Centralized(1.5)"
 
 if not os.path.exists(os.path.abspath(dir)):
     os.makedirs(os.path.abspath(dir))

### 2017-10-01 RealWorld/MultiNomialGoodnessOfFit-1stLevel.py

@@ -1,0 +1,126 @@
+import csv
+import Divergence
+import statistics
+import random
+import scipy.stats as stats
+import sys
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import math
+
+
+input_dir = "Correct"
+input_dir_err = "Centralized(1.1)"
+
+error_rate = 0.5
+correct_cnt = 0
+correct_recognized = 0
+error_cnt = 0
+error_recognized = 0
+
+T99s = [0, 6.635, 9.210, 11.345, 13.277, 15.086, 16.812, 18.475, 20.090, 21.666, 23.209, 24.725, 26.217, 27.688,
+        29.141, 30.578, 32.000, 33.409, 34.805, 36.191, 37.566, 38.932, 40.289, 41.638, 42.980, 44.314]
+T95s = [0, 3.841, 5.991, 7.815, 9.488, 11.070, 12.592, 14.067, 15.507, 16.919, 18.307, 19.675, 21.026, 22.362,
+        23.685, 24.996, 26.296, 27.587, 28.869, 30.144, 31.410, 32.671, 33.924, 35.172, 36.415, 37.652]
+c_th = 10  # TODO: c_th?
+m = 0
+P = []
+c = []
+
+print("\nTest %s Cheating..." % input_dir_err)
+
+
+def KLD(p, q):
+    # TODO: Complete this
+    d = 0.0
+    for i in range(25):
+        if (p[i] != 0) and (q[i] != 0):
+            d += p[i] * math.log(p[i] / q[i])
+    return d
+
+
+for n in range(30, 325):
+    is_err = False
+    declare_err = False
+    W = 0
+    kld_min = 999
+    c_min = 999
+    if random.uniform(0.0, 1.0) < error_rate:
+        # Error
+        is_err = True
+        reader_err = csv.reader(open("%s/%d.csv" % (input_dir_err, n), 'r'))
+        data_err = list(int(row[2]) for row in reader_err)
+        W = len(data_err)
+
+        error_cnt += 1
+
+        dropped, dist = Divergence.histogram(data_err, step=1)
+
+    else:
+        # Correct
+        reader = csv.reader(open("%s/%d.csv" % (input_dir, n), 'r'))
+        data = list(int(row[2]) for row in reader)
+        W = len(data)
+
+        correct_cnt += 1
+
+        dropped, dist = Divergence.histogram(data, step=1)
+
+    # Regularize dist
+    tmp_dist = {}
+    nbins = 0
+    for i in range(25):
[…]

### 2017-10-01 Synthetic/MultiNomialGoodnessOfFit-2ndLevel.py

@@ -1,0 +1,129 @@
+import csv
+import Divergence
+import statistics
+import random
+import scipy.stats as stats
+import sys
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import math
+
+
+input_dir = "Correct"
+input_dir_err = "Centralized"
+
+time_span = 300
+error_rate = 0.9
+step = 1.17
+correct_cnt = 0
+correct_recognized = 0
+error_cnt = 0
+error_recognized = 0
+
+T99s = [0, 6.635, 9.210, 11.345, 13.277, 15.086, 16.812, 18.475, 20.090, 21.666, 23.209, 24.725, 26.217, 27.688,
+        29.141, 30.578, 32.000, 33.409, 34.805, 36.191, 37.566, 38.932, 40.289, 41.638, 42.980, 44.314]
+T95s = [0, 3.841, 5.991, 7.815, 9.488, 11.070, 12.592, 14.067, 15.507, 16.919, 18.307, 19.675, 21.026, 22.362,
+        23.685, 24.996, 26.296, 27.587, 28.869, 30.144, 31.410, 32.671, 33.924, 35.172, 36.415, 37.652]
+c_th = 10  # TODO: c_th?
+m = 0
+P = []
+c = []
+
+print("\nTest %s Cheating..." % input_dir_err)
+
+
+def KLD(p, q):
+    # TODO: Complete this
+    d = 0.0
+    for i in range(25):
+        if (p[i] != 0) and (q[i] != 0):
+            d += p[i] * math.log(p[i] / q[i])
+    return d
+
+
+for n in range(30, 325):
+    is_err = False
+    declare_err = False
+    W = 0
+    kld_min = 999
+    c_min = 999
+    if random.uniform(0.0, 1.0) < error_rate:
+        # Error
+        is_err = True
+        reader_err = csv.reader(open("%s/%d.csv" % (input_dir_err, n), 'r'))
+        tmp_freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader_err), time_span)
+        data_err = list(tmp_freq.values())
+        W = len(data_err)
+
+        error_cnt += 1
+
+        dropped, dist = Divergence.histogram(data_err, step)
+
+    else:
+        # Correct
+        reader = csv.reader(open("%s/%d.csv" % (input_dir, n), 'r'))
+        tmp_freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), time_span)
[…]

### 2017-10-01 Synthetic/PlotROC.py

@@ -3,37 +3,55 @@ matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
 alphas = [0.1, 0.3, 0.5, 0.7, 0.9]
-TPRs1 = [
-    [1, 0.99, 0.828, 0.556, 0.263],
-    [1, 0.989, 0.827, 0.424, 0.28],
-    [1, .993, .771, .579, .281],
-    [1, .991, .717, .473, .276],
-    [1, .97, .686, .5, .318]
-]
-FPRs1 = [
-    [0.165, 0.018, 0.006, 0.008, 0.004],
-    [0.17, 0.015, 0.007, 0.006, 0.003],
-    [.16, .015, .014, .005, .007],
-    [.104, .004, .01, .007, 0],
-    [.127, .023, .004, .013, 0]
-]
+# # Our approach
+# TPRs1 = [
+#     [1, 0.99, 0.828, 0.556, 0.263],
+#     [1, 0.989, 0.827, 0.424, 0.28],
+#     [1, .993, .771, .579, .281],
+#     [1, .991, .717, .473, .276],
+#     [1, .97, .686, .5, .318]
+# ]
+# FPRs1 = [
+#     [0.165, 0.018, 0.006, 0.008, 0.004],
+#     [0.17, 0.015, 0.007, 0.006, 0.003],
+#     [.16, .015, .014, .005, .007],
+#     [.104, .004, .01, .007, 0],
+#     [.127, .023, .004, .013, 0]
+# ]
+#
+# TPRs2 = [
+#     [1, 1, .867, .655, .346],
+#     [1, 1, .833, .357, .085],
+#     [1, 1, .770, .188, .048],
+#     [1, 1, .832, .090, .028],
+#     [1, 1, 1, .215, .015]
+# ]
+# FPRs2 = [
+#     [.376, .064, .008, 0, 0],
+#     [.386, .076, .001, 0, 0],
+#     [.357, .108, .014, 0, 0],
+#     [.352, .146, .040, .047, .012],
+#     [.346, .111, .059, .080, 0]
+# ]
 
-TPRs2 = [
-    [1, 1, .867, .655, .346],
-    [1, 1, .833, .357, .085],
-    [1, 1, .770, .188, .048],
-    [1, 1, .832, .090, .028],
-    [1, 1, 1, .215, .015]
-]
-FPRs2 = [
-    [.376, .064, .008, 0, 0],
-    [.386, .076, .001, 0, 0],
-    [.357, .108, .014, 0, 0],
[…]

### 2017-10-01 Synthetic/TestFirstOrder.py

@@ -31,7 +31,7 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Centralized(1.5)"
+input_dir_err = "Centralized"
 
 error_rate = 0.5
 

### 2017-10-01 Synthetic/TestSecondOrder.py

@@ -29,7 +29,7 @@ def linearBalancedThreshold(ua, sa, ub, sb, alpha):
         return sol2
 
 input_dir = "Correct"
-input_dir_err = "Centralized(1.5)"
+input_dir_err = "Centralized"
 
 error_rate = 0.5
 #sigma_coefficient = 3  # Don't think about this now

### 2017-10-07 Paper/Template/paper.tex
Version for upload

@@
 		It is hard to detect a single record that is alerted but still remain in correct value scopes, but if many data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
-		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution.
+		According to our observation, typical manipulations on numerical data will lead to a drift or distortion of its original distribution.
 For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones.
-In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions.
-Comparing with a estimated ground truth, each data collection can be mapped into a single real number within a definite interval.
+		To address problems caused by data manipulation, we propose a novel technique which sorts out manipulated data collections from normal ones by adopting statistical distance.
+		In this paper, we focus on a concrete data manipulation problem: click farming in online shops, and try to apply our technique to pick out those dishonest sellers.
+		We use Jensen-Shannon divergence as the similarity measurement among different distributions.
+Comparing with an estimated ground truth, each data collection can be mapped into a single real number within a definite interval.
 Then a gaussian classifier can be applied to detect outliers derived from manipulated data.
-\textcolor{red}{[This is not clear at all.
-Why sets == windows?
-Also the whole paragraph fails to tell a clear story especially what you did and why you did.
-Moreover, you need to outline your contributions explicitly] To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence.
-And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.}
-	The details of our technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.
+To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence.
+		In the dynamic environments, these evidence sets are modified after every data collection is checked, in which manner they act intuitively as slide windows and keep up to the evolving features in dynamic scenarios.
+		Our contribution includes: 1) A brief review on data anomaly detection and a study on the problem of click farming; 2) Detailed description of both basic and dynamic framework of our technique, resolving several technical difficulties of distribution estimation and automated adaptive threshold; 3) Real world data experiments that test efficiency of our technique and a comparison with a previous work on the same topic.
+		%The details of our technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.
 
@@
 
-			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection.
+			Detection approaches can be categorized into three types according to whether data is labeled: \textit{supervised}, \textit{semi-supervised} and \textit{unsupervised} anomaly detection.
 As the name suggests, supervised detection methods train models on completely labeled data, while unsupervised detection leverages data without any labeling.
@@
 
-			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% of them had seen \textcolor{red}{people around them click farmed ????}and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}.
-American researchers reported in 2015 that over 11000 sellers were detected to have click farmed records and only 2.2\% of 4000 investigaed sellers had been penalized because of the cheating attempts~\cite{netease2015research}.
-\textcolor{red}{in which market?}
+			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% are aware of click farm and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}.
+American researchers reported in 2015 that over 11000 sellers on Taobao were detected to have click farmed records and only 2.2\% of 4000 investigaed dishonest sellers had been penalized because of the cheating attempts~\cite{netease2015research}.
 
@@
 
-			\begin{figure}[ht]
+			\begin{figure}[t]
 				\centering
 				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
-				\caption{Example Cumulative Distribution Function of Original And Click Farmed Daily Transaction Data}
+				\caption{Example cumulative distribution function of original and click farmed daily transaction data}
 				\label{fig:example-ecdf}
@@
 		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
-Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers\textcolor{red}{wrong!
-how about 0?}:
+Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers:
 		\begin{equation}
-			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+}
+			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+} \cup \{0\}
 		\end{equation}
@@
 		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records.
-For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
+For example, traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
 Manipulation on those data (e.g.
@@
 			\end{equation}
-			which will give a best partition size, where $c$ is a constant relative to the shape of distribution (e.g.
+			will give a best partition size, where $c$ is a constant relative to the shape of distribution (e.g.
 for normal distribution, $c=1.05$).
@@
 However, a fixed threshold requires specific analysis in the certain scenario, manual observation and tuning of parameters, which involves lots of human labour.
-The rule of ``$3 \sigma$'' \textcolor{red}{need citation or simple explanation here}can be used to automatically determine a threshold.
+The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous.
+It can be used to automatically determine a threshold.
 But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided.
@@
 This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model.
-\textcolor{red}{WHAT do you want to say here? This sentence seems weird. However, in the scenarios that better models can be calculated, distributions here can be replaced to produce better results. }
+			Certainly, if stronger assumptions can be included to provide a more precise model, this component in the framework can be replaced to give better results.
 			For the simplicity of our proposal, we deem the distributions of JSDs to be gaussian.
@@
 The optimal threshold will minimize total errors and yield an optimal outcome.
-\textcolor{red}{The only requirement for this technique is another evidence set containing data point derived from anomalous data collections.}
+Another evidence set is thus required for estimating $PDF_a(x)$.
 
-			However, this is not accurate enough, since equation (\ref{equ:linear-weight}) implicates an assumption that the chances are the same for a new data collection to be either anomalous or not.
+			However, this is not accurate enough, since E.q.(\ref{equ:linear-weight}) implicates an assumption that the chances are the same for a new data collection to be either anomalous or not.
 If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as:
@@
 			Section~\ref{sec:exp-threshold} compares some estimations for optimal threshold under a real world circumstance.
-It shows the difference among calculators and that equation(\ref{equ:linear-balanced}) outperforms others when $PDF_n(x)$ and $PDF_a(x)$ are actually gaussian.
+It shows the difference among calculators and that E.q.(\ref{equ:linear-balanced}) outperforms others when $PDF_n(x)$ and $PDF_a(x)$ are actually gaussian.
 
-		\subsection{Dynamic DCAD}\label{sec:alg-dynamic}
+		\subsection{Dynamic Detection}\label{sec:alg-dynamic}
 			Algorithm~\ref{alg:static} regards every data collection to be sampled from a static environment.
@@
 			\item How to emulate different types of click farming?
-			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:alg-basic} applicable and accurate in real world data sets.
+			\item Is the analysis in section~\ref{sec:related-realworld} and~\ref{sec:alg-basic} applicable and accurate in real world data sets?
 			\item Is the technique efficient against click farming? And How sensitive will the classifier be confronting different magnitude of click farming?
@@
 It sees a trend of daily sale which is slightly moving as the time goes.
-And the daily selling distributions, as is shown in Fig.~\ref{fig:sale-distribution-sample}, display a roughly similar shape.
+And the daily selling distributions, as is shown in Fig.~\ref{fig:sale-distribution-sample}, display a roughly similar shape with each other.
 
@@
 			To play the role of purchasing platform, we surveillance two levels of transaction distribution.
-The first level is simply drawing a histogram aligned to time spans.
+The first level is to simply draw a histogram aligned to time spans.
 The second level is to draw a histogram on the sub-volumes in each time span.
@@
 Each input collection has a probability of $\alpha$ to be anomalous, namely, click farmed.
-The algorithm checks each collection with 1st or 2nd level histogram and give an answer of true or false.
-Several metrics were explored in the following experiments.
+The algorithm checked each collection with 1st or 2nd level histogram and gave an answer of true or false.
+Several metrics are explored in the following experiments.
 
@@
 As displayed in the left two columns in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click-farmed ones abruptly violates the original shape.
-However, as a clever click farmer, equalized click farming \textcolor{red}{did not in the least distorted the distribution.} Most of them escape the security check under the perfect disguise.
+However, as a clever click farmer, equalized click farming did not in the least distort the distribution.
+Most of them escape the check under perfect disguises.
 			But when it comes to 2nd level histograms, the ``clever disguise'' does not work any longer.
@@
 And in the 2nd level histogram, sub-volumes of every 300 seconds were counted, producing more data points in the 2nd level data collections.
-Then, constant $c$ in E.q.(\ref{equ:step-size}) was also set to 0.5 given that the 2nd level histogram was also approximately a linear function.
+Then, constant $c$ in E.q.(\ref{equ:step-size}) was also set to 0.5.
 			We tested algorithm performance for $\alpha \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$, with $\mathbb{E}_N$ and $\mathbb{E}_A$ the same configuration as before.
@@
 No matter how much proportion in them is anomalous, the algorithm always gives a high accuracy.
-That is because the adaptive threshold was designed to minimize the number of total errors, which was not relevant directly to TPR or FPR.
-When $\alpha$ was increasing, there were less data collections added into $\mathbb{E}_N$.
-Thus the update of $\mathbb{E}_N$ became slower and FPR went higher.
-On the contrary, TPR became higher as $\alpha$ increased.
-Moreover, since $|\mathbb{E}_N| > |\mathbb{E}_A|$, it needs more collection instances for $|\mathbb{E}_N|$ then that for $|\mathbb{E}_A|$ to keep up to the trend.
-Therefore, it was faster of FPR to increase than that of TPR.
-As a result of that, there were more false alarms emerged and ACC went lower, as $\alpha$ increased from 0.1 to 0.5.
-After that, however, although FPR was still increasing, total number of normal instances decreased dramatically and those false alarms contributed less to total errors.
-Therefore, ACC rose up again.
-\textcolor{red}{present tense!
-Throughout the experiment section, the problem is always.
-You should know when to use past and when present!}
+That is because the adaptive threshold is designed to minimize the number of total errors, which is not relevant directly to TPR or FPR.
+When $\alpha$ is increasing, there are less data collections added into $\mathbb{E}_N$.
+Thus the update of $\mathbb{E}_N$ becomes slower and FPR goes higher.
+On the contrary, TPR becomes higher as $\alpha$ increases.
+Since $|\mathbb{E}_N| > |\mathbb{E}_A|$, it needs more collection instances for $|\mathbb{E}_N|$ then that for $|\mathbb{E}_A|$ to keep up to the trend.
+Therefore, it is faster of FPR to increase than that of TPR.
+As a result of that, there are more false alarms emerged and ACC drops lower, when $\alpha$ increases from 0.1 to 0.5.
+After that, however, although FPR is still increasing, total number of normal instances decreases dramatically and those false alarms contribute less to total errors.
+Therefore, ACC rises up again.
 
@@
 However the 2nd level classifier is less sensitive.
-That is because the 1st level histogram provides more probability entries than 2nd level histograms do.
+That is because the 1st level histogram provides more probability entries than the 2nd level histograms does.
 Data collections are compressed from 1st to 2nd level.
-But for real world click farming behaviours (usually, $\nu > 1$) both classifiers can be efficient enough.
+For real world click farming behaviours (usually, $\nu > 1$) both classifiers can be efficient enough.
 
@@
 After having tested each level of classifier and each type of anomalies, we got 4 F1 scores and added them up.
-Equation 5 gives best performance.
+E.q.(5) gives best performance.
 Then those equations were tested on large amount of gaussian distributed data instances.
 90K and 10K data points were sampled from 500 pairs of random gaussian distributions which represent normal and anomalous distributions respectively, yielding 500 F1 scores for each equation.
-We compared the average score and discovered that equation 9 gives the best result.
+We compared the average score and discovered that E.q.(9) gives the best result.
 
-			Equation 9 gives best classification result for two gaussian distributions but does not outperform others in real world data.
+			E.q.(9) gives best classification result for two gaussian distributions but does not outperform others in real world data.
 Part of the reasons are mentioned in section~\ref{sec:alg-threshold}.
@@
 		\subsection{Comparison: Multinomial Goodness-of-Fit}
-			There has been few research on collective anomaly from the aspect of data collection distribution.
-In 2011, Wang et.
-al had proposed a technique, \textit{Multinomial Goodness-of-Fit}(MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence which is indeed a hypothesis test on distributions~\cite{wang2011statistical}.
-The following experiments were performed on the synthetic data sets by MGoF, providing the comparison baseline of our approach.
+			Wang et.
+al proposed a technique, \textit{Multinomial Goodness-of-Fit} (MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence, and is fundamentally a hypothesis test on distributions~\cite{wang2011statistical}.
+			MGoF divides the observed data sequence into several windows.
+It quantizes data in each window into a histogram and check these estimated distributions against several hypothesis.
+If the target distribution rejects all provided hypothesis, it is considered an anomaly and preserved as a new candidate of null hypothesis.
+If the target distribution failed to reject some hypothesis, then it is considered a supporting evidence of the one that yields most similarity.
+Furthermore, if the number of supporting evidence is larger than a threshold $c_{th}$, it is classified as non-anomaly.
+
+			MGoF is the best competitor out of the similar techniques, and we use it as our baseline against our approach. The following experiments were performed on the synthetic data sets for MGoF.
 
 			We first tested performance of MGoF with different $\alpha$'s.
-Here $T$ is set to the point correspond to 0.95 in chi-square cumulative distribution function, and $c_{th}$ is set to 10.
+Here $T$ is set to the point corresponding to 0.95 in chi-square cumulative distribution function, and $c_{th}$ is set to 10.
 For simplicity, we only tested on 1st level classification against centralized click farming and 2nd level classification against equalized click farming.
@@
 			\includegraphics[width=0.49\linewidth]{fig/ROC-Nu-MGOF.png}
-			\caption{These two diagrams show the ROC curve of MGoF with same parameters in the former experiment.
-Results were generated by classifying against centralized click farmed data via 1st level histograms.
-By adopting different $\alpha$'s and $\nu$'s, we can find that the classifier is not so sensitive as that provided in our technique.}
+			\caption{These two diagrams show the ROC curve of MGoF with same parameters.
+The results were generated by classifying against centralized click-farmed data via 1st level histograms.
+By adopting different $\alpha$'s and $\nu$'s, we can find that the classifier is not so sensitive as provided in our technique.}
 			\label{fig:roc-mgof}
@@
 
-		Left half of the table sees both trends of increasing FPR and ACC.
-That is because MGoF always classify as anomalous the first $c_{th}$ distributions correspond to certain null hypothesis.
-Thus when $\alpha$ increases, the proportion of misclassified normal collections also becomes larger.
-While those anomalies are still considered anomalous.
+		The left half of the table shows both trends of increasing FPR and ACC.
+That is because MGoF always classifies as anomalous the first $c_{th}$ distributions supporting every null hypothesis.
+Thus when $\alpha$ increases, the proportion of misclassified normal collections also becomes larger, while those anomalies are still considered anomalous.
 And given that the total number of normal collections drops down, the overall accuracy tends to increase as more instances are correctly classified as anomalous.
 However, the right half shows a different trend.
-The basic reason is that MGoF uses KLD instead of JSD.
-In the Taobao dataset, the discrete estimation of collect distributions oscillate a lot, leading to many situations that the prerequisite of KLD is unsatisfied.
+One reason is that MGoF uses KLD other than JSD.
+In the Taobao dataset, the discrete estimation of distributions oscillates a lot, leading to that the prerequisite of KLD is often unsatisfied.
 Thus the calculation of KLD may not give a correct measurement.
@@
 Thus it shows a more significant deviation from our expectation.
-Another reason that it shows highly unstable trends is that it simply adopts a threshold which is relative only to the hypothesis of normal data.
-The threshold value requires lots of observation and tuning and still may not be adaptive to most of the circumstances.
 
-		Another main drawback of MGoF is that its learning procedure of anomalous probability hypothesis is inefficient.
-To maintain a comprehensive knowledge of the behaviour of anomalies, MGoF has to reserve a single hypothesis entry for every type of them.
+		%\textcolor{green}{The other reason why it shows highly unstable is that it simply adopts a threshold, which is relative only to the hypothesis of normal data.
+The threshold value requires lots of observation and tuning, and may not be adaptive to most of the circumstances.}
+
+		MGoF's learning procedure of anomalous probability hypothesis is inefficient.
+To maintain a comprehensive knowledge of anomalies, MGoF has to reserve a single hypothesis entry for every type of them.
 But in reality, it is always the case that we face the heterogeneity of outliers.
-However in our technique, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections.
+In the Taobao's data set, there can be tens of anomalous distribution caused solely by centralized click farming.
+It takes a long time to discover every possible type of anomaly.
+Besides, if there happens to be more than $c_{th}$ anomalous distributions of the same type, later discovered collections will no longer declared to be anomalous any more.
+		However, in our technique, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections.
 
 		Fig.~\ref{fig:roc-mgof} shows two ROC curves as comparisons with those in Fig.~\ref{fig:roc-alpha} and~\ref{fig:roc-magnitude}.
-For classifiers in MGoF, they are vulnerable to a high error rate.
-While our technique outperforms at any proportion of click farmed data and also more efficient.
-For a relatively small magnitude of click farming, the classifier of MGoF quickly breaks down and degraded to be trivial.
-On the contrary, our techniques provides classifier sensitive enough even toward a relatively small magnitude of click farming.
+For the classifiers of MGoF, they  compromise to a high error rate.
+Because more anomalies gathered together and the algorithm recognizes them as clusters of normal data.
+		For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold cannot automatically rise up and is thus much lower to optimal.
 
 	\section{Conclusion \& Future Work}\label{sec:conclusion}
-		This paper proposes an dynamic collective anomaly detection technique with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
-Different from existing algorithms designed for collective anomalies, our approach employs statistical distance as the similarity measurement, mapping data collections to a restricted one dimensional space.
+		This paper proposes a dynamic collective anomaly detection technique with adaptive threshold, which helps detect data manipulations in modern data pipelines and data centres.
+Different from existing algorithms designed for collective anomalies, our approach employs statistical distance as the similarity measurement, mapping data collections to a restricted one-dimensional space.
 We explored several technical points involved in the design of the algorithm and performed a thorough experiment to test its efficiency.
-It showed that the algorithm can efficiently discover anomalies within the data collections and the classifier is sensitive enough toward real world data manipulations.
+The comparison experiment also illustrates the advantages of our technique.
+It can be concluded that the our technique can efficiently discover anomalies within the data collections and the classifier is sensitive enough toward real world data manipulations.
 
-		\textcolor{red}{[This paragraph tells no future work but only incomplete work.
-You should at least find a reference technique, either from papers or common sense, as a baseline.] However, the modelling of the JSD distributions is not precise enough.
-The efficiency of different adaptive thresholds should be tested on different real world circumstances to get a more complete view of their performances.
-Moreover, a comparison with other collective detection algorithm should be adopted in the future to get an performance overview of similar algorithms.
-Since the algorithm adapts to the slowly evolving feature, when attacks disguise itself in the long run as if it was one of the changing features, the technique may fail to detect.
-In this case, other techniques may be applied as assistances.}
-
-\section*{Acknowledgment}
+%\section*{Acknowledgment}
 

### 2019-11-26 Algorithms.py
更新研究

@@ -1,0 +1,332 @@
+from Divergence import *
+from Utils import *
+import statistics
+import numpy as np
+
+
+def sdd_r(collections, step=None, alpha=None, metric=kullbackLeiblerDivergence):
+    """
+    SDD-R算法
+
+    :param collections: 数据群集合。例如：[{1, 1, 2, 2, 3}, {-1, -1, 0}， {0, 1, 1, 2, 2}]
+    :param step: 统计直方图时的步长，默认为None（自动计算）
+    :param alpha: 估计的错误概率，默认为None（使用3σ阈值）
+    :param metric: 统计距离度量函数，默认为kullbackLeiblerDivergence
+    :return: 异常的数据群下标。例如上例中应该返回：[1]
+    """
+    # 计算直方图步长 #
+    if step is None:
+        # 以第一个数据collection为基准 #
+        sample = collections[0]
+        sample_sigma = statistics.stdev(sample)
+        step = 1.05 * sample_sigma * (len(sample) ** -0.2)
+
+    # 计算reference以及divergence分布 #
+    distributions = [histogram(collection, step)[1] for collection in collections]
+    reference = blendDistributions(distributions)
+    divergences = [metric([dist, reference]) for dist in distributions]
+
+    if alpha is None:
+        # 使用3σ阈值 #
+        divergences_mu = statistics.mean(divergences)
+        divergences_sigma = statistics.stdev(divergences, divergences_mu)
+        return [idx for idx in range(len(divergences)) if divergences[idx] > (3 * divergences_sigma - divergences_mu)]
+    else:
+        # 使用rank #
+        order = list(np.argsort(divergences))
+        order.reverse()
+        return order[:int(alpha * len(collections))]
+
+
+def sdd_r_rank(collections, step=None, metric=kullbackLeiblerDivergence):
+    """
+    SDD-R 异常度排序
+
+    :param collections: 数据群集合。例如：[{1, 1, 2, 2, 3}, {-1, -1, 0}， {0, 1, 1, 2, 2}]
+    :param step: 统计直方图时的步长，默认为None（自动计算）
+    :param metric: 统计距离度量函数，默认为kullbackLeiblerDivergence
+    :return: 数据群下标排序，根据异常度从高到低排序
+    """
+    # 计算直方图步长 #
+    if step is None:
+        # 以第一个数据collection为基准 #
+        sample = collections[0]
+        sample_sigma = statistics.stdev(sample)
+        step = 1.05 * sample_sigma * (len(sample) ** -0.2)
+
[…]

### 2019-11-26 Divergence.py

@@ -2,21 +2,37 @@ import math
 
 
 def getDistribution(sample):
-    frequency = {}
+    """
+    计算样本中各个值的频率。
+
+    :param sample: 数值数组，如：[1, 2, 1, 0.5, -5]
+    :return: 两个map：
+        1) 各个值的频次映射，结构为：<value, frequency>，如：{-5:1, 0.5:1, 1:2, 2: 1}
+        2) 各个值的频率映射，结构为：<value, frequency>，如：{-5:0.2, 0.5:0.2, 1:0.4, 2: 0.2}
+    """
+    counts = {}
     cnt = 0
     for obj in sample:
         cnt += 1
-        if obj in frequency:
-            frequency[obj] += 1
+        if obj in counts:
+            counts[obj] += 1
         else:
-            frequency[obj] = 1
-    distribution = {}
-    for i in frequency:
-        distribution[i] = frequency[i] / cnt
-    return frequency, distribution
+            counts[obj] = 1
+    frequencies = {}
+    for value, cnt in counts.items():
+        frequencies[value] = cnt / len(sample)
+    return counts, frequencies
 
 
 def blendDistributions(distributions):
+    """
+    取一系列分布的平均分布。
+
+    :param distributions: 分布数组，每一个分布都是<value, probability>的map。其中value的类型都为数值。如：
+    [{1:0.4, -1:0.6}, {-5:0.2, 0.5:0.2, 1:0.4, 2: 0.2}, {0:0.3, 1:0.3, 2:0.4}]
+    :return: 分布的平均。结构为：<value, probability>如：{1:0.367, -1:0.2, -5:0.067,
+     0.5:0.067, 2:0.2, 0:0.1, }
+    """
     total = {}
     for dist in distributions:
         for i in dist:
@@ -30,22 +46,167 @@ def blendDistributions(distributions):
     return total
 
 
-def jsd(p, q):
-    total = blendDistributions([p, q])
+def kullbackLeiblerDivergence(distributions):
+    """
+    计算两个分布的Kullback-Leibler Divergence。两个分布的结构都是<value, probability>。在这里
+    原始定义需要被扩充以适应当P和Q的定义域不满足原始定义需求的情况。即，只考虑x∈(X_P ∩ X_Q)
 
-    d = 0.0
-    for i in p:
-        d += p[i] * math.log(p[i] / total[i])
-    for i in q:
[…]

### 2019-11-26 Drawings.py

@@ -1,0 +1,591 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+# import matplotlib.axis as ax
+from Divergence import *
+import numpy as np
+
+
+DEFAULT = "#1F77B4"
+RED = '#E74C3C'
+GREEN = '#117A65'
+ORANGE = '#FF9900'
+BLACK = '#000000'
+
+
+def drawClickFarmComparison():
+    print("Drawing click farming comparison figure...")
+    figure = plt.figure(figsize=(7, 7), dpi=300)
+    days = [5, 113, 287]
+    data_normal_file = open('Koubei/RawCorrect.csv', 'r')
+    data_normal = data_normal_file.readlines()
+    collection_normal = [
+        [int(num) for num in data_normal[d].strip('\n').split('\t')] for d in days
+    ]
+    data_normal_file.close()
+
+    data_centralized_file = open('Koubei/RawCentralized.csv', 'r')
+    data_centralized = data_centralized_file.readlines()
+    collection_centralized = [
+        [int(num) for num in data_centralized[d].strip('\n').split('\t')] for d in days
+    ]
+    data_centralized_file.close()
+
+    data_equalized_file = open('Koubei/RawEqualized.csv', 'r')
+    data_equalized = data_equalized_file.readlines()
+    collection_equalized = [
+        [int(num) for num in data_equalized[d].strip('\n').split('\t')] for d in days
+    ]
+    data_equalized_file.close()
+
+    step = 1
+    hist_normal = [histogram(collection, step)[1] for collection in collection_normal]
+    hist_centralized = [histogram(collection, step)[1] for collection in collection_centralized]
+    hist_equalized = [histogram(collection, step)[1] for collection in collection_equalized]
+
+    lim_x = 24
+    lim_y = 0.25
+    for col in range(3):
+        # Draw Normal Data #
+        plt.subplot(3, 3, 1 * 3 + col + 1)
+        xs = []
+        ys = []
+        for x, y in hist_normal[col].items():
+            xs.append(x)
+            ys.append(y)
+        plt.bar(xs, ys, color=RED, label="Normal")
+        plt.xlim(0, lim_x)
+        plt.ylim(0, lim_y)
+        plt.xticks(())
+        if 0 != col:
+            plt.yticks(())
+        else:
[…]

### 2019-11-26 Experiments.py

@@ -1,0 +1,1061 @@
+from typing import List
+
+from Utils import *
+from Divergence import *
+from Algorithms import *
+import numpy as np
+import statistics
+import time
+
+
+EXP_DUPLICATE = 5
+
+
+def testPerformanceOnKoubei():
+    # 加载数据 #
+    correct_data_raw = loadCollectionFromFile("Koubei/RawCorrect.csv")
+    centralized_data_raw = loadCollectionFromFile("Koubei/RawCentralized.csv")
+    equalized_data_raw = loadCollectionFromFile("Koubei/RawEqualized.csv")
+
+    correct_data_syn = loadCollectionFromFile("Koubei/SynCorrect.csv")
+    centralized_data_syn = loadCollectionFromFile("Koubei/SynCentralized.csv")
+    equalized_data_syn = loadCollectionFromFile("Koubei/SynEqualized.csv")
+
+    # 设置参数 #
+    alpha = 0.1
+    num_anomalies = int(alpha * len(correct_data_raw))
+    anomaly_indices_array = [
+        sorted(np.random.choice(range(len(correct_data_raw)), num_anomalies, replace=False)) for _ in range(EXP_DUPLICATE)
+    ]
+    print("Anomalies:")
+    for i in range(EXP_DUPLICATE):
+        print(anomaly_indices_array[i])
+
+    sample = correct_data_syn[0]
+    sample_sigma = statistics.stdev(sample)
+    level1_step_syn = 1.05 * sample_sigma * (len(sample) ** -0.2)
+
+    evidence_normal_raw = correct_data_raw[:30]
+    evidence_centralized_raw = centralized_data_raw[:10]
+    evidence_equalized_raw = equalized_data_raw[:10]
+    evidence_normal_raw_level2 = [histogram(collection, 1)[0].values() for collection in evidence_normal_raw]
+    evidence_centralized_raw_level2 = [histogram(collection, 1)[0].values() for collection in evidence_centralized_raw]
+    evidence_equalized_raw_level2 = [histogram(collection, 1)[0].values() for collection in evidence_equalized_raw]
+
+    evidence_normal_syn = correct_data_syn[:30]
+    evidence_centralized_syn = centralized_data_syn[:10]
+    evidence_equalized_syn = equalized_data_syn[:10]
+    evidence_normal_syn_level2 = [histogram(collection, level1_step_syn)[0].values() for collection in evidence_normal_syn]
[…]

### 2019-11-26 KoubeiDataConverter.py

@@ -1,0 +1,37 @@
+def convertData(dir):
+    ofile = open("%s.csv" % dir, 'w')
+    for i in range(325):
+        ifile = open("./%s/%d.csv" % (dir, i), 'r')
+        lines = ifile.readlines()
+
+        # 转换第一列 #
+        time = lines[0].strip('\n').split(',')[2]
+        ofile.write("%s" % time)
+
+        # 转换其余列 #
+        for j in range(1, len(lines)):
+            time = lines[j].strip('\n').split(',')[2]
+            ofile.write("\t%s" % time)
+        ofile.write('\n')
+        ifile.close()
+    ofile.close()
+
+
+if __name__ == '__main__':
+    convertData("RawCorrect")
+    convertData("RawCentralized")
+    convertData("RawEqualized")
+
+    convertData("SynCorrect")
+    convertData("SynCentralized")
+    convertData("SynCentralized(1.1)")
+    convertData("SynCentralized(1.2)")
+    convertData("SynCentralized(1.3)")
+    convertData("SynCentralized(1.4)")
+    convertData("SynCentralized(1.5)")
+    convertData("SynCentralized(1.6)")
+    convertData("SynCentralized(1.7)")
+    convertData("SynCentralized(1.8)")
+    convertData("SynCentralized(1.9)")
+    convertData("SynCentralized(3x)")
+    convertData("SynEqualized")

### 2019-11-26 OldStory/RealWorld-Old/CompareDaily.py

@@ -1,0 +1,73 @@
+import csv
+import math
+import os
+import statistics
+from itertools import *
+
+import matplotlib
+
+import Divergence
+
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+
+input_dir = "Frequencies"
+input_dir_fake_centralized = "Fake_Centralized_Frequencies"
+input_dir_fake_equalized = "Fake_Equalized_Frequencies"
+distributions = []
+distributions_fake_centralized = []
+distributions_fake_equalized = []
+
+for file in os.listdir(os.path.abspath(input_dir)):
+    with open("%s/%s" % (input_dir, file), 'r') as f:
+        reader = csv.reader(f)
+        distribution = {}
+        for row in islice(reader, 0, None):
+            distribution[int(row[0])] = float(row[2])
+        distributions += [distribution]
+
+for file in os.listdir(os.path.abspath(input_dir_fake_centralized)):
+    with open("%s/%s" % (input_dir_fake_centralized, file), 'r') as f:
+        reader = csv.reader(f)
+        distribution = {}
+        for row in islice(reader, 0, None):
+            distribution[int(row[0])] = float(row[2])
+        distributions_fake_centralized += [distribution]
+
+for file in os.listdir(os.path.abspath(input_dir_fake_equalized)):
+    with open("%s/%s" % (input_dir_fake_equalized, file), 'r') as f:
+        reader = csv.reader(f)
+        distribution = {}
+        for row in islice(reader, 0, None):
+            distribution[int(row[0])] = float(row[2])
+        distributions_fake_equalized += [distribution]
+
+total_distribution = Divergence.blendDistributions(distributions)
+jsds = []
+jsds_fake_centralized = []
+jsds_fake_equalized = []
+
+for distribution in distributions:
+    jsds += [Divergence.jsd(distribution, total_distribution)]
+
+for distribution in distributions_fake_centralized:
+    jsds_fake_centralized += [Divergence.jsd(distribution, total_distribution)]
+
+for distribution in distributions_fake_equalized:
+    jsds_fake_equalized += [Divergence.jsd(distribution, total_distribution)]
+
+mu = statistics.mean(jsds)
+sigma = math.sqrt(statistics.variance(jsds))
+print(jsds)
+print("mu: %f" % (mu))
+print("sigma: %f" % (sigma))
+
[…]

### 2019-11-26 OldStory/RealWorld-Old/CompareFrequency.py

@@ -1,0 +1,64 @@
+import csv
+import math
+import os
+import statistics
+from itertools import *
+
+import matplotlib
+
+import Divergence
+
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+
+input_dir = "Frequencies"
+input_dir_cen = "Fake_Centralized_Frequencies"
+input_dir_equ = "Fake_Equalized_Frequencies"
+dists = []
+dists_cen = []
+dists_equ = []
+
+for file in os.listdir(os.path.abspath(input_dir)):
+    with open("%s/%s" % (input_dir, file), 'r') as f:
+        reader = csv.reader(f)
+        dists += [Divergence.getDistribution(list(int(row[1]) for row in islice(reader, 0, None)))]
+
+for file in os.listdir(os.path.abspath(input_dir_cen)):
+    with open("%s/%s" % (input_dir_cen, file), 'r') as f:
+        reader = csv.reader(f)
+        dists_cen += [Divergence.getDistribution(list(int(row[1]) for row in islice(reader, 0, None)))]
+
+for file in os.listdir(os.path.abspath(input_dir_equ)):
+    with open("%s/%s" % (input_dir_equ, file), 'r') as f:
+        reader = csv.reader(f)
+        dists_equ += [Divergence.getDistribution(list(int(row[1]) for row in islice(reader, 0, None)))]
+
+total_distribution = Divergence.blendDistributions(dists)
+jsds = []
+jsds_fake_centralized = []
+jsds_fake_equalized = []
+
+for distribution in dists:
+    jsds += [Divergence.jsd(distribution, total_distribution)]
+
+for distribution in dists_cen:
+    jsds_fake_centralized += [Divergence.jsd(distribution, total_distribution)]
+
+for distribution in dists_equ:
+    jsds_fake_equalized += [Divergence.jsd(distribution, total_distribution)]
+
+mu = statistics.mean(jsds)
+sigma = math.sqrt(statistics.variance(jsds))
+print(jsds)
+print("mu: %f" % (mu))
+print("sigma: %f" % (sigma))
+
+figure = plt.figure()
+zeros = [0] * len(jsds)
+plt.plot(jsds, zeros, "ro", ms=1, label="normal")
+plt.plot(jsds_fake_centralized, [0.5] * len(jsds), "bo", ms=1, label="centralized")
[…]

### 2019-11-26 OldStory/RealWorld-Old/EcdfPlot.py

@@ -1,0 +1,33 @@
+import csv
+from itertools import *
+import os
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.patches as patches
+
+input_dir = "Fake_Equalized_Frequencies"
+output_dir = "Fake_Equalized_Ecdfs"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+figure = plt.figure()
+for file in os.listdir(os.path.abspath(input_dir)):
+    print("Processing: " + file)
+    with open("%s/%s" % (input_dir, file), 'r') as f:
+        reader = csv.reader(f)
+        prob = {}
+        for row in islice(reader, 0, None):
+            prob[int(row[0])] = float(row[2])
+
+        cprob = 0.0
+        y = []
+        for i in range(0, 25):
+            if i in prob:
+                cprob += prob[i]
+            y += [cprob]
+
+        plt.plot(range(0, 25), y)
+        plt.savefig("%s/%s.png" % (output_dir, file))
+        figure.clear()

### 2019-11-26 OldStory/RealWorld-Old/Fake_Centralized.py

@@ -1,0 +1,40 @@
+import csv
+from itertools import *
+from datetime import time
+import os
+import random
+
+input_dir = "Inputs"
+output_dir = "Fake_Centralized_Frequencies"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+for file in os.listdir(os.path.abspath(input_dir)):
+    print("Processing: " + file)
+    with open("%s/%s" % (input_dir, file), "r") as f:
+        freq = {}
+        cnt = 0
+        reader = csv.reader(f)
+        for row in islice(reader, 0, None):
+            cnt += 1
+            hour = int(row[2].split(' ')[1].split(":")[0])
+            if hour in freq:
+                freq[hour] += 1
+            else:
+                freq[hour] = 1
+
+        # Randomly modify records in 1 to 5 hours
+        n = random.randint(1, 3)
+        tmp = list(freq.keys())
+        for i in range(0, n):
+            ridx = random.randint(0, len(tmp) - 1)
+            idx = tmp[ridx]
+            del tmp[ridx]
+            new_freq = int(freq[idx] * random.uniform(5.0, 7.0))
+            cnt += new_freq - freq[idx]
+            freq[idx] = new_freq
+
+        with open("%s/%s" % (output_dir, file), 'w') as of:
+            for i in freq:
+                of.write("%d,%d,%f\n" % (i, freq[i], freq[i] / cnt))

### 2019-11-26 OldStory/RealWorld-Old/Fake_Equalized.py

@@ -1,0 +1,32 @@
+import csv
+from itertools import *
+from datetime import time
+import os
+import random
+
+input_dir = "Inputs"
+output_dir = "Fake_Equalized_Frequencies"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+for file in os.listdir(os.path.abspath(input_dir)):
+    print("Processing: " + file)
+    with open("%s/%s" % (input_dir, file), "r") as f:
+        freq = {}
+        cnt = 0
+        reader = csv.reader(f)
+        for row in islice(reader, 0, None):
+            hour = int(row[2].split(' ')[1].split(":")[0])
+            if hour in freq:
+                freq[hour] += 1
+            else:
+                freq[hour] = 1
+
+        for i in freq:
+            freq[i] *= int(random.uniform(2.0, 3.0))
+            cnt += freq[i]
+
+        with open("%s/%s" % (output_dir, file), 'w') as of:
+            for i in freq:
+                of.write("%d,%d,%f\n" % (i, freq[i], freq[i] / cnt))

### 2019-11-26 OldStory/RealWorld-Old/SplitInput.py

@@ -1,0 +1,29 @@
+import csv
+from itertools import *
+from datetime import date
+import os
+
+#fname = input("File Name: ")
+#path = input("Output Directory: ")
+fname = "1629.csv"
+dirpath = "./Inputs"
+d = os.path.abspath(dirpath)
+print("Split files into: ", d)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+base_date = date(2015, 7, 1)
+ofiles = {}
+
+with open(fname) as file:
+    reader = csv.reader(file)
+    for row in islice(reader, 0, None):
+        paras = row[2].split(' ')[0].split('-')
+        row_date = date(int(paras[0]), int(paras[1]), int(paras[2]))
+        days = (row_date - base_date).days
+        if days not in ofiles:
+            ofiles[days] = open("%s/%d.csv" % (dirpath, days), "w")
+        ofiles[days].write(row[0] + ',' + row[1] + ',' + row[2] + '\n')
+
+for of in ofiles:
+    ofiles[of].close()

### 2019-11-26 OldStory/RealWorld-Old/Statistics.py

@@ -1,0 +1,27 @@
+import csv
+from itertools import *
+from datetime import time
+import os
+
+input_dir = "Inputs"
+output_dir = "Frequencies"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+for file in os.listdir(os.path.abspath(input_dir)):
+    print("Processing: " + file)
+    with open("%s/%s" % (input_dir, file), "r") as f:
+        freq = {}
+        cnt = 0
+        reader = csv.reader(f)
+        for row in islice(reader, 0, None):
+            cnt += 1
+            hour = int(row[2].split(' ')[1].split(":")[0])
+            if hour in freq:
+                freq[hour] += 1
+            else:
+                freq[hour] = 1
+        with open("%s/%s" % (output_dir, file), 'w') as of:
+            for i in freq:
+                of.write("%d,%d,%f\n" % (i, freq[i], freq[i] / cnt))

### 2019-11-26 OldStory/RealWorld-Old/TotalSellsPlot.py

@@ -1,0 +1,15 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+with open("count.csv", 'r') as f:
+    y = []
+    for row in f:
+        y += [int(row)]
+
+    figure = plt.figure(figsize=(6, 6), dpi=100)
+    plt.plot(range(len(y)), y, ms=1)
+    plt.xlabel("Day", fontsize='x-large')
+    plt.ylabel("Transaction Volume", fontsize='x-large')
+    plt.savefig("TotalSells.png")
+

### 2019-11-26 OldStory/RealWorld-Old/count.sh

@@ -1,0 +1,4 @@
+for i in $(seq 133 488)
+do
+    <Inputs/$i.csv wc -l >> count.csv
+done

### 2019-11-26 OldStory/RealWorld/SamplePDF.py

@@ -1,0 +1,94 @@
+import csv
+# import Divergence
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.axis as ax
+
+days = (5, 113, 287)
+lim_x = 24
+lim_y = 0.25
+
+figure = plt.figure(figsize=(7, 7), dpi=100)
+for ii in range(3):
+    day = days[ii]
+    reader = csv.reader(open("Correct/%d.csv" % day, 'r'))
+    reader_cen = csv.reader(open("Centralized/%d.csv" % day, 'r'))
+    reader_equ = csv.reader(open("Equalized/%d.csv" % day, 'r'))
+
+    # freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), step=1)
+    # freq_cen, dropped = Divergence.histogram(list(int(row[2]) for row in reader_cen), step=1)
+    # freq_equ, dropped = Divergence.histogram(list(int(row[2]) for row in reader_equ), step=1)
+    #
+    # data = freq.values()
+    # data_cen = freq_cen.values()
+    # data_equ = freq_equ.values()
+    # step = 21.48
+
+    data = list(int(row[2]) for row in reader)
+    data_cen = list(int(row[2]) for row in reader_cen)
+    data_equ = list(int(row[2]) for row in reader_equ)
+
+    step = 1
+
+    dropped, hist = Divergence.histogram(data, step)
+    droped, hist_cen = Divergence.histogram(data_cen, step)
+    dropped, hist_equ = Divergence.histogram(data_equ, step)
+
+    id = 1 * 3 + ii + 1
+    plt.subplot(3, 3, id)
+    x = []
+    y = []
+    for i in hist:
+        x += [i]
+        y += [hist[i]]
+    plt.bar(x, y, color='r', label="Normal")
+    plt.xlim(0, lim_x)
+    plt.ylim(0, lim_y)
+    plt.xticks(())
+    if 0 != ii:
+        plt.yticks(())
+    else:
+        plt.legend(loc="upper right")
+        plt.ylabel("Probability", fontsize='x-large')
+
+    id = 0 * 3 + ii + 1
+    plt.subplot(3, 3, id)
+    x = []
+    y = []
+    for i in hist_cen:
+        x += [i]
+        y += [hist_cen[i]]
[…]

### 2019-11-26 OldStory/Synthetic/GenerateCentralized.py

@@ -1,0 +1,64 @@
+import csv
+import itertools
+import os
+import numpy
+# import Divergence
+# import matplotlib
+# matplotlib.use('Agg')
+# import matplotlib.pyplot as plt
+
+ratio = 0.9
+
+input_dir = "Correct"
+output_dir = "Centralized(%.1f)" % (1 + ratio)
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+for file in os.listdir(input_dir):
+    print("Processing: ", file)
+    with open("%s/%s" % (input_dir, file), 'r') as ifile:
+        with open("%s/%s" % (output_dir, file), 'w') as ofile:
+            cnt = 0
+            for line in ifile:
+                cnt += 1
+                ofile.write(line)
+            #num_new = numpy.random.randint(int(cnt * 1.5), int(cnt * 2.0))
+            num_new = int(cnt * ratio)
+            center = numpy.random.randint(10, 21)
+            for item in numpy.random.normal(center * 3600, 1.5 * 3600, num_new):
+                if (item >= (7 * 3600)) and (item < 24 * 3600):
+                    ofile.write("921013,1629,%d\n" % int(item))
+
+# # Check two examples
+# f = open("brackets.txt", 'r')
+# min_val = int(f.readline())
+# max_val = int(f.readline())
+# f.close()
+#
+# figure = plt.figure(figsize=(1400/300, 1400/300), dpi=300)
+# with open("%s/134.csv" % input_dir, 'r') as f:
+#     reader = csv.reader(f)
+#     records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+#     distribution = Divergence.histogramNaive(min_val, max_val, records)
+#     x = []
+#     y = []
+#     for i in distribution:
+#         x += [i]
+#         y += [distribution[i]]
+#     plt.bar(x, y, color="red")
+#     plt.savefig("Sample.png")
+#     figure.clear()
+#
+# with open("%s/134.csv" % output_dir, 'r') as f:
+#     reader = csv.reader(f)
+#     records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+#     distribution = Divergence.histogramNaive(min_val, max_val, records)
+#     x = []
+#     y = []
+#     for i in distribution:
+#         x += [i]
+#         y += [distribution[i]]
+#     plt.bar(x, y, color="blue")
+#     plt.savefig("SampleCentralized.png")
+#     figure.clear()

### 2019-11-26 OldStory/SyntheticStatic-Old/CompareDaily.py

@@ -1,0 +1,89 @@
+import csv
+import itertools
+import math
+import os
+import statistics
+
+import matplotlib
+
+import Divergence
+
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+
+input_dir = "Inputs"
+input_dir_fake_centralized = "InputsCentralized"
+input_dir_fake_equalized = "InputsEqualized"
+distributions = []
+distributions_fake_centralized = []
+distributions_fake_equalized = []
+
+f = open("brackets.txt", 'r')
+min_val = int(f.readline())
+max_val = int(f.readline())
+f.close()
+
+print("Calculating Distributions(Real)...")
+for file in os.listdir(os.path.abspath(input_dir)):
+    with open("%s/%s" % (input_dir, file), 'r') as f:
+        reader = csv.reader(f)
+        records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+        distribution = Divergence.histogramNaive(min_val, max_val, records)
+        distributions += [distribution]
+
+print("Calculating Distributions(Centralized Cheating)...")
+for file in os.listdir(os.path.abspath(input_dir_fake_centralized)):
+    with open("%s/%s" % (input_dir_fake_centralized, file), 'r') as f:
+        reader = csv.reader(f)
+        records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+        distribution = Divergence.histogramNaive(min_val, max_val, records)
+        distributions_fake_centralized += [distribution]
+
+print("Calculating Distributions(Equalized Cheating)...")
+for file in os.listdir(os.path.abspath(input_dir_fake_equalized)):
+    with open("%s/%s" % (input_dir_fake_equalized, file), 'r') as f:
+        reader = csv.reader(f)
+        records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+        distribution = Divergence.histogramNaive(min_val, max_val, records)
+        distributions_fake_equalized += [distribution]
+
+total_distribution = Divergence.blendDistributions(distributions)
+jsds = []
+jsds_fake_centralized = []
+jsds_fake_equalized = []
+
+print("Calculating JSDs(Real)...")
+for distribution in distributions:
+    jsds += [Divergence.jsd(distribution, total_distribution)]
+
+print("Calculating JSDs(Centralized Cheating)...")
[…]

### 2019-11-26 OldStory/SyntheticStatic-Old/EcdfPlot.py

@@ -1,0 +1,34 @@
+import csv
+from itertools import *
+import os
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.patches as patches
+
+input_dir = "Distributions"
+output_dir = "Ecdfs"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+figure = plt.figure()
+for file in os.listdir(os.path.abspath(input_dir)):
+    print("Processing: " + file)
+    with open("%s/%s" % (input_dir, file), 'r') as f:
+        reader = csv.reader(f)
+        prob = {}
+        for row in islice(reader, 0, None):
+            prob[int(row[0])] = float(row[1])
+
+        cprob = 0.0
+        y = []
+        x = range(-500, 1500)
+        for i in x:
+            if i in prob:
+                cprob += prob[i]
+            y += [cprob]
+
+        plt.plot(x, y)
+        plt.savefig("%s/%s.png" % (output_dir, file))
+        figure.clear()

### 2019-11-26 OldStory/SyntheticStatic-Old/Emulate.py

@@ -1,0 +1,99 @@
+import csv
+import itertools
+import math
+import os
+import statistics
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+import Divergence
+
+
+input_dir = "Inputs"
+input_dir_cen = "InputsCentralized"
+input_dir_equ = "InputsEqualized"
+
+f = open("brackets.txt", 'r')
+min_val = int(f.readline())
+max_val = int(f.readline())
+f.close()
+
+for pw in range(1, 11):
+#for nbins in [4, 8, 16, 32, 64, 128, 256, 512, 1024]:
+    dists = []
+    jsds = []
+    jsds_cen = []
+    jsds_equ = []
+    nbins = 2 ** pw
+    print("N bins: ", nbins)
+
+    # Record History
+    print("Reading History...")
+    num_hists = 30
+    for i in range(133, 133 + num_hists):
+        with open("%s/%d.csv" % (input_dir, i), 'r') as f:
+            reader = csv.reader(f)
+            records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+            distribution = Divergence.histogramNaive(min_val, max_val, records, nbins=nbins)
+            dists += [distribution]
+
+    # Test Rest Days
+    print("Performing Tests...")
+    for i in range(133 + num_hists, 489):
+        total_dist = Divergence.blendDistributions(dists)
+
+        if not os.path.exists(os.path.abspath("%s/%d.csv" % (input_dir, i))):
+            continue
+
+        # Calculate Real Distribution
+        f = open("%s/%d.csv" % (input_dir, i), 'r')
+        reader = csv.reader(f)
+        records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+        distribution = Divergence.histogramNaive(min_val, max_val, records, nbins=nbins)
+        jsds += [Divergence.jsd(total_dist, distribution)]
+        dists += [distribution]
+        f.close()
+
+        # Calculate Centralized Distribution
+        f = open("%s/%d.csv" % (input_dir_cen, i), 'r')
+        reader = csv.reader(f)
+        records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+        distribution = Divergence.histogramNaive(min_val, max_val, records, nbins=nbins)
+        jsds_cen += [Divergence.jsd(total_dist, distribution)]
[…]

### 2019-11-26 OldStory/SyntheticStatic-Old/Generate.py

@@ -1,0 +1,24 @@
+import csv
+import os
+import itertools
+import random
+
+
+input_dir = "../RealWorld/Inputs"
+output_dir = "Inputs"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+for file in os.listdir(input_dir):
+    ifile = open("%s/%s" % (input_dir, file), 'r')
+    ofile = open("%s/%s" % (output_dir, file), 'w')
+    reader = csv.reader(ifile)
+    for row in itertools.islice(reader, 0, None):
+        hh = int(row[2].split(" ")[1].split(":")[0])
+        mm = random.randint(0, 59)
+        ss = random.randint(0, 59)
+        t = hh * 3600 + mm * 60 + ss
+        ofile.write("%s,%s,%d\n" % (row[0], row[1], t))
+    ifile.close()
+    ofile.close()

### 2019-11-26 OldStory/SyntheticStatic-Old/GenerateCentralized.py

@@ -1,0 +1,61 @@
+import csv
+import itertools
+import os
+import numpy
+import Divergence
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+input_dir = "Inputs"
+output_dir = "InputsCentralized"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+for file in os.listdir(input_dir):
+    print("Processing: ", file)
+    with open("%s/%s" % (input_dir, file), 'r') as ifile:
+        with open("%s/%s" % (output_dir, file), 'w') as ofile:
+            cnt = 0
+            for line in ifile:
+                cnt += 1
+                ofile.write(line)
+            num_new = numpy.random.randint(int(cnt * 1.5), int(cnt * 2.0))
+            center = numpy.random.randint(10, 21)
+            for item in numpy.random.normal(center * 3600, 1.5 * 3600, num_new):
+                if (item >= (7 * 3600)) and (item < 24 * 3600):
+                    ofile.write("921013,1629,%d\n" % int(item))
+
+# # Check two examples
+# f = open("brackets.txt", 'r')
+# min_val = int(f.readline())
+# max_val = int(f.readline())
+# f.close()
+#
+# figure = plt.figure(figsize=(1400/300, 1400/300), dpi=300)
+# with open("%s/134.csv" % input_dir, 'r') as f:
+#     reader = csv.reader(f)
+#     records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+#     distribution = Divergence.histogramNaive(min_val, max_val, records)
+#     x = []
+#     y = []
+#     for i in distribution:
+#         x += [i]
+#         y += [distribution[i]]
+#     plt.bar(x, y, color="red")
+#     plt.savefig("Sample.png")
+#     figure.clear()
+#
+# with open("%s/134.csv" % output_dir, 'r') as f:
+#     reader = csv.reader(f)
+#     records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+#     distribution = Divergence.histogramNaive(min_val, max_val, records)
+#     x = []
+#     y = []
+#     for i in distribution:
+#         x += [i]
+#         y += [distribution[i]]
+#     plt.bar(x, y, color="blue")
+#     plt.savefig("SampleCentralized.png")
+#     figure.clear()

### 2019-11-26 OldStory/SyntheticStatic-Old/GenerateEqualized.py

@@ -1,0 +1,46 @@
+import csv
+import itertools
+import os
+import numpy
+import Divergence
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+input_dir = "Inputs"
+output_dir = "InputsEqualized"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+# for file in os.listdir(input_dir):
+#     print("Processing: ", file)
+#     with open("%s/%s" % (input_dir, file), 'r') as ifile:
+#         with open("%s/%s" % (output_dir, file), 'w') as ofile:
+#             cnt = 0
+#             for line in ifile:
+#                 cnt += 1
+#                 ofile.write(line)
+#             num_new = numpy.random.randint(int(cnt * 1.5), int(cnt * 2.0))
+#             for item in numpy.random.randint(7 * 3600, 24 * 3600, num_new):
+#                 ofile.write("921013,1629,%d\n" % int(item))
+
+# Plot one example distribution
+f = open("brackets.txt", 'r')
+min_val = int(f.readline())
+max_val = int(f.readline())
+f.close()
+
+figure = plt.figure(figsize=(1400/300, 1400/300), dpi=300)
+with open("%s/134.csv" % output_dir, 'r') as f:
+    reader = csv.reader(f)
+    records = (int(row[2]) for row in itertools.islice(reader, 0, None))
+    distribution = Divergence.histogramNaive(min_val, max_val, records)
+    x = []
+    y = []
+    for i in distribution:
+        x += [i]
+        y += [distribution[i]]
+    plt.bar(x, y, color="green")
+    plt.savefig("SampleEqualized.png")
+    figure.clear()

### 2019-11-26 OldStory/SyntheticStatic-Old/Statistics.py

@@ -1,0 +1,25 @@
+import csv
+import itertools
+import os
+
+import Divergence
+
+input_dir = "Inputs"
+output_dir = "Distributions"
+d = os.path.abspath(output_dir)
+if not os.path.exists(d):
+    os.makedirs(d)
+
+f = open("brackets.txt", 'r')
+min_val = int(f.readline())
+max_val = int(f.readline())
+f.close()
+
+for file in os.listdir(input_dir):
+    print("Processing: ", file)
+    with open("%s/%s" % (input_dir, file), 'r') as ifile:
+        reader = csv.reader(ifile)
+        distribution = Divergence.histogramNaive(min_val, max_val, (int(row[2]) for row in itertools.islice(reader, 0, None)))
+        with open("%s/%s" % (output_dir, file), 'w') as ofile:
+            for i in distribution:
+                ofile.write("%d,%f\n" % (i, distribution[i]))

### 2019-11-26 OldStory/SyntheticStatic-Old/TotalSellsPlot.py

@@ -1,0 +1,13 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+with open("CountEqualized.csv", 'r') as f:
+    y = []
+    for row in f:
+        y += [int(row)]
+
+    figure = plt.figure(figsize=(1400/300, 1400/300), dpi=300)
+    plt.plot(range(len(y)), y, ms=1)
+    plt.savefig("TotalSellsEqualized.png")
+

### 2019-11-26 OldStory/SyntheticStatic-Old/TryHistogram.py

@@ -1,0 +1,80 @@
+import csv
+import itertools
+import Divergence
+import statistics
+import math
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+
+f = open("brackets.txt", 'r')
+min_val = int(f.readline())
+max_val = int(f.readline())
+f.close()
+
+dists = []
+total_data = []
+for i in range(134, 164):
+    with open("Inputs/%d.csv" % i, 'r') as f:
+        reader = csv.reader(f)
+        records = list(int(row[2]) for row in itertools.islice(reader, 0, None))
+        distribution = Divergence.histogramNaive(min_val, max_val, records)
+        dists += [distribution]
+        total_data += records
+
+total_cnt = len(total_data)
+sigma = statistics.stdev(total_data)
+step = math.pow(total_cnt / 30, -0.2) * sigma * 0.5
+num_bins = (max_val - min_val) / step
+print(max_val, min_val)
+print(total_cnt)
+print(sigma)
+print("Step: ", step)
+print("Num Bins: ", num_bins)
+print("Bin Width: ", (max_val - min_val) / 50)
+
+# # Check two examples
+# figure = plt.figure(figsize=(1800/300, 600/300), dpi=300)
+#
+# ifile = open("Inputs/134.csv", 'r')
+# ifile_cen = open("InputsCentralized/134.csv", 'r')
+# ifile_equ = open("InputsEqualized/134.csv", 'r')
+#
+# records = list(int(row[2]) for row in itertools.islice(csv.reader(ifile), 0, None))
+# records_cen = list(int(row[2]) for row in itertools.islice(csv.reader(ifile_cen), 0, None))
+# records_equ = list(int(row[2]) for row in itertools.islice(csv.reader(ifile_equ), 0, None))
+#
+# for pw in range(10):
+#     nbins = 2 ** (pw + 1)
+#     step = (max_val - min_val) / nbins
+#     distribution = Divergence.getDistribution(math.floor((i - min_val) / step) for i in records)
+#     distribution_cen = Divergence.getDistribution(math.floor((i - min_val) / step) for i in records_cen)
+#     distribution_equ = Divergence.getDistribution(math.floor((i - min_val) / step) for i in records_equ)
+#
+#     plt.subplot(131)
+#     x = []
+#     y = []
+#     for i in distribution:
+#         x += [i]
+#         y += [distribution[i]]
[…]

### 2019-11-26 OldStory/SyntheticStatic-Old/count.sh

@@ -1,0 +1,4 @@
+for i in $(seq 133 488)
+do
+    <InputsEqualized/$i.csv wc -l >> CountEqualized.csv
+done

### 2019-11-26 OldStory/tmp/ecdf.R

@@ -1,0 +1,12 @@
+o <- read.csv("original.csv", header = FALSE, stringsAsFactor = FALSE)
+d <- read.csv("dropped.csv", header = FALSE, stringsAsFactor = FALSE)
+o <- o$V1
+d <- d$V1
+
+fo <- ecdf(o)
+fd <- ecdf(d)
+
+mato <- cbind(unique(o), fo(unique(o)))
+matd <- cbind(unique(d), fd(unique(d)))
+write.csv(mato, file = "ecdf_original.csv")
+write.csv(matd, file = "ecdf_dropped.csv")

### 2019-11-26 OldStory/tmp/ecdf.m

@@ -1,0 +1,19 @@
+%subplot(2, 1, 1)
+
+o = csvread("ecdf_original.csv")(:, [2, 3]);
+d = csvread("ecdf_dropped.csv")(:, [2, 3]);
+plot(o(:, 1), o(:, 2), 'rx', 'markersize', 2, d(:, 1), d(:, 2), 'bo', 'markersize', 2)
+legend("Original", "Modified")
+
+%subplot(2, 2, 3)
+%o = csvread("original.csv");
+%d = csvread("dropped.csv");
+%[on ov] = hist(o, 100);
+%[dn dv] = hist(d, 100);
+%plot(ov, on, 'r', dv, dn, 'b')
+
+%subplot(2, 2, 4)
+%[on ov] = hist(o, 50);
+%[dn dv] = hist(d, 50);
+%plot(ov, on, 'r', dv, dn, 'b')
+

### 2019-11-26 OldStory/tmp/rand.py

@@ -1,0 +1,13 @@
+import random
+from itertools import *
+
+print("Start")
+with open("original.csv", 'rt') as infile:
+    with open("dropped.csv", 'w') as outfile:
+        for line in infile:
+            if (0.2 > random.random()): #modify
+                i = int(int(line) * 0.1);
+                outfile.write(str(i) + '\n')
+            else:
+                outfile.write(line)
+

### 2019-11-26 RealWorld/SamplePDF.py

@@ -1,94 +1,0 @@
-import csv
-import Divergence
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-import matplotlib.axis as ax
-
-days = (5, 113, 287)
-lim_x = 24
-lim_y = 0.25
-
-figure = plt.figure(figsize=(7, 7), dpi=100)
-for ii in range(3):
-    day = days[ii]
-    reader = csv.reader(open("Correct/%d.csv" % day, 'r'))
-    reader_cen = csv.reader(open("Centralized/%d.csv" % day, 'r'))
-    reader_equ = csv.reader(open("Equalized/%d.csv" % day, 'r'))
-
-    # freq, dropped = Divergence.histogram(list(int(row[2]) for row in reader), step=1)
-    # freq_cen, dropped = Divergence.histogram(list(int(row[2]) for row in reader_cen), step=1)
-    # freq_equ, dropped = Divergence.histogram(list(int(row[2]) for row in reader_equ), step=1)
-    #
-    # data = freq.values()
-    # data_cen = freq_cen.values()
-    # data_equ = freq_equ.values()
-    # step = 21.48
-
-    data = list(int(row[2]) for row in reader)
-    data_cen = list(int(row[2]) for row in reader_cen)
-    data_equ = list(int(row[2]) for row in reader_equ)
-
-    step = 1
-
-    dropped, hist = Divergence.histogram(data, step)
-    droped, hist_cen = Divergence.histogram(data_cen, step)
-    dropped, hist_equ = Divergence.histogram(data_equ, step)
-
-    id = 1 * 3 + ii + 1
-    plt.subplot(3, 3, id)
-    x = []
-    y = []
-    for i in hist:
-        x += [i]
-        y += [hist[i]]
-    plt.bar(x, y, color='r', label="Normal")
-    plt.xlim(0, lim_x)
-    plt.ylim(0, lim_y)
-    plt.xticks(())
-    if 0 != ii:
-        plt.yticks(())
-    else:
-        plt.legend(loc="upper right")
-        plt.ylabel("Probability", fontsize='x-large')
-
-    id = 0 * 3 + ii + 1
-    plt.subplot(3, 3, id)
-    x = []
-    y = []
-    for i in hist_cen:
-        x += [i]
-        y += [hist_cen[i]]
[…]

### 2019-11-26 Synthetic/GenerateCentralized.py

@@ -1,64 +1,0 @@
-import csv
-import itertools
-import os
-import numpy
-import Divergence
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-
-ratio = 0.5
-
-input_dir = "Correct"
-output_dir = "Centralized(%.1f)" % (1 + ratio)
-d = os.path.abspath(output_dir)
-if not os.path.exists(d):
-    os.makedirs(d)
-
-for file in os.listdir(input_dir):
-    print("Processing: ", file)
-    with open("%s/%s" % (input_dir, file), 'r') as ifile:
-        with open("%s/%s" % (output_dir, file), 'w') as ofile:
-            cnt = 0
-            for line in ifile:
-                cnt += 1
-                ofile.write(line)
-            #num_new = numpy.random.randint(int(cnt * 1.5), int(cnt * 2.0))
-            num_new = int(cnt * ratio)
-            center = numpy.random.randint(10, 21)
-            for item in numpy.random.normal(center * 3600, 1.5 * 3600, num_new):
-                if (item >= (7 * 3600)) and (item < 24 * 3600):
-                    ofile.write("921013,1629,%d\n" % int(item))
-
-# # Check two examples
-# f = open("brackets.txt", 'r')
-# min_val = int(f.readline())
-# max_val = int(f.readline())
-# f.close()
-#
-# figure = plt.figure(figsize=(1400/300, 1400/300), dpi=300)
-# with open("%s/134.csv" % input_dir, 'r') as f:
-#     reader = csv.reader(f)
-#     records = (int(row[2]) for row in itertools.islice(reader, 0, None))
-#     distribution = Divergence.histogramNaive(min_val, max_val, records)
-#     x = []
-#     y = []
-#     for i in distribution:
-#         x += [i]
-#         y += [distribution[i]]
-#     plt.bar(x, y, color="red")
-#     plt.savefig("Sample.png")
-#     figure.clear()
-#
-# with open("%s/134.csv" % output_dir, 'r') as f:
-#     reader = csv.reader(f)
-#     records = (int(row[2]) for row in itertools.islice(reader, 0, None))
-#     distribution = Divergence.histogramNaive(min_val, max_val, records)
-#     x = []
-#     y = []
-#     for i in distribution:
-#         x += [i]
-#         y += [distribution[i]]
-#     plt.bar(x, y, color="blue")
-#     plt.savefig("SampleCentralized.png")
-#     figure.clear()

### 2019-11-26 SyntheticDataGenerator.py

@@ -1,0 +1,258 @@
+import numpy as np
+from Utils import *
+
+
+def genUniform(collection_size, sample_size):
+    COLLECTION_SIZE = collection_size
+    SAMPLE_SIZE = sample_size
+    print()
+
+    # Generate Correct Data Collections #
+    INFIMUM = 0
+    SUPREMUM = 10
+    FLUCTUATION = 5
+
+    print("Generating Correct Uniform Samples...")
+    output_file = open("Synthetic/UniformCorrect.csv", 'w')
+    for _ in range(SAMPLE_SIZE):
+        infimum = INFIMUM + FLUCTUATION * np.random.random() - FLUCTUATION / 2
+        supremum = SUPREMUM + FLUCTUATION * np.random.random() - FLUCTUATION / 2
+        collection = (supremum - infimum) * np.random.random_sample(COLLECTION_SIZE) + infimum
+        output_file.write("%f" % collection[0])
+        output_file.writelines("\t%f" % collection[i] for i in range(1, COLLECTION_SIZE))
+        output_file.write('\n')
+    output_file.close()
+
+    print("Generating Anomalous Uniform Samples...")
+    # Generate Anomalous Data Collections #
+    INFIMUM -= FLUCTUATION
+    SUPREMUM += FLUCTUATION
+
+    output_file = open("Synthetic/UniformAnomalous.csv", 'w')
+    for _ in range(SAMPLE_SIZE):
+        infimum = INFIMUM + FLUCTUATION * np.random.random() - FLUCTUATION / 2
+        supremum = SUPREMUM + FLUCTUATION * np.random.random() - FLUCTUATION / 2
+        collection = (supremum - infimum) * np.random.random_sample(COLLECTION_SIZE) + infimum
+        output_file.write("%f" % collection[0])
+        output_file.writelines("\t%f" % collection[i] for i in range(1, COLLECTION_SIZE))
+        output_file.write('\n')
+    output_file.close()
+
+    print("Uniform Distribution Generation Done.")
+
+
+def genGaussian(collection_size, sample_size):
+    COLLECTION_SIZE = collection_size
+    SAMPLE_SIZE = sample_size
+    print()
+
+    # Generate Correct Data Collections #
+    MU = 0
[…]

### 2019-11-26 Utils.py

@@ -1,0 +1,73 @@
+def loadCollectionFromFile(path):
+    """
+    根据数据文件的固定格式加载数据。
+
+    :param path: 数据文件路径
+    :return: 数据群的列表
+    """
+    data_file = open(path, 'r')
+    data = data_file.readlines()
+    collection = [[float(num) for num in line.strip('\n').split('\t')] for line in data]
+    data_file.close()
+    return collection
+
+
+def calculateConfusionMatrix(sample_size, anomalies, predicted_anomalies):
+    TP = 0
+    FP = 0
+    for i in predicted_anomalies:
+        if i in anomalies:
+            TP += 1
+        else:
+            FP += 1
+    FN = len(anomalies) - TP
+    TN = sample_size - len(anomalies) - FP
+    return TP, TN, FP, FN
+
+
+def calculateROC(anomaly_array, ranked_array):
+    # 计算所有的混淆矩阵 #
+    confusion_matrix_lists = []
+    for i in range(len(anomaly_array)):
+        anomaly = anomaly_array[i]
+        rank = ranked_array[i]
+        confusion_matrix_list = []
+        for k in range(len(rank)):
+            confusion_matrix_list.append(calculateConfusionMatrix(len(rank), anomaly, rank[:k]))
+        confusion_matrix_lists.append(confusion_matrix_list)
+
+    # 对所有对应位置的混淆矩阵求平均 #
+    average_confusion_matrix_list = []
+    for k in range(len(confusion_matrix_lists[0])):
+        confusion_matrixes = [confusion_matrix_list[k] for confusion_matrix_list in confusion_matrix_lists]
+        dim_len = len(confusion_matrixes[0])
+        average_confusion_matrix = tuple(
+            sum(confusion_matrix[dim] for confusion_matrix in confusion_matrixes) / len(confusion_matrixes)
+            for dim in range(dim_len)
+        )
+        average_confusion_matrix_list.append(average_confusion_matrix)
+        # for t in average_confusion_matrix_list:
+        #     s = ''
+        #     for v in t:
+        #         s += str(v) + ','
+        #     print(s)
+        # print("-----")
+
+    # 根据绘制点的数量要求找到绘制点，使点在图像上尽量平均 #
+    coordinates = [(FP / (FP + TN), TP / (TP + FN)) for TP, TN, FP, FN in average_confusion_matrix_list]
+    # first_half = round(points / 2)
+    # last_half = points - 1 - first_half
[…]

### 2019-12-06 Paper/FullPaper/paper.tex
把文章修改为ICME模板

% IEEE Paper Template for US-LETTER Page Size (V1)
% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
% Permission is granted to distribute and revise this file provided that
% this header remains intact.
%
% REVISION HISTORY
% 20080211 changed some space characters in the title-author block
%
\documentclass[10pt,conference,letterpaper]{article}
\usepackage{times,amsmath,amsfonts,epsfig}
\usepackage{graphicx}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{color}
\usepackage{flushend}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{cuted}
\usepackage{rotating}
\usepackage{caption}
%
\title{Statistical Detection of Collective Data Anomalies}
\date{}
%
%\author{%
%	% author names are typeset in 11pt, which is the default size in the author block
%	{Ruoyu Wang{\small$^{1}$}, Daniel Sun{\small$^{2}$}, Guoqiang Li{\small$^{1*}$} }%
%	% add some space between author names and affils
%	\vspace{1.6mm}\\
%	\fontsize{10}{10}\selectfont\itshape
%	% 20080211 CAUSAL PRODUCTIONS
%	% separate superscript on following line from affiliation using narrow space
%	$^{1}$\,School of Software, Shanghai Jiao Tong University, China\\
%	\fontsize{9}{9}\selectfont\ttfamily\upshape
%	%
%	% 20080211 CAUSAL PRODUCTIONS
%	% in the following email addresses, separate the superscript from the email address 
%	% using a narrow space \,
%	% the reason is that Acrobat Reader has an option to auto-detect urls and email
%	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
%	% in the email address and corrupts it.
%	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
%	\{solftwarewry,li.g\}@sjtu.edu.cn
%	% add some space between email and affil
%	\vspace{1.2mm}\\
%	\fontsize{10}{10}\selectfont\rmfamily\itshape
%	% 20080211 CAUSAL PRODUCTIONS
%	% separated superscript on following line from affiliation using narrow space \,
%	\,Data61, CSIRO, Australia\\
%	\fontsize{9}{9}\selectfont\ttfamily\upshape
%	% 20080211 CAUSAL PRODUCTIONS
%	% removed ~ from pre-superscript since it does not seem to serve any purpose
%	$^{2}$\,daniel.sun@data61.csiro.au
%}

%
\begin{document}
\maketitle
%
	\begin{abstract} 
		Attackers infiltrate databases and software systems to not only steal chunks of data and hold them for ransom, but also alter certain parts, setting up traps harder to discover and causing damages unlikely to recover.
		Without referring to data source, it is hard to detect a single record that is altered but still remain in correct value scopes. However, the change, especially to a subset of data, can be observed and detected in a collective scale. 
		In this paper, we present a collective detection technique based on statistical divergence. \textcolor{red}{Statistical divergence detection was explored in multimedia applications. But it is still underdeveloped in big data era due to data irregularity.} The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
		Our technique continuously evaluates metrics as evolving features and calculate adaptive threshold to meet the best mathematical expectation.
		To illustrate details of the technique and explore its efficiency, we case-studied a real world problem of click farming detection against malicious online sellers. The evaluation shows that these techniques provided efficient classifiers. They were also sufficiently sensitive to a much smaller magnitude of data alteration, compared with real world malicious behaviours. Thus, it is applicable in the real world. 
	\end{abstract}

% NOTE keywords are not used for conference papers so do not populate them
% \begin{keywords}
% keyword-1, keyword-2, keyword-3
% \end{keywords}
%
	\section{Introduction}
		Major improvements in data acquisition, transmission and storage are to increase data availability and affordability. Currently, there are more than 2.7ZB data in the digital universe~\cite{bigDataStatistics} and the growing speed is doubling every two years.
		It has already been hard and will be much harder in the future to harness the exploding volume of data that has resulted in many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\cite{saha2014data}. Those data anomalies may arise due to both internal and external reasons.

		On one hand, components inside systems may generate problematic source data. For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\cite{rassam2014adaptive}. Data packages will be lost if sensor nodes fail to connect to network or some sensor hubs break down~\cite{herodotou2014scalable}. Also, human operators act as a heavily vulnerable part to bugs and mistakes. Malicious insiders even deliberately modify system configurations for fatal compromises~\cite{schuster2015vc3}. A study shows that 65\% of organizations state that human errors are the main  cause of data problems~\cite{humanError} .

		On the other hand, data manipulation~\cite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability. \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
		If data is compromised, it will severely affect mining and learning algorithms and further change the final decision driven by the data. In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.

		It is hard to detect a single record that is alerted but still remain in correct value scopes, but if sufficient data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
		According to our observation, typical manipulations on numerical data will lead to a drift or distortion of its original distribution. For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones. 
		To address problems caused by data manipulation, we propose a novel technique which sorts out manipulated data collections from normal ones by adopting statistical divergence.
		\textcolor{red}{Statistical divergence detection was explored in multimedia applications. But it is still underdeveloped in big data era due to data irregularity.}
		In this paper, we focus on a concrete data manipulation problem: click farming in online shops, and try to apply our technique to pick out those dishonest sellers.
		Our techniques maps data collections to points in distribution spaces and reduce the problem to classical point anomaly detection.
		Optimizations estimate ground truth, mapping each data collection into a single real number within a definite interval. Then a Gaussian classifier can be applied to detect outliers derived from manipulated data. To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by statistical divergence.
		In the dynamic environments, these evidence sets are modified after every data collection is checked, in which manner they act intuitively as slide windows and keep up to the evolving features in dynamic scenarios.
		Our contribution includes: 1) A brief review on data anomaly detection and a study on the problem of click farming; 2) Detailed description of both basic and optimized framework of our technique, resolving several technical difficulties such as automated adaptive threshold; 3) Real world and synthetic data experiments that test efficiency of our technique and a comparison with a previous work on the same topic.

		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related work on data anomaly detection and describes a real world problem. Section~\ref{sec:preliminaries} introduces statistical distance. Details of proposed technique are introduced in section~\ref{sec:algorithm-details}. Then section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm. Finally, the paper is concluded in section~\ref{sec:conclusion}.

	\section{Related Work}\label{sec:related-work}
		\subsection{Data Anomaly Detection}
			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.
			Anomaly detection algorithms deal with input data in the form of points (or records), sequences, graphs and spatial and geographical relationships.~\cite{chandola2009anomaly} According to relationships within data records, outliers can be classified into \textit{point anomalies}, \textit{contextual (or conditional) anomalies} and \textit{collective anomalies}.~\cite{goldberger2000components}

			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} catch most attention. Others adopted tree isolation~\cite{zhang2017lshiforest}, model based~\cite{yin2016model} and statistical methods~\cite{zhu2002statstream} in certain applications.

			To detect collective anomalies,~\cite{caudell1993adaptive} adopts the \textit{ART (Adoptive Resonance Theory)} neural networks to detect time-series anomalies. \textit{Box Modeling} is proposed in ~\cite{chan2005modeling}. \textit{Longest Common Subsequence} was leveraged in~\cite{budalakoti2006anomaly} as similarity metric for symbolic sequence. Markovian modeling techniques are also popular in this domain\cite{ye2000markov,warrender1999detecting,pavlov2003sequence}. \cite{yu2015glad} depicts groups in social media as combinations of different ``roles'' and compare groups according to the proportion of each role within each group.

			Wang et al. proposed a technique, \textit{Multinomial Goodness-of-Fit} (MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence, and is fundamentally a hypothesis test on distributions~\cite{wang2011statistical}.
			MGoF divides the observed data sequence into several windows. It quantifies data in each window into a histogram and check these estimated distributions against several hypothesis. If the target distribution rejects all provided hypothesis, it is considered an anomaly and preserved as a new candidate of null hypothesis. If the target distribution failed to reject some hypothesis, then it is considered a supporting evidence of the one that yields most similarity. Furthermore, if the number of supporting evidence is larger than a threshold $c_{th}$, it is classified as non-anomaly.

			MGoF is the best competitor out of the similar techniques, and we use it as our baseline against our approach.

		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
%			Since the establishment of Taobao in 2003, its online business platform has been growing from a follower in the market to the No.1 service provider in B2B and B2C markets, 
			Taobao possesses a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}. Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products. Under the super-pressure caused by massive competitors, a number of the sellers choose to use some cheating techniques to raise reputation and sale volumes, then improve rankings in search lists.

			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of customer accounts to create fake transaction records and give high remarks on products. Professional click farmers are usually well organized groups or companies containing thousands of people.
%			Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions. 
			Some companies even develop professional applications that can be deployed on common PCs to improve productivity~\cite{zhao2016on}.

			There are two types of click farming behaviours: Centralized and Equalized. Centralized click farming refers to the scenarios that transactions are randomly generated throughout the day. A significant feature of this approach is that the cheating transactions usually assemble together in a short period of time since most workers work at the same time. Equalized click farming refers to the circumstances that click farms are arranged by some well programmed applications or teams carefully managed and strictly commit transactions according to a timetable. Thus the transaction distribution may not vary too much with and without click farming.

			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% are aware of click farm and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}. American researchers reported in 2015 that over 11000 sellers on Taobao were detected to have click farmed records and only 2.2\% of 4000 investigated dishonest sellers had been penalized because of the cheating attempts~\cite{netease2015research}.

			Current detection techniques for click farming mainly focus on user behaviours, such as browsing frequencies and periods, most common purchasing time, favourite products, remarks and whether they communicate with sellers~\cite{simpleDetection}. Those techniques require the platform to keep lots of records and user features. However, the detection can be easily bypassed by trained workers and some well programmed applications.

			\begin{figure}[t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
				\caption{Example cumulative distribution function of original and click farmed daily transaction data}
				\label{fig:example-ecdf}
			\end{figure}

			Although it is hard to classify users as honest or malicious, we can still find clues from the sellers' aspect. For normal sellers, their customers are usually similar since choices of products are seldom changed. Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable. No matter how much alike between honest users and robots or the employed workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution. To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records and emulated the circumstances if it had been click farmed (see section~\ref{sec:exp-methodology}). Fig.~\ref{fig:example-ecdf} shows the difference between normal and click farmed distributions of one day in the data set.
			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.

	\section{Preliminaries}\label{sec:preliminaries}
		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold. Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers: 
		\begin{equation}
			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+} \cup \{0\}
		\end{equation}

		Divergence between two distributions $P$ and $Q$, written as $D(P||Q)$, satisfies:

		\begin{enumerate}
			\item $D(P||Q) \ge 0, \forall P, Q \in \mathbb{S}$
			\item $D(P||Q) = 0$, if and only if $P=Q$
		\end{enumerate}

		For our purposes, we do not require the function $D$ to have the property: $D(P||Q) = D(Q||P)$. But we do need it to be true that if $Q$ is more similar with $P$ than $U$, then $D(Q||P) < D(U||P)$. There are ways to calculate divergence,	several frequently used divergence metrics are as follows:

		\subsection{Kullback-Leibler Divergence}
			Let $P,Q$ be discrete probability distributions, $Q(x)=0$ implies $P(x)=0$ for $\forall x$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:

			\begin{equation}
				KLD(P||Q) = \sum_{Q(x)\ne 0} P(x)log\Big(\frac{P(x)}{Q(x)}\Big)
			\end{equation}

			For $P,Q$ being continuous distributions:

			\begin{equation}
				KLD(P||Q) = \int_{q(x) \ne 0} p(x)log\frac{p(x)}{q(x)}dx
			\end{equation}

		\subsection{Jensen-Shannon Divergence}
			Let $P,Q$ be discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:

			\begin{equation}
				JSD(P||Q) = \frac{1}{2}KLD(P||M) + \frac{1}{2}KLD(Q||M)
			\end{equation}
			where $\displaystyle M = \frac{1}{2}(P+Q)$.

			A more generalized form is defined to be:

%			{\small
			\begin{equation}
					JSD(P_1, \dots, P_n) = H\Big(\sum_{i=1}^n\pi_i P_i\Big) - \sum_{i=1}^n\pi_iH(P_i)
			\end{equation}
%			}
			where $H$ is Shannon Entropy, $\displaystyle M = \sum_{i=1}^{n}\pi_iP_i$ and $\displaystyle \sum_{i=1}^{n}\pi_i = 1$.

			Especially, if $\displaystyle \pi_i = \frac{1}{n}$, then:
			\begin{equation}
				JSD(P_1, \dots, P_n) = \frac{1}{n}\sum_{i=1}^{n}KLD(P_i||M)
			\end{equation}

			Jensen-Shannon divergence has some fine properties:
			\begin{enumerate}
				\item $JSD(P||Q) = JSD(Q||P), \forall P, Q\in \mathbb{S}$.
				\item $0 \le JSD(P_1, \dots, P_n) \le log_k(n)$. If a $k$ based algorithm is adopted.
				\item To calculate $JSD(P||Q)$, it need not necessarily to be true that $Q(x)=0$ implies $P(x)=0$.
			\end{enumerate}

		\subsection{Bhattacharyya Distance}
			Let $P,Q$ be discrete probability distributions over same domain $X$, \textit{Bhattacharyya Distance} between $P$ and $Q$ is defined to be:

			\begin{equation}
				BD(P||Q) = -ln\Big(\sum_{x\in X}\sqrt{P(x)Q(x)}\Big)
			\end{equation}

		\subsection{Hellinger Distance}
			Let $P,Q$ be discrete probability distributions, \textit{Hellinger Distance} between $P$ and $Q$ is defined to be:

			\begin{equation}
				HD(P||Q) = \frac{1}{\sqrt{2}}\sqrt{\sum_x\bigg(\sqrt{P(x)} - \sqrt{Q(x)}\bigg)^2}
			\end{equation}

		\subsection{Kolmogorov-Smirnov Statistic}
			Let $P,Q$ be discrete one-dimensional probability distributions, $CDF_P$ and $CDF_Q$ are their cumulative probability functions respectively, \textit{Kolmogorov-Smirnov Statistic} between $P$ and $Q$ is defined to be:

			\begin{equation}
				KSS(P||Q) = \sup_x | CDF_P(x) - CDF_Q(x) |
			\end{equation}

	\section{Statistical Detection}\label{sec:algorithm-details}

		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records. For example, traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale. Manipulation on those data (e.g. Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger an alarm.

		\subsection{Statistical Divergence Detection with Reference(SDD-R)}\label{sec:alg-opt-reference}
			From Section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions. In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the symmetric divergence between two connected nodes. From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies. This may work if anomalous nodes do not compose a large proportion. However the procedure will be too complicated to work out with large amounts of data. If it is assured that data collections form only one cluster, some optimizations can be applied to reduce complexity.

			Alternatively we can provide a frame of reference that generates absolute coordinates rather than the relative ones. This optimization is feasible if data collections form one single cluster in distribution space. This is true in most reality scenarios given that distribution is adopted to depict a macro property which comes out as one universal conclusion. In other words , if multiple distributions are used to describe subgroups of entire sample space, then a conclusive one can be obtained by averaging all these sub-distributions. Therefore, we can use an estimate cluster center as reference and test distances between the reference and each other data collections(Algorithm~\ref{alg:sdd-r}), yielding absolute distances.

			\begin{algorithm}[!t]
				\caption{SDD-R}
				\label{alg:sdd-r}
				\begin{algorithmic}[1]
					\Require Data Collections $\mathbb{D} = \{D_1, \dots, D_n\}$
					\Require Estimated anomalous probability $\alpha$
					\Ensure Anomalous Data Collections
					\For {$i \gets 1$ to $n$}
						\State $P_i \gets$ the distribution of $D_i$
					\EndFor
					\State $P_R \gets \frac{1}{n}\sum_{i = 1}^n P_i$
					\For {$i \gets 1$ to $n$}
						\State $d_i \gets D(P_i||P_R)$
					\EndFor
					\State $\mathcal{N}(\mu, \sigma) \gets$ Gaussian distribution estimated by $d_i$
					\State \Return $\{D_i | \frac{d_i - \mu}{\sigma} > 3 \}$
				\end{algorithmic}
			\end{algorithm}

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/JSD-Dist.png}
				\caption{Distribution of Jensen-Shannon divergence on Taobao data set(without click farming) used in the experiments.}
				\label{fig:jsd-dist}
			\end{figure}

			Fig.~\ref{fig:jsd-dist} shows distribution of all divergences against the reference. It can be approximated as a Gaussian distribution though the true one may differ a little more from the standard Gaussian than the expected estimation error. That is due to the unknown randomness within real world data. Few assumptions can be applied in real world data sets, no mention that data volume is sometimes relatively low. This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model. 
			Certainly, if stronger assumptions can be included to provide a more precise model, this component in the framework can be replaced to give better results.
			For the simplicity of our proposal, we deem the distributions of divergences to be Gaussian.

			By this approach, time complexity can be reduced from quadratic to linear. Fig.~\ref{fig:raw-overview} in Section~\ref{sec:exp-raw} demonstrates the result of the above process. Red distribution refer to the distances calculated from normal data collections, blue and green ones are from click-farmed data collections. Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value.

		\subsection{Optimization: Statistical Divergence Detection with Evidence(SDD-E)}
			It is possible to further optimize SDD-R if we can provide this algorithm with evidence(Algorithm~\ref{alg:sdd-e}).

			\begin{algorithm}[!t]
				\caption{SDD-E}
				\label{alg:sdd-e}
				\begin{algorithmic}[1]
					\Require Evidence set with normal data collections $\mathbb{E}_N = \{N_1, \dots, N_n\}$
					\Require Evidence set with anomalous data collections $\mathbb{E}_A = \{A_1, \dots, A_m\}$
					\Require Estimated anomalous probability $\alpha$
					\Require New data collection $\mathbb{D} = \{D_1, \dots, D_l\}$
					\Ensure Anomalous data collections in $\mathbb{D}$
					\For{$i \gets 1$ to $n$}
						\State $P_{N_i} \gets$ distribution of $D_{N_i}$\label{line:hist-1}
					\EndFor
					\For{$i \gets 1$ to $m$}
						\State $P_{A_i} \gets$ distribution of $D_{A_i}$\label{line:hist-2}
					\EndFor
					\State $P_R \gets \frac{1}{n}\sum_{i=1}^{n}P_{N_i}$
					\For{$i \gets 1$ to $n$}
						\State $d_{N_i} \gets D(P_{N_i}||P_R)$
					\EndFor
					\For{$i \gets 1$ to $m$}
						\State $d_{A_i} \gets D(P_{A_i}||P_R)$
					\EndFor
					\State $\mathcal{N}_N(\mu_N, \sigma_N) \gets$ normal distribution estimated from $\{d_{N_1}, \dots, d_{N_n}\}$
					\State $\mathcal{N}_A(\mu_A, \sigma_A) \gets$  normal distribution estimated from $\{d_{A_1}, \dots, d_{A_m}\}$
					\State $T \gets$ proper threshold derived from $\mathcal{N}_N$, $\mathcal{N}_A$ and $\alpha$
					\For{$i \gets 1$ to $l$}
						\State $P_i \gets$ distribution of $D_i$
						\State $d_i \gets D(P_i||P_R)$
					\EndFor
					\State \Return $\{D_i|d_i > T\}$
				\end{algorithmic}
			\end{algorithm}

			Evidences enables the algorithm to not only refine estimation of real distribution but also build knowledge of anomalous collections, which is similar to the parameter estimation within a certain sample set.

			According to the property of statistical divergence, we can infer that the true distribution of divergences calculated from normal data collections are close to but not exactly a Gaussian distribution $\mathcal{N}(\mu, \sigma)$ since for each point, there are both definite upper and lower bounds instead of infinities. Therefore, $\mu$ should be slightly larger than zero($\mu = 0 \iff P_i = P_j, \forall P_i, P_j \in \mathbb{E}_N$, for real world data sets, this is highly unlikely). Time complexity for this algorithm is still linear but with a larger coefficient.

			For certain divergence, it is possible to compare similarity from one distribution against multiple others, such as Jensen-Shannon Divergence. Although it reduces time complexity, it sacrifices unaffordable accuracy because divergence among multiple distribution dilutes differences. Take JSD as an example, suppose $P(1) = P(2) = P(3) = \frac{1}{3}$ and $Q(1) = \frac{1}{6}, Q(2) = \frac{1}{3}, Q(3) = \frac{1}{2}$, then $JSD(P||Q) \approx 0.033$ and $JSD(P, P, P, Q) \approx 0.024$.

			This algorithm can be slightly modified to deal with concept drift(for example, trading trend changes over time for online shops as they are often in the process of expanding or dwindling) by turning the two evidence sets as sliding windows and adopting certain update strategies such as \textit{Least Recently Used}(LRU). Time complexity for this optimization is $O(n\cdot(|\mathbb{E}_N|+|\mathbb{E}_A|)\cdot T_D)$, where $T_D$ denotes time complexity of divergence calculation.

		\subsection{Threshold}\label{sec:alg-threshold}
			One important factor in algorithm SDD-E is the value of threshold. A lower threshold rejects more instances, improving the sensitivity of anomalous data while increasing the number of false alarms. A higher threshold provide higher true negative rates yet neglecting more possible threats.

			A naive but prevalent approach is to set a fixed value as the threshold(As is shown in Algorithm~\ref{alg:sdd-r}). This approach is easy to implement and may give satisfying results in specific cases. However, a fixed threshold requires specific analysis in the certain scenario, manual observations and tuning of parameters, which involves lots of human labour. The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous. It can be used to automatically determine a threshold. But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided. It would be either lower than the optimum if anomalous data lies far away from the normal cluster, or higher than the optimum if the anomalies sit close to the cluster centre.

			Fortunately, applying divergence as the distance measurement among data collections provides a fine property. With a reference distribution, divergences of normal data collections form a quasi-Gaussian distribution as we have seen in section \ref{sec:alg-opt-reference}. The same applies to those anomalous ones.

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
				\caption{Threshold can be determined either by a probability density value, or a radius from the centre. In the scenario shown in the figure, the threshold can be determined by the position between two centres of the distribution, denoted as ``T'' here. This form of threshold can also be applied to other types of distributions even there is no intersection between these two.}
				\label{fig:example-threshold}
			\end{figure}

			Moreover, as is verified in experiments, the meta-distribution of anomalous data collections lies in the right-hand-side to the normal one on the real line. As shown in Fig~\ref{fig:example-threshold}, the black curve ($PDF_{normal}(x)$ or in short $PDF_n(x)$) displays the probability density function (PDF) fitting those divergences calculated from normal data collections; the blue curve ($PDF_{anomalous}(x)$ or in short $PDF_a(x)$) displays the PDF derived from anomalous data collections. Threshold is chosen to minimize total errors(both false negative and false positive).

			Suppose:
			\begin{align}
				PDF_n(x) &\approx \mathcal{N}(\mu_n, \sigma_n)\\
				PDF_a(x) &\approx \mathcal{N}(\mu_a, \sigma_a)
			\end{align}

			Then the optimal threshold $T$ is calculated by E.q.(\ref{equ:equal-weight}). The optimal threshold will minimize total errors and yield an optimal outcome.
			However, this is not accurate enough, since E.q.(\ref{equ:equal-weight}) implicates an assumption that chances are the same for a new data collection to be either anomalous or not. If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as E.q.(\ref{equ:linear-weight}), where $\alpha$ is the anomaly probability.

			\begin{align}\label{equ:equal-weight}
				T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{a}(x)dx +
				\int_{T}^{\sup(D)}PDF_{n}(x)dx \nonumber\\
				& \approx \mathop{\arg\min}_{T}
				\int_{-\infty}^{T}
				\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
				+ \int_{T}^{+\infty}
				\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx \nonumber\\
				& = \begin{cases}
				\displaystyle
				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{\sigma_a}{\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
				\displaystyle \frac{\mu_n + \mu_a}{2}, & \sigma_a = \sigma_n
				\end{cases}
			\end{align}

			Note: when $\sigma_a \ne \sigma_n$, keep the root s.t. $\displaystyle \frac{T - \mu_a}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{T - \mu_n}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$

			\begin{align}\label{equ:linear-weight}
				T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
				(1-\alpha)\int_{T}^{\sup(D)}PDF_{n}(x)dx\nonumber\\
				& \approx \mathop{\arg\min}_{T}
				\alpha\int_{-\infty}^{T}
				\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
				+ 
				(1-\alpha)\int_{T}^{+\infty}
				\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\nonumber\\
				& = \begin{cases}
				\displaystyle
				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{(1 - \alpha)\sigma_a}{\alpha\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
				\displaystyle
				\frac{\mu_n + \mu_a}{2} + \frac{k^2ln\frac{1 - \alpha}{\alpha}}{\mu_a - \mu_n}, & \sigma_a = \sigma_n = k
				\end{cases}
			\end{align}

			Note: when $\sigma_a \ne \sigma_n$, keep the root s.t. $\displaystyle \frac{\alpha (T - \mu_a)}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{(1 - \alpha) (T - \mu_n)}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$

			Moreover, with an estimated anomaly probability, SDD-R can be also optimized by ranking all data collections according to their divergence value and select first $n \cdot \alpha$ ones with highest values as anomalies.

	\section{Evaluation}\label{sec:evaluation}
		Our algorithm was implemented and interpreted in Python 3.5.2. All experiments were tested on Ubuntu 16.04. In the following experiments, we figured out properties of real world data and performance of our technique against anomalous data collections. We also made a comparison among variations of SDD algorithms and MGoF.\footnote{All resources and more detailed experiment results can be retrieved online: https://github.com/TramsWang/StatisticalAnomalyDetection}

		\subsection{Methodology}\label{sec:exp-methodology}
			We adopted two data sets: 1) Koubei sellers' transaction records\footnote{https://tianchi.aliyun.com/competition/information.htm?raceId=231591}; 2) Synthetic random distribution data set. Koubei data set was provided by Alibaba Tian Chi big data competition where all records were collected from real world business scenarios. It contained information about seller features, user payments and browsing behaviour. We randomly chose one seller (ID: 1629) and extracted transaction history of this seller, records ranging from Nov. 11th 2015 to Oct. 31st 2016. Entire transaction set was then divided into 325 collections, each containing records in one day. Fig.~\ref{fig:daily-transaction-volume} and~\ref{fig:sale-distribution-sample} give an overview of it.

			\begin{figure}[!t]
				\centering
				\includegraphics[width=0.75\linewidth]{fig/DailyTransactionVolume.png}
				\caption{Changing of the daily sales volume shows that environment of online sales had been changing all the time.}
				\label{fig:daily-transaction-volume}
			\end{figure}

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/SaleDistributions.png}
				\caption{We selected 3 days randomly and drew sales distribution by counting hourly volume. Although sales volume has changed from day to day, the shape of the distribution remain almost alike.}
				\label{fig:sale-distribution-sample}
			\end{figure}

			Two types of click-farmed data was generated according to patterns described in section~\ref{sec:related-realworld}. To emulate centralized click farming, we randomly inserted some Gaussian-distributed transactions in the chosen collection. As for emulating the equalized click farmers, we simply doubled each record in the chosen collection to make the new distribution exactly the same as the original one, which is harder for the online platform to discover.
			Usually, the click-farmed transactions are several times more than the volume it originally has, if the seller hires a group of organized workers. In our experiments, we use $\nu$ to denote the magnitude coefficient of click farming. Hence $|D_{anomalous}| = (1 + \nu)|D_{normal}|$. In the following experiments without extra illustration, we adopted $\nu = 1$.

			One defect of this data set is that the detailed time stamp is aligned at each hour of the day due to desensitization. We constructed an enhanced data set by assigning every time stamp a random value for minutes and seconds. Therefore, the enhanced data set should be closer to the reality.

			The synthetic data set was divided into four sections. First two sections contained sample sets drawn from a uniform and a Gaussian distribution respectively. The third section used a mixture of one uniform distribution and two Gaussian distributions to simulate a random-shaped distribution. Moreover, we made the random-shaped distribution drift slightly to form the last section of test data. Corresponding anomalies were drown from distributions with deviated parameters respectively.

			We adopted histograms to depict distributions of any shape. Surely, the kernel density estimation approaches will give smooth and continuous estimations on any sampled data. But the computational cost will be too much to afford. Step size of histograms is chosen by:
			\begin{equation}\label{equ:step-size}
				l = c \sigma k^{-0.2},
			\end{equation}
			where $k$ is sample size, $c$ is a constant relative to the shape of distribution (e.g. for normal distribution, $c=1.05$) and $\sigma$ the standard deviation. For data sets with a large number of elements, a random sampling method, such as Monte-Carlo method, can be applied to speed up the estimation procedure.

			Divergence metric adopted in each SDD algorithms was Jensen-Shannon divergence if no specific notation is made. However, MGoF used only Kullback-Leibler divergence due to its special mechanism. We use a ``+'' to denote algorithms optimized by a given $\alpha$.

		\subsection{Experiments on Koubei Data Set}\label{sec:exp-raw}
			We first tested our algorithms on Koubei data set in order to see whether and why the algorithm works. Anomalies were random selected days replaced by corresponding click farmed version. To play the role of purchasing platform, we investigated two levels of transaction distribution. The first level is to simply draw a histogram aligned to time spans. The second level is to draw a histogram on the sub-volumes in each time span(i.e. a histogram on frequencies in the first level histogram, as shown in Fig.~\ref{fig:histogram-example}).

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/HistogramExample.png}
				\caption{Examples of 1st and 2nd Level Histogram}
				\label{fig:histogram-example}
			\end{figure}

			On the raw data set, we had no choice but to set one hour a basket. While on the enhanced data set, we adopted E.q.(\ref{equ:step-size}) to determine step size automatically.
			To test SDD-E, we randomly selected 30 correct days and 10 click farmed days as normal and anomalous evidence respectively.
			Here $\alpha = 0.2$. The results are shown in Table~\ref{tab:result-koubei-raw} and \ref{tab:result-koubei-enhanced}.

			\begin{sidewaystable}
				\centering
				\caption{Performance on Raw Data}
				\label{tab:result-koubei-raw}
				\footnotesize
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					\multirow{3}{*}{\textbf{}} & \multicolumn{8}{c|}{\textbf{Centralized}} & \multicolumn{8}{c|}{\textbf{Equalized}} \\ \cline{2-17} 
					& \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} & \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} \\ \cline{2-17} 
					& \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} \\ \hline
					\textbf{SDD-R} & 89.51 & 48.75 & 63.12 & 266.77 & 21.97 & \textbf{99.38} & 35.98 & 11.12 & 6.67 & 0.63 & 1.14 & 249.15 & 21.22 & 72.50 & 32.83 & 7.81 \\ \hline
					\textbf{SDD-R+} & 91.25 & 91.25 & \textbf{91.25} & \textbf{265.96} & \textbf{61.88} & 61.88 & 61.88 & 10.08 & 9.38 & 9.38 & 9.38 & \textbf{247.31} & \textbf{44.38} & 44.38 & 44.38 & 6.92 \\ \hline
					\textbf{SDD-E Static} & \textbf{92.46} & 68.75 & 78.86 & 292.50 & 36.55 & 98.13 & 53.26 & 5.75 & 6.67 & 0.63 & 1.14 & 271.45 & 36.07 & 86.25 & 50.86 & 5.64 \\ \hline
					\textbf{SDD-E Static+} & 85.02 & 32.50 & 47.02 & 293.77 & 46.24 & 91.88 & 61.52 & 5.95 & 10.00 & 0.63 & 1.18 & 272.71 & 43.60 & 76.25 & \textbf{55.48} & 5.68 \\ \hline
					\textbf{SDD-E Dynamic} & 49.11 & \textbf{99.38} & 65.73 & 699.97 & 23.01 & \textbf{99.38} & 37.37 & 245.65 & 10.36 & \textbf{18.13} & \textbf{13.18} & 681.09 & 22.09 & \textbf{93.13} & 35.71 & 242.85 \\ \hline
					\textbf{SDD-E Dynamic+} & 73.21 & 98.75 & 84.09 & 701.06 & 48.02 & 96.25 & \textbf{64.07} & 255.43 & 8.15 & 6.88 & 7.46 & 681.89 & 40.79 & 78.13 & 53.59 & 253.03 \\ \hline
					\textbf{MGoF} & 14.08 & 21.88 & 17.13 & 292.14 & 13.01 & 4.38 & 6.55 & \textbf{3.64} & \textbf{12.50} & 3.13 & 5.00 & 250.42 & 12.50 & 3.13 & 5.00 & \textbf{3.71} \\ \hline
				\end{tabular}

				\vskip\baselineskip
				\caption{Performance on Enhanced Data}
				\label{tab:result-koubei-enhanced}
				\footnotesize
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					\multirow{3}{*}{\textbf{}} & \multicolumn{8}{c|}{\textbf{Centralized}} & \multicolumn{8}{c|}{\textbf{Equalized}} \\ \cline{2-17} 
					& \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} & \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} \\ \cline{2-17} 
					& \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} \\ \hline
					\textbf{SDD-R} & 81.54 & 41.88 & 55.33 & 238.61 & 17.49 & 92.50 & 29.42 & 13.86 & 6.67 & 0.63 & 1.14 & 239.44 & 21.15 & 71.88 & 32.69 & 12.08 \\ \hline
					\textbf{SDD-R+} & \textbf{91.25} & 91.25 & \textbf{91.25} & \textbf{236.94} & 36.88 & 36.88 & 36.88 & 12.98 & 8.13 & 8.13 & 8.13 & \textbf{236.47} & 38.75 & 38.75 & 38.75 & 11.03 \\ \hline
					\textbf{SDD-E Static} & 88.31 & 67.50 & 76.52 & 257.60 & 31.99 & 92.50 & 47.54 & 9.74 & 6.67 & 0.63 & 1.14 & 257.65 & 34.49 & 91.25 & 50.06 & 9.37 \\ \hline
					\textbf{SDD-E Static+} & 69.67 & 13.13 & 22.09 & 259.30 & \textbf{42.12} & 73.75 & \textbf{53.62} & 9.59 & 10.00 & 0.63 & 1.18 & 258.45 & \textbf{44.17} & 82.50 & \textbf{57.54} & 9.32 \\ \hline
					\textbf{SDD-E Dynamic} & 42.93 & \textbf{99.38} & 59.96 & 1106.25 & 20.12 & \textbf{95.63} & 33.25 & 277.70 & 10.57 & \textbf{17.50} & \textbf{13.18} & 1108.93 & 20.30 & \textbf{94.38} & 33.42 & 271.74 \\ \hline
					\textbf{SDD-E Dynamic+} & 69.18 & 98.13 & 81.15 & 1110.81 & 33.25 & 87.50 & 48.19 & 292.60 & 7.06 & 3.75 & 4.90 & 1118.00 & 37.21 & 80.63 & 50.92 & 283.50 \\ \hline
					\textbf{MGoF} & 13.97 & 17.50 & 15.54 & 294.08 & 14.66 & 8.13 & 10.45 & \textbf{8.01} & \textbf{12.50} & 3.13 & 5.00 & 250.10 & 18.42 & 8.75 & 11.86 & \textbf{7.55} \\ \hline
				\end{tabular}
			\end{sidewaystable}

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/Raw1stLevelHist.png}
				\caption{1st level histogram of day 5, 113 and 287, each day in a column. Distributions after centralized and equalized click farming are in 1st and 3rd rows correspondingly. And the original distributions are shown in the 2nd row.}
				\label{fig:raw-hist-1st}
			\end{figure}

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/RawOverview2nd.png}
				\caption{This figure shows distribution of JSD values(on 2nd level histograms) of normal and two types of click farming data. Divergences were calculated according to a reference averaged among all correct distributions.}
				\label{fig:raw-overview}
			\end{figure}

			When classifying toward 1st level histograms, centralized click farming behaviours can be easily discovered. As displayed in the first two rows in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click-farmed ones abruptly violated the original shape. However, as a clever click farmer, equalized click farming did not in the least distort the distribution. Most of them escaped the check under perfect disguises.
			But when it came to 2nd level histograms, the ``clever disguise'' did not work any longer. It can be clearly seen in Fig.~\ref{fig:raw-overview} that distribution of divergence of both click farming types shows an obvious deviation from the normal one.

			The result showed that our technique outperformed MGoF in every real world cases.
			SDD-E provided best performance, yet it consumed the most computing power. Comparison among SDD-R revealed improvement of reference as well as the importance of threshold under this technique. Although dynamic SDD-E consumes more computation power, it is clear that dynamic SDD-E is capable of tracing the gradual shift of environment. MGoF turned out to be the worst since it always mark several false positive when $c_{th}$ had not been met and much more false negatives when similar errors occurred too many.

			Parameter $\alpha$ improved total accuracy of dynamic SDD-E algorithm by 10-20\% as was supposed. It also increased its F1 by more than 20\%. $\alpha$ made a great difference in SDD-R as well, which illustrated that divergence sorted almost all collections in correct order according to the averaged reference. However, static SDD-E did not show the same improvement. Since environment drift took greater influence in the result. In comparison with $\alpha$, adaptive threshold given by evidence sets did not bring the most improvement. But this threshold can be applied together with other optimizations such as slide windows.

		\subsection{Test against Anomaly Proportion and Magnitude}\label{sec:exp-synthetic}
			In this experiment, we tested algorithm performance under various anomaly proportion and magnitude. $\alpha$ ranged from 0.1 to 0.9 when $\nu = 1$ and $\nu \in [0.1, 0.9]$ when $\alpha = 0.1$, other settings remains the same.

			\begin{figure}[!t]
				\includegraphics[width=\linewidth]{fig/AccuracyOnAnomalyProbability.png}

				\includegraphics[width=\linewidth]{fig/F1OnAnomalyProbability.png}
				\caption{Accuracy and F1 on Different Anomaly Probabilities}
				\label{fig:anomaly-probability}
			\end{figure}

			Fig.~\ref{fig:anomaly-probability} shows that our technique outperformed MGoF and was relatively stable when dealing with all proportions of 1st level centralized anomalies. SDD-E performed even better since it maintains knowledge of both normal and anomalous distributions and calculates the threshold according to the best expectation. However, it relies on the accuracy of distribution estimation. When it came to 2nd level distributions, histograms became much coarser since data available was highly limited and thus its performance suffered dramatically.

			MGoF tended to classify every distribution as anomaly, therefore benefited most by larger $\alpha$. It always classifies as anomalous the first $c_{th}$ distributions supporting every null hypothesis. Thus when $\alpha$ increased, the proportion of misclassified normal collections also became larger, while those anomalies were still considered anomalous. And given that the total number of normal collections drops down, the overall accuracy tended to increase as more instances are correctly classified as anomalous. However, the right half shows a different trend. One reason is that MGoF uses KLD other than JSD. In the Koubei dataset, the discrete estimation of distributions oscillated in a wide range, leading to that the prerequisite of KLD is often unsatisfied. Thus the calculation of KLD may not give a correct measurement. Furthermore, the 2nd histogram provided fewer probability entries than the 1st level did. Thus it shows a more significant deviation from our expectation.
			For the classifiers of MGoF, they  compromised to a high error rate. Because more anomalies gathered together and the algorithm recognized them as clusters of normal data.

			\begin{figure}[!t]
				\includegraphics[width=\linewidth]{fig/PerformanceOnAnomalyMagnitude.png}
				\caption{Accuracy and F1 on Different Anomaly Magnitudes}
				\label{fig:anomaly-magnitude}
			\end{figure}

			From Fig.~\ref{fig:anomaly-magnitude} we can conclude that our algorithms are still the best, given that they are most sensitive toward tiny anomalous variations. However, static SDD-E did not rise until $\nu > 1$, this is because it suffered from fluctuation on the trade environment at the mean time. MGoF is not sensitive toward minor anomalies either.
			For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold could not automatically rise up and was thus far from to optimal.

		\subsection{Results on Synthetic Data Set}
			In this experiment, we tested all seven algorithms on totally synthetic data sets. Results are shown in TABLE~\ref{tab:performance-synthetic}. It shows that our technique can be applied towards any kind of distributions. And these techniques worked better under irregular distributions since difference were clearer among these. Comparison between SDD-R and static SDD-E 
			shows that adaptive thresholds provided more flexible classifiers. Results under random-shape drifting proves the efficiency of sliding windows toward drifting context.

			\begin{sidewaystable}
				\centering
				\caption{Performance Comparison on Synthetic Data Sets}
				\label{tab:performance-synthetic}
				\footnotesize
				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					\multirow{2}{*}{\textbf{}} & \multicolumn{4}{c|}{\textbf{Uniform}} & \multicolumn{4}{c|}{\textbf{Gaussian}} & \multicolumn{4}{c|}{\textbf{Random-shape}} & \multicolumn{4}{c|}{\textbf{Random-shape with Drift}} \\ \cline{2-17} 
					& \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} \\ \hline
					\textbf{SDD-R} & 10.00 & \textbf{100.00} & 18.18 & 349.42 & 24.78 & 69.20 & 36.49 & 401.82 & 10.00 & \textbf{100.00} & 18.18 & 351.65 & 9.97 & \textbf{99.00} & 18.11 & 353.65 \\ \hline
					\textbf{SDD-R+} & 22.40 & 22.40 & 22.40 & 348.49 & 34.40 & 34.40 & 34.40 & \textbf{398.02} & 58.40 & 58.40 & 58.40 & \textbf{350.87} & 1.20 & 1.20 & 1.20 & \textbf{346.67} \\ \hline
					\textbf{SDD-E Static} & 43.71 & 82.60 & 57.17 & 372.74 & 33.34 & 66.60 & 44.44 & 410.72 & 69.24 & 93.20 & 79.45 & 372.77 & 12.34 & 97.20 & 21.91 & 369.63 \\ \hline
					\textbf{SDD-E Static+} & \textbf{75.10} & 60.20 & \textbf{66.83} & 371.72 & \textbf{45.93} & 45.80 & \textbf{45.86} & 412.95 & \textbf{89.52} & 85.40 & \textbf{87.41} & 368.97 & 12.60 & 94.20 & 22.23 & 370.12 \\ \hline
					\textbf{SDD-E Dynamic} & 18.53 & 81.80 & 30.21 & 6808.58 & 20.28 & \textbf{71.40} & 31.58 & 8985.92 & 25.90 & 97.40 & 40.92 & 5881.37 & 13.44 & 97.20 & 23.61 & 5747.19 \\ \hline
					\textbf{SDD-E Dynamic+} & 27.85 & 25.60 & 26.68 & 8019.23 & 26.19 & 56.40 & 35.77 & 9197.94 & 77.60 & 79.40 & 78.49 & 6408.12 & \textbf{50.55} & 84.00 & \textbf{63.11} & 6176.57 \\ \hline
					\textbf{MGoF} & 10.94 & 4.40 & 6.28 & \textbf{347.97} & 10.08 & 51.60 & 16.87 & 571.93 & 6.40 & 13.60 & 8.70 & 440.26 & 2.75 & 11.60 & 4.45 & 509.58 \\ \hline
				\end{tabular}

				\begin{multicols}{2}
					\includegraphics[width=\linewidth]{fig/F1OnDivergenceMetric.png}
					\captionof{figure}{F1 under Different Divergence Metric}
					\label{fig:divergence-metric-f1}
					\includegraphics[width=.8\linewidth]{fig/ROCUnderDifferentMetrics.png}
					\captionof{figure}{ROC under Different Divergence Metric}
					\label{fig:divergence-metric-roc}
				\end{multicols}
			\end{sidewaystable}

			The last experiment was carried out on random-shaped distribution data set, with $alpha=0.1$ and rest parameters the same. Under different divergence metrics mentioned in section~\ref{sec:preliminaries}, F1 scores were calculated among all SDD algorithms and ROC curves were recorded on SDD-R and static SDD-E. Given that MGoF was defined specifically on Kullback-Leibler divergence, it cannot be tested in the same way. Results are shown in Fig.~\ref{fig:divergence-metric-f1} and Fig.~\ref{fig:divergence-metric-roc}.

			It is indicated that Jensen-Shannon divergence is suited to all techniques due to its symmetry. Kullback-Leibler divergence provides more evident differences when references were given. Bhattacharyya distance and Hellinger distance turned out almost as good as Jensen-Shannon divergence, but they consumed less time. Kolmogorov-Smirnov Statistic performed relatively poor since it considers only the largest gap between two distributions, which provides little information.

		\subsection{Discussion}
			MGoF's learning procedure of anomalous probability hypothesis is inefficient. To maintain a comprehensive knowledge of anomalies, MGoF has to reserve a single hypothesis entry for every type of them. But in reality, it is always the case that we face the heterogeneity of outliers. In the Koubei data set, there can be tens of anomalous distributions caused solely by centralized click farming. It takes a long time to discover every possible type of anomaly. Besides, if there happens to be more than $c_{th}$ anomalous distributions of the same type, later discovered collections will no longer declared to be anomalous any more.

			However, in SDD-R and SDD-E, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections. These techniques are suitable to all typical divergence metrics and consumes little computation power(except dynamic SDD-E). The only drawback is they require comprehensive estimation of target distributions. Although other parameters need estimation as well, they are naturally addressable under big data circumstances.

	\section{Conclusion}\label{sec:conclusion}
		This paper proposes a series of collective anomaly detection techniques, which helps detect data manipulations in modern data pipelines and data centres. Different from existing algorithms designed for collective anomalies, our approach employs statistical distance as the similarity measurement. We explored several technical points involved in the design of the algorithm and performed a thorough experiment to test its efficiency. The comparison experiment also illustrated the advantages of our technique. It can be concluded that the our technique can efficiently discover anomalies within the data collections and the classifier is sensitive enough toward real world data manipulations.

%\section*{Acknowledgment}

	\bibliographystyle{IEEEtran}

	\bibliography{IEEEabrv,paper}

%%	\newpage
%	\onecolumn
%	\appendix \label{sec:appendix}
%	Here are the two equations for threshold calculation:
%	\subsection{Estimation without $\alpha$}
%		\begin{align}\label{equ:equal-weight}
%			T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{a}(x)dx +
%			\int_{T}^{\sup(D)}PDF_{n}(x)dx \nonumber\\
%			& \approx \mathop{\arg\min}_{T}
%			\int_{-\infty}^{T}
%			\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
%			+ \int_{T}^{+\infty}
%			\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx \nonumber\\
%			& = \begin{cases}
%				\displaystyle
%				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{\sigma_a}{\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
%				\displaystyle \frac{\mu_n + \mu_a}{2}, & \sigma_a = \sigma_n
%			\end{cases}
%		\end{align}
%		
%		Note: when $\sigma_a \ne \sigma_n$, keep the one s.t. $\displaystyle \frac{T - \mu_a}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{T - \mu_n}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
%	
%	\subsection{Estimation with $\alpha$}
%		\begin{align}\label{equ:linear-weight}
%			T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
%			(1-\alpha)\int_{T}^{\sup(D)}PDF_{n}(x)dx\nonumber\\
%			& \approx \mathop{\arg\min}_{T}
%			\alpha\int_{-\infty}^{T}
%			\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
%			+ 
%			(1-\alpha)\int_{T}^{+\infty}
%			\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\nonumber\\
%			& = \begin{cases}
%				\displaystyle
%				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{(1 - \alpha)\sigma_a}{\alpha\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
%				\displaystyle
%				\frac{\mu_n + \mu_a}{2} + \frac{k^2ln\frac{1 - \alpha}{\alpha}}{\mu_a - \mu_n}, & \sigma_a = \sigma_n = k
%			\end{cases}
%		\end{align}
%		
%		Note: when $\sigma_a \ne \sigma_n$, keep the one s.t. $\displaystyle \frac{\alpha (T - \mu_a)}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{(1 - \alpha) (T - \mu_n)}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$

\end{document}

In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those occurred at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years. And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}. System configuration problems, as a matter of fact, are also responsible for the disturbing situation. They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

### 2019-12-06 Paper/ICME Template/Appendices.tex
把文章修改为ICME模板

--- 2019-12-06 Paper/FullPaper/paper.tex
@@
-% IEEE Paper Template for US-LETTER Page Size (V1)
-% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
-% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
-% Permission is granted to distribute and revise this file provided that
-% this header remains intact.
-%
-% REVISION HISTORY
-% 20080211 changed some space characters in the title-author block
-%
 \documentclass[10pt,conference,letterpaper]{article}
@@
 \usepackage{caption}
-%
-\title{Statistical Detection of Collective Data Anomalies}
+\usepackage{ulem}
+\usepackage[left=2.00cm, right=2.00cm, top=2.00cm, bottom=2.00cm]{geometry}
+
+\title{Appendices}
 \date{}
-%
-%\author{%
-%	% author names are typeset in 11pt, which is the default size in the author block
-%	{Ruoyu Wang{\small$^{1}$}, Daniel Sun{\small$^{2}$}, Guoqiang Li{\small$^{1*}$} }%
-%	% add some space between author names and affils
-%	\vspace{1.6mm}\\
-%	\fontsize{10}{10}\selectfont\itshape
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% separate superscript on following line from affiliation using narrow space
-%	$^{1}$\,School of Software, Shanghai Jiao Tong University, China\\
-%	\fontsize{9}{9}\selectfont\ttfamily\upshape
-%	%
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% in the following email addresses, separate the superscript from the email address 
-%	% using a narrow space \,
-%	% the reason is that Acrobat Reader has an option to auto-detect urls and email
-%	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
-%	% in the email address and corrupts it.
-%	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
-%	\{solftwarewry,li.g\}@sjtu.edu.cn
-%	% add some space between email and affil
-%	\vspace{1.2mm}\\
-%	\fontsize{10}{10}\selectfont\rmfamily\itshape
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% separated superscript on following line from affiliation using narrow space \,
-%	\,Data61, CSIRO, Australia\\
-%	\fontsize{9}{9}\selectfont\ttfamily\upshape
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% removed ~ from pre-superscript since it does not seem to serve any purpose
-%	$^{2}$\,daniel.sun@data61.csiro.au
-%}
 
-%
 \begin{document}
 	\maketitle
-%
-	\begin{abstract} 
-		Attackers infiltrate databases and software systems to not only steal chunks of data and hold them for ransom, but also alter certain parts, setting up traps harder to discover and causing damages unlikely to recover.
-		Without referring to data source, it is hard to detect a single record that is altered but still remain in correct value scopes.
-However, the change, especially to a subset of data, can be observed and detected in a collective scale.
-		In this paper, we present a collective detection technique based on statistical divergence.
-\textcolor{red}{Statistical divergence detection was explored in multimedia applications.
-But it is still underdeveloped in big data era due to data irregularity.} The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
-		Our technique continuously evaluates metrics as evolving features and calculate adaptive threshold to meet the best mathematical expectation.
-		To illustrate details of the technique and explore its efficiency, we case-studied a real world problem of click farming detection against malicious online sellers.
-The evaluation shows that these techniques provided efficient classifiers.
-They were also sufficiently sensitive to a much smaller magnitude of data alteration, compared with real world malicious behaviours.
-Thus, it is applicable in the real world.
-	\end{abstract}
-
-% NOTE keywords are not used for conference papers so do not populate them
-% \begin{keywords}
-% keyword-1, keyword-2, keyword-3
-% \end{keywords}
-%
-	\section{Introduction}
-		Major improvements in data acquisition, transmission and storage are to increase data availability and affordability.
-Currently, there are more than 2.7ZB data in the digital universe~\cite{bigDataStatistics} and the growing speed is doubling every two years.
-		It has already been hard and will be much harder in the future to harness the exploding volume of data that has resulted in many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
-		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\cite{saha2014data}. Those data anomalies may arise due to both internal and external reasons.
-
-		On one hand, components inside systems may generate problematic source data.
-For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\cite{rassam2014adaptive}.
-Data packages will be lost if sensor nodes fail to connect to network or some sensor hubs break down~\cite{herodotou2014scalable}.
-Also, human operators act as a heavily vulnerable part to bugs and mistakes.
-Malicious insiders even deliberately modify system configurations for fatal compromises~\cite{schuster2015vc3}.
-A study shows that 65\% of organizations state that human errors are the main  cause of data problems~\cite{humanError} .
-
-		On the other hand, data manipulation~\cite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability.
-\textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
-		If data is compromised, it will severely affect mining and learning algorithms and further change the final decision driven by the data.
-In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.
-
-		It is hard to detect a single record that is alerted but still remain in correct value scopes, but if sufficient data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
-		According to our observation, typical manipulations on numerical data will lead to a drift or distortion of its original distribution.
-For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones.
-		To address problems caused by data manipulation, we propose a novel technique which sorts out manipulated data collections from normal ones by adopting statistical divergence.
-		\textcolor{red}{Statistical divergence detection was explored in multimedia applications. But it is still underdeveloped in big data era due to data irregularity.}
-		In this paper, we focus on a concrete data manipulation problem: click farming in online shops, and try to apply our technique to pick out those dishonest sellers.
-		Our techniques maps data collections to points in distribution spaces and reduce the problem to classical point anomaly detection.
-		Optimizations estimate ground truth, mapping each data collection into a single real number within a definite interval.
-Then a Gaussian classifier can be applied to detect outliers derived from manipulated data.
-To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by statistical divergence.
-		In the dynamic environments, these evidence sets are modified after every data collection is checked, in which manner they act intuitively as slide windows and keep up to the evolving features in dynamic scenarios.
-		Our contribution includes: 1) A brief review on data anomaly detection and a study on the problem of click farming; 2) Detailed description of both basic and optimized framework of our technique, resolving several technical difficulties such as automated adaptive threshold; 3) Real world and synthetic data experiments that test efficiency of our technique and a comparison with a previous work on the same topic.
-
-		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related work on data anomaly detection and describes a real world problem.
-Section~\ref{sec:preliminaries} introduces statistical distance.
-Details of proposed technique are introduced in section~\ref{sec:algorithm-details}.
-Then section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm.
-Finally, the paper is concluded in section~\ref{sec:conclusion}.
-
-	\section{Related Work}\label{sec:related-work}
-		\subsection{Data Anomaly Detection}
-			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.
-			Anomaly detection algorithms deal with input data in the form of points (or records), sequences, graphs and spatial and geographical relationships.~\cite{chandola2009anomaly} According to relationships within data records, outliers can be classified into \textit{point anomalies}, \textit{contextual (or conditional) anomalies} and \textit{collective anomalies}.~\cite{goldberger2000components}
-
-			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} catch most attention.
-Others adopted tree isolation~\cite{zhang2017lshiforest}, model based~\cite{yin2016model} and statistical methods~\cite{zhu2002statstream} in certain applications.
-
-			To detect collective anomalies,~\cite{caudell1993adaptive} adopts the \textit{ART (Adoptive Resonance Theory)} neural networks to detect time-series anomalies.
-\textit{Box Modeling} is proposed in ~\cite{chan2005modeling}.
-\textit{Longest Common Subsequence} was leveraged in~\cite{budalakoti2006anomaly} as similarity metric for symbolic sequence.
-Markovian modeling techniques are also popular in this domain\cite{ye2000markov,warrender1999detecting,pavlov2003sequence}.
-\cite{yu2015glad} depicts groups in social media as combinations of different ``roles'' and compare groups according to the proportion of each role within each group.
-
-			Wang et al.
-proposed a technique, \textit{Multinomial Goodness-of-Fit} (MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence, and is fundamentally a hypothesis test on distributions~\cite{wang2011statistical}.
-			MGoF divides the observed data sequence into several windows.
-It quantifies data in each window into a histogram and check these estimated distributions against several hypothesis.
-If the target distribution rejects all provided hypothesis, it is considered an anomaly and preserved as a new candidate of null hypothesis.
-If the target distribution failed to reject some hypothesis, then it is considered a supporting evidence of the one that yields most similarity.
-Furthermore, if the number of supporting evidence is larger than a threshold $c_{th}$, it is classified as non-anomaly.
-
-			MGoF is the best competitor out of the similar techniques, and we use it as our baseline against our approach.
-
-		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
-%			Since the establishment of Taobao in 2003, its online business platform has been growing from a follower in the market to the No.1 service provider in B2B and B2C markets, 
-			Taobao possesses a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}.
-Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products.
-Under the super-pressure caused by massive competitors, a number of the sellers choose to use some cheating techniques to raise reputation and sale volumes, then improve rankings in search lists.
-
-			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of customer accounts to create fake transaction records and give high remarks on products.
-Professional click farmers are usually well organized groups or companies containing thousands of people.
-%			Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions. 
-			Some companies even develop professional applications that can be deployed on common PCs to improve productivity~\cite{zhao2016on}.
-
-			There are two types of click farming behaviours: Centralized and Equalized.
-Centralized click farming refers to the scenarios that transactions are randomly generated throughout the day.
-A significant feature of this approach is that the cheating transactions usually assemble together in a short period of time since most workers work at the same time.
-Equalized click farming refers to the circumstances that click farms are arranged by some well programmed applications or teams carefully managed and strictly commit transactions according to a timetable.
-Thus the transaction distribution may not vary too much with and without click farming.
-
-			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% are aware of click farm and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}.
-American researchers reported in 2015 that over 11000 sellers on Taobao were detected to have click farmed records and only 2.2\% of 4000 investigated dishonest sellers had been penalized because of the cheating attempts~\cite{netease2015research}.
-
-			Current detection techniques for click farming mainly focus on user behaviours, such as browsing frequencies and periods, most common purchasing time, favourite products, remarks and whether they communicate with sellers~\cite{simpleDetection}.
-Those techniques require the platform to keep lots of records and user features.
-However, the detection can be easily bypassed by trained workers and some well programmed applications.
-
-			\begin{figure}[t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
-				\caption{Example cumulative distribution function of original and click farmed daily transaction data}
-				\label{fig:example-ecdf}
-			\end{figure}
-
-			Although it is hard to classify users as honest or malicious, we can still find clues from the sellers' aspect.
-For normal sellers, their customers are usually similar since choices of products are seldom changed.
-Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable.
-No matter how much alike between honest users and robots or the employed workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
-To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records and emulated the circumstances if it had been click farmed (see section~\ref{sec:exp-methodology}).
-Fig.~\ref{fig:example-ecdf} shows the difference between normal and click farmed distributions of one day in the data set.
-			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
 
@@
 			Let $P,Q$ be discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:
-
 			\begin{equation}
@@
 			A more generalized form is defined to be:
-
-%			{\small
 			\begin{equation}
@@
 			\end{equation}
-%			}
 			where $H$ is Shannon Entropy, $\displaystyle M = \sum_{i=1}^{n}\pi_iP_i$ and $\displaystyle \sum_{i=1}^{n}\pi_i = 1$.
@@
 			\end{equation}
-
 			Jensen-Shannon divergence has some fine properties:
@@
 
-	\section{Statistical Detection}\label{sec:algorithm-details}
-
-		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records.
-For example, traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
-Manipulation on those data (e.g.
-Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger an alarm.
-
-		\subsection{Statistical Divergence Detection with Reference(SDD-R)}\label{sec:alg-opt-reference}
-			From Section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions.
-In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the symmetric divergence between two connected nodes.
-From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies.
-This may work if anomalous nodes do not compose a large proportion.
-However the procedure will be too complicated to work out with large amounts of data.
-If it is assured that data collections form only one cluster, some optimizations can be applied to reduce complexity.
-
-			Alternatively we can provide a frame of reference that generates absolute coordinates rather than the relative ones.
-This optimization is feasible if data collections form one single cluster in distribution space.
-This is true in most reality scenarios given that distribution is adopted to depict a macro property which comes out as one universal conclusion.
-In other words , if multiple distributions are used to describe subgroups of entire sample space, then a conclusive one can be obtained by averaging all these sub-distributions.
-Therefore, we can use an estimate cluster center as reference and test distances between the reference and each other data collections(Algorithm~\ref{alg:sdd-r}), yielding absolute distances.
-
-			\begin{algorithm}[!t]
-				\caption{SDD-R}
-				\label{alg:sdd-r}
-				\begin{algorithmic}[1]
-					\Require Data Collections $\mathbb{D} = \{D_1, \dots, D_n\}$
-					\Require Estimated anomalous probability $\alpha$
-					\Ensure Anomalous Data Collections
-					\For {$i \gets 1$ to $n$}
-						\State $P_i \gets$ the distribution of $D_i$
-					\EndFor
-					\State $P_R \gets \frac{1}{n}\sum_{i = 1}^n P_i$
-					\For {$i \gets 1$ to $n$}
-						\State $d_i \gets D(P_i||P_R)$
-					\EndFor
-					\State $\mathcal{N}(\mu, \sigma) \gets$ Gaussian distribution estimated by $d_i$
-					\State \Return $\{D_i | \frac{d_i - \mu}{\sigma} > 3 \}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/JSD-Dist.png}
-				\caption{Distribution of Jensen-Shannon divergence on Taobao data set(without click farming) used in the experiments.}
-				\label{fig:jsd-dist}
-			\end{figure}
-
-			Fig.~\ref{fig:jsd-dist} shows distribution of all divergences against the reference.
-It can be approximated as a Gaussian distribution though the true one may differ a little more from the standard Gaussian than the expected estimation error.
-That is due to the unknown randomness within real world data.
-Few assumptions can be applied in real world data sets, no mention that data volume is sometimes relatively low.
-This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model.
-			Certainly, if stronger assumptions can be included to provide a more precise model, this component in the framework can be replaced to give better results.
-			For the simplicity of our proposal, we deem the distributions of divergences to be Gaussian.
-
-			By this approach, time complexity can be reduced from quadratic to linear.
-Fig.~\ref{fig:raw-overview} in Section~\ref{sec:exp-raw} demonstrates the result of the above process.
-Red distribution refer to the distances calculated from normal data collections, blue and green ones are from click-farmed data collections.
-Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value.
-
-		\subsection{Optimization: Statistical Divergence Detection with Evidence(SDD-E)}
-			It is possible to further optimize SDD-R if we can provide this algorithm with evidence(Algorithm~\ref{alg:sdd-e}).
-
-			\begin{algorithm}[!t]
-				\caption{SDD-E}
-				\label{alg:sdd-e}
-				\begin{algorithmic}[1]
-					\Require Evidence set with normal data collections $\mathbb{E}_N = \{N_1, \dots, N_n\}$
-					\Require Evidence set with anomalous data collections $\mathbb{E}_A = \{A_1, \dots, A_m\}$
-					\Require Estimated anomalous probability $\alpha$
-					\Require New data collection $\mathbb{D} = \{D_1, \dots, D_l\}$
-					\Ensure Anomalous data collections in $\mathbb{D}$
-					\For{$i \gets 1$ to $n$}
-						\State $P_{N_i} \gets$ distribution of $D_{N_i}$\label{line:hist-1}
-					\EndFor
-					\For{$i \gets 1$ to $m$}
-						\State $P_{A_i} \gets$ distribution of $D_{A_i}$\label{line:hist-2}
-					\EndFor
-					\State $P_R \gets \frac{1}{n}\sum_{i=1}^{n}P_{N_i}$
-					\For{$i \gets 1$ to $n$}
-						\State $d_{N_i} \gets D(P_{N_i}||P_R)$
-					\EndFor
-					\For{$i \gets 1$ to $m$}
-						\State $d_{A_i} \gets D(P_{A_i}||P_R)$
-					\EndFor
-					\State $\mathcal{N}_N(\mu_N, \sigma_N) \gets$ normal distribution estimated from $\{d_{N_1}, \dots, d_{N_n}\}$
-					\State $\mathcal{N}_A(\mu_A, \sigma_A) \gets$  normal distribution estimated from $\{d_{A_1}, \dots, d_{A_m}\}$
-					\State $T \gets$ proper threshold derived from $\mathcal{N}_N$, $\mathcal{N}_A$ and $\alpha$
-					\For{$i \gets 1$ to $l$}
-						\State $P_i \gets$ distribution of $D_i$
-						\State $d_i \gets D(P_i||P_R)$
-					\EndFor
-					\State \Return $\{D_i|d_i > T\}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			Evidences enables the algorithm to not only refine estimation of real distribution but also build knowledge of anomalous collections, which is similar to the parameter estimation within a certain sample set.
-
-			According to the property of statistical divergence, we can infer that the true distribution of divergences calculated from normal data collections are close to but not exactly a Gaussian distribution $\mathcal{N}(\mu, \sigma)$ since for each point, there are both definite upper and lower bounds instead of infinities.
-Therefore, $\mu$ should be slightly larger than zero($\mu = 0 \iff P_i = P_j, \forall P_i, P_j \in \mathbb{E}_N$, for real world data sets, this is highly unlikely).
-Time complexity for this algorithm is still linear but with a larger coefficient.
-
-			For certain divergence, it is possible to compare similarity from one distribution against multiple others, such as Jensen-Shannon Divergence.
-Although it reduces time complexity, it sacrifices unaffordable accuracy because divergence among multiple distribution dilutes differences.
-Take JSD as an example, suppose $P(1) = P(2) = P(3) = \frac{1}{3}$ and $Q(1) = \frac{1}{6}, Q(2) = \frac{1}{3}, Q(3) = \frac{1}{2}$, then $JSD(P||Q) \approx 0.033$ and $JSD(P, P, P, Q) \approx 0.024$.
-
-			This algorithm can be slightly modified to deal with concept drift(for example, trading trend changes over time for online shops as they are often in the process of expanding or dwindling) by turning the two evidence sets as sliding windows and adopting certain update strategies such as \textit{Least Recently Used}(LRU).
-Time complexity for this optimization is $O(n\cdot(|\mathbb{E}_N|+|\mathbb{E}_A|)\cdot T_D)$, where $T_D$ denotes time complexity of divergence calculation.
-
-		\subsection{Threshold}\label{sec:alg-threshold}
-			One important factor in algorithm SDD-E is the value of threshold.
-A lower threshold rejects more instances, improving the sensitivity of anomalous data while increasing the number of false alarms.
-A higher threshold provide higher true negative rates yet neglecting more possible threats.
-
-			A naive but prevalent approach is to set a fixed value as the threshold(As is shown in Algorithm~\ref{alg:sdd-r}).
-This approach is easy to implement and may give satisfying results in specific cases.
-However, a fixed threshold requires specific analysis in the certain scenario, manual observations and tuning of parameters, which involves lots of human labour.
-The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous.
-It can be used to automatically determine a threshold.
-But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided.
-It would be either lower than the optimum if anomalous data lies far away from the normal cluster, or higher than the optimum if the anomalies sit close to the cluster centre.
-
-			Fortunately, applying divergence as the distance measurement among data collections provides a fine property.
-With a reference distribution, divergences of normal data collections form a quasi-Gaussian distribution as we have seen in section \ref{sec:alg-opt-reference}.
-The same applies to those anomalous ones.
-
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
-				\caption{Threshold can be determined either by a probability density value, or a radius from the centre.
-In the scenario shown in the figure, the threshold can be determined by the position between two centres of the distribution, denoted as ``T'' here.
-This form of threshold can also be applied to other types of distributions even there is no intersection between these two.}
-				\label{fig:example-threshold}
-			\end{figure}
-
-			Moreover, as is verified in experiments, the meta-distribution of anomalous data collections lies in the right-hand-side to the normal one on the real line.
-As shown in Fig~\ref{fig:example-threshold}, the black curve ($PDF_{normal}(x)$ or in short $PDF_n(x)$) displays the probability density function (PDF) fitting those divergences calculated from normal data collections; the blue curve ($PDF_{anomalous}(x)$ or in short $PDF_a(x)$) displays the PDF derived from anomalous data collections.
-Threshold is chosen to minimize total errors(both false negative and false positive).
-
+	\section{Adaptive Threshold Calculation}
 		Suppose:
 		\begin{align}
-				PDF_n(x) &\approx \mathcal{N}(\mu_n, \sigma_n)\\
-				PDF_a(x) &\approx \mathcal{N}(\mu_a, \sigma_a)
+			PDF_normal(x) &\approx \mathcal{N}(\mu_n, \sigma_n)\\
+			PDF_anomalous(x) &\approx \mathcal{N}(\mu_a, \sigma_a)
 		\end{align}
-
-			Then the optimal threshold $T$ is calculated by E.q.(\ref{equ:equal-weight}). The optimal threshold will minimize total errors and yield an optimal outcome.
-			However, this is not accurate enough, since E.q.(\ref{equ:equal-weight}) implicates an assumption that chances are the same for a new data collection to be either anomalous or not.
-If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as E.q.(\ref{equ:linear-weight}), where $\alpha$ is the anomaly probability.
 
@@
 
-			Moreover, with an estimated anomaly probability, SDD-R can be also optimized by ranking all data collections according to their divergence value and select first $n \cdot \alpha$ ones with highest values as anomalies.
-
-	\section{Evaluation}\label{sec:evaluation}
-		Our algorithm was implemented and interpreted in Python 3.5.2.
-All experiments were tested on Ubuntu 16.04.
-In the following experiments, we figured out properties of real world data and performance of our technique against anomalous data collections.
-We also made a comparison among variations of SDD algorithms and MGoF.\footnote{All resources and more detailed experiment results can be retrieved online: https://github.com/TramsWang/StatisticalAnomalyDetection}
-
-		\subsection{Methodology}\label{sec:exp-methodology}
-			We adopted two data sets: 1) Koubei sellers' transaction records\footnote{https://tianchi.aliyun.com/competition/information.htm?raceId=231591}; 2) Synthetic random distribution data set.
-Koubei data set was provided by Alibaba Tian Chi big data competition where all records were collected from real world business scenarios.
-It contained information about seller features, user payments and browsing behaviour.
-We randomly chose one seller (ID: 1629) and extracted transaction history of this seller, records ranging from Nov.
-11th 2015 to Oct.
-31st 2016.
-Entire transaction set was then divided into 325 collections, each containing records in one day.
-Fig.~\ref{fig:daily-transaction-volume} and~\ref{fig:sale-distribution-sample} give an overview of it.
-
+	\section{Extra Insights on Koubei Data Set}
 		\begin{figure}[!t]
 			\centering
-				\includegraphics[width=0.75\linewidth]{fig/DailyTransactionVolume.png}
+			\includegraphics[width=0.5\linewidth]{fig/DailyTransactionVolume.png}
 			\caption{Changing of the daily sales volume shows that environment of online sales had been changing all the time.}
@@
 			\centering
-				\includegraphics[width=\linewidth]{fig/SaleDistributions.png}
+			\includegraphics[width=.7\linewidth]{fig/SaleDistributions.png}
 			\caption{We selected 3 days randomly and drew sales distribution by counting hourly volume. Although sales volume has changed from day to day, the shape of the distribution remain almost alike.}
@@
 		\end{figure}
-
-			Two types of click-farmed data was generated according to patterns described in section~\ref{sec:related-realworld}.
-To emulate centralized click farming, we randomly inserted some Gaussian-distributed transactions in the chosen collection.
-As for emulating the equalized click farmers, we simply doubled each record in the chosen collection to make the new distribution exactly the same as the original one, which is harder for the online platform to discover.
-			Usually, the click-farmed transactions are several times more than the volume it originally has, if the seller hires a group of organized workers.
-In our experiments, we use $\nu$ to denote the magnitude coefficient of click farming.
-Hence $|D_{anomalous}| = (1 + \nu)|D_{normal}|$.
-In the following experiments without extra illustration, we adopted $\nu = 1$.
-
-			One defect of this data set is that the detailed time stamp is aligned at each hour of the day due to desensitization.
-We constructed an enhanced data set by assigning every time stamp a random value for minutes and seconds.
-Therefore, the enhanced data set should be closer to the reality.
-
-			The synthetic data set was divided into four sections.
-First two sections contained sample sets drawn from a uniform and a Gaussian distribution respectively.
-The third section used a mixture of one uniform distribution and two Gaussian distributions to simulate a random-shaped distribution.
-Moreover, we made the random-shaped distribution drift slightly to form the last section of test data.
-Corresponding anomalies were drown from distributions with deviated parameters respectively.
-
-			We adopted histograms to depict distributions of any shape.
-Surely, the kernel density estimation approaches will give smooth and continuous estimations on any sampled data.
-But the computational cost will be too much to afford.
-Step size of histograms is chosen by:
-			\begin{equation}\label{equ:step-size}
-				l = c \sigma k^{-0.2},
-			\end{equation}
-			where $k$ is sample size, $c$ is a constant relative to the shape of distribution (e.g.
-for normal distribution, $c=1.05$) and $\sigma$ the standard deviation.
-For data sets with a large number of elements, a random sampling method, such as Monte-Carlo method, can be applied to speed up the estimation procedure.
-
-			Divergence metric adopted in each SDD algorithms was Jensen-Shannon divergence if no specific notation is made.
-However, MGoF used only Kullback-Leibler divergence due to its special mechanism.
-We use a ``+'' to denote algorithms optimized by a given $\alpha$.
-
-		\subsection{Experiments on Koubei Data Set}\label{sec:exp-raw}
-			We first tested our algorithms on Koubei data set in order to see whether and why the algorithm works.
-Anomalies were random selected days replaced by corresponding click farmed version.
-To play the role of purchasing platform, we investigated two levels of transaction distribution.
-The first level is to simply draw a histogram aligned to time spans.
-The second level is to draw a histogram on the sub-volumes in each time span(i.e.
-a histogram on frequencies in the first level histogram, as shown in Fig.~\ref{fig:histogram-example}).
 
@@
 		\end{figure}
-
-			On the raw data set, we had no choice but to set one hour a basket. While on the enhanced data set, we adopted E.q.(\ref{equ:step-size}) to determine step size automatically.
-			To test SDD-E, we randomly selected 30 correct days and 10 click farmed days as normal and anomalous evidence respectively.
-			Here $\alpha = 0.2$. The results are shown in Table~\ref{tab:result-koubei-raw} and \ref{tab:result-koubei-enhanced}.
-
-			\begin{sidewaystable}
-				\centering
-				\caption{Performance on Raw Data}
-				\label{tab:result-koubei-raw}
-				\footnotesize
-				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-					\hline
-					\multirow{3}{*}{\textbf{}} & \multicolumn{8}{c|}{\textbf{Centralized}} & \multicolumn{8}{c|}{\textbf{Equalized}} \\ \cline{2-17} 
-					& \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} & \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} \\ \cline{2-17} 
-					& \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} \\ \hline
-					\textbf{SDD-R} & 89.51 & 48.75 & 63.12 & 266.77 & 21.97 & \textbf{99.38} & 35.98 & 11.12 & 6.67 & 0.63 & 1.14 & 249.15 & 21.22 & 72.50 & 32.83 & 7.81 \\ \hline
-					\textbf{SDD-R+} & 91.25 & 91.25 & \textbf{91.25} & \textbf{265.96} & \textbf{61.88} & 61.88 & 61.88 & 10.08 & 9.38 & 9.38 & 9.38 & \textbf{247.31} & \textbf{44.38} & 44.38 & 44.38 & 6.92 \\ \hline
-					\textbf{SDD-E Static} & \textbf{92.46} & 68.75 & 78.86 & 292.50 & 36.55 & 98.13 & 53.26 & 5.75 & 6.67 & 0.63 & 1.14 & 271.45 & 36.07 & 86.25 & 50.86 & 5.64 \\ \hline
-					\textbf{SDD-E Static+} & 85.02 & 32.50 & 47.02 & 293.77 & 46.24 & 91.88 & 61.52 & 5.95 & 10.00 & 0.63 & 1.18 & 272.71 & 43.60 & 76.25 & \textbf{55.48} & 5.68 \\ \hline
-					\textbf{SDD-E Dynamic} & 49.11 & \textbf{99.38} & 65.73 & 699.97 & 23.01 & \textbf{99.38} & 37.37 & 245.65 & 10.36 & \textbf{18.13} & \textbf{13.18} & 681.09 & 22.09 & \textbf{93.13} & 35.71 & 242.85 \\ \hline
-					\textbf{SDD-E Dynamic+} & 73.21 & 98.75 & 84.09 & 701.06 & 48.02 & 96.25 & \textbf{64.07} & 255.43 & 8.15 & 6.88 & 7.46 & 681.89 & 40.79 & 78.13 & 53.59 & 253.03 \\ \hline
-					\textbf{MGoF} & 14.08 & 21.88 & 17.13 & 292.14 & 13.01 & 4.38 & 6.55 & \textbf{3.64} & \textbf{12.50} & 3.13 & 5.00 & 250.42 & 12.50 & 3.13 & 5.00 & \textbf{3.71} \\ \hline
-				\end{tabular}
-
-				\vskip\baselineskip
-				\caption{Performance on Enhanced Data}
-				\label{tab:result-koubei-enhanced}
-				\footnotesize
-				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-					\hline
-					\multirow{3}{*}{\textbf{}} & \multicolumn{8}{c|}{\textbf{Centralized}} & \multicolumn{8}{c|}{\textbf{Equalized}} \\ \cline{2-17} 
-					& \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} & \multicolumn{4}{c|}{\textbf{1st Level}} & \multicolumn{4}{c|}{\textbf{2nd Level}} \\ \cline{2-17} 
-					& \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} \\ \hline
-					\textbf{SDD-R} & 81.54 & 41.88 & 55.33 & 238.61 & 17.49 & 92.50 & 29.42 & 13.86 & 6.67 & 0.63 & 1.14 & 239.44 & 21.15 & 71.88 & 32.69 & 12.08 \\ \hline
-					\textbf{SDD-R+} & \textbf{91.25} & 91.25 & \textbf{91.25} & \textbf{236.94} & 36.88 & 36.88 & 36.88 & 12.98 & 8.13 & 8.13 & 8.13 & \textbf{236.47} & 38.75 & 38.75 & 38.75 & 11.03 \\ \hline
-					\textbf{SDD-E Static} & 88.31 & 67.50 & 76.52 & 257.60 & 31.99 & 92.50 & 47.54 & 9.74 & 6.67 & 0.63 & 1.14 & 257.65 & 34.49 & 91.25 & 50.06 & 9.37 \\ \hline
-					\textbf{SDD-E Static+} & 69.67 & 13.13 & 22.09 & 259.30 & \textbf{42.12} & 73.75 & \textbf{53.62} & 9.59 & 10.00 & 0.63 & 1.18 & 258.45 & \textbf{44.17} & 82.50 & \textbf{57.54} & 9.32 \\ \hline
-					\textbf{SDD-E Dynamic} & 42.93 & \textbf{99.38} & 59.96 & 1106.25 & 20.12 & \textbf{95.63} & 33.25 & 277.70 & 10.57 & \textbf{17.50} & \textbf{13.18} & 1108.93 & 20.30 & \textbf{94.38} & 33.42 & 271.74 \\ \hline
-					\textbf{SDD-E Dynamic+} & 69.18 & 98.13 & 81.15 & 1110.81 & 33.25 & 87.50 & 48.19 & 292.60 & 7.06 & 3.75 & 4.90 & 1118.00 & 37.21 & 80.63 & 50.92 & 283.50 \\ \hline
-					\textbf{MGoF} & 13.97 & 17.50 & 15.54 & 294.08 & 14.66 & 8.13 & 10.45 & \textbf{8.01} & \textbf{12.50} & 3.13 & 5.00 & 250.10 & 18.42 & 8.75 & 11.86 & \textbf{7.55} \\ \hline
-				\end{tabular}
-			\end{sidewaystable}
 
@@
 			\centering
-				\includegraphics[width=\linewidth]{fig/RawOverview2nd.png}
-				\caption{This figure shows distribution of JSD values(on 2nd level histograms) of normal and two types of click farming data.
-Divergences were calculated according to a reference averaged among all correct distributions.}
-				\label{fig:raw-overview}
+			\includegraphics[width=\linewidth]{fig/JSD-Dist.png}
+			\caption{Distribution of Jensen-Shannon divergence on Taobao data set(without click farming) used in the experiments.}
+			\label{fig:jsd-dist}
 		\end{figure}
 
-			When classifying toward 1st level histograms, centralized click farming behaviours can be easily discovered.
-As displayed in the first two rows in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click-farmed ones abruptly violated the original shape.
-However, as a clever click farmer, equalized click farming did not in the least distort the distribution.
-Most of them escaped the check under perfect disguises.
-			But when it came to 2nd level histograms, the ``clever disguise'' did not work any longer.
-It can be clearly seen in Fig.~\ref{fig:raw-overview} that distribution of divergence of both click farming types shows an obvious deviation from the normal one.
+	\section{Results on Synthetic Data Set}
+		The synthetic data set was divided into four sections.
+First two sections contained sample sets drawn from a uniform and a Gaussian distribution respectively.
+The third section used a mixture of one uniform distribution and two Gaussian distributions to simulate a random-shaped distribution.
+Moreover, we made the random-shaped distribution drift slightly to form the last section of test data.
+Corresponding anomalies were drown from distributions with deviated parameters respectively.
 
-			The result showed that our technique outperformed MGoF in every real world cases.
-			SDD-E provided best performance, yet it consumed the most computing power.
-Comparison among SDD-R revealed improvement of reference as well as the importance of threshold under this technique.
-Although dynamic SDD-E consumes more computation power, it is clear that dynamic SDD-E is capable of tracing the gradual shift of environment.
-MGoF turned out to be the worst since it always mark several false positive when $c_{th}$ had not been met and much more false negatives when similar errors occurred too many.
-
-			Parameter $\alpha$ improved total accuracy of dynamic SDD-E algorithm by 10-20\% as was supposed.
-It also increased its F1 by more than 20\%.
-$\alpha$ made a great difference in SDD-R as well, which illustrated that divergence sorted almost all collections in correct order according to the averaged reference.
-However, static SDD-E did not show the same improvement.
-Since environment drift took greater influence in the result.
-In comparison with $\alpha$, adaptive threshold given by evidence sets did not bring the most improvement.
-But this threshold can be applied together with other optimizations such as slide windows.
-
-		\subsection{Test against Anomaly Proportion and Magnitude}\label{sec:exp-synthetic}
-			In this experiment, we tested algorithm performance under various anomaly proportion and magnitude.
-$\alpha$ ranged from 0.1 to 0.9 when $\nu = 1$ and $\nu \in [0.1, 0.9]$ when $\alpha = 0.1$, other settings remains the same.
-
-			\begin{figure}[!t]
-				\includegraphics[width=\linewidth]{fig/AccuracyOnAnomalyProbability.png}
-
-				\includegraphics[width=\linewidth]{fig/F1OnAnomalyProbability.png}
-				\caption{Accuracy and F1 on Different Anomaly Probabilities}
-				\label{fig:anomaly-probability}
-			\end{figure}
-
-			Fig.~\ref{fig:anomaly-probability} shows that our technique outperformed MGoF and was relatively stable when dealing with all proportions of 1st level centralized anomalies.
-SDD-E performed even better since it maintains knowledge of both normal and anomalous distributions and calculates the threshold according to the best expectation.
-However, it relies on the accuracy of distribution estimation.
-When it came to 2nd level distributions, histograms became much coarser since data available was highly limited and thus its performance suffered dramatically.
-
-			MGoF tended to classify every distribution as anomaly, therefore benefited most by larger $\alpha$.
-It always classifies as anomalous the first $c_{th}$ distributions supporting every null hypothesis.
-Thus when $\alpha$ increased, the proportion of misclassified normal collections also became larger, while those anomalies were still considered anomalous.
-And given that the total number of normal collections drops down, the overall accuracy tended to increase as more instances are correctly classified as anomalous.
-However, the right half shows a different trend.
-One reason is that MGoF uses KLD other than JSD.
-In the Koubei dataset, the discrete estimation of distributions oscillated in a wide range, leading to that the prerequisite of KLD is often unsatisfied.
-Thus the calculation of KLD may not give a correct measurement.
-Furthermore, the 2nd histogram provided fewer probability entries than the 1st level did.
-Thus it shows a more significant deviation from our expectation.
-			For the classifiers of MGoF, they  compromised to a high error rate. Because more anomalies gathered together and the algorithm recognized them as clusters of normal data.
-
-			\begin{figure}[!t]
-				\includegraphics[width=\linewidth]{fig/PerformanceOnAnomalyMagnitude.png}
-				\caption{Accuracy and F1 on Different Anomaly Magnitudes}
-				\label{fig:anomaly-magnitude}
-			\end{figure}
-
-			From Fig.~\ref{fig:anomaly-magnitude} we can conclude that our algorithms are still the best, given that they are most sensitive toward tiny anomalous variations.
-However, static SDD-E did not rise until $\nu > 1$, this is because it suffered from fluctuation on the trade environment at the mean time.
-MGoF is not sensitive toward minor anomalies either.
-			For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold could not automatically rise up and was thus far from to optimal.
-
-		\subsection{Results on Synthetic Data Set}
 		In this experiment, we tested all seven algorithms on totally synthetic data sets.
@@
 
-		\subsection{Discussion}
-			MGoF's learning procedure of anomalous probability hypothesis is inefficient.
-To maintain a comprehensive knowledge of anomalies, MGoF has to reserve a single hypothesis entry for every type of them.
-But in reality, it is always the case that we face the heterogeneity of outliers.
-In the Koubei data set, there can be tens of anomalous distributions caused solely by centralized click farming.
-It takes a long time to discover every possible type of anomaly.
-Besides, if there happens to be more than $c_{th}$ anomalous distributions of the same type, later discovered collections will no longer declared to be anomalous any more.
-
-			However, in SDD-R and SDD-E, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections.
-These techniques are suitable to all typical divergence metrics and consumes little computation power(except dynamic SDD-E).
-The only drawback is they require comprehensive estimation of target distributions.
-Although other parameters need estimation as well, they are naturally addressable under big data circumstances.
-
-	\section{Conclusion}\label{sec:conclusion}
-		This paper proposes a series of collective anomaly detection techniques, which helps detect data manipulations in modern data pipelines and data centres.
-Different from existing algorithms designed for collective anomalies, our approach employs statistical distance as the similarity measurement.
-We explored several technical points involved in the design of the algorithm and performed a thorough experiment to test its efficiency.
-The comparison experiment also illustrated the advantages of our technique.
-It can be concluded that the our technique can efficiently discover anomalies within the data collections and the classifier is sensitive enough toward real world data manipulations.
-
-%\section*{Acknowledgment}
-
-	\bibliographystyle{IEEEtran}
-
-	\bibliography{IEEEabrv,paper}
-
-%%	\newpage
-%	\onecolumn
-%	\appendix \label{sec:appendix}
-%	Here are the two equations for threshold calculation:
-%	\subsection{Estimation without $\alpha$}
-%		\begin{align}\label{equ:equal-weight}
-%			T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{a}(x)dx +
-%			\int_{T}^{\sup(D)}PDF_{n}(x)dx \nonumber\\
-%			& \approx \mathop{\arg\min}_{T}
-%			\int_{-\infty}^{T}
-%			\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-%			+ \int_{T}^{+\infty}
-%			\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx \nonumber\\
-%			& = \begin{cases}
-%				\displaystyle
-%				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{\sigma_a}{\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
-%				\displaystyle \frac{\mu_n + \mu_a}{2}, & \sigma_a = \sigma_n
-%			\end{cases}
-%		\end{align}
-%		
-%		Note: when $\sigma_a \ne \sigma_n$, keep the one s.t.
-$\displaystyle \frac{T - \mu_a}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{T - \mu_n}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
-%	
-%	\subsection{Estimation with $\alpha$}
-%		\begin{align}\label{equ:linear-weight}
-%			T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
-%			(1-\alpha)\int_{T}^{\sup(D)}PDF_{n}(x)dx\nonumber\\
-%			& \approx \mathop{\arg\min}_{T}
-%			\alpha\int_{-\infty}^{T}
-%			\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-%			+ 
-%			(1-\alpha)\int_{T}^{+\infty}
-%			\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\nonumber\\
-%			& = \begin{cases}
-%				\displaystyle
-%				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{(1 - \alpha)\sigma_a}{\alpha\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
-%				\displaystyle
-%				\frac{\mu_n + \mu_a}{2} + \frac{k^2ln\frac{1 - \alpha}{\alpha}}{\mu_a - \mu_n}, & \sigma_a = \sigma_n = k
-%			\end{cases}
-%		\end{align}
-%		
-%		Note: when $\sigma_a \ne \sigma_n$, keep the one s.t.
-$\displaystyle \frac{\alpha (T - \mu_a)}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{(1 - \alpha) (T - \mu_n)}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
-
 \end{document}
-
-In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those occurred at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years.
-And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}.
-System configuration problems, as a matter of fact, are also responsible for the disturbing situation.
-They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

### 2019-12-06 Paper/ICME Template/TemplateVersion.tex
把文章修改为ICME模板

--- 2019-12-06 Paper/FullPaper/paper.tex
@@
-% IEEE Paper Template for US-LETTER Page Size (V1)
-% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
-% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
-% Permission is granted to distribute and revise this file provided that
-% this header remains intact.
-%
-% REVISION HISTORY
-% 20080211 changed some space characters in the title-author block
-%
-\documentclass[10pt,conference,letterpaper]{article}
-\usepackage{times,amsmath,amsfonts,epsfig}
-\usepackage{graphicx}
+% Template for ICME 2020 paper; to be used with:
+%          spconf.sty  - ICASSP/ICIP/ICME LaTeX style file, and
+%          IEEEbib.bst - IEEE bibliography style file.
+% --------------------------------------------------------------------------
+\documentclass{article}
+\usepackage{spconf,amsmath,epsfig,amsfonts}
 \usepackage{algorithm,algorithmicx,algpseudocode}
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
-\usepackage{color}
-\usepackage{flushend}
+\usepackage{rotating}
+\usepackage{caption}
+\usepackage{ulem}
 \usepackage{multirow}
 \usepackage{multicol}
-\usepackage{cuted}
-\usepackage{rotating}
-\usepackage{caption}
+
+\let\OLDthebibliography\thebibliography
+\renewcommand\thebibliography[1]{
+  \OLDthebibliography{#1}
+  \setlength{\parskip}{0pt}
+  \setlength{\itemsep}{0pt plus 0.3ex}
+}
+
+\pagestyle{empty}
+
+\begin{document}\sloppy
+
+	% Example definitions.
+	% --------------------
+	\def\x{{\mathbf x}}
+	\def\L{{\cal L}}
+
+	% Title.
+	% ------
+	\title{Statistical Detection of Collective Data Fraud}
 	%
-\title{Statistical Detection of Collective Data Anomalies}
-\date{}
-%
-%\author{%
-%	% author names are typeset in 11pt, which is the default size in the author block
-%	{Ruoyu Wang{\small$^{1}$}, Daniel Sun{\small$^{2}$}, Guoqiang Li{\small$^{1*}$} }%
-%	% add some space between author names and affils
-%	\vspace{1.6mm}\\
-%	\fontsize{10}{10}\selectfont\itshape
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% separate superscript on following line from affiliation using narrow space
-%	$^{1}$\,School of Software, Shanghai Jiao Tong University, China\\
-%	\fontsize{9}{9}\selectfont\ttfamily\upshape
-%	%
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% in the following email addresses, separate the superscript from the email address 
-%	% using a narrow space \,
-%	% the reason is that Acrobat Reader has an option to auto-detect urls and email
-%	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
-%	% in the email address and corrupts it.
-%	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
-%	\{solftwarewry,li.g\}@sjtu.edu.cn
-%	% add some space between email and affil
-%	\vspace{1.2mm}\\
-%	\fontsize{10}{10}\selectfont\rmfamily\itshape
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% separated superscript on following line from affiliation using narrow space \,
-%	\,Data61, CSIRO, Australia\\
-%	\fontsize{9}{9}\selectfont\ttfamily\upshape
-%	% 20080211 CAUSAL PRODUCTIONS
-%	% removed ~ from pre-superscript since it does not seem to serve any purpose
-%	$^{2}$\,daniel.sun@data61.csiro.au
-%}
+	% Single address.
+	% ---------------
+	%\name{Anonymous ICME submission}
+	%Address and e-mail should NOT be added in the submission paper. They should be present only in the camera ready paper. 
+	\address{}
 
-%
-\begin{document}
 	\maketitle
-%
+
 	\begin{abstract}
-		Attackers infiltrate databases and software systems to not only steal chunks of data and hold them for ransom, but also alter certain parts, setting up traps harder to discover and causing damages unlikely to recover.
-		Without referring to data source, it is hard to detect a single record that is altered but still remain in correct value scopes.
-However, the change, especially to a subset of data, can be observed and detected in a collective scale.
+		Statistical divergence is widely applied in multimedia processing, basically due to regularity and explainable features displayed in data.
+However, in a broader range of data realm, these advantages may not out-stand, and therefore a more general approach is required.
+In data detection, statistical divergence can be used as an similarity measurement based on collective features.
 		In this paper, we present a collective detection technique based on statistical divergence.
-\textcolor{red}{Statistical divergence detection was explored in multimedia applications.
-But it is still underdeveloped in big data era due to data irregularity.} The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
-		Our technique continuously evaluates metrics as evolving features and calculate adaptive threshold to meet the best mathematical expectation.
-		To illustrate details of the technique and explore its efficiency, we case-studied a real world problem of click farming detection against malicious online sellers.
+		The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
+%		Our technique continuously evaluates metrics as evolving features and calculates adaptive threshold to meet the best mathematical expectation.
+%		To illustrate details of the technique and explore its efficiency, we case-studied a real world problem of click farming detection against malicious online sellers.
 The evaluation shows that these techniques provided efficient classifiers.
 They were also sufficiently sensitive to a much smaller magnitude of data alteration, compared with real world malicious behaviours.
-Thus, it is applicable in the real world.
+		Evaluation shows that it is applicable in the real world. 
 	\end{abstract}
 
-% NOTE keywords are not used for conference papers so do not populate them
-% \begin{keywords}
-% keyword-1, keyword-2, keyword-3
-% \end{keywords}
-%
+	\begin{keywords}
+		Statistical divergence, collective, fraud, detection
+	\end{keywords}
+
 	\section{Introduction}
-		Major improvements in data acquisition, transmission and storage are to increase data availability and affordability.
-Currently, there are more than 2.7ZB data in the digital universe~\cite{bigDataStatistics} and the growing speed is doubling every two years.
-		It has already been hard and will be much harder in the future to harness the exploding volume of data that has resulted in many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
-		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\cite{saha2014data}. Those data anomalies may arise due to both internal and external reasons.
+		\label{sec:intro}
+		Statistical divergence is widely applied in multimedia processing.
+Prevalent applications include multimedia event detection~\cite{amid2014unsupervised}, content classification~\cite{moreno2004kullback,park2005classification} and qualification~\cite{pheng2016kullback,goldberger2003efficient}.
+It has been attracting more attention since the dawn of big data era, basically due to regularity and interpretable features displayed in the data.
+However, in a broader range of data realm, these advantages may not out-stand (e.g.
+in online sales data records).
+It requires a more general approach.
 
-		On one hand, components inside systems may generate problematic source data.
-For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\cite{rassam2014adaptive}.
-Data packages will be lost if sensor nodes fail to connect to network or some sensor hubs break down~\cite{herodotou2014scalable}.
-Also, human operators act as a heavily vulnerable part to bugs and mistakes.
-Malicious insiders even deliberately modify system configurations for fatal compromises~\cite{schuster2015vc3}.
-A study shows that 65\% of organizations state that human errors are the main  cause of data problems~\cite{humanError} .
-
-		On the other hand, data manipulation~\cite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability.
-\textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
-		If data is compromised, it will severely affect mining and learning algorithms and further change the final decision driven by the data.
+		Data manipulation from outside hackers composes another potential threat of data frauds.
+\textit{Data Manipulation} here, according to a NSA definition, refers to behaviours which ``change information contained in those systems, rather than stealing data and holding it for ransom''.
 		In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.
 
-		It is hard to detect a single record that is alerted but still remain in correct value scopes, but if sufficient data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
+		It is hard to detect a single record that is altered but still remains in correct value scopes, but if sufficient data records are altered to change a final decision, we can still detect malicious data manipulation behaviours.
 		According to our observation, typical manipulations on numerical data will lead to a drift or distortion of its original distribution.
-For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones.
-		To address problems caused by data manipulation, we propose a novel technique which sorts out manipulated data collections from normal ones by adopting statistical divergence.
-		\textcolor{red}{Statistical divergence detection was explored in multimedia applications. But it is still underdeveloped in big data era due to data irregularity.}
-		In this paper, we focus on a concrete data manipulation problem: click farming in online shops, and try to apply our technique to pick out those dishonest sellers.
-		Our techniques maps data collections to points in distribution spaces and reduce the problem to classical point anomaly detection.
+		To address problems caused by data manipulation, we proposed a novel technique which sorts out manipulated data collections from normal ones by adopting statistical divergence.
+		In this paper, we focus on a concrete data manipulation problem: click farming in online shops, and try to apply our technique to pick out dishonest behaviours.
+		Our technique maps data collections to points in distribution spaces and reduce the problem to classical point anomaly detection.
 		Optimizations estimate ground truth, mapping each data collection into a single real number within a definite interval.
@@
 To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by statistical divergence.
-		In the dynamic environments, these evidence sets are modified after every data collection is checked, in which manner they act intuitively as slide windows and keep up to the evolving features in dynamic scenarios.
-		Our contribution includes: 1) A brief review on data anomaly detection and a study on the problem of click farming; 2) Detailed description of both basic and optimized framework of our technique, resolving several technical difficulties such as automated adaptive threshold; 3) Real world and synthetic data experiments that test efficiency of our technique and a comparison with a previous work on the same topic.
+		In the dynamic environments, these evidence sets act intuitively as slide windows and keep up to the evolving features in dynamic scenarios.
+		Our contribution includes: 1) A brief review on data fraud detection and a study on the problem of click farming; 2) Detailed description of both basic and optimized framework of our technique, resolving several technical difficulties such as automated adaptive threshold; 3) Comprehensive experiments that test efficiency of our technique and a comparison with previous work on similar topic.
 
-		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related work on data anomaly detection and describes a real world problem.
-Section~\ref{sec:preliminaries} introduces statistical distance.
+		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related work on data anomaly detection and briefly introduces click farming.
 		Details of proposed technique are introduced in section~\ref{sec:algorithm-details}.
@@
 		\subsection{Data Anomaly Detection}
-			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.
-			Anomaly detection algorithms deal with input data in the form of points (or records), sequences, graphs and spatial and geographical relationships.~\cite{chandola2009anomaly} According to relationships within data records, outliers can be classified into \textit{point anomalies}, \textit{contextual (or conditional) anomalies} and \textit{collective anomalies}.~\cite{goldberger2000components}
+			Statistical divergence was applied mainly as classifiers on multimedia content~\cite{park2005classification}, especially as kernels in SVMs~\cite{moreno2004kullback}.
+As a similarity measurement, it can also be used in qualitative and quantitative analysis in image evaluation~\cite{pheng2016kullback,goldberger2003efficient}.
+\cite{amid2014unsupervised} adopted divergence to detect events in multimedia streams.
 
-			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} catch most attention.
+%			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.
+%			Anomaly detection algorithms deal with input data in the form of points (or records), sequences, graphs and spatial and geographical relationships.~\cite{chandola2009anomaly} According to relationships within data records, outliers can be classified into \textit{point anomalies}, \textit{contextual (or conditional) anomalies} and \textit{collective anomalies}.~\cite{goldberger2000components}
+
+%			Currently, distance based~\cite{cao2014scalable,cao2017multi} and feature evolving algorithms~\cite{masud2013classification,li2015discovery,shao2014prototype} catch most attention.
 Others adopted tree isolation~\cite{zhang2017lshiforest}, model based~\cite{yin2016model} and statistical methods~\cite{zhu2002statstream} in certain applications.
@@
 proposed a technique, \textit{Multinomial Goodness-of-Fit} (MGoF), to analyze likelihood ratio of distributions via Kullback-Leibler divergence, and is fundamentally a hypothesis test on distributions~\cite{wang2011statistical}.
-			MGoF divides the observed data sequence into several windows.
+%			MGoF divides the observed data sequence into several windows.
 It quantifies data in each window into a histogram and check these estimated distributions against several hypothesis.
@@
 Furthermore, if the number of supporting evidence is larger than a threshold $c_{th}$, it is classified as non-anomaly.
-
 			MGoF is the best competitor out of the similar techniques, and we use it as our baseline against our approach.
@@
 		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
-%			Since the establishment of Taobao in 2003, its online business platform has been growing from a follower in the market to the No.1 service provider in B2B and B2C markets, 
-			Taobao possesses a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}.
-Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products.
-Under the super-pressure caused by massive competitors, a number of the sellers choose to use some cheating techniques to raise reputation and sale volumes, then improve rankings in search lists.
-
-			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of customer accounts to create fake transaction records and give high remarks on products.
-Professional click farmers are usually well organized groups or companies containing thousands of people.
-%			Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions. 
-			Some companies even develop professional applications that can be deployed on common PCs to improve productivity~\cite{zhao2016on}.
-
+			Click farming is the behaviour that online sellers use a large number of customer accounts to create fake transaction records and give high remarks on products.
 			There are two types of click farming behaviours: Centralized and Equalized.
-Centralized click farming refers to the scenarios that transactions are randomly generated throughout the day.
-A significant feature of this approach is that the cheating transactions usually assemble together in a short period of time since most workers work at the same time.
-Equalized click farming refers to the circumstances that click farms are arranged by some well programmed applications or teams carefully managed and strictly commit transactions according to a timetable.
-Thus the transaction distribution may not vary too much with and without click farming.
-
-			A research performed in China showed that 81.9\% of investigated people had heard of the behaviour of click farming, 51.2\% are aware of click farm and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}.
-American researchers reported in 2015 that over 11000 sellers on Taobao were detected to have click farmed records and only 2.2\% of 4000 investigated dishonest sellers had been penalized because of the cheating attempts~\cite{netease2015research}.
-
-			Current detection techniques for click farming mainly focus on user behaviours, such as browsing frequencies and periods, most common purchasing time, favourite products, remarks and whether they communicate with sellers~\cite{simpleDetection}.
-Those techniques require the platform to keep lots of records and user features.
+			Equalized click farming refers to scenarios where behaviours are well organised while centralized does not.
+			Current detection techniques for click farming mainly focus on user behaviours.
+Those techniques require platforms to keep records on user features.
 However, the detection can be easily bypassed by trained workers and some well programmed applications.
 
-			\begin{figure}[t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
-				\caption{Example cumulative distribution function of original and click farmed daily transaction data}
-				\label{fig:example-ecdf}
-			\end{figure}
-
 			Although it is hard to classify users as honest or malicious, we can still find clues from the sellers' aspect.
-For normal sellers, their customers are usually similar since choices of products are seldom changed.
-Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable.
-No matter how much alike between honest users and robots or the employed workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
-To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records and emulated the circumstances if it had been click farmed (see section~\ref{sec:exp-methodology}).
-Fig.~\ref{fig:example-ecdf} shows the difference between normal and click farmed distributions of one day in the data set.
+			No matter how much alike between honest users and malicious workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution.
 			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.
 
-	\section{Preliminaries}\label{sec:preliminaries}
-		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
-		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold.
-Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers:
-		\begin{equation}
-			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+} \cup \{0\}
-		\end{equation}
-
-		Divergence between two distributions $P$ and $Q$, written as $D(P||Q)$, satisfies:
-
-		\begin{enumerate}
-			\item $D(P||Q) \ge 0, \forall P, Q \in \mathbb{S}$
-			\item $D(P||Q) = 0$, if and only if $P=Q$
-		\end{enumerate}
-
-		For our purposes, we do not require the function $D$ to have the property: $D(P||Q) = D(Q||P)$.
-But we do need it to be true that if $Q$ is more similar with $P$ than $U$, then $D(Q||P) < D(U||P)$.
-There are ways to calculate divergence,	several frequently used divergence metrics are as follows:
-
-		\subsection{Kullback-Leibler Divergence}
-			Let $P,Q$ be discrete probability distributions, $Q(x)=0$ implies $P(x)=0$ for $\forall x$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:
-
-			\begin{equation}
-				KLD(P||Q) = \sum_{Q(x)\ne 0} P(x)log\Big(\frac{P(x)}{Q(x)}\Big)
-			\end{equation}
-
-			For $P,Q$ being continuous distributions:
-
-			\begin{equation}
-				KLD(P||Q) = \int_{q(x) \ne 0} p(x)log\frac{p(x)}{q(x)}dx
-			\end{equation}
-
-		\subsection{Jensen-Shannon Divergence}
-			Let $P,Q$ be discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:
-
-			\begin{equation}
-				JSD(P||Q) = \frac{1}{2}KLD(P||M) + \frac{1}{2}KLD(Q||M)
-			\end{equation}
-			where $\displaystyle M = \frac{1}{2}(P+Q)$.
-
-			A more generalized form is defined to be:
-
-%			{\small
-			\begin{equation}
-					JSD(P_1, \dots, P_n) = H\Big(\sum_{i=1}^n\pi_i P_i\Big) - \sum_{i=1}^n\pi_iH(P_i)
-			\end{equation}
-%			}
-			where $H$ is Shannon Entropy, $\displaystyle M = \sum_{i=1}^{n}\pi_iP_i$ and $\displaystyle \sum_{i=1}^{n}\pi_i = 1$.
-
-			Especially, if $\displaystyle \pi_i = \frac{1}{n}$, then:
-			\begin{equation}
-				JSD(P_1, \dots, P_n) = \frac{1}{n}\sum_{i=1}^{n}KLD(P_i||M)
-			\end{equation}
-
-			Jensen-Shannon divergence has some fine properties:
-			\begin{enumerate}
-				\item $JSD(P||Q) = JSD(Q||P), \forall P, Q\in \mathbb{S}$.
-				\item $0 \le JSD(P_1, \dots, P_n) \le log_k(n)$. If a $k$ based algorithm is adopted.
-				\item To calculate $JSD(P||Q)$, it need not necessarily to be true that $Q(x)=0$ implies $P(x)=0$.
-			\end{enumerate}
-
-		\subsection{Bhattacharyya Distance}
-			Let $P,Q$ be discrete probability distributions over same domain $X$, \textit{Bhattacharyya Distance} between $P$ and $Q$ is defined to be:
-
-			\begin{equation}
-				BD(P||Q) = -ln\Big(\sum_{x\in X}\sqrt{P(x)Q(x)}\Big)
-			\end{equation}
-
-		\subsection{Hellinger Distance}
-			Let $P,Q$ be discrete probability distributions, \textit{Hellinger Distance} between $P$ and $Q$ is defined to be:
-
-			\begin{equation}
-				HD(P||Q) = \frac{1}{\sqrt{2}}\sqrt{\sum_x\bigg(\sqrt{P(x)} - \sqrt{Q(x)}\bigg)^2}
-			\end{equation}
-
-		\subsection{Kolmogorov-Smirnov Statistic}
-			Let $P,Q$ be discrete one-dimensional probability distributions, $CDF_P$ and $CDF_Q$ are their cumulative probability functions respectively, \textit{Kolmogorov-Smirnov Statistic} between $P$ and $Q$ is defined to be:
-
-			\begin{equation}
-				KSS(P||Q) = \sup_x | CDF_P(x) - CDF_Q(x) |
-			\end{equation}
-
 	\section{Statistical Detection}\label{sec:algorithm-details}
-
-		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records.
-For example, traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale.
-Manipulation on those data (e.g.
-Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger an alarm.
-
-		\subsection{Statistical Divergence Detection with Reference(SDD-R)}\label{sec:alg-opt-reference}
-			From Section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions.
+		\subsection{Statistical Divergence Detection with Reference (SDD-R)}\label{sec:alg-opt-reference}
+			Statistical divergence only provides a distance between two or more distributions.
 In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the symmetric divergence between two connected nodes.
@@
 
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/JSD-Dist.png}
-				\caption{Distribution of Jensen-Shannon divergence on Taobao data set(without click farming) used in the experiments.}
-				\label{fig:jsd-dist}
-			\end{figure}
-
-			Fig.~\ref{fig:jsd-dist} shows distribution of all divergences against the reference.
-It can be approximated as a Gaussian distribution though the true one may differ a little more from the standard Gaussian than the expected estimation error.
+			Distribution of all divergences against the reference can be approximated as a Gaussian distribution though the true one may differ a little more from the standard Gaussian than the expected estimation error.
 That is due to the unknown randomness within real world data.
@@
 			One important factor in algorithm SDD-E is the value of threshold.
-A lower threshold rejects more instances, improving the sensitivity of anomalous data while increasing the number of false alarms.
+%			A lower threshold rejects more instances, improving the sensitivity of anomalous data while increasing the number of false alarms.
 A higher threshold provide higher true negative rates yet neglecting more possible threats.
-
 			A naive but prevalent approach is to set a fixed value as the threshold(As is shown in Algorithm~\ref{alg:sdd-r}).
-This approach is easy to implement and may give satisfying results in specific cases.
+%			This approach is easy to implement and may give satisfying results in specific cases.
 			However, a fixed threshold requires specific analysis in the certain scenario, manual observations and tuning of parameters, which involves lots of human labour.
-The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous.
+%			The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous.
 It can be used to automatically determine a threshold.
@@
 			Fortunately, applying divergence as the distance measurement among data collections provides a fine property.
-With a reference distribution, divergences of normal data collections form a quasi-Gaussian distribution as we have seen in section \ref{sec:alg-opt-reference}.
+With a reference distribution, divergences of normal data collections form a quasi-Gaussian distribution.
 The same applies to those anomalous ones.
@@
 				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
-				\caption{Threshold can be determined either by a probability density value, or a radius from the centre.
-In the scenario shown in the figure, the threshold can be determined by the position between two centres of the distribution, denoted as ``T'' here.
-This form of threshold can also be applied to other types of distributions even there is no intersection between these two.}
+				\caption{Optimal threshold should minimize the size of shadow under curve.}
 				\label{fig:example-threshold}
@@
 			Moreover, as is verified in experiments, the meta-distribution of anomalous data collections lies in the right-hand-side to the normal one on the real line.
-As shown in Fig~\ref{fig:example-threshold}, the black curve ($PDF_{normal}(x)$ or in short $PDF_n(x)$) displays the probability density function (PDF) fitting those divergences calculated from normal data collections; the blue curve ($PDF_{anomalous}(x)$ or in short $PDF_a(x)$) displays the PDF derived from anomalous data collections.
+As shown in Fig~\ref{fig:example-threshold}, the black curve displays the probability density function (PDF) fitting those divergences calculated from normal data collections; the blue curve displays the PDF derived from anomalous data collections.
 Threshold is chosen to minimize total errors(both false negative and false positive).
 
-			Suppose:
-			\begin{align}
-				PDF_n(x) &\approx \mathcal{N}(\mu_n, \sigma_n)\\
-				PDF_a(x) &\approx \mathcal{N}(\mu_a, \sigma_a)
-			\end{align}
-
-			Then the optimal threshold $T$ is calculated by E.q.(\ref{equ:equal-weight}). The optimal threshold will minimize total errors and yield an optimal outcome.
-			However, this is not accurate enough, since E.q.(\ref{equ:equal-weight}) implicates an assumption that chances are the same for a new data collection to be either anomalous or not.
-If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as E.q.(\ref{equ:linear-weight}), where $\alpha$ is the anomaly probability.
-
-			\begin{align}\label{equ:equal-weight}
-				T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{a}(x)dx +
-				\int_{T}^{\sup(D)}PDF_{n}(x)dx \nonumber\\
-				& \approx \mathop{\arg\min}_{T}
-				\int_{-\infty}^{T}
-				\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-				+ \int_{T}^{+\infty}
-				\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx \nonumber\\
-				& = \begin{cases}
-				\displaystyle
-				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{\sigma_a}{\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
-				\displaystyle \frac{\mu_n + \mu_a}{2}, & \sigma_a = \sigma_n
-				\end{cases}
-			\end{align}
-
-			Note: when $\sigma_a \ne \sigma_n$, keep the root s.t.
-$\displaystyle \frac{T - \mu_a}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{T - \mu_n}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
-
-			\begin{align}\label{equ:linear-weight}
-				T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
-				(1-\alpha)\int_{T}^{\sup(D)}PDF_{n}(x)dx\nonumber\\
-				& \approx \mathop{\arg\min}_{T}
-				\alpha\int_{-\infty}^{T}
-				\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-				+ 
-				(1-\alpha)\int_{T}^{+\infty}
-				\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\nonumber\\
-				& = \begin{cases}
-				\displaystyle
-				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{(1 - \alpha)\sigma_a}{\alpha\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
-				\displaystyle
-				\frac{\mu_n + \mu_a}{2} + \frac{k^2ln\frac{1 - \alpha}{\alpha}}{\mu_a - \mu_n}, & \sigma_a = \sigma_n = k
-				\end{cases}
-			\end{align}
-
-			Note: when $\sigma_a \ne \sigma_n$, keep the root s.t.
-$\displaystyle \frac{\alpha (T - \mu_a)}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{(1 - \alpha) (T - \mu_n)}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
+			Then the optimal threshold $T$ is calculated by minimizing total errors.
+			However, this is not accurate enough, it implicates an assumption that chances are the same for a new data collection to be either anomalous or not.
+If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as minimizing expected errors, where we use $\alpha$ to denote anomaly probability.
 
@@
 		\subsection{Methodology}\label{sec:exp-methodology}
-			We adopted two data sets: 1) Koubei sellers' transaction records\footnote{https://tianchi.aliyun.com/competition/information.htm?raceId=231591}; 2) Synthetic random distribution data set.
-Koubei data set was provided by Alibaba Tian Chi big data competition where all records were collected from real world business scenarios.
-It contained information about seller features, user payments and browsing behaviour.
-We randomly chose one seller (ID: 1629) and extracted transaction history of this seller, records ranging from Nov.
-11th 2015 to Oct.
-31st 2016.
+			We adopted Koubei sellers' transaction records\footnote{https://tianchi.aliyun.com/competition/information.htm?raceId=231591} in experiments.
+It was provided by Alibaba Tian Chi big data competition where all records were collected from real world business scenarios.
+%			It contained information about seller features, user payments and browsing behaviour.
+We randomly chose one seller (ID: 1629) and extracted transaction history of this seller.
 Entire transaction set was then divided into 325 collections, each containing records in one day.
-Fig.~\ref{fig:daily-transaction-volume} and~\ref{fig:sale-distribution-sample} give an overview of it.
-
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=0.75\linewidth]{fig/DailyTransactionVolume.png}
-				\caption{Changing of the daily sales volume shows that environment of online sales had been changing all the time.}
-				\label{fig:daily-transaction-volume}
-			\end{figure}
-
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/SaleDistributions.png}
-				\caption{We selected 3 days randomly and drew sales distribution by counting hourly volume. Although sales volume has changed from day to day, the shape of the distribution remain almost alike.}
-				\label{fig:sale-distribution-sample}
-			\end{figure}
-
 			Two types of click-farmed data was generated according to patterns described in section~\ref{sec:related-realworld}.
-To emulate centralized click farming, we randomly inserted some Gaussian-distributed transactions in the chosen collection.
+%			To emulate centralized click farming, we randomly inserted some Gaussian-distributed transactions in the chosen collection.
 As for emulating the equalized click farmers, we simply doubled each record in the chosen collection to make the new distribution exactly the same as the original one, which is harder for the online platform to discover.
-			Usually, the click-farmed transactions are several times more than the volume it originally has, if the seller hires a group of organized workers.
+%			Usually, the click-farmed transactions are several times more than the volume it originally has, if the seller hires a group of organized workers.
 			In our experiments, we use $\nu$ to denote the magnitude coefficient of click farming.
@@
 
-			The synthetic data set was divided into four sections.
-First two sections contained sample sets drawn from a uniform and a Gaussian distribution respectively.
-The third section used a mixture of one uniform distribution and two Gaussian distributions to simulate a random-shaped distribution.
-Moreover, we made the random-shaped distribution drift slightly to form the last section of test data.
-Corresponding anomalies were drown from distributions with deviated parameters respectively.
-
-			We adopted histograms to depict distributions of any shape.
-Surely, the kernel density estimation approaches will give smooth and continuous estimations on any sampled data.
-But the computational cost will be too much to afford.
-Step size of histograms is chosen by:
-			\begin{equation}\label{equ:step-size}
-				l = c \sigma k^{-0.2},
-			\end{equation}
-			where $k$ is sample size, $c$ is a constant relative to the shape of distribution (e.g.
-for normal distribution, $c=1.05$) and $\sigma$ the standard deviation.
-For data sets with a large number of elements, a random sampling method, such as Monte-Carlo method, can be applied to speed up the estimation procedure.
+%			We adopted histograms to depict distributions of any shape, step size of which is chosen by:
+%			\begin{equation}\label{equ:step-size}
+%				l = c \sigma k^{-0.2},
+%			\end{equation}
+%			where $k$ is sample size, $c$ is a constant relative to the shape of distribution (e.g. for normal distribution, $c=1.05$) and $\sigma$ the standard deviation.
 
@@
 		\subsection{Experiments on Koubei Data Set}\label{sec:exp-raw}
-			We first tested our algorithms on Koubei data set in order to see whether and why the algorithm works.
+			We first tested our algorithms to see whether and why the algorithm works.
 Anomalies were random selected days replaced by corresponding click farmed version.
@@
 The second level is to draw a histogram on the sub-volumes in each time span(i.e.
-a histogram on frequencies in the first level histogram, as shown in Fig.~\ref{fig:histogram-example}).
-
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/HistogramExample.png}
-				\caption{Examples of 1st and 2nd Level Histogram}
-				\label{fig:histogram-example}
-			\end{figure}
-
-			On the raw data set, we had no choice but to set one hour a basket. While on the enhanced data set, we adopted E.q.(\ref{equ:step-size}) to determine step size automatically.
+a histogram on frequencies in the first level histogram).
 			To test SDD-E, we randomly selected 30 correct days and 10 click farmed days as normal and anomalous evidence respectively.
@@
 				\centering
-				\includegraphics[width=\linewidth]{fig/Raw1stLevelHist.png}
-				\caption{1st level histogram of day 5, 113 and 287, each day in a column.
-Distributions after centralized and equalized click farming are in 1st and 3rd rows correspondingly.
-And the original distributions are shown in the 2nd row.}
-				\label{fig:raw-hist-1st}
-			\end{figure}
-
-			\begin{figure}[!t]
-				\centering
 				\includegraphics[width=\linewidth]{fig/RawOverview2nd.png}
@@
 			When classifying toward 1st level histograms, centralized click farming behaviours can be easily discovered.
-As displayed in the first two rows in Fig.~\ref{fig:raw-hist-1st}, normal collections share a similar distribution while centralized click-farmed ones abruptly violated the original shape.
-However, as a clever click farmer, equalized click farming did not in the least distort the distribution.
-Most of them escaped the check under perfect disguises.
-			But when it came to 2nd level histograms, the ``clever disguise'' did not work any longer.
+It is because normal collections share a similar distribution while centralized click-farmed ones abruptly violated the original shape.
+			When it came to 2nd level histograms, equalized click farming were also effectively discovered.
 It can be clearly seen in Fig.~\ref{fig:raw-overview} that distribution of divergence of both click farming types shows an obvious deviation from the normal one.
 
-			The result showed that our technique outperformed MGoF in every real world cases.
+			The result showed that our technique outperformed MGoF in every real world case.
 			SDD-E provided best performance, yet it consumed the most computing power.
 Comparison among SDD-R revealed improvement of reference as well as the importance of threshold under this technique.
-Although dynamic SDD-E consumes more computation power, it is clear that dynamic SDD-E is capable of tracing the gradual shift of environment.
+It is also clear that dynamic SDD-E is capable of tracing the gradual shift of environment.
 MGoF turned out to be the worst since it always mark several false positive when $c_{th}$ had not been met and much more false negatives when similar errors occurred too many.
@@
 When it came to 2nd level distributions, histograms became much coarser since data available was highly limited and thus its performance suffered dramatically.
-
-			MGoF tended to classify every distribution as anomaly, therefore benefited most by larger $\alpha$.
+%			MGoF tended to classify every distribution as anomaly, therefore benefited most by larger $\alpha$.
 It always classifies as anomalous the first $c_{th}$ distributions supporting every null hypothesis.
@@
 
-		\subsection{Results on Synthetic Data Set}
-			In this experiment, we tested all seven algorithms on totally synthetic data sets.
-Results are shown in TABLE~\ref{tab:performance-synthetic}.
-It shows that our technique can be applied towards any kind of distributions.
-And these techniques worked better under irregular distributions since difference were clearer among these.
-Comparison between SDD-R and static SDD-E
-			shows that adaptive thresholds provided more flexible classifiers. Results under random-shape drifting proves the efficiency of sliding windows toward drifting context.
-
-			\begin{sidewaystable}
-				\centering
-				\caption{Performance Comparison on Synthetic Data Sets}
-				\label{tab:performance-synthetic}
-				\footnotesize
-				\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-					\hline
-					\multirow{2}{*}{\textbf{}} & \multicolumn{4}{c|}{\textbf{Uniform}} & \multicolumn{4}{c|}{\textbf{Gaussian}} & \multicolumn{4}{c|}{\textbf{Random-shape}} & \multicolumn{4}{c|}{\textbf{Random-shape with Drift}} \\ \cline{2-17}
-					& \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} & \textbf{Pre(\%)} & \textbf{Rec(\%)} & \textbf{F1(\%)} & \textbf{T(ms)} \\ \hline
-					\textbf{SDD-R} & 10.00 & \textbf{100.00} & 18.18 & 349.42 & 24.78 & 69.20 & 36.49 & 401.82 & 10.00 & \textbf{100.00} & 18.18 & 351.65 & 9.97 & \textbf{99.00} & 18.11 & 353.65 \\ \hline
-					\textbf{SDD-R+} & 22.40 & 22.40 & 22.40 & 348.49 & 34.40 & 34.40 & 34.40 & \textbf{398.02} & 58.40 & 58.40 & 58.40 & \textbf{350.87} & 1.20 & 1.20 & 1.20 & \textbf{346.67} \\ \hline
-					\textbf{SDD-E Static} & 43.71 & 82.60 & 57.17 & 372.74 & 33.34 & 66.60 & 44.44 & 410.72 & 69.24 & 93.20 & 79.45 & 372.77 & 12.34 & 97.20 & 21.91 & 369.63 \\ \hline
-					\textbf{SDD-E Static+} & \textbf{75.10} & 60.20 & \textbf{66.83} & 371.72 & \textbf{45.93} & 45.80 & \textbf{45.86} & 412.95 & \textbf{89.52} & 85.40 & \textbf{87.41} & 368.97 & 12.60 & 94.20 & 22.23 & 370.12 \\ \hline
-					\textbf{SDD-E Dynamic} & 18.53 & 81.80 & 30.21 & 6808.58 & 20.28 & \textbf{71.40} & 31.58 & 8985.92 & 25.90 & 97.40 & 40.92 & 5881.37 & 13.44 & 97.20 & 23.61 & 5747.19 \\ \hline
-					\textbf{SDD-E Dynamic+} & 27.85 & 25.60 & 26.68 & 8019.23 & 26.19 & 56.40 & 35.77 & 9197.94 & 77.60 & 79.40 & 78.49 & 6408.12 & \textbf{50.55} & 84.00 & \textbf{63.11} & 6176.57 \\ \hline
-					\textbf{MGoF} & 10.94 & 4.40 & 6.28 & \textbf{347.97} & 10.08 & 51.60 & 16.87 & 571.93 & 6.40 & 13.60 & 8.70 & 440.26 & 2.75 & 11.60 & 4.45 & 509.58 \\ \hline
-				\end{tabular}
-
-				\begin{multicols}{2}
-					\includegraphics[width=\linewidth]{fig/F1OnDivergenceMetric.png}
-					\captionof{figure}{F1 under Different Divergence Metric}
-					\label{fig:divergence-metric-f1}
-					\includegraphics[width=.8\linewidth]{fig/ROCUnderDifferentMetrics.png}
-					\captionof{figure}{ROC under Different Divergence Metric}
-					\label{fig:divergence-metric-roc}
-				\end{multicols}
-			\end{sidewaystable}
-
-			The last experiment was carried out on random-shaped distribution data set, with $alpha=0.1$ and rest parameters the same.
-Under different divergence metrics mentioned in section~\ref{sec:preliminaries}, F1 scores were calculated among all SDD algorithms and ROC curves were recorded on SDD-R and static SDD-E.
-Given that MGoF was defined specifically on Kullback-Leibler divergence, it cannot be tested in the same way.
-Results are shown in Fig.~\ref{fig:divergence-metric-f1} and Fig.~\ref{fig:divergence-metric-roc}.
-
-			It is indicated that Jensen-Shannon divergence is suited to all techniques due to its symmetry.
-Kullback-Leibler divergence provides more evident differences when references were given.
-Bhattacharyya distance and Hellinger distance turned out almost as good as Jensen-Shannon divergence, but they consumed less time.
-Kolmogorov-Smirnov Statistic performed relatively poor since it considers only the largest gap between two distributions, which provides little information.
-
 		\subsection{Discussion}
@@
 			However, in SDD-R and SDD-E, that is not a problem since it can map and gather all anomalies together and draw a universal boundary between them and all normal collections.
-These techniques are suitable to all typical divergence metrics and consumes little computation power(except dynamic SDD-E).
-The only drawback is they require comprehensive estimation of target distributions.
+These techniques are suitable to all typical divergence metrics and consume little computation power(except dynamic SDD-E).
+The only drawback is that they require comprehensive estimation of target distributions.
 Although other parameters need estimation as well, they are naturally addressable under big data circumstances.
@@
 
-%\section*{Acknowledgment}
-
-	\bibliographystyle{IEEEtran}
-
-	\bibliography{IEEEabrv,paper}
-
-%%	\newpage
-%	\onecolumn
-%	\appendix \label{sec:appendix}
-%	Here are the two equations for threshold calculation:
-%	\subsection{Estimation without $\alpha$}
-%		\begin{align}\label{equ:equal-weight}
-%			T &= \mathop{\arg\min}_{T} \int_{0}^{T}PDF_{a}(x)dx +
-%			\int_{T}^{\sup(D)}PDF_{n}(x)dx \nonumber\\
-%			& \approx \mathop{\arg\min}_{T}
-%			\int_{-\infty}^{T}
-%			\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-%			+ \int_{T}^{+\infty}
-%			\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx \nonumber\\
-%			& = \begin{cases}
-%				\displaystyle
-%				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{\sigma_a}{\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
-%				\displaystyle \frac{\mu_n + \mu_a}{2}, & \sigma_a = \sigma_n
-%			\end{cases}
-%		\end{align}
-%		
-%		Note: when $\sigma_a \ne \sigma_n$, keep the one s.t.
-$\displaystyle \frac{T - \mu_a}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{T - \mu_n}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
-%	
-%	\subsection{Estimation with $\alpha$}
-%		\begin{align}\label{equ:linear-weight}
-%			T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
-%			(1-\alpha)\int_{T}^{\sup(D)}PDF_{n}(x)dx\nonumber\\
-%			& \approx \mathop{\arg\min}_{T}
-%			\alpha\int_{-\infty}^{T}
-%			\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
-%			+ 
-%			(1-\alpha)\int_{T}^{+\infty}
-%			\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\nonumber\\
-%			& = \begin{cases}
-%				\displaystyle
-%				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{(1 - \alpha)\sigma_a}{\alpha\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
-%				\displaystyle
-%				\frac{\mu_n + \mu_a}{2} + \frac{k^2ln\frac{1 - \alpha}{\alpha}}{\mu_a - \mu_n}, & \sigma_a = \sigma_n = k
-%			\end{cases}
-%		\end{align}
-%		
-%		Note: when $\sigma_a \ne \sigma_n$, keep the one s.t.
-$\displaystyle \frac{\alpha (T - \mu_a)}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{(1 - \alpha) (T - \mu_n)}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
+% References should be produced using the bibtex program from suitable
+% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
+% style file from IEEE produces unsorted bibliography list.
+% -------------------------------------------------------------------------
+\bibliographystyle{IEEEbib}
+\bibliography{TemplateVersion}
 
 \end{document}
-
-In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those occurred at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years.
-And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}.
-System configuration problems, as a matter of fact, are also responsible for the disturbing situation.
-They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

### 2019-12-06 Drawings.py

@@ -154,17 +154,17 @@ def drawDivergenceWithReference():
     coordinates = sorted(dist_jsd_normal.items(), key=lambda kv: kv[0])
     xs = [c[0] * step for c in coordinates]
     ys = [c[1] for c in coordinates]
-    plt.plot(xs, ys, '.-', ms=5, color=RED, label='Normal')
+    plt.plot(xs, ys, 'o-', ms=5, color=BLACK, label='Normal')
 
     coordinates = sorted(dist_jsd_centralized.items(), key=lambda kv: kv[0])
     xs = [c[0] * step for c in coordinates]
     ys = [c[1] for c in coordinates]
-    plt.plot(xs, ys, 'x-', ms=5, label='Centralized')
+    plt.plot(xs, ys, 'x--', ms=5, color=BLACK, label='Centralized')
 
     coordinates = sorted(dist_jsd_equalized.items(), key=lambda kv: kv[0])
     xs = [c[0] * step for c in coordinates]
     ys = [c[1] for c in coordinates]
-    plt.plot(xs, ys, 'o-', ms=5, color=GREEN, label='Equalized')
+    plt.plot(xs, ys, 'v-.', ms=5, color=BLACK, label='Equalized')
 
     plt.xlabel("JSD", fontsize='large')
     plt.ylabel("Probability")
@@ -178,55 +178,57 @@ def drawDifferentAnomalyProbability():
     print("Drawing performance on different anomaly probability figure...")
     # 加载数据 #
     acc_1st_centralized = [
-        [97.16923077, 98.03076923, 90.95384615, 93.41538462, 88.30769231],
-        [94.95384615, 97.90769231, 85.41538462, 93.90769231, 78.52307692],
-        [88.55384615, 98.03076923, 82.33846154, 94.83076923, 70.09230769],
-        [73.41538462, 98.4, 81.47692308, 95.01538462, 61.10769231],
-        [49.04615385, 98.64615385, 83.63076923, 95.01538462, 51.01538462],
-        [37.72307692, 99.13846154, 90.46153846, 96.8, 56.67692308],
-        [41.04615385, 99.01538462, 97.90769231, 97.04615385, 56.06153846],
-        [60, 99.26153846, 98.09230769, 98.58461538, 66.83076923],
-        [79.69230769, 98.89230769, 89.84615385, 87.75384615, 89.53846154],
[…]

### 2019-12-09 Paper/FullPaper/paper.tex
完成ICME模板文章

@@
 \usepackage{caption}
+\usepackage{ulem}
 %
-\title{Statistical Detection of Collective Data Anomalies}
+\title{Statistical Detection of Collective Data Fraud}
 \date{}
@@
 	\begin{abstract} 
-		Attackers infiltrate databases and software systems to not only steal chunks of data and hold them for ransom, but also alter certain parts, setting up traps harder to discover and causing damages unlikely to recover.
-		Without referring to data source, it is hard to detect a single record that is altered but still remain in correct value scopes.
-However, the change, especially to a subset of data, can be observed and detected in a collective scale.
+		Statistical divergence is widely applied in multimedia processing, basically due to regularity and explainable features displayed in data.
+However, in a broader range of data realm, these advantages may not out-stand, and therefore a more general approach is required.
+		In data detection, statistical divergence can be used as an similarity measurement based on collective features.
 		In this paper, we present a collective detection technique based on statistical divergence.
-\textcolor{red}{Statistical divergence detection was explored in multimedia applications.
-But it is still underdeveloped in big data era due to data irregularity.} The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
-		Our technique continuously evaluates metrics as evolving features and calculate adaptive threshold to meet the best mathematical expectation.
+The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
+		Our technique continuously evaluates metrics as evolving features and calculates adaptive threshold to meet the best mathematical expectation.
 		To illustrate details of the technique and explore its efficiency, we case-studied a real world problem of click farming detection against malicious online sellers.
@@
 	\section{Introduction}
-		Major improvements in data acquisition, transmission and storage are to increase data availability and affordability.
+		Statistical divergence is widely applied in multimedia processing.
+Prevalent applications include multimedia event detection~\cite{amid2014unsupervised}, content classification~\cite{moreno2004kullback,park2005classification} and qualification~\cite{pheng2016kullback,goldberger2003efficient}.
+It has been attracting more attention since the dawn of big data era, basically due to regularity and interpretable features displayed in the data.
+However, in a broader range of data realm, these advantages may not out-stand (e.g.
+in online sales data records).
+It requires a more general approach.
+
 		Currently, there are more than 2.7ZB data in the digital universe~\cite{bigDataStatistics} and the growing speed is doubling every two years.
@@
 For measurable reshaping, we can enclose data collections with similar distribution patterns and filter out those strangely shaped ones.
-		To address problems caused by data manipulation, we propose a novel technique which sorts out manipulated data collections from normal ones by adopting statistical divergence.
-		\textcolor{red}{Statistical divergence detection was explored in multimedia applications. But it is still underdeveloped in big data era due to data irregularity.}
+		To address problems caused by data manipulation, we proposed a novel technique which sorts out manipulated data collections from normal ones by adopting statistical divergence.
 		In this paper, we focus on a concrete data manipulation problem: click farming in online shops, and try to apply our technique to pick out those dishonest sellers.
-		Our techniques maps data collections to points in distribution spaces and reduce the problem to classical point anomaly detection.
+		Our technique maps data collections to points in distribution spaces and reduce the problem to classical point anomaly detection.
 		Optimizations estimate ground truth, mapping each data collection into a single real number within a definite interval.
@@
 		\subsection{Data Anomaly Detection}
+			Statistical divergence was applied mainly as classifiers on multimedia content~\cite{park2005classification}, especially as kernels in SVMs~\cite{moreno2004kullback}.
+As a similarity measurement, it can also be used in qualitative and quantitative analysis in image evaluation~\cite{pheng2016kullback,goldberger2003efficient}.
+\cite{amid2014unsupervised} adopted divergence to detect events in multimedia streams.
+
 			Anomaly detection, also known as outlier detection, has been studied for a long time and discussed in diverse research domains, such as fraud detection, intrusion detection, system monitoring, fault detection and event detection in sensor networks.

### 2019-12-09 Paper/ICME Template/TemplateVersion.tex
完成ICME模板文章

@@
 \usepackage{multicol}
+\usepackage{cuted}
 
@@
 	\begin{abstract}
-		Statistical divergence is widely applied in multimedia processing, basically due to regularity and explainable features displayed in data.
+		Statistical divergence is widely applied in multimedia processing, basically due to regularity and interpretable features displayed in data.
 However, in a broader range of data realm, these advantages may not out-stand, and therefore a more general approach is required.
-In data detection, statistical divergence can be used as an similarity measurement based on collective features.
+In data detection, statistical divergence can be used as a similarity measurement based on collective features.
 		In this paper, we present a collective detection technique based on statistical divergence.
@@
 
-		Data manipulation from outside hackers composes another potential threat of data frauds.
+		General data frauds can be caused by manipulation from outside hackers.
+%		Data manipulation from outside hackers composes another potential threat of data frauds.
 		\textit{Data Manipulation} here, according to a NSA definition, refers to behaviours which ``change information contained in those systems, rather than stealing data and holding it for ransom''.
@@
 			Click farming is the behaviour that online sellers use a large number of customer accounts to create fake transaction records and give high remarks on products.
-			There are two types of click farming behaviours: Centralized and Equalized.
-			Equalized click farming refers to scenarios where behaviours are well organised while centralized does not.
+			There are two types of click farming behaviours: centralized and equalized.
+			Equalized click farming refers to scenarios where behaviours are well organised while centralized one does not.
 			Current detection techniques for click farming mainly focus on user behaviours.
@@
 		\subsection{Statistical Divergence Detection with Reference (SDD-R)}\label{sec:alg-opt-reference}
-			Statistical divergence only provides a distance between two or more distributions.
-In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the symmetric divergence between two connected nodes.
+			Distortion or drift of certain distribution can be quantified by statistical divergence.
+			It provides a distance between two or more distributions.
+In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the symmetric divergence between two compared nodes.
 From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies.
@@
 					\Require Data Collections $\mathbb{D} = \{D_1, \dots, D_n\}$
-					\Require Estimated anomalous probability $\alpha$
+					\Require Divergence metric $div$
+%					\Require Estimated anomalous probability $\alpha$
 					\Ensure Anomalous Data Collections
@@
 					\For {$i \gets 1$ to $n$}
-					\State $d_i \gets D(P_i||P_R)$
+					\State $d_i \gets div(P_i||P_R)$
 					\EndFor
@@
 Fig.~\ref{fig:raw-overview} in Section~\ref{sec:exp-raw} demonstrates the result of the above process.
-Red distribution refer to the distances calculated from normal data collections, blue and green ones are from click-farmed data collections.
+Solid line refer to the distances calculated from normal data collections, dashed and dash-dotted ones are from click-farmed data collections.
 Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value.
@@
 					\Require Evidence set with anomalous data collections $\mathbb{E}_A = \{A_1, \dots, A_m\}$
+					\Require Divergence metric $div$
 					\Require Estimated anomalous probability $\alpha$
@@
 					\Ensure Anomalous data collections in $\mathbb{D}$
-					\For{$i \gets 1$ to $n$}
-					\State $P_{N_i} \gets$ distribution of $D_{N_i}$\label{line:hist-1}
+					\For{each $N_i\in \mathbb{E}_N, A_j\in \mathbb{E}_A, D_k\in \mathbb{D}$}
+						\State $P_{N_i} \gets$ distribution of $N_i$\label{line:hist-1}
+						\State $P_{A_j} \gets$ distribution of $A_j$\label{line:hist-2}
+						\State $P_k \gets$ distribution of $D_k$
 					\EndFor
-					\For{$i \gets 1$ to $m$}
-					\State $P_{A_i} \gets$ distribution of $D_{A_i}$\label{line:hist-2}
+
+%					\For{$i \gets 1$ to $n$}
+%					\State $P_{N_i} \gets$ distribution of $N_i$\label{line:hist-1}
+%					\EndFor
+%					\For{$i \gets 1$ to $m$}
+%					\State $P_{A_i} \gets$ distribution of $A_i$\label{line:hist-2}
+%					\EndFor
+					\State $P_R \gets \frac{1}{n}\sum_{i=1}^{n}P_{N_i}$
+					\For{each $N_i\in \mathbb{E}_N, A_j\in \mathbb{E}_A$}
+						\State $d_{N_i} \gets div(P_{N_i}||P_R)$
+						\State $d_{A_j} \gets div(P_{A_j}||P_R)$
 					\EndFor
-					\State $P_R \gets \frac{1}{n}\sum_{i=1}^{n}P_{N_i}$
-					\For{$i \gets 1$ to $n$}
-					\State $d_{N_i} \gets D(P_{N_i}||P_R)$
-					\EndFor
-					\For{$i \gets 1$ to $m$}
-					\State $d_{A_i} \gets D(P_{A_i}||P_R)$
-					\EndFor
+%					\For{$i \gets 1$ to $n$}
+%					\State $d_{N_i} \gets div(P_{N_i}||P_R)$
+%					\EndFor
+%					\For{$i \gets 1$ to $m$}
+%					\State $d_{A_i} \gets div(P_{A_i}||P_R)$
+%					\EndFor
 					\State $\mathcal{N}_N(\mu_N, \sigma_N) \gets$ normal distribution estimated from $\{d_{N_1}, \dots, d_{N_n}\}$
@@
 					\State $T \gets$ proper threshold derived from $\mathcal{N}_N$, $\mathcal{N}_A$ and $\alpha$
-					\For{$i \gets 1$ to $l$}
-					\State $P_i \gets$ distribution of $D_i$
-					\State $d_i \gets D(P_i||P_R)$
-					\EndFor
-					\State \Return $\{D_i|d_i > T\}$
+%					\For{$i \gets 1$ to $l$}
+%					\State $P_i \gets$ distribution of $D_i$
+%					\State $d_i \gets div(P_i||P_R)$
+%					\EndFor
+%					\State \Return $\{D_i|d_i > T\}$
+					\State \Return $\{D_i | div(P_i||P_R) > T\}$
 				\end{algorithmic}
@@
 		\subsection{Threshold}\label{sec:alg-threshold}
+			\begin{figure}[t]
+				\centering
+				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
+				\caption{Optimal threshold should minimize the size of shadow under curve.}
+				\label{fig:example-threshold}
+			\end{figure}
+
 			One important factor in algorithm SDD-E is the value of threshold.
@@
 
-			Fortunately, applying divergence as the distance measurement among data collections provides a fine property.
+%			Fortunately, applying divergence as the distance measurement among data collections provides a fine property.
 With a reference distribution, divergences of normal data collections form a quasi-Gaussian distribution.
@@
 
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
-				\caption{Optimal threshold should minimize the size of shadow under curve.}
-				\label{fig:example-threshold}
-			\end{figure}
-
-			Moreover, as is verified in experiments, the meta-distribution of anomalous data collections lies in the right-hand-side to the normal one on the real line.
+%			Moreover, as is verified in experiments, the meta-distribution of anomalous data collections lies in the right-hand-side to the normal one on the real line.
 As shown in Fig~\ref{fig:example-threshold}, the black curve displays the probability density function (PDF) fitting those divergences calculated from normal data collections; the blue curve displays the PDF derived from anomalous data collections.
 			Threshold is chosen to minimize total errors(both false negative and false positive).
-
-			Then the optimal threshold $T$ is calculated by minimizing total errors.
+%			Then the optimal threshold $T$ is calculated by minimizing total errors.
 			However, this is not accurate enough, it implicates an assumption that chances are the same for a new data collection to be either anomalous or not.
 If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as minimizing expected errors, where we use $\alpha$ to denote anomaly probability.
+			Suppose: $PDF_normal(x) \sim \mathcal{N}(\mu_n, \sigma_n)$ and $PDF_anomalous(x) \sim \mathcal{N}(\mu_a, \sigma_a)$, then adaptive threshold can be calculated by E.q.(\ref{equ:linear-weight}).
 
 			Moreover, with an estimated anomaly probability, SDD-R can be also optimized by ranking all data collections according to their divergence value and select first $n \cdot \alpha$ ones with highest values as anomalies.
+
+			\begin{table*}
+				\footnotesize
+				\begin{align}\label{equ:linear-weight}
+				T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
+				(1-\alpha)\int_{T}^{\sup(D)}PDF_{n}(x)dx\nonumber\\
+				& \approx \mathop{\arg\min}_{T}
+				\alpha\int_{-\infty}^{T}
+				\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
+				+ 
+				(1-\alpha)\int_{T}^{+\infty}
+				\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\nonumber\\
+				& = \begin{cases}
+				\displaystyle
+				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{(1 - \alpha)\sigma_a}{\alpha\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
+				\displaystyle
+				\frac{\mu_n + \mu_a}{2} + \frac{k^2ln\frac{1 - \alpha}{\alpha}}{\mu_a - \mu_n}, & \sigma_a = \sigma_n = k
+				\end{cases}
+				\end{align}
+
+				Note: when $\sigma_a \ne \sigma_n$, keep the root s.t.
+$\displaystyle \frac{\alpha (T - \mu_a)}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{(1 - \alpha) (T - \mu_n)}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
+			\end{table*}
 
@@
 In the following experiments, we figured out properties of real world data and performance of our technique against anomalous data collections.
-We also made a comparison among variations of SDD algorithms and MGoF.\footnote{All resources and more detailed experiment results can be retrieved online: https://github.com/TramsWang/StatisticalAnomalyDetection}
+We also made a comparison among variations of SDD algorithms and MGoF.
+%		\footnote{All resources and more detailed experiment results can be retrieved online: https://github.com/TramsWang/StatisticalAnomalyDetection}
+		\footnote{All resources and more detailed experiment results can be viewed in supplemental material.}
 
@@
 			SDD-E provided best performance, yet it consumed the most computing power.
-Comparison among SDD-R revealed improvement of reference as well as the importance of threshold under this technique.
+Comparison between SDD-R and MGoF revealed improvement of reference as well as the importance of threshold under this technique.
 It is also clear that dynamic SDD-E is capable of tracing the gradual shift of environment.
@@
 MGoF is not sensitive toward minor anomalies either.
-			For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold could not automatically rise up and was thus far from to optimal.
+			For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold could not automatically rise up and was thus far from optimal.
 
